\section{Introduction}

The proliferation of data, resulting from the continuous increase in IoT (Internet of Things) device deployments, has resulted in the emergence of cloud data storage and associated processing services. Centralized cloud solutions are considered insufficient for novel applications such as holographic communications with strict requirements, including low delay and high bandwidth. As a complementary solution, edge computing brings cloud services closer to users and allows different edge devices to run heterogeneous applications that use and produce all data types. Thus, prominent solutions are required for moving data, storing it, and processing it throughout the Edge-Cloud continuum and in between. Therefore, a seamless cooperation between computing, caching, and communication (3C) is essential. Recent studies (see Table \ref{tabe:RelatedWork}) have focused on this collaboration mainly at the edge, addressing the management of 3C resources and ignoring an essential factor that \textit{the network can no longer be considered as a bare data transport medium.} 

With recent advances in network virtualization and softwarization, seamless 3C collaboration will be possible at points between edge and cloud \cite{zeng2021guest}. In particular, In-Network Computing (INC) has emerged as a new paradigm in which network core infrastructures do not just transmit data but also act on it (e.g., perform computation and caching). 
INC refers to the offloading of application-specific tasks from the end-host to the programmable network devices (e.g., programmable switch, Smart Network Interface Card (NIC)). Since INC performs computing inside the network, the transaction terminates within the path, thereby avoiding unpredictable latency in the communication path. Besides benefiting from the pipeline design of network devices, INC offers higher orders of magnitude in terms of throughput processing capacity than can be achieved by an end-host server.
The rapid evolution of Programmable Network Devices (PND) such as Barefoot Tofino switches \cite {Tofino} facilitate data plane programmability to perform computer-like functions such as data aggregation, task scheduling, and traffic classification in the network.
Thus, INC is becoming another pillar of technological enablers - network computerization - towards seamless 3C collaboration in the Edge-Cloud Continuum.



This paper provides a comprehensive review of the literature examining the synergy between INC and 3Cs. We provide a systematic analysis of how current research addresses developments and contributions made in INC and builds an implicit layer supporting 3C cooperation in the cloud-Edge continuum.



\begin{table*}
\caption{Related Work Classification}\label{tabe:RelatedWork}
\centering
\begin{adjustbox}{width=1\textwidth}
%\small
\begin{tabular}{|l|l|l|l|l|l|} 

\hline
\multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{Paper}}}   & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{year}}} & \multicolumn{3}{c|}{\textbf{ Content Coverage}}  &  \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Contribution}}}  \\ 
\cline{3-5}
\multicolumn{1}{|c|}{}  & \multicolumn{1}{c|}{} & \textit{\textbf{\qquad Cloud}}  & \textit{\textbf{\qquad Core}}  & \textit{\textbf{\qquad Edge}} &  \multicolumn{1}{c|}{}  \\ 
\hline

C.Wang et \textit{al.} \cite{8060515} & 2018 & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular}   & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching\end{tabular} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular}         &                       
\begin{tabular}[c]{@{}l@{}}Integration of Networking, Caching, and Computing in Wireless Systems: \\A Survey, Some Research Issues, and Challenges\end{tabular}\\
\hline


S.Wang et \textit{al.} \cite{7883826}   & 2017                                                & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\end{tabular}            & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching\end{tabular} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular}                  & \begin{tabular}[c]{@{}l@{}} A Survey on Mobile Edge Networks: \\Convergence of Computing, Caching, and Communications\end{tabular}  \\ 
\hline

M.Mehrabi et \textit{.al} \cite{8896954}       & 2019        & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\end{tabular}      & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching\end{tabular} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular}                  &  \begin{tabular}[c]{@{}l@{}}Device-Enhanced MEC: Multi-Access Edge Computing (MEC) Aided by\\~End Device Computation and Caching: A Survey\end{tabular}    \\ 
\hline

P.Mach et~\textit{.al} \cite{7879258}      & 2017       &        &    & 
\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular}                  &  Mobile Edge Computing: A Survey on Architecture and Computation Offloading\\ 
\hline


X.Wang et~\textit{.al} \cite{8976180}  & 2020  &     &     & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular}   &  Convergence of Edge Computing and Deep Learning: A Comprehensive Survey  \\ 
\hline

J.Ren~~\textit{.al} \cite{10.1145/3362031} & 2019    & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching\end{tabular}         &    & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching~\\Computing\end{tabular}                 &   \begin{tabular}[c]{@{}l@{}}A Survey on End-Edge-Cloud Orchestrated Network Computing Paradigms: \\Transparent Computing, Mobile Edge Computing, Fog Computing, and Cloudlet\end{tabular}  \\ 
\hline

Y.Zhao~\textit{.al} \cite{8758431}      & 2019                                                & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\\Caching\end{tabular} &                                                                                                 & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching\end{tabular}                             & Edge Computing and Networking: A Survey on Infrastructures and Applications\\ 
\hline

NC.Luong .al \cite{8714026} & 2019   &      &   & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\\Caching\\Computing\end{tabular} & \begin{tabular}[c]{@{}l@{}}  Applications of Deep Reinforcement Learning in Communications and Networking:\\ A Survey\end{tabular} \\ 
\hline

Q Luo~\textit{.al} \cite{9519636}\ & 2021  &    &        & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\\Caching\\Computing\end{tabular} &  Resource Scheduling in Edge Computing: A Survey \\ 
\hline

L.Bittencourt~\textit{.al} \cite{bittencourt2018internet}  & 2018    & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication \end{tabular} & & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\end{tabular}  &  The Internet of Things, Fog and Cloud continuum: Integration and challenge    \\ 
\hline

B.Sonkoly~\textit{.al} \cite{placementSurvey} & 2021    &   &    & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Caching\\Computing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Survey on Placement Methods in the Edge and Beyond\end{tabular} \\ 
\hline
J.Santos et~\textit{.al} \cite{9476028} & 2021   &   &    &\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}} Caching \end{tabular} & 
\begin{tabular}[c]{@{}l@{}}Towards Low-Latency Service Delivery in a Continuum of Virtual Resources:\\State-of-the-Art and Research Directions\end{tabular}                              \\ 
\hline
S. Kianipseh et~\textit{.al} \cite{INC22} & 2022   &  \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}} Computing\end{tabular} & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\\Caching\\Computing\end{tabular} &\begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Computing\end{tabular}  & 
\begin{tabular}[c]{@{}l@{}}A Survey on In-Network computing: Programmable Data Plane And technology specific applications\end{tabular}                              \\ 
\hline

Our Review & 2022   &   \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\\Caching\\Computing\end{tabular}   & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\\Caching\\Computing\end{tabular}  & \begin{tabular}{@{\labelitemi\hspace{\dimexpr\labelsep+0.5\tabcolsep}}l@{}}Communication\\Caching\\Computing\end{tabular}    & \begin{tabular}[c]{@{}l@{}} A Review of the In-Network Computing and Its Role in the Edge-Cloud Continuum\end{tabular}  \\
\hline
\end{tabular}
\end{adjustbox} 
\end{table*}

Our contributions are summarized as follows.
\begin{itemize}
\item An overview of today's distributed computing landscape and related services is given.

\item An extensive description of in-network computing, including a taxonomy, technological enablers, and implementation techniques, is provided.

\item A detailed analysis of several use cases emphasizes the need for in-network computing to meet the stringent requirements of emerging applications.

\item The challenges of in-network computing are examined from various perspectives, including equipment implementation, architectural design, regulation, and business.

\item Opportunities and future directions, such as the development of autonomous networks, the integration of artificial intelligence into networks, and the addition of control aspects to 3C, are discussed.

\end{itemize}


The remainder of this paper is organized as follows. We describe the existing computing landscape in Section \ref{ComputingParadigm}. In Section \ref{INC}, we lay the foundation for the entire survey by describing the fundamental concepts of INC. Section \ref{INC_Enablers} describes key INC enablers. Service provisioning functionalities in INC environments are presented in Section \ref{ResourceAllocation}. We describe main INC implementation approaches in Section \ref{Implementation}. Finally, Section \ref{Challenges} highlights the challenges and the opportunities related to INC as well as open research directions. 

\input{Content/computing_paradigms}