\begin{thebibliography}{00}

\bibitem{xung}Hetzel, M. \& Reichert, H. Smart infrastructure: A research junction. {\em IEEE International Smart Cities Conference (ISC2)}. pp. 1–4 (2021)

\bibitem{decoint}Bieshaar, M. \& Reitberger, G. Detecting Intentions of Vulnerable Road Users Based on Collective Intelligence. {\em CoRR}. abs/1809.03916 (2018)


\bibitem{reitberger}Reitberger, G. \& Zernetsch, S. Cooperative Tracking of Cyclists Based on Smart Devices and Infrastructure. {\em 2018 21st International Conference On Intelligent Transportation Systems (ITSC)}. pp. 436-443 (2018)


\bibitem{continental}AG, C. Continental Launches Smart City Mobility and Transportation Hub for Safer and Smarter Cities. (https://www.continental.com/en-us/press-/press-releases/smart-city-mobility-205048) (2018)


\bibitem{eilbrecht}Eilbrecht, J. \& Bieshaar, M. Model-predictive planning for autonomous vehicles anticipating intentions of vulnerable road users by artificial neural networks. {\em 2017 IEEE Symposium Series On Computational Intelligence, SSCI 2017, Honolulu, HI, USA, November 27 - Dec. 1, 2017}. pp. 1-8 (2017)


\bibitem{koper}Goldhammer, M. \& Stiegel, E. Cooperative multi sensor network for traffic safety applications at intersections. {\em 2012 15th International IEEE Conference On Intelligent Transportation Systems}. pp. 1178-1183 (2012)


\bibitem{koper_data}Strigel, E. \& Meissner, D. The Ko-PER intersection laserscanner and video dataset. {\em 17th International IEEE Conference On Intelligent Transportation Systems (ITSC)}. pp. 1900-1901 (2014)


\bibitem{zernensch}Zernetsch, S. \& Reichert, H. Trajectory Forecasts with Uncertainties of Vulnerable Road Users by Means of Neural Networks. {\em 2019 IEEE Intelligent Vehicles Symposium (IV)}. pp. 810-815 (2019)


\bibitem{kress}Kress, V. \& Jung, J. Human Pose Estimation in Real Traffic Scenes. {\em 2018 IEEE Symposium Series On Computational Intelligence (SSCI)}. pp. 518-523 (2018)


\bibitem{bieshaar}Bieshaar, M. \& Zernetsch, S. Cooperative Starting Movement Detection of Cyclists Using Convolutional Neural Networks and a Boosted Stacking Ensemble. {\em CoRR}. abs/1803.03487 (2018)

\bibitem{dlr}DLR Institute of Transportation Systems AIM Research Intersection: Instrument for traffic detection and behavior assessment for a complex urban intersection. {\em Journal Of Large-scale Research Facilities}. Volume 2 pp. A65 (2016)


\bibitem{ulm}Ulm University. Pilotanalage für vernetztes Fahren. (https://www.uni-ulm.de/in/mrm/forschung/infrastruktur/pilotanlage-fuer-vernetztes-fahren) (2019)


\bibitem{survey}Shirazi, M. \& Morris, B. Looking at Intersections: A Survey of Intersection Monitoring, Behavior and Safety Analysis of Recent Studies. {\em IEEE Transactions On Intelligent Transportation Systems}. pp. 1-21 (2016,8)


\bibitem{highD}Krajewski, R. \& Bock, J. The highD Dataset: A Drone Dataset of Naturalistic Vehicle Trajectories on German Highways for Validation of Highly Automated Driving Systems. {\em 2018 21st International Conference On Intelligent Transportation Systems (ITSC)}. pp. 2118-2125 (2018)


\bibitem{inD}Bock, J. \& Krajewski, R. The inD Dataset: A Drone Dataset of Naturalistic Road User Trajectories at German Intersections. {\em 2020 IEEE Intelligent Vehicles Symposium (IV)}. pp. 1929-1934 (2020)


\bibitem{rounD}Krajewski, R. \& Moers, T. The rounD Dataset: A Drone Dataset of Road User Trajectories at Roundabouts in Germany. {\em 2020 IEEE 23rd International Conference On Intelligent Transportation Systems (ITSC)}. pp. 1-6 (2020)


\bibitem{nuscenes}Caesar, H. \& Bankiti, V. nuScenes: A multimodal dataset for autonomous driving. {\em ArXiv Preprint ArXiv:1903.11027}. (2019)


\bibitem{waymo_prediction}Sun, P. \& Kretzschmar, H. Scalability in Perception for Autonomous Driving: Waymo Open Dataset. {\em Proceedings Of The IEEE/CVF Conference On Computer Vision And Pattern Recognition (CVPR)}. (2020,6)


\bibitem{waymo_motion}Ettinger, S. \& Cheng, S. Large Scale Interactive Motion Forecasting for Autonomous Driving: The Waymo Open Motion Dataset. {\em Proceedings Of The IEEE/CVF International Conference On Computer Vision (ICCV)}. pp. 9710-9719 (2021,10)


\bibitem{pie}Rasouli, A. \& Kotseruba, I. PIE: A Large-Scale Dataset and Models for Pedestrian Intention Estimation and Trajectory Prediction. {\em International Conference On Computer Vision (ICCV)}. (2019)


\bibitem{eth}Pellegrini, S. \& Ess, A. You'll never walk alone: Modeling social behavior for multi-target tracking. {\em 2009 IEEE 12th International Conference On Computer Vision}. pp. 261-268 (2009)


\bibitem{ucy}Lerner, A. \& Chrysanthou, Y. Crowds by example. {\em Computer Graphics Forum}. pp. 655-664 (2007)


\bibitem{ssd}Robicquet, A. \& Sadeghian, A. Learning social etiquette: Human trajectory understanding in crowded scenes. {\em European Conference On Computer Vision}. pp. 549-565 (2016)


\bibitem{gc}Yi, S. \& Li, H. Understanding pedestrian behaviors from stationary crowd groups. {\em Proceedings Of The IEEE Conference On Computer Vision And Pattern Recognition}. pp. 3488-3496 (2015)


\bibitem{decoint_dataset}Zernetsch, S. VRU Trajectory Dataset. , https://www.th-ab.de/vru-trajectory-dataset (2020)

\bibitem{nelder_mead}Nelder, J. \& Mead, R. A Simplex Method for Function Minimization. {\em The Computer Journal}. \textbf{7}, 308-313 (1965,1)


\bibitem{arun_1987}Arun, K. \& Huang, T. Least-Squares Fitting of Two 3-D Point Sets. {\em IEEE Transactions On Pattern Analysis And Machine Intelligence}. PAMI-9, 698-700 (1987)


\bibitem{bar_shalom_2001}Bar-Shalom, Y. \& Li, X. Estimation with Applications to Tracking and Navigation: Theory Algorithms and Software. (John Wiley,2001)


\bibitem{imm_blair_shalom}Blair, W. \& Bar-Shalom, T. Tracking maneuvering targets with multiple sensors: does more data always mean better estimates?. {\em IEEE Transactions On Aerospace And Electronic Systems}. \textbf{32}, 450-456 (1996)


\bibitem{imm_genovese}Genovese, A. The interacting multiple model algorithm for accurate state estimation of maneuvering targets. {\em Johns Hopkins APL Technical Digest (Applied Physics Laboratory)}. Volume 22 pp. 614-623 (2001,10)


\bibitem{imm_diff_models_states}Yuan, T. \& Bar-Shalom, Y. A Multiple IMM Estimation Approach with Unbiased Mixing for Thrusting Projectiles. {\em IEEE Transactions On Aerospace And Electronic Systems}. Volume 48, 3250-3267 (2012)


\bibitem{bernardin_2008}Bernardin, K. \& Stiefelhagen, R. Evaluating Multiple Object Tracking Performance: The CLEAR MOT Metrics. {\em EURASIP Journal On Image And Video Processing}. 2008, 246-309 (2008)


\bibitem{pitre_2005}Ryan, R. \& Vesselin, P. A comparative study of multiple-model algorithms for maneuvering target tracking. {\em Signal Processing, Sensor Fusion, And Target Recognition XIV}. pp. 549 - 560 (2005), https://doi.org/10.1117/12.609681


\bibitem{hartley_2004}Hartley, R. \& Zisserman, A. Multiple View Geometry in Computer Vision. (Cambridge University Press,2004)


\bibitem{openCV3_kaehler}Kaehler, A. \& Bradski, G. Learning OpenCV 3: Computer Vision in C++ with the OpenCV Library. (O'Reilly Media, Inc.,2016)


\bibitem{kitti_2012}Geiger, A. \& Lenz, P. Are we ready for Autonomous Driving? The KITTI Vision Benchmark Suite. {\em Conference On Computer Vision And Pattern Recognition (CVPR)}. (2012)


\bibitem{kitti_2015}Menze, M. \& Geiger, A. Object Scene Flow for Autonomous Vehicles. {\em Conference On Computer Vision And Pattern Recognition (CVPR)}. (2015)


\bibitem{shift_2022}Sun, T. \& Segu, M. SHIFT: A Synthetic Driving Dataset for Continuous Multi-Task Domain Adaptation. {\em Computer Vision And Pattern Recognition}. (2022)


\bibitem{carla_2017}Dosovitskiy, A. \& Ros, G.  CARLA: An Open Urban Driving Simulator. {\em Proceedings Of The 1st Annual Conference On Robot Learning}. pp. 1-16 (2017)


\bibitem{citr}Yang, D. \& Ozguner, U. Top-view Trajectories: A Pedestrian Dataset of Vehicle-Crowd Interaction from Controlled Experiments and Crowded Campus.  (2019,6)


\bibitem{cityscapes_2016}Cordts, M. \& Omran, M. The Cityscapes Dataset for Semantic Urban Scene Understanding. {\em Proc. Of The IEEE Conference On Computer Vision And Pattern Recognition (CVPR)}. (2016)


\bibitem{bdd100k}Yu, F., Chen, H. \& Others. BDD100K: A Diverse Driving Dataset for Heterogeneous Multitask Learning. {\em CVPR} pp. 2633-2642 (2020)


\bibitem{once}Mao, J., Niu, M. \& Others One Million Scenes for Autonomous Driving: ONCE Dataset. {\em NeurIPS}. (2021)


\bibitem{atc}Brscic, D., Kanda, T., Ikeda, T. \& Miyashita, T. Person Tracking in Large Public Spaces Using 3-D Range Sensors. {\em Human-Machine Systems, IEEE Transactions On}. pp. 522-534 (2013)

\end{thebibliography}

