%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% 
%\documentclass[english,aps,superscriptaddress,showkeys,showpacs,prepri]{revtex4}
\documentclass[english,aps,superscriptaddress,showkeys,showpacs,prepri,twocolumn]{revtex4}
\usepackage[T1]{fontenc}
\pdfoutput=1
%\usepackage[latin9]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\usepackage{units}
\usepackage{bbding}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage{sidecap}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\usepackage[utf8]{inputenc}
\usepackage{lmodern} % load a font with all the characters

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\@ifundefined{textcolor}{}
{%
 \definecolor{BLACK}{gray}{0}
 \definecolor{WHITE}{gray}{1}
 \definecolor{RED}{rgb}{1,0,0}
 \definecolor{GREEN}{rgb}{0,1,0}
 \definecolor{BLUE}{rgb}{0,0,1}
 \definecolor{CYAN}{cmyk}{1,0,0,0}
 \definecolor{MAGENTA}{cmyk}{0,1,0,0}
 \definecolor{YELLOW}{cmyk}{0,0,1,0}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\usepackage[sort&compress,numbers]{natbib} 
\bibliographystyle{apsrev4-1} 
\usepackage{doi}
\usepackage{hyperref}

\makeatother

\usepackage{babel}
\begin{document}

\title{NIMROD Modeling of Quiescent H-mode: Reconstruction Considerations and
Saturation Mechanism}

\author{J. R. King}
\affiliation{Tech-X Corporation, 5621 Arapahoe Ave. Boulder, CO 80303, USA}

\author{K. H. Burrell}
\affiliation{General Atomics, PO Box 85608, San Diego, CA 92186–5608, USA}

\author{A. M. Garofalo}
\affiliation{General Atomics, PO Box 85608, San Diego, CA 92186–5608, USA}

\author{R. J. Groebner}
\affiliation{General Atomics, PO Box 85608, San Diego, CA 92186–5608, USA}

\author{S. E. Kruger}
\affiliation{Tech-X Corporation, 5621 Arapahoe Ave. Boulder, CO 80303, USA}

\author{A. Y. Pankin}
\affiliation{Tech-X Corporation, 5621 Arapahoe Ave. Boulder, CO 80303, USA}

\author{P. B. Snyder}
\affiliation{General Atomics, PO Box 85608, San Diego, CA 92186–5608, USA}

\date{draft \today}
\begin{abstract}
The extended-MHD NIMROD code [C.R.~Sovinec and J.R.~King, J.~Comput.~Phys.~{\bf
229}, 5803 (2010)] models broadband-MHD activity from a reconstruction of a
quiescent H-mode shot on the DIII-D tokamak [J. L. Luxon, Nucl. Fusion 42, 614
(2002)]. Computations with the reconstructed toroidal and
poloidal ion flows exhibit low-$n_\phi$ perturbations ($n_\phi\simeq1-5$) that
grow and saturate into a turbulent-like MHD state. The workflow used to project
the reconstructed state onto the NIMROD basis functions re-solves the
Grad-Shafranov equation and extrapolates profiles to include scrape-off-layer
currents. Evaluation of the transport from the turbulent-like MHD state leads
to a relaxation of the density and temperature profiles. 
Published version: Nucl. Fusion 57 022002 (2017) [\url{http://dx.doi.org/10.1088/0029-5515/57/2/022002}]
\end{abstract}

\keywords{broadband-MHD,
extended-MHD modeling,
quiescent H-mode,
tokamak pedestal}

\pacs{52.30.Ex 52.35.Py, 52.55.Fa, 52.55.Tn, 52.65.Kj}
\maketitle

%--------------------------------------------------
\input{definitions}   % Useful abbreviations
\input{introduction}
\input{reconstruction}
%\input{linear}   
\input{nonlinear}
\input{transport}
%\input{magneticComp}
\input{conclusions} 
\appendix
%--------------------------------------------------

\begin{acknowledgments}
We thank Carl Sovinec and Eric Held for discussions involving the nonlinear
dynamics of this work, Jim Myra and Dan D'Ippolito for discussions pertaining
to the SOL treatment in the initial state, Stuart Hudson and Todd Evans for
discussions regarding magnetic field structure and the reviewers for detailed
comments on the manuscript. This material is based on work supported by the
U.S.  Department of Energy Office of Science and the SciDAC Center for Extended
MHD Modeling under contract numbers DE-FC02-06ER54875, DE-FC02-08ER54972
(Tech-X collaborators) and DE-FC02-04ER54698 (General Atomics Collaborators).
This research used resources of the Argonne Leadership Computing Facility,
which is a DOE Office of Science User Facility supported under contract
No.~DE-AC02-06CH11357,  and resources of the National Energy Research
Scientific Computing Center, a DOE Office of Science User Facility supported by
the Office of Science of the U.S.  Department of Energy under contract
No.~DE-AC02-05CH11231.
\end{acknowledgments}

\bibliographystyle{apsrev4-1}
\bibliography{Biblio}

\end{document}
