\documentclass[10pt, conference, letterpaper]{IEEEtran}%draftcls
%\documentclass{sig-alternate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{array}

\usepackage{mdwmath}
\usepackage{mdwtab}

\usepackage[dvips]{graphicx}

\usepackage{float}
%\usepackage{fixltx2e}
\usepackage{stfloats}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage[tight,footnotesize]{subfigure}
\usepackage[small]{caption}%\usepackage[caption=false]{caption}
%	\DeclareCaptionType{copyrightbox}
%\usepackage[font=footnotesize]{subfig}
\usepackage{epstopdf}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{paralist}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{mathbbol}
\usepackage{times}
%\usepackage[english,ruled,vlined,linesnumbered,algonl]{algorithm2e}
\usepackage{booktabs}
\usepackage{verbatim}
\newcommand{\hmmax}{0}
\newcommand{\bmmax}{2}
\usepackage{bm}			% bold math even for greek letters


\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\renewcommand{\thetheorem}{\arabic{theorem}}
\newtheorem{definition}{Definition}
\newtheorem{optimization}{Optimization Problem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{result}{Result}

\usepackage[table]{xcolor}
\usepackage{color,colortbl}
\newcommand{\blue}[1]{\textcolor[rgb]{0.00,0.00,1.00}{{#1}}}
\newcommand{\red}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\green}[1]{\textcolor[rgb]{0.00,0.50,0.00}{\textbf{#1}}}
\definecolor{Gray}{gray}{0.9}

\newcommand{\eq}[1]{Eq.~\eqref{#1}}


\newcommand{\y}{\textcolor[rgb]{0.00,0.50,0.00}{\boldmath{\checkmark}}}
\newcommand{\n}{\textcolor[rgb]{1.00,0.00,0.00}{\boldmath{$\times$}}}


\newcommand{\ie}{i.e., \@}
\newcommand{\bgp}{\texttt{bgp-degree }}
\newcommand{\Dix}{D(i|x)}


 \usepackage[normalem]{ulem}
%\linespread{0.97}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%\title{Performance Analysis of Inter-domain SDN}
%\title{Performance Analysis of Inter-domain Routing Centralization}
\title{Can SDN Accelerate BGP Convergence?\\ {\LARGE A Performance Analysis of Inter-domain Routing Centralization}}%{\LARGE A Performance Analysis of Inter-domain Routing Centralization}}% and BGP Convergence Time}
\author{Pavlos Sermpezis\\FORTH, Greece\\sermpezis@ics.forth.gr \and
		Xenofontas Dimitropoulos\\FORTH / University of Crete, Greece\\fontas@ics.forth.gr }
		
		
\maketitle
\begin{abstract}
\input{Abstract}
\end{abstract}

\section{Introduction}\label{sec:intro}
\input{Introduction}

\section{Model}\label{sec:model}
\input{Model}

\section{Data-Plane Connectivity}\label{sec:data-plane}
\input{Analysis_data_plane}

\section{Control-Plane Convergence}\label{sec:control-plane}
\input{Analysis_convergence}

\section{Related Work}
\input{Related}

\section{Conclusion}\label{sec:conclusion}
\input{Conclusion}



%\section{Extras}
%\input{Extras}


%\bibliographystyle{IEEEbib}
\bibliographystyle{ieeetr}
%\bibliographystyle{IEEEtran}	
\begin{thebibliography}{10}

\bibitem{Kent-secure-BGP-JSAC-2000}
S.~Kent, C.~Lynn, and K.~Seo, ``Secure border gateway protocol (s-bgp),'' {\em
  IEEE Journal on Selected Areas in Communications}, vol.~18, no.~4,
  pp.~582--592, 2000.

\bibitem{Subramanian-listen-whisper-NSDI-2004}
L.~Subramanian, V.~Roth, I.~Stoica, S.~Shenker, and R.~Katz, ``Listen and
  whisper: Security mechanisms for bgp,'' in {\em Proc. NSDI}, 2004.

\bibitem{Labozitz-Delayed-convergence-CCR-2000}
C.~Labovitz, A.~Ahuja, A.~Bose, and F.~Jahanian, ``Delayed {I}nternet routing
  convergence,'' {\em ACM SIGCOMM Computer Communication Review}, vol.~30,
  no.~4, pp.~175--187, 2000.

\bibitem{Kushman-Can-Hear-CCR-2007}
N.~Kushman, S.~Kandula, and D.~Katabi, ``Can you hear me now?!: it must be
  {BGP},'' {\em ACM SIGCOMM Computer Communication Review}, vol.~37, no.~2,
  pp.~75--84, 2007.

\bibitem{Oliveira-Quantifying-Path-Exploration-ToN-2009}
R.~Oliveira, B.~Zhang, D.~Pei, and L.~Zhang, ``Quantifying path exploration in
  the {I}nternet,'' {\em Networking, IEEE/ACM Transactions on}, vol.~17, no.~2,
  pp.~445--458, 2009.

\bibitem{Gupta-SDX-CCR-2014}
A.~Gupta, L.~Vanbever, M.~Shahbaz, S.~Donovan, B.~Schlinker, N.~Feamster,
  J.~Rexford, S.~Shenker, R.~Clark, and E.~Katz-Bassett, ``{SDX}: A software
  defined internet exchange,'' {\em ACM SIGCOMM Comput. Commun. Rev.}, vol.~44,
  no.~4, pp.~551--562, 2014.

\bibitem{Kotronis-CXP-SOSR-2016}
{Kotronis, V. and Kloeti, R. and Rost, M. and Georgopoulos, P. and Ager, B. and
  Schmidt, S. and Dimitropoulos, X.}, ``Stitching inter-domain paths over
  {IXPs},'' in {\em ACM SOSR}, 2016.

\bibitem{Thai-Decoupling-BGP-Conext-2012}
P.~W. Thai and J.~C. de~Oliveira, ``Decoupling bgp policy from routing with
  programmable reactive policy control,'' in {\em Proc. ACM CoNEXT Student},
  2012.

\bibitem{Rothenberg-Revisiting-RCP-HotSDN-2012}
C.~Rothenberg, M.~Nascimento, M.~Salvador, C.~Corr{\^e}a, S.~C. de~Lucena, and
  R.~Raszuk, ``Revisiting routing control platforms with the eyes and muscles
  of software-defined networking,'' in {\em Proc. ACM HotSDN}, 2012.

\bibitem{Bennesby-Innovating-IDrouting-AINA-2014}
R.~Bennesby, E.~Mota, P.~Fonseca, and A.~Passito, ``Innovating on interdomain
  routing with an inter-sdn component,'' in {\em Proc. IEEE AINA}, 2014.

\bibitem{Lin-Seamless-Internetworking-Demo-Sigcomm-2013}
P.~Lin, J.~Hart, U.~Krishnaswamy, T.~Murakami, M.~Kobayashi, A.~Al-Shabibi,
  K.-C. Wang, and J.~Bi, ``Seamless interworking of sdn and ip,'' in {\em Proc.
  ACM SIGCOMM 2013 (demo)}, 2013.

\bibitem{Kotronis-Routing-Centralization-ComNets-2015}
V.~Kotronis, A.~G{\"a}mperli, and X.~Dimitropoulos, ``Routing centralization
  across domains via sdn: A model and emulation framework for {BGP}
  evolution,'' {\em Computer Networks}, pp.~--, 2015.

\bibitem{Gibb-Outsourcing-NF-HotSDN-2012}
G.~Gibb, H.~Zeng, and N.~McKeown, ``Outsourcing network functionality,'' in
  {\em Proc. ACM HotSDN}, 2012.

\bibitem{survey-bgp-nanog}
{{NANOG} mailing list archives}, ``{A survey on {BGP} convergence}.''
  \url{http://seclists.org/nanog/2017/Jan/55}, Jan. 2017.

\bibitem{fibbing-sigcomm-2015}
S.~Vissicchio, O.~Tilmans, L.~Vanbever, and J.~Rexford, ``Central control over
  distributed routing,'' {\em ACM SIGCOMM Computer Communication Review},
  vol.~45, no.~4, pp.~43--56, 2015.

\bibitem{supercharge-me-2015}
M.~Alan~Chang, T.~Holterbach, M.~Happe, and L.~Vanbever, ``Supercharge me:
  Boost router convergence with sdn,'' {\em ACM SIGCOMM Comput. Commun. Rev.},
  vol.~45, no.~4, pp.~341--342, 2015.

\bibitem{Newman:Networks-book}
M.~Newman, {\em Networks: An Introduction}.
\newblock Oxford University Press, Inc., 2010.

\bibitem{AS-relationships-dataset}
``The {CAIDA} {AS} relationships dataset.''
  \url{http://data.caida.org/datasets/as-relationships/}, 01 Nov. 2016.

\bibitem{stable-internet-routing-TON-2001}
L.~Gao and J.~Rexford, ``Stable internet routing without global coordination,''
  {\em IEEE/ACM Transactions on Networking (TON)}, vol.~9, no.~6, pp.~681--692,
  2001.

\bibitem{as-rank-website}
``{AS}-rank, {CAIDA}.'' \url{http://as-rank.caida.org}.

\bibitem{Chiu-One-Hop-Away-IMC-2015}
Y.-C. Chiu, B.~Schlinker, A.~B. Radhakrishnan, E.~Katz-Bassett, and
  R.~Govindan, ``Are we one hop away from a better internet?,'' in {\em Proc.
  ACM IMC}, 2015.

\bibitem{convergence-properties-BGP_ComNets-2011}
R.~Viswanathan, K.~K. Sabnani, R.~J. Holt, and A.~N. Netravali, ``Expected
  convergence properties of bgp,'' {\em Computer Networks}, vol.~55, no.~8,
  pp.~1957--1981, 2011.

\bibitem{stability-inter-domain-Infocom-2009}
R.~Sami, M.~Schapira, and A.~Zohar, ``Searching for stability in interdomain
  routing,'' in {\em Proc. IEEE INFOCOM}, 2009.

\bibitem{Schlinker-PEERING-HotNets-2014}
B.~Schlinker, K.~Z. I., Cunha, N.~Feamster, and E.~Katz-Bassett, ``Peering: An
  as for us,'' in {\em Proc. ACM HotNets 2014}, \url{https://peering.usc.edu}.

\bibitem{ARTEMIS-Demo-Sigcomm-2016}
G.~Chaviaras, P.~Gigis, P.~Sermpezis, and X.~Dimitropoulos, ``{ARTEMIS}:
  Real-time detection and automatic mitigation for bgp prefix hijacking,'' in
  {\em Proc. ACM SIGCOMM Demo}, 2016.

\bibitem{bgpmon}
``{BGP}mon.'' \url{http://www.bgpmon.io}.

\bibitem{ripe-ris}
``{RIPE RIS}.'' \url{http://ris.ripe.net/}.

\bibitem{periscope}
\url{http://www.caida.org/tools/utilities/looking-glass-api/}.

\bibitem{Oehlert1992}
G.~W. Oehlert, ``A note on the delta method,'' {\em The American Statistician},
  vol.~46, no.~1, pp.~27--29, 1992.

\bibitem{Let-the-market-BGP-sigcomm-2011}
P.~Gill, M.~Schapira, and S.~Goldberg, ``Let the market drive deployment: A
  strategy for transitioning to bgp security,'' in {\em ACM SIGCOMM Computer
  Communication Review}, vol.~41, pp.~14--25, 2011.

\bibitem{how-secure-goldberg-ComNet-2014}
S.~Goldberg, M.~Schapira, P.~Hummon, and J.~Rexford, ``How secure are secure
  interdomain routing protocols?,'' vol.~70, pp.~260--287, Elsevier, 2014.

\bibitem{Jumpstarting-BGP-sigcomm-2016}
A.~Cohen, Y.~Gilad, A.~Herzberg, and M.~Schapira, ``Jumpstarting bgp security
  with path-end validation,'' in {\em Proc. ACM SIGCOMM 2016}, 2016.

\bibitem{RPKI-deployment-2016}
Y.~Gilad, A.~Cohen, A.~Herzberg, M.~Schapira, and H.~Shulman, ``Are we there
  yet? on {RPKI}'s deployment and security.'' NDSS 2017, to appear,
  \url{http://eprint.iacr.org/2016/1010.pdf}, 2016.

\bibitem{AS-relationships-IMC-2013}
M.~Luckie, B.~Huffaker, A.~Dhamdhere, V.~Giotsas, {\em et~al.}, ``As
  relationships, customer cones, and validation,'' in {\em Proc. ACM IMC},
  2013.

\bibitem{multilateral-peering-conext-2013}
V.~Giotsas, S.~Zhou, M.~Luckie, and k.~claffy, ``Inferring multilateral
  peering,'' in {\em Proc. ACM CoNEXT}, 2013.

\end{thebibliography}
%\bibliography{references}




%\newpage
\appendices
\input{Appendix}


\end{document}
 