\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jcappub} % for details on the use of the package, please
                     % see the JCAP-author-manual

\usepackage[T1]{fontenc} % if needed
\usepackage{subcaption}
\usepackage{physics}



\title{\boldmath Effects of Neutrino Masses and Asymmetries on Dark Matter Halo Assembly}


%% %simple case: 2 authors, same institution
%% \author{A. Uthor}
%% \author{and A. Nother Author}
%% \affiliation{Institution,\\Address, Country}

% more complex case: 4 authors, 3 institutions, 2 footnotes
\author[a]{Hiu Wing Wong}
\author[a]{and Ming-chung Chu}

% The "\note" macro will give a warning: "Ignoring empty anchor..."
% you can safely ignore it.

\affiliation[a]{Department of Physics, The Chinese University of Hong Kong, Shatin NT, Hong Kong}
%\affiliation[b]{Another University,\\different-address, Country}
%\affiliation[c]{A School for Advanced Studies,\\some-location, Country}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{hwwong@phy.cuhk.edu.hk}
\emailAdd{mcchu@phy.cuhk.edu.hk}





\abstract{Massive cosmological neutrinos suppress the Large-Scale Structure (LSS) in the Universe by smoothing the cosmic over-densities, and hence structure formation is delayed relative to that in the standard Lambda-Cold Dark Matter ($\Lambda$CDM) model.
We characterize the merger and mass accretion history of dark matter halos with the halo formation time $a_{1/2}$, tree entropy $s$ and halo leaf function $\ell(X)$ and measure them using neutrino-involved N-body simulations. 
We show that a non-zero sum of neutrino masses $M_\nu$ delays the $a_{1/2}$ for halos with virial mass between $10^{13} M_\odot$ and $3\times 10^{13} M_\odot$, whereas a non-zero neutrino asymmetry parameter $\eta^2$ has the opposite effect.
While the mean tree entropy $\bar s$ does not depend significantly on either $M_\nu$ or $\eta^2$, the halo leaf function does.  Furthermore, the dependencies of $\ell$ on $M_\nu$ and $\eta^2$ have significant evolution in redshift $z$, with the relative contributions of $M_\nu$ and $\eta^2$ showing a sigmoid-like transition as a function of $z$ around $z \approx 0.6$.
Together with the matter power spectrum, these halo parameters allow us to break the parameter degeneracy between $M_\nu$ and $\eta^2$ so that they can both be constrained in principle.
}
\keywords{cosmological simulations, cosmological neutrinos, neutrino masses from cosmology, neutrino properties}
%\arxivnumber{XXXX.XXXXXX}



\begin{document}
\maketitle
\flushbottom

\input{Maintext/Introduction}
\input{Maintext/grid-based}
\input{Maintext/halo-stat}
\input{Maintext/result}
\input{Maintext/conclusion}


\acknowledgments
We acknowledge Shek Yeung for modifying \texttt{CosmoMC} to fit the Planck 2018 data with different neutrino cosmologies and performing all the MCMC refittings. 
HWW thanks Jianxiong Chen for his mentorship on N-body simulations and Zhichao Zeng for discussion on neutrino-involved simulations.
All simulations were performed using the Central Research Computing Cluster at CUHK.
This work is supported partially by grants from the Research Grants Council of the Hong Kong Special Administrative Region, China (Project Nos. AoE/P-404/18 and C7015-19G).


\appendix
\input{Maintext/linear-evo}
\input{Maintext/posterior}



% The bibliography will probably be heavily edited during typesetting.
% We'll parse it and, using the arxiv number or the journal data, will
% query inspire, trying to verify the data (this will probalby spot
% eventual typos) and retrive the document DOI and eventual errata.
% We however suggest to always provide author, title and journal data:
% in short all the informations that clearly identify a document.

\begin{thebibliography}{99}

\bibitem{PP} Particle Data Group collaboration, C. Patrignani et al, \emph{Review of Particle Physics}, \emph{Chin. Phys.} {\bf C40} (2016) 100001. 

\bibitem{FARZAN200159} Y. Farzan, O. L. G. Peres, A. Yu. Smirnov,
\emph{Neutrino Mass Spectrum and Future Beta Decay Experiments}, \emph{Nuclear Physics B} {\bf 612} (2001) 59-97
\href{https://arxiv.org/abs/hep-ph/0105105}{ [hepo-ph/0105105]}.

\bibitem{Planck2018} Planck Collaboration, N.Aghnanim et la.,  \emph{Planck 2018 results. VI. Cosmological parameters}, \emph{A\&A} {\bf A6} (2020) 641
\href{https://arxiv.org/abs/1807.06209}{ [arxiv:1807.06209]}.

\bibitem{M nu} S. R. Choudhury and S. Hannestad, \emph{Updated results on neutrino mass and mass hierarchy from cosmology with
Planck 2018 likelihoods}, \emph{JCAP} {\bf 07} (2020) 037
\href{https://arxiv.org/abs/1907.12598}{ [arxiv:1907.12598]}.


\bibitem{camb} A. Lewis, A. Challinor, and A. Lasenby, \emph{Efficient computation of CMB anisotropies in closed FRW models}, \emph{ApJ} {\bf 538} (2000) 473-476
\href{https://arxiv.org/abs/astro-ph/9911177}{ [astro-ph/9911177]}.

\bibitem{class} D. Blas, J. Lesgourgues, and T. Tram, \emph{The Cosmic Linear Anisotropy Solving System (CLASS) II: Approximation schemes} , \emph{JCAP} {\bf 07} (2011) 034
\href{https://arxiv.org/abs/1104.2933}{ [arxiv:1104.2933]}.

\bibitem{part}J. Brandbyge and S. Hannestad \emph{Resolving Cosmic Neutrino Structure: A Hybrid Neutrino N-body Scheme}, \emph{JCAP} {\bf01} (2010) 021 \href{https://arxiv.org/abs/0908.1969}{[arxiv:0908.1969]}.

\bibitem{grid} J. Brandbyge and S. Hannestad, \emph{Grid Based Linear Neutrino Perturbations in Cosmological N-body Simulations}, \emph{JCAP} {\bf05} (2009) 002, \href{https://arxiv.org/abs/0812.3149}{[arxiv:0812.3149]}.

\bibitem{grid2} Y. Ali-Haimoud and S. Bird, \emph{An effcient implementation of massive neutrinos in non-linear structure formation simulations}, \emph{MNRAS} {\bf428} (2013) 3375 \href{https://arxiv.org/abs/1209.0461}{[arxiv:1209.0461]}.

\bibitem{Carton} Z. Zheng, S. Yeung and M. C. Chu, \emph{Effects of neutrino mass and asymmetry on cosmological structure formation}, \emph{JCAP} {\bf03} (2019) 015
\href{https://arxiv.org/abs/1808.00357}{ [arxiv:1808.00357]}.

\bibitem{Yvvone}J. Z. Chen, A. Upadhye and Yvonne Y. Y. Wong, \emph{One line to run them all: SuperEasy massive neutrino linear response in
N-body simulations}, \href{https://arxiv.org/abs/2011.12504}{[arxiv:2011.12504]}.

\bibitem{Yvvone fluid}J. Z. Chen, A. Upadhye and Yvonne Y. Y. Wong, \emph{The cosmic neutrino background as a collection of fluids in large-scale structure simulations}, 
\href{https://arxiv.org/abs/2011.12503}{[arxiv:2011.12503]}.

\bibitem{nuconcept} J. Dakin, J. Brandbyge, S. Hannestad, T. Haugbølle and T. Tram,  \emph{$\nu$CONCEPT: Cosmological neutrino simulations from the non-linear Boltzmann hierarchy}, \emph{JCAP} {\bf02} (2019) 052
\href{https://arxiv.org/abs/1712.03944}{[arxiv:1712.03944]}.

\bibitem{mu} G. Barenboim, W. H. Kinney and W. Park, \emph{ Flavor versus mass eigenstates in neutrino asymmetries: implications for cosmology}, \emph{Eur. Phys. J. C.} {\bf 77} (2017) 590
\href{https://arxiv.org/abs/1609.03200}{ [arxiv:1609.03200]}.


\bibitem{nu CMB} K.N. Abazajian et al, \emph{Neutrino Physics from the Cosmic Microwave Background and Large Scale Structure}, \emph{Astropart. Phys.} {\bf63} (2015) 66-80 \href{https://arxiv.org/abs/1309.5383}{ [arxiv:1309.5383]}.

\bibitem{bbn1} G. Mangano, G. Miele, S. Pastor, O. Pisanti, S. Sarikas, \emph{Constraining the cosmic radiation density due to lepton number with Big Bang Nucleosynthesis}, \emph{JCAP} {\bf03} (2011) 035 \href{https://arxiv.org/abs/1011.0916v3}{[arxiv:1011.0916]}.

\bibitem{bbn2} A.D. Dolgov, S.H. Hansen, S. Pastor, S.T. Petcov, G.G. Raffelt, D.V. Semikoz, \emph{A.D. Dolgov, S.H. Hansen, S. Pastor, S.T. Petcov, G.G. Raffelt, D.V. Semikoz}, \emph{Nucl. Phys. B} {\bf632} (2002) 363-382 \href{https://arxiv.org/abs/hep-ph/0201287}{[hep-ph/021287]}.


\bibitem{cosmomc} A. Lewis and S. Bridle, \emph{Cosmological parameters from CMB and other data: a Monte-Carlo
approach}, \emph{Phys. Rev. D} {\bf66} (2002) 103511 \href{https://arxiv.org/abs/astro-ph/0205436}{[astro-ph/0205436]}.


\bibitem{formtime} D. H. Zhao, Y. P. Jing, H. J. Mo, and G. Börner, \emph{Accurate universal models for the mass accretion histories and concentrations of dark matter halos}, \emph{ApJ} {\bf707} (2009) 354 \href{https://arxiv.org/abs/0811.0828}{[arxiv:0811.0828]}.

\bibitem{eta_effect} S. Yeung, King Lau and M.-C. Chu, \emph{Relic neutrino degeneracies and their impact on cosmological parameters}, \emph{JCAP} {\bf04} (2021) 024 \href{https://arxiv.org/abs/2010.01696}{[arxiv:2010.01696]}

\bibitem{tree entropy} D. Obreschkow, P. J. Elahi, C. P. Lagos, R. J. J. Poulton and A. D. Ludlow, \emph{Characterising the Structure of Halo Merger Trees Using a Single Parameter: The Tree Entropy}, \emph{MNRAS} {\bf 493} (2020) 4551-4569 \href{https://arxiv.org/abs/1911.11959}{ [arxiv:1911.11959]}.

\bibitem{Gadget2} V. Springel, \emph{The cosmological simulation code GADGET-2}, \emph{MNRAS} {\bf 364} (2005) 1105-1134
\href{https://arxiv.org/abs/astro-ph/0505010}{ [astro-ph/0505010]}.

\bibitem{LBE}S. Xiang and L. Feng, \emph{The formation of the cosmological structure}
, \emph{2ed, Astronomical Series
of NAOC}, Chinese Science and Technology Press (2012), 257-261.


\bibitem{music} O. Hahn and T. Abel, \emph{Multi-scale initial conditions for cosmological simulations}, \emph{NMRAS} {\bf415} (2011) 2101-2121 \href{https://arxiv.org/abs/1103.6031}{ [arxiv:1103.6031]}.


\bibitem{rockstar} P. S. Behroozi, R. H. Wechsler and H. Y. Wu, \emph{The Rockstar Phase-Space Temporal Halo Finder and the Velocity Offsets of Cluster Cores}, \emph{ApJ} {\bf762} (2013) 109 \href{https://arxiv.org/abs/1110.4372}{ [arxiv:1110.4372]}.

\bibitem{ct} P. S. Behroozi et al, \emph{Gravitationally Consistent Halo Catalogs and Merger Trees for Precision Cosmology}, \emph{ApJ} {\bf 763} (2013) 18 \href{https://arxiv.org/abs/1110.4370}{[arxiv:1110.4370]}.

\bibitem{Kuan} K. Wang et al, \emph{Concentrations of Dark Haloes Emerge from Their Merger Histories}, \emph{MNRAS} {\bf 498} (2020) 4450-4464 \href{https://arxiv.org/abs/2004.13732}{ [arxiv:2004.13732]}.




\bibitem{Wang_2011_2}Huiyuan Wang, H. J. Mo, Y.P. Jing, Xiaohu Yang and Yu Wang, \emph{Internal properties and environments of dark matter halos}, \emph{MNRAS} {\bf 413} (2011) 1974-1990, \href{https://arxiv.org/abs/1007.0612}{[arxiv/1007.0612]}.


\bibitem{Wang_2011} Huiyuan Wang, H. J. Mo, Xiaohu Yang and Frank C. van den Bosch, \emph{Reconstructing the cosmic velocity and tidal fields with galaxy groups selected from the Sloan Digital Sky Survey}, \emph{MNRAS} {\bf 420} 2012 1809–1824, \href{https://arxiv.org/abs/1108.1008}{[arxiv:1108.1008]}.

\bibitem{Lim_2015} Seunghwan Lim, Houjun Mo, Huiyuan Wang and Xiaohu Yang, \emph{An observational proxy of halo assembly time and its correlation with galaxy properties}, \emph{MNRAS}, {\bf 455} (2016) 499-510, \href{https://arxiv.org/abs/1502.01256}{[arxiv:1502.01256]}.


\bibitem{halo bias}T. Lazeyras, F. Villaescusa-Navarro and M. Viel, \emph{The impact of massive neutrinos on halo assembly bias}, \emph{JCAP} {\bf 03} (2021) 022,  \href{https://arxiv.org/abs/2008.12265}{[arxiv:2008.12265]} .

% Please avoid comments such as "For a review'', "For some examples",
% "and references therein" or move them in the text. In general,
% please leave only references in the bibliography and move all
% accessory text in footnotes.

% Also, please have only one work for each \bibitem.

%\bibitem{a} Author, \emph{Title}, \emph{J. Abbrev.} {\bf vol} (year) pg.

%\bibitem{b} Author, \emph{Title}, arxiv:1234.5678.

%\bibitem{c} Author, \emph{Title}, Publisher (year).



\end{thebibliography}
\end{document}
