\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jcappub} % for details on the use of the package, please
                     % see the JCAP-author-manual

\usepackage[T1]{fontenc} % if needed

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subcaption} % For sub-figures
\usepackage{graphicx}
\usepackage[all]{nowidow}
\usepackage[utf8]{inputenc}
\usepackage{multicol}

\newcommand{\apj}{Astrophysical Journal}
\newcommand{\apjl}{Astrophysical Journal, Letters}
\newcommand{\apjs}{Astrophysical Journal, Supplement}
\newcommand{\araa}{Annual Review of Astron and Astrophysics}
\newcommand{\pasp}{Publications of the ASP}
\newcommand{\mnras}{Monthly Notices of the RAS}


\definecolor{ShamrockGreen}{rgb}{0.0, 0.62, 0.38}
\newcommand{\mjdnote}[1]{{\color{red} (MJD: #1)}}
\newcommand{\rv}[1]{{\footnotesize\color{red}\bf RV: #1}}

\newcommand{\update}[1]{{\leavevmode\color{ShamrockGreen}#1}}


\title{Constraining axion-like particles using the white dwarf initial-final mass relation}


%% %simple case: 2 authors, same institution
\author{Matthew J. Dolan,}
\author[1]{Frederick J. Hiskens,\note{Corresponding author}}
\author{and Raymond R. Volkas}
\affiliation{ARC Centre of Excellence for Dark Matter Particle Physics, School of Physics, The University of Melbourne, Victoria 3010, Australia}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{dolan@unimelb.edu.au}
\emailAdd{fhiskens@student.unimelb.edu.au}
\emailAdd{raymondv@unimelb.edu.au}

\keywords{axions, stars, white and brown dwarfs}
\arxivnumber{2102.00379}


\abstract{Axion-like particles (ALPs), a class of pseudoscalars common to many extensions of the Standard Model, have the capacity to drain energy from the interiors of stars. Consequently, stellar evolution can be used to derive many constraints on ALPs. We study the influence that keV-MeV scale ALPs which interact exclusively with photons can exert on the helium-burning shells of asymptotic giant branch stars, the late-life evolutionary phase of stars with initial masses less than $8M_{\odot}$. We establish the sensitivity of the final stellar mass to such energy-loss for ALPs with masses currently permitted by stellar evolution bounds. A semi-empirical constraint on the white dwarf initial-final mass relation (IFMR) derived from observation of double white dwarf binaries is then used to exclude part of a currently unconstrained region of ALP parameter space, the cosmological triangle. The derived constraint relaxes when the ALP decay length becomes shorter than the width of the helium-burning shell. Other potential sources for stellar constraints on  ALPs are also discussed.}



\begin{document}
\maketitle
\flushbottom

\input{Introduction/Introduction}
\input{Section2/Sec2}
\input{Section3/Sec3}
\input{Section4/Sec4}
\input{Section5/Sec5}
\input{Section6/Sec6}


\appendix
\input{AppA/AppA}
\input{AppB/AppB}
\input{AppC/AppC}

\acknowledgments
We would like to thank Katie Auchettl for her invaluable insight and assistance, as well as Jeff Andrews, Pierluca Carenza and Felix Kahlhoefer for helpful comments and discussion. This work was supported in part by the Australian Research Council and the Australian Government Research Training Program Scholarship initiative.

\bibliographystyle{JHEP}
\bibliography{bibliography}
\end{document}
