\documentclass[journal]{IEEEtran}
\usepackage[backend=bibtex,style=numeric,citestyle=numeric-comp,sorting=none]{biblatex}
\usepackage{xcolor}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{caption}                

\usepackage{array}
\usepackage{multirow}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{adjustbox}
\usepackage{booktabs, multirow} 
 \usepackage{makecell}
\usepackage{comment}
\usepackage{tabularx}
\usepackage{soul}

\bibliography{stateofart}
\providecommand{\keywords}[1]{\textbf{\textit{Index terms---}} #1}
\begin{document}

\title{A Review of the In-Network Computing and Its Role in the Edge-Cloud Continuum}

%{A Comprehensive Review of In-Network Computing: Challenges and Opportunities}
%{In-Network Computing in the Mist-Edge-Cloud Continuum: A Comprehensive Survey}
%{A Comprehensive Review of In-Network Computing: Challenges and Opportunities}


\author{
    \IEEEauthorblockN{Manel Gherari\IEEEauthorrefmark{1}, Fatemeh Aghaali Akbari\IEEEauthorrefmark{4}, Sama Habibi\IEEEauthorrefmark{3}, Soukaina Ouledsidi Ali\IEEEauthorrefmark{1}, Zakaria Ait Hmitti\IEEEauthorrefmark{1}, Youcef Kardjadja\IEEEauthorrefmark{2}, Muhammad Saqib\IEEEauthorrefmark{1}}, Adyson Magalhaes Maia\IEEEauthorrefmark{2}, Marsa Rayani\IEEEauthorrefmark{4}, 
    Ece Gelal Soyak\IEEEauthorrefmark{5}, Halima Elbiaze\IEEEauthorrefmark{1}, Ozgur Ercetin\IEEEauthorrefmark{3}, Yacine Ghamri-Doudane\IEEEauthorrefmark{2}, Roch Glitho\IEEEauthorrefmark{4}, Wessam Ajib\IEEEauthorrefmark{1}
    
    \IEEEauthorblockA{\IEEEauthorrefmark{1} Université du Québec à Montréal, Montreal, Canada\\}
    \IEEEauthorblockA{\IEEEauthorrefmark{2} La Rochelle University, La Rochelle, France\\}
    \IEEEauthorblockA{\IEEEauthorrefmark{3} Sabanci University, Istanbul, Turkey\\}
    \IEEEauthorblockA{\IEEEauthorrefmark{4} Concordia University, Montreal, Canada\\}
    \IEEEauthorblockA{\IEEEauthorrefmark{5} Bahcesehir University, Istanbul, Turkey\\}
}
% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}

Future networks are anticipated to enable exciting applications and industrial services ranging from Multisensory Extended Reality to Holographic and Haptic communication.  
These services are accompanied by high bandwidth requirements and/or require low latency and low reliability, which leads to the need for scarce and expensive resources.
Cloud and edge computing offer different functionalities to these applications that require communication, computing, and caching (3C) resources working collectively. Hence, a paradigm shift is necessary to enable the joint management of the 3Cs in the edge-cloud continuum.
We argue that In-Network Computing (INC) is the missing element that completes the edge-cloud continuum. This paper provides a detailed analysis of the driving use-cases, explores the synergy between INC and 3C, and emphasizes the crucial role of INC. A discussion on the opportunities and challenges posed by INC is held from various perspectives, including hardware implementation, architectural design, and regulatory and commercial aspects.

\end{abstract}

\keywords{In-Network Computing, Edge-Cloud Continuum, Programmable Network Device, Communication, computing, and caching integration}


\IEEEpeerreviewmaketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Content/introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\input{Content/computing_paradigms}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Content/INC}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Content/challenges_opportunities_C4}
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Content/Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% use section* for acknowledgment
\section*{Acknowledgment}
The authors would like to thank all SCORING project team members.


% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.%\%ifCLASSOPTIONcaptionsoff
  % \newpage
\printbibliography
\end{document}

