\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables


\usepackage{graphicx}
\usepackage{color}
\usepackage{soul}
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{amsmath}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Octave,                 % the language of the code
  morekeywords={*,...},           % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,                   % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}



\newif\iffinal

% Un-comment this line to see proposal without comments
%\finaltrue

\iffinal
  \newcommand\yadu[1]{}
  \newcommand\kyle[1]{}
  \newcommand\eamon[1]{}
\else
  \newcommand\yadu[1]{{\color{blue}[Yadu: #1]}}
  \newcommand\kyle[1]{{\color{red}[Kyle: #1]}}
  \newcommand\eamon[1]{{\color{purple}[Eamon: #1]}}
\fi

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[ScienceCloud'17]{Workshop on Scientific Cloud Computing}{June 2017}{Washington, DC USA} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{15.00}


\begin{document}
\title{Enabling Interactive Analytics of Secure Data using Cloud Kotta}
%\subtitle{Extended Abstract}



\author{Yadu N. Babuji, Kyle Chard, and Eamon Duede}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{Computation Institute, University of Chicago and Argonne National Laboratory}
  \streetaddress{5735 S Ellis Ave}
  \city{Chicago} 
  \state{Illinois} 
  \postcode{60637}
}
\email{{yadu, chard, eduede}@uchicago.edu}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Y. Babuji et al.}


\begin{abstract}
Research, especially in the social sciences and humanities, is increasingly
reliant on the application of data science methods to analyze large amounts
of (often private) data. Secure data enclaves provide a solution for managing and analyzing private data. However, such enclaves do not readily support
discovery science---a form of exploratory or interactive analysis by which researchers 
execute a range of (sometimes large) analyses in an iterative and collaborative
manner. 
The batch computing model offered by many data enclaves is well suited to executing
large compute tasks; however it is far from ideal for day-to-day discovery science.
As researchers must submit jobs to queues and wait for results, the high latencies inherent in queue-based, batch computing systems hinder interactive
analysis.
%Data science occurs at human pace and
%that involves iterative development which requires interactive systems. Latencies offered
%by typical queue based system slow down development.
In this paper we describe how we have augmented the Cloud Kotta secure data enclave
to support collaborative and interactive analysis of sensitive data.
Our model uses Jupyter notebooks as a flexible analysis environment 
and Python language constructs to support the execution of arbitrary 
functions on private data within this secure framework.
\end{abstract}


% Maybe remove the upper case at some point.
\newcommand{\NAMENS} {\textsc{Cloud Kotta}} % No space aftewards (for brackets etc.)
\newcommand{\NAME} {\textsc{Cloud Kotta }}



% make the title area
\maketitle


\input{introduction}
\input{background}
\input{arch}
\input{applications}
\input{related}
\input{summary}

% conference papers do not normally have an appendix


% use section* for acknowledgment
\section*{Acknowledgments}


The authors would like to thank Nathan Bartley and Alexander Belikov for testing the system in its early stages of development.



\bibliographystyle{ACM-Reference-Format}
\bibliography{references}


\end{document}


