\section{Positivity of Pressure and Density  for the Euler Equations}\label{se_phys_cons}
We saw that the GT-scheme, if $\alpha$ satisfies \textbf{Condition $F$}, in turn satisfies a discrete per cell entropy inequality. The same mechanism will be used in the following paragraph to enforce positive pressure and/or density for numerical solutions of the Euler equations of gas dynamics \cite{Harten83b}:
\begin{equation}
	\label{eq:Euler}
	u =(\rho, \rho v, E) 
\quad f(\rho, \rho v, E) = \begin{bmatrix} \rho v \\ \rho v^2 + p\\ v(E + p) \end{bmatrix} 
\quad p = (\gamma - 1)\left (E - \frac 1 2 \rho v^2 \right).
\end{equation}
	This system is equipped with the following entropy-entropy flux pair 
\begin{equation} \label{eq:EulerPE}
U(\rho, \rho v, E) = - \rho S  \quad F(\rho, \rho v, E) = - \rho v S \quad S = \ln(p \rho^{- \gamma}).
\end{equation}
One easily validates that while the density is one of the conserved variables and hence a linear functional of the conserved variables the pressure is a concave functional. 
But as we are interested in preserving the positivity one can equally enforce the negativity of the negative pressure and negative density, making the task equivalent to enforcing upper bounds on convex functionals. It is known from literature, cf.  \cite{zhang2011maximum} and references therein, that  both  Godunov and Lax-Friedrichs schemes are positivity preserving under a CFL condition. In the following $g$ will stand for the flux of a positivity preserving dissipative scheme and our convex functionals that should be enforced are denoted by $c_1(u) = -p(u)$ and $c_2 = -\rho(u)$. The counterparts of \textbf{Condition $F$} are \textbf{Condition $\rho$} and \textbf{Condition $P$}.
\begin{definition}[\textbf{Condition $\rho$}]
	The parameter $\alpha$ is said to satisfy \textbf{Condition $\rho$} for cell $k$ if 
	\[
		\begin{aligned}
	c_2\of{u^n_k + 2\lambda \left(	\fnn_{\alpha_{k-\frac 1 2}} + f(u^n_k)\right) } \leq 0 \quad
	 c_2\of{u^n_k + 2\lambda \left( f^n_{k} - \fnn_{\alpha_{k+\frac 1 2}}\right) } \leq 0
		\end{aligned}
	\]
	holds.
\end{definition}


\begin{definition}[\textbf{Condition P}]
	The parameter $\alpha$ is said to satisfy \textbf{Condition P} for cell $k$ if 
	\[
	\begin{aligned}
	c_1\of{u^n_k + 2\lambda \left(	\fnn_{\alpha_{k-\frac 1 2}} + f(u^n_k)\right)} \leq 0 \quad
	 c_1\of {u^n_k + 2\lambda \left(f^n_{k} - \fnn_{\alpha_{k+\frac 1 2}}\right)} \leq 0
	 \end{aligned}
	\]
	holds
	\end{definition}
We note that the equivalent of lemma \ref{lem:EalpBound} is in this case
\begin{lemma}
	\textbf{Condition P}  is fulfilled if one of the following conditions is satisfied for $k+\frac 1 4$ and $k-\frac 1 4$.
	\begin{enumerate}
		\item It holds $c_1\of{u^n_k + 2\lambda \left(h^n_{k+\frac 1 2} - f^n_k\right)} \leq 0$ and $\alpha \in [0, 1]$ is arbitrary.
		\item It holds $c_1\of{u^n_k + 2\lambda \left(h^n_{k+\frac 1 2} - f^n_k\right)} > 0$ and $\alpha \geq \frac{c_1\of{u^n_k + 2\lambda \left(h^n_{k+\frac 1 2} - f^n_k\right)}}{c_1\of{u^n_k + 2\lambda \left(h^n_{k+\frac 1 2} - f^n_k\right)} - c_1\of{u^n_k + 2\lambda \left(g^n_{k+\frac 1 2} - f^n_k\right)}}$.
	\end{enumerate}
	\begin{proof}
		The first condition follows from the fact that for the dissipative scheme holds
		\[
		c_1\of{u^n_k + 2\lambda \left(g^n_{k-\frac 1 2} - f^n_k\right)} \leq 0
		\]
		and therefore one concludes
		\[
			\begin{aligned}
		c_1 &\of{u^n_k + 2\lambda (f^{GT}_{\alpha_{k-\frac 1 2}} - f^n_k)} \\
		= &c_1\of{\alpha\left(u^n_k + 2\lambda \left(g^n_{{k-\frac 1 2}} - f^n_k\right) \right) + (1-\alpha) \left(u^n_k + 2\lambda \left(h^n_{{k-\frac 1 2}} - f^n_k}\right)\right) \\
		\leq &\alpha c_1\of{u^n_k + 2\lambda \left(g^n_{k-\frac 1 2} - f^n_k\right)} + (1-\alpha)c_1\of{ u^n_k + 2\lambda \left(h^n_{k-\frac 1 2} - \fnn_k\right)} \leq 0
			\end{aligned}
		\]
		because both values in the convex combination on the right hand side are smaller than zero. The same holds for $\alpha_{k+\frac 1 2}$ The second part is obviously just a statement that implies the second line of the above statement.
	\end{proof}
\end{lemma}


\begin{lemma}
	If \textbf{Condition P}  is satisfied holds
	\[
		p\of{u^n_k + \lambda \left(\fnn_{\alpha_{k-\frac 1 2}} - \fnn_{\alpha_{k+\frac 1 2}} \right)} \geq 0,
	\]
	whenever the CFL restriction $\lambda c_{max} < 0.5$ is respected.
	\begin{proof}
		The convexity implies as before
		\[
		\begin{aligned}
			-p\of{u^{n+1}_k} = &c_1\of{u^{n+1}_k} = c_1\of{u^n_k + \lambda\left(\fnn_{\alpha_{k- \frac 1 2}} - \fnn_{\alpha_{k+\frac 1 2}}\right)} \\
			= &c_1\of{\frac{u^n_k + 2 \lambda \left (\fnn_{\alpha_{k-\frac 1 2}} - f^n_k\right) + u^n_k + 2\lambda\left(f^n_k - \fnn_{\alpha_{k+\frac 1 2}}\right)  }{2}} \\
			\leq &\frac 1 2 \left (c_1 \of {u^n_k + 2 \lambda \left(\fnn_{\alpha - \frac 1 2} - f^n_k\right)} + c_1 \of {u^n_k  + 2\lambda\left(f^n_k - \fnn_{\alpha + \frac 1 2}\right)} \right) \\ 
			\leq& 0.
			\end{aligned}
		\]
		\end{proof}
	\end{lemma}
	The result for \textbf{Condition $\rho$} is obviously the same and this results apply for every convex functional that is bounded by the low order scheme used in the construction. \\
Conditions on the physical constraints are not new and used in many approaches. We like to recommend the following papers from the literature which uses at least from our point of view similar ideas \cite{rueda2022subcell, kuzmin2020monolithic, kuzmin2021Limiter}.
