%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% 
%\documentclass[english,aps,superscriptaddress,showkeys,showpacs,prepri]{revtex4}
\documentclass[english,aps,superscriptaddress,showkeys,showpacs,prepri,twocolumn]{revtex4}
\usepackage[T1]{fontenc}
\pdfoutput=1
%\usepackage[latin9]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\usepackage{units}
\usepackage{bbding}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\usepackage[utf8]{inputenc}
\usepackage{lmodern} % load a font with all the characters

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\@ifundefined{textcolor}{}
{%
 \definecolor{BLACK}{gray}{0}
 \definecolor{WHITE}{gray}{1}
 \definecolor{RED}{rgb}{1,0,0}
 \definecolor{GREEN}{rgb}{0,1,0}
 \definecolor{BLUE}{rgb}{0,0,1}
 \definecolor{CYAN}{cmyk}{1,0,0,0}
 \definecolor{MAGENTA}{cmyk}{0,1,0,0}
 \definecolor{YELLOW}{cmyk}{0,0,1,0}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\usepackage[sort&compress,numbers]{natbib} 
\bibliographystyle{apsrev4-1} 
\usepackage{doi}
\usepackage{hyperref}

\makeatother

\usepackage{babel}
\begin{document}

\title{
The Impact of Collisionality, FLR and Parallel Closure Effects on Instabilities
in the Tomakak Pedestal:   Numerical Studies with the NIMROD code
}
%Edge NIMROD studies and verification:\\ideal-MHD modification by collisionality, \\FLR and parallel-closure effects.}

\author{J. R. King}
\affiliation{Tech-X Corporation, 5621 Arapahoe Ave. Boulder, CO 80303, USA}

\author{A. Y. Pankin}
\affiliation{Tech-X Corporation, 5621 Arapahoe Ave. Boulder, CO 80303, USA}

\author{S. E. Kruger}
\affiliation{Tech-X Corporation, 5621 Arapahoe Ave. Boulder, CO 80303, USA}

\author{P. B. Snyder}
\affiliation{General Atomics, PO Box 85608, San Diego, CA 92186–5608, USA}

\begin{abstract}
The extended-MHD NIMROD code [C.R.~Sovinec and J.R.~King, J.~Comput.~Phys.~{\bf
229}, 5803 (2010)] is verified against the ideal-MHD ELITE code [H.R.~Wilson
\textit{et al.}~Phys.~Plasmas {\bf 9}, 1277 (2002)] on a diverted tokamak
discharge. When the NIMROD model complexity is increased incrementally,
resistive and first-order finite-Larmour radius effects are destabilizing and
stabilizing, respectively. The full result is compared to local analytic
calculations which are found to overpredict both the resistive destabilization
and drift stabilization in comparison to the NIMROD computations.
Published version: Phys. Plasmas 23, 062123 (2016) [\url{http://dx.doi.org/10.1063/1.4954302}]
\end{abstract}

\keywords{edge localized modes, peeling-ballooning modes, extended-MHD,
code verification}

\pacs{52.30.Ex 52.35.Py, 52.55.Fa, 52.55.Tn, 52.65.Kj}
\maketitle

%--------------------------------------------------
\input{definitions}   % Useful abbreviations
\input{introduction}
\input{benchmark}   
\input{xMHD}
\input{analyticComp}
\input{densityScan}
\input{conclusions} 
\appendix
%--------------------------------------------------

\begin{acknowledgments}
We thank Carl Sovinec, Chris Hegna and Nate Ferraro for discussions involving
this paper and N.~Aiba for providing the Meudas-1 equilibrium. This material is
based on work supported by US Department of Energy, Office of Science, Office
of Fusion Energy Sciences under award numbers DE-FC02-06ER54875 and
DE-FC02-08ER54972. This research used resources of the National Energy Research
Scientific Computing Center, a DOE Office of Science User Facility supported by
the Office of Science of the U.S. Department of Energy under Contract
No.~DE-AC02-05CH11231.
\end{acknowledgments}
\bibliographystyle{apsrev4-1}
\bibliography{Biblio}

\end{document}
