\documentclass{llncs}

\newcommand{\cL}{{\cal L}}
\let\terms\undefined
\input{preamble}

\renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}

\title{Temporal Stream Logic: \\[0.2em] Synthesis beyond the
  Bools\thanks{Supported by the European Research Council (ERC) Grant
    OSARES (No.\ 683300), the Collaborative Research Center (TRR 248,
    389792660), and the National Science Foundation (NSF) Grant
    CCF-1302327.}}

\author{
       Bernd Finkbeiner\inst{1}
  \and Felix Klein\inst{1}
  \and Ruzica Piskac\inst{2}
  \and Mark Santolucito\inst{2}
}

\institute{Saarland University, Saarbrücken, Germany
  \and
Yale University, New Haven, USA}

\maketitle

\begin{abstract}
  Reactive systems that operate in environments with complex data,
  such as mobile apps or embedded controllers with many sensors, are
  difficult to synthesize.  Synthesis tools usually fail for such
  systems because the state space resulting from the discretization
  of the data is too large.  We introduce TSL, a new temporal logic
  that separates control and data. We provide a CEGAR-based synthesis
  approach for the construction of implementations that are guaranteed
  to satisfy a TSL specification for all possible instantiations of
  the data processing functions.  TSL provides an attractive trade-off
  for synthesis. On the one hand, synthesis from TSL, unlike synthesis
  from standard temporal logics, is undecidable in general. On the
  other hand, however, synthesis from TSL is scalable, because it is
  independent of the complexity of the \mbox{handled} data.  Among
  other benchmarks, we have successfully synthesized a music player
  Android app and a controller for an autonomous vehicle in the Open
  Race Car Simulator (TORCS).
\end{abstract}

\section{Introduction}
\label{sec:intro}
\input{intro}

\section{Motivating Example}
\label{sec:motiv}
\input{motivatingExample}

\section{Preliminaries}
\label{sec:prelim}
\input{prelims}

\section{Temporal Stream Logic}
\label{sec:TSL}
\input{tsl}

\section{TSL Properties}
\label{sec:props}
\input{solvingtsl}

\section{TSL Synthesis}
\label{sec:synth}
\input{synth}

\section{Experimental Results}
\label{sec:eval}
\input{eval}

\section{Related Work}
\label{sec:related}
\input{related}

\section{Conclusions}
\label{sec:conclusions}
\input{conclusions}

%% Bibliography
\bibliographystyle{splncs}
\bibliography{biblio}

\newpage

\appendix
\section{Appendix}
\input{appendix}

\end{document}
