\begin{thebibliography}{BGR84}
%%%%%%%
%\bibitem[]{}{},{\em },{}.


\bibitem[AM69]{AM69}
{M. F. Atiyah, I. G. McDonald},
{\em Introduction to commutative algebra}, 
{Addison-Wesley Publishing Co., Reading, Mass.-London-Don Mills, Ont. 1969}.


\bibitem[Bou89]{Bou89}
{N. Bourbaki},
{\em General topology. Chapters 1--4,} 
Translated from the French. Reprint of the 1989 English translation. Elements of Mathematics (Berlin). Springer-Verlag, Berlin, 1998.


\bibitem[Bou90]{Bou90}
{N. Bourbaki},
{\em Algebra II. Chapters 4--7,} 
Translated from the 1981 French edition by P. M. Cohn and J. Howie. Reprint of the 1990 English edition.  Elements of Mathematics (Berlin). Springer-Verlag, Berlin, 2003.






\bibitem[BGR84]{BGR84}
{S. Bosch, U. G\"{u}ntzer, R. Remmert},
{\em Non-Archimedean analysis. A systematic approach to rigid analytic geometry,} 
{Grundlehren der Mathematischen Wissenschaften {\textbf{261}}. Springer-Verlag, Berlin, 1984. }



\bibitem[BV]{BV}
{K. Buzzard, A. Verberkmoes},
{\em Stably uniform affinoids are sheafy,}
{preprint available at http://arxiv.org/abs/1404.7020v2}





\bibitem[FK]{FK}
{K. Fujiwara, F. Kato},
{\em Foundations of rigid geometry I},
{available at http://arxiv.org/abs/1308.4734v5}



\bibitem[Har77]{Har77}
{R.~Hartshorne},
{\em Algebraic Geometry.},
{Grad. Texts in Math., no {\textbf{52}}, Springer-Verlag, New York, 1977}.




\bibitem[Hub93]{Hub93}
{R. Huber},
{\em Continuous valuations},
{Math. Z. {\textbf{212}} (1993), no. 3, 455--477}.

\bibitem[Hub94]{Hub94}
{R. Huber},
{\em A generalization of formal schemes and rigid analytic varieties.},
{ Math. Z. {\textbf{217}} (1994), no. 4, 513--551}.



\bibitem[Hub96]{Hub96}
{R. Huber},
{\em \'{E}tale cohomology of rigid analytic varieties and adic spaces},
{Aspects of Mathematics, E30. Friedr. Vieweg and Sohn, Braunschweig, 1996.}



\bibitem[Mat89]{Mat89}
{H. Matsumura},
{\em Commutative ring theory}
{Translated from the Japanese by M. Reid. Second edition. Cambridge Studies in Advanced Mathematics, 
{\textbf{8}}. Cambridge University Press, Cambridge, 1989.}


\bibitem[Mih16]{Mih16}
{T. Mihara},
{\em On Tate's acyclicity and uniformity of Berkovich spectra and adic spectra,}
{Israel J. Math. {\textbf{216}} (2016), no. 1, 61--105.}


\end{thebibliography}