%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%


\begin{thebibliography}{99.}%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references if
% the subject of your book is from the field
% "Mathematics, Physics, Statistics, Computer Science"
%
% Contribution

\bibitem{AJ13}
Acemoglu, D., Jensen, M.K.: Aggregate comparative statics. Games and Economic Behavior \textbf{81}, 27-49 (2013)


\bibitem{AJ15}
 Acemoglu, D., Jensen, M.K.: Robust comparative statics in large
dynamic economies. Journal of Political Economy \textbf{123}, 587-640 (2015)

\bibitem{AJW15}
Adlakha, S., Johari, R., Weintraub, G.Y.: Equilibria of dynamic
games with many players: Existence, approximation, and market
structure. J. Econ. Theory \textbf{156}, 269-316 (2015)



\bibitem{AS95}
Altman, E., Stidham, S.: Optimality of monotonic policies for two-action Markovian decision processes, with applications to control of queues with delayed information. Queueing Systems \textbf{21}, 267-291 (1995)


\bibitem{A96}
Amir R.: Sensitivity analysis of multisector optimal
economic dynamics. Journal of Mathematical Economics \textbf{25}, 123-141 (1996)


\bibitem{A03}
Asmussen, S.: Applied Probability and Queues, 2nd edn.
Springer, New York (2003)


\bibitem{AR14}
Athreya, K.B., Roy, V.: When is a Markov chain regenerative? Statistics and Probability Letters \textbf{84}, 22-26 (2014)




\bibitem{B13}
 Babichenko, Y.: Best-reply dynamics in large binary-choice anonymous games. Games and Economic Behavior \textbf{81}, 130-144 (2013)

\bibitem{B12}
 Bardi, M.: Explicit solutions of some linear-quadratic mean field games. Netw. Heterogeneous
Media \textbf{7}, 243-261 (2012)

\bibitem{BR11}
Bauerle, N., Rieder, U.: Markov Decision Processes with Applications to Finance.
Springer, Berlin (2011)

\bibitem{B85}
Becker R. A.:
Comparative dynamics in aggregate models of optimal capital accumulation. Quarterly Journal of Economics \textbf{100}, 1235-1256 (1985)




\bibitem{BFY13}
Bensoussan, A., Frehse, J., Yam, P.: Mean Field Games and Mean
Field Type Control Theory.  Springer, New York (2013)





\bibitem{B15}
 Biswas, A.: Mean field games with ergodic cost for discrete time Markov processes,
preprint, arXiv:1510.08968, 2015.




\bibitem{BS00}
Bonnans, J.F., Shapiro, A.: Perturbation Analysis of Optimization Problems. Springer-Verlag, New York (2000)


\bibitem{BD01}
 Brock, W.A., Durlauf, S. N.: Discrete choice with social interactions. Rev. Econ. Studies \textbf{68}, 235-260 (2001)





\bibitem{C14}
Caines, P.E.: Mean field games. In: Samad, T., Baillieul, J.  (eds.) Encyclopedia of Systems and Control. Springer-Verlag, Berlin (2014)

\bibitem{CHM17}
 Caines, P.E.,  Huang, M., Malham\'e, R.P.: Mean Field Games. In:  Basar, T.,  Zaccour, G. (eds.)
    Handbook of Dynamic
Game Theory, pp. 345-372,  Springer, Berlin  (2017)

\bibitem{C12}
Cardaliaguet, P.: Notes on mean field games, University of Paris, Dauphine (2012)

\bibitem{CD18}
Carmona R.,  Delarue, F.: Probabilistic Theory of Mean Field Games with Applications,
vol I and II.  Springer, Cham (2018)


\bibitem{D63}
Dorato, P.: On sensitivity in optimal control systems. IEEE Transactions on Automatic Control \textbf{8}, 256-257 (1963)



\bibitem{FV97}
Filar, J.A., Vrieze, K.: Competitive Markov
Decision Processes. Springer, New York (1997)


\bibitem{GMS10}
Gomes, D. A.,  Mohr, J., Souza, R.R.: Discrete time, finite state space mean field games. J. Math. Pures Appl. \textbf{93} 308-328, (2010)



\bibitem{HL93}
Hernandez-Lerma, O.: Adaptive Markov Control Processes. Springer-Verlag, New York (1989)

\bibitem{H39}
Hicks, J. R.:  Value and Capital.  Clarendon Press, Oxford
 (1939)




\bibitem{HCM03}
Huang, M., Caines, P.E., Malham\'e, R.P.: Individual and mass
behaviour in large population stochastic wireless power control
problems: Centralized and Nash equilibrium solutions. Proc.
42nd IEEE Conference on Decision and Control, pp. 98-105,  Maui, HI (2003)



\bibitem{HCM07}
Huang, M., Caines, P.E., Malham\'e, R.P.: Large-population
cost-coupled LQG problems with nonuniform agents: Individual-mass
behavior and decentralized $\varepsilon$-Nash equilibria. IEEE
Trans. Autom. Control \textbf{52}, 1560-1571 (2007)





\bibitem{HM16Chen}
Huang, M., Ma, Y.: Mean field stochastic games: Monotone costs
and threshold policies (in Chinese), Sci. Sin. Math. (special issue in
honour of the 80th birthday of Prof. H-F. Chen) \textbf{46}, 1445-1460 (2016)


\bibitem{HM17}Huang, M., Ma, Y.: Mean field stochastic games with binary action
spaces and monotone costs. arXiv:1701.06661v1, 2017.

\bibitem{HMcdc17}
Huang, M., Ma, Y.:
Mean field stochastic games with binary actions: Stationary threshold policies.
Proc. 56th IEEE Conference on Decision and Control, Melbourne, Australia,  pp. 27-32 (2017)


\bibitem{HMC06}
Huang, M., Malham\'e, R.P., Caines, P.E.: Large population stochastic dynamic games: Closed-loop McKean-Vlasov systems and the Nash certainty equivalence principle. Commun.  Inform.  Systems \textbf{6}, 221-251 (2006)


\bibitem{HZ18}
Huang, M., Zhou, M..: Linear quadratic mean field games: Asymptotic solvability and relation to the fixed point approach.  IEEE Transactions on Automatic Control (2018, in revision, conditionally accepted)



\bibitem{IK92}
Ito, K., Kunisch, K.: Sensitivity analysis of solutions to optimization problems in Hilbert spaces with applications
to optimal control and estimation. J. Differential Equations \textbf{99}, 1-40 (1992)


\bibitem{JR88}
Jovanovic, B., Rosenthal, R.W.: Anonymous
sequential games. Journal of Mathematical Economics \textbf{17}, 77-87 (1988)




\bibitem{JAW11}
Jiang, L., Anantharam, V., Walrand, J.:
How bad are selfish investments in network security?
 IEEE/ACM Trans. Networking \textbf{19}, 549-560 (2011)


\bibitem{K12}
Kolokoltsov, V.N.:
Nonlinear Markov games on a finite state space (mean-field and
binary interactions).
International J. Statistics Probability \textbf{1}, 77-91 (2012)




\bibitem{K89}
Kress, R.: Linear Integral Equations. Springer, Berlin (1989)




\bibitem{LL07}
Lasry, J.-M., Lions, P.-L.: Mean field games. Japan. J.
Math. \textbf{2}, 229-260 (2007)



\bibitem{LB08}
Lelarge, M., Bolot, J.: A local mean field analysis of security investments
in networks. Proc. ACM SIGCOMM NetEcon, Seattle, WA, pp. 25-30,
 2008


\bibitem{LZ08}
Li, T., Zhang, J.-F.: Asymptotically optimal decentralized control
for large population stochastic multiagent systems. IEEE Trans.
Autom. Control \textbf{53}, 1643-1660 (2008)





 \bibitem{MP10}
Manfredia, P., Posta, P.D., d\'Onofrio, A., Salinelli, E., Centrone, F., Meo, C., Poletti, P.:
Optimal vaccination choice, vaccination games, and rational exemption:
An appraisal.  Vaccine \textbf{28}, 98-109 (2010)


\bibitem{MT09}
Meyn, S., Tweedie, R. L.: Markov Chains and Stochastic Stability, 2nd ed. Cambridge University Press, Cambridge (2009)


\bibitem{MS94}
Milgrom, P., Shannon, C.:  Monotone comparative statics. Econometrica \textbf{62}, 157-80 (1994)


\bibitem{MB17}
Moon, J.,  Basar, T.: Linear quadratic risk-sensitive and robust mean field games. IEEE
Trans. Autom. Control \textbf{62},  1062-1077 (2017)


\bibitem{MS02}
M\"uller, A., Stoyan, D.: Comparison Methods for Stochastic Models and Risks.
Wiley, Chichester (2002)




\bibitem{O73}
Oniki, H.: Comparative dynamics (sensitivity analysis) in optimal control theory.
J. Econ. Theory \textbf{6}, 265-283 (1973)


\bibitem{STR18}
Saldi, N., Basar, T., Raginsky, M.:
Markov-Nash equilibria in mean-field games with discounted cost.
SIAM J. Control Optimization \textbf{56}, 4256-4287 (2018)



\bibitem{S83}
Samuelson, P.A.: Foundations of Economic Analysis, enlarged edn., Harvard University Press, Cambridge, MA (1983)

\bibitem{S73}
Schelling, T.C.: Hockey helmets, concealed weapons, and daylight saving: A study of binary
choices with externalities. The Journal of Conflict Resolution \textbf{17}, 381-428 (1973)



\bibitem{S95}
Selten, R.: An axiomatic theory of a risk dominance measure
for bipolar games with linear incentives. Games and Econ. Behav. \textbf{8}, 213-263 (1995)


\bibitem{S53}
 Shapley, L.S.: Stochastic games. Proc. Natl. Acad. Sci. \textbf{39}, 1095-1100 (1953)



\bibitem{SW93}
Sigman, K., Wolff, R.W.: A review of regenerative processes. SIAM Rev. \textbf{35}, 269-288 (1993)


\bibitem{S06}
Sun, Y.: The exact law of large numbers via Fubini extension and
characterization of insurable risks. J. Econ. Theory \textbf{126}, 31-69 (2006)

\bibitem{T98}
Topkis, D.M.: Supermodularity and Complementarity.  Princeton Univ. Press,
Princeton (1998)



\bibitem{WWA11}
 Walker, M.,  Wooders, J.,   Amir, R.:
Equilibrium play in matches: Binary Markov games. Games and Economic Behavior \textbf{71}, 487-502 (2011)

\bibitem{WBR08}
Weintraub, G.Y., Benkard, C.L., Van Roy, B.:  Markov perfect
industry dynamics with many firms. Econometrica \textbf{76}, 1375-1411 (2008)


\bibitem{Y11}
Yong, J.: Linear-quadratic optimal control problems for mean-field stochastic differential
equations. SIAM J. Control Optim.  \textbf{51},  2809-2838 (2013)



\bibitem{ZH17}
Zhou, M., Huang, M.: Mean field games with Poisson point processes and impulse control. Proc. 56th IEEE Conference on Decision and Control, Melbourne, Australia  pp. 3152-3157 (2017)



\end{thebibliography}
