\documentclass[a4paper,envcountsame]{llncs}
\setcounter{tocdepth}{3}

\usepackage{url}
\sloppy
\spnewtheorem{dfn}{Definition}{\bfseries}{\itshape}
\spnewtheorem{lem}{Lemma}{\bfseries}{\itshape}
\spnewtheorem{thm}{Theorem}{\bfseries}{\itshape}
\spnewtheorem{cor}{Corollary}{\bfseries}{\itshape}
\spnewtheorem{prp}{Proposition}{\bfseries}{\itshape}
\spnewtheorem*{rmk}{Remark}{\itshape}{}
\spnewtheorem{invariant}[lemma]{Invariant}{\bfseries}{\itshape}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{amssymb,amsmath}
\usepackage[basic]{complexity}
\usepackage{thmtools}
\usepackage{times}
\usepackage{float}

\usepackage{xcolor}
\usepackage{xspace}
\usepackage{paralist}
\usepackage{comment}

\usepackage{booktabs}
\usepackage{todonotes}

\usepackage{graphicx}
\usepackage{subfig}

\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes}
\usetikzlibrary{automata}
\usetikzlibrary{decorations.pathmorphing}

\usepackage[ruled,vlined,linesnumbered,nokwfunc,algo2e]{algorithm2e_}
\DontPrintSemicolon
\SetAlCapFnt{\normalfont\scshape}
\SetProcNameSty{textsc}
\SetFuncSty{textsc}

\input{shortcuts}

\setlength\floatsep{0.1em}
\setlength\textfloatsep{0.1em}
\setlength\intextsep{0.1em}

\pagestyle{plain}

\begin{document}
\mainmatter

\title{Symbolic Algorithms for Graphs and Markov Decision Processes with Fairness Objectives\vspace{-2mm}}
\author{Krishnendu Chatterjee$^1$, Monika Henzinger$^2$, Veronika Loitzenbauer$^3$, \\ Simin Oraee$^4$, and Viktor Toman$^1$\vspace{-1mm}}
\institute{$^1$ IST Austria, Klosterneuburg, Austria \\
			$^2$ University of Vienna, Austria \\
            	$^3$ Johannes Kepler University Linz, Austria \\
            	$^4$ Max Planck Institute for Software Systems, Kaiserslautern, Germany}

\maketitle
\vspace{-4mm}
\begin{abstract}
Given a model and a specification, the fundamental model-checking problem asks
for algorithmic verification of whether the model satisfies the specification.
We consider graphs and Markov decision processes (MDPs), which are fundamental 
models for reactive systems.
One of the very basic specifications that arise in verification of reactive systems
is the strong fairness (aka Streett) objective. Given different types of 
requests and corresponding grants, the objective requires that for each type, if the 
request event happens infinitely often, then the corresponding grant event 
must also happen infinitely often. 
All $\omega$-regular objectives can be expressed as Streett objectives
and hence they are canonical in verification. 
To handle the state-space explosion, symbolic algorithms are required that operate on a
succinct implicit representation of the system rather than explicitly accessing
the system.
While explicit algorithms for graphs and MDPs with Streett objectives have been 
widely studied, there has been no improvement of the basic symbolic algorithms.
The worst-case numbers of symbolic steps required for the basic symbolic algorithms 
are as follows: quadratic for graphs and cubic for MDPs.
In this work we present the first sub-quadratic symbolic algorithm for graphs 
with Streett objectives, and our algorithm is sub-quadratic even for MDPs.
Based on our algorithmic insights we present an implementation of the new symbolic
approach and show that it improves the existing approach on several academic benchmark
examples.
\end{abstract}

\input{1_intro}
\input{2_defin}
\input{3_lss}
\input{4_graphs}
\input{5_mecs}
\input{6_mdps}
\input{7_exper}
\input{8_conc}

\subsubsection*{Acknowledgements.}
K.~C. and M.~H.\ are partially supported by
the Vienna Science and Technology Fund (WWTF) grant ICT15-003.
K.~C.\ is partially supported by
the Austrian Science Fund (FWF): S11407-N23 (RiSE/SHiNE), and an ERC Start Grant (279307: Graph Games).
V.~T. \ is partially supported by
the European Union’s Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie Grant Agreement No. 665385.
V.~L.~is partially supported by
the Austrian Science Fund (FWF): S11408-N23 (RiSE/SHiNE), the ISF grant \#1278/16, and an ERC Consolidator Grant (project MPM).
For M.~H.\ and V.~L.\ the research leading to these results has received funding from
the European Research Council under the European Union's Seventh Framework Programme (FP/2007-2013) / ERC Grant Agreement no. 340506.

\bibliographystyle{splncs03}
\bibliography{literature}

\clearpage
\section*{Appendix}
\appendix
\input{9_app}

\end{document}
