\documentclass[12pt]{article}

\usepackage{mathptmx,amsmath,amssymb,amsfonts,amsthm,a4wide}
\usepackage{graphicx,color,xcolor,pictex,epstopdf,url,algorithm,algorithmic,caption, comment}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{remark}{Remark}[section]
\mathsurround=1pt
\parskip=3pt
\parindent=0pt
\belowdisplayskip=4pt plus2pt minus 1pt
\abovedisplayskip=4pt plus2pt minus 1pt
\definecolor{brdarkblue}{rgb}{0.0, 0.0, 0.7}
\definecolor{brdarkgreen}{rgb}{0.0, 0.7, 0.0}
\definecolor{bkdarkcyan}{rgb}{0.0, 0.5, 0.5}
\definecolor{bkcyan}{rgb}{0.0, 0.6, 0.7}
\def\widevec#1{\overline{\vec{#1}}}

%\newcommand{\Margin}[1]{\marginpar{\textcolor{blue}{{\small#1}}}}
%\newcommand{\revision}[1]{\textcolor{blue}{#1}}
\newcommand{\Margin}[1]{}
\newcommand{\revision}[1]{#1}
%\newcommand{\rerevision}[1]{\textcolor{blue}{#1}}
\newcommand{\rerevision}[1]{{#1}}

\begin{document}
\title{Determining damping terms in fractional wave equations}
\author{Barbara Kaltenbacher\footnote{
Department of Mathematics,
Alpen-Adria-Universit\"at Klagenfurt.
barbara.kaltenbacher@aau.at.}
\and
William Rundell\footnote{
Department of Mathematics,
Texas A\&M University,
%College Station,
Texas 77843. % USA.
rundell@math.tamu.edu}
}
%\author{}
\date{\vskip-3ex}
\maketitle
\begin{abstract}
This paper deals with the inverse problem of recovering an arbitrary number of
fractional damping terms in a wave equation.
We develop several approaches on uniqueness and reconstruction, some of them
relying on Tauberian theorems that provide relations between the asymptotic
behaviour of solutions in time and Laplace domains.
The possibility of additionally recovering space-dependent coefficients
or initial data is discussed.
The resulting methods for reconstructing coefficients and fractional orders in
these terms are tested numerically. 
In addition, we provide an analysis of the forward problem consisting of
a multiterm fractional wave equation.
\end{abstract}

\leftline{\small \qquad\qquad
{\bf Keywords:} %Fractionally damped wave equation,
Inverse problems, multiterm fractional PDE, fractionally damped wave equation}
\smallskip
\leftline{\small \qquad\qquad 
\textbf{{\textsc msc} 2020} {\bf classification:} 35R30, 35R11, 35L10, 78A46}

\input introduction
\input forward
\input uniqueness
\input recon_meth
\input reconstructions
%\input appendix

\subsection*{Acknowledgment}
\vskip-4pt
\noindent
The work of the first author was supported by the Austrian Science Fund {\sc fwf}
under the grants P30054 and {\sc doc}78.

%\nobreak
\noindent
The work of the second author was supported
in part by the
National Science Foundation through award {\sc dms}-2111020.

%\bibliographystyle{plain}
%\bibliography{bk,bk-br,br,numerics}
\begin{thebibliography}{10}

\bibitem{Atanackovic_etal:2014}
Teodor~M. Atanackovi\'{c}, Stevan Pilipovi\'{c}, Bogoljub Stankovi\'{c}, and
  Du\v{s}an Zorica.
\newblock {\em Fractional Calculus with Applications in Mechanics}.
\newblock John Wiley \& Sons, Ltd, 2014.

\bibitem{bagley1986fractional}
Ronald~L Bagley and Peter~J Torvik.
\newblock On the fractional calculus model of viscoelastic behavior.
\newblock {\em Journal of Rheology}, 30(1):133--155, 1986.

\bibitem{CaiChenFangHolm_survey2018}
Wei Cai, Wen Chen, Jun Fang, and Sverre Holm.
\newblock {A survey on fractional derivative modeling of power-law
  frequency-dependent viscous dissipative and scattering attenuation in
  acoustic wave propagation}.
\newblock {\em Applied Mechanics Reviews}, 70(3), 06 2018.

\bibitem{Caputo:1967}
Michele Caputo.
\newblock Linear models of dissipation whose {$Q$} is almost frequency
  independent -- {II}.
\newblock {\em Geophys. J. Int.}, 13(5):529--539, 1967.

\bibitem{CaputoMainardi:1971a}
Michele Caputo and Francesco Mainardi.
\newblock A new dissipation model based on memory mechanism.
\newblock {\em Pure Appl. Geophys.}, 91(1):134--147, 1971.

\bibitem{CCPR:1997}
K.~Chadan, D.~Colton, L.~P\"{a}iv\"{a}rinta, and W.~Rundell.
\newblock {\em An Introduction to Inverse Scattering and Inverse Spectral
  Problems}.
\newblock SIAM Monographs on Mathematical Modeling and Computation. SIAM, 1997.

\bibitem{DiethelmFord:2004}
Kai Diethelm and Neville~J. Ford.
\newblock Multi-order fractional differential equations and their numerical
  solution.
\newblock {\em Appl. Math. Comput.}, 154(3):621--640, 2004.

\bibitem{Dzjbashian:1966}
Mkhitar~M. Djrbashian.
\newblock {\em Integralnye preobrazovaniya i predstavleniya funktsiiv
  kompleksnoi oblasti}.
\newblock Izdat. ``Nauka'', Moscow, 1966.

\bibitem{Djrbashian:1993}
Mkhitar~M. Djrbashian.
\newblock {\em Harmonic {A}nalysis and {B}oundary {V}alue {P}roblems in the
  {C}omplex {D}omain}.
\newblock Birkh\"auser, Basel, 1993.

\bibitem{Eggermont:1987}
Paul P.~B. Eggermont.
\newblock On {G}alerkin methods for {A}bel-type integral equations.
\newblock {\em SIAM Journal on Numerical Analysis}, 25:1093--1117, 1988.

\bibitem{Evans:2010}
Lawrence~C. Evans.
\newblock {\em Partial differential equations}, volume~19 of {\em Graduate
  Studies in Mathematics}.
\newblock American Mathematical Society, Providence, RI, second edition, 2010.

\bibitem{Feller:1971}
William Feller.
\newblock {\em An introduction to probability theory and its applications.
  {V}ol. {II}}.
\newblock John Wiley \& Sons, Inc., New York-London-Sydney, second edition,
  1971.

\bibitem{Garrappa}
Roberto Garrappa.
\newblock \url{https://www.dm.uniba.it/members/garrappa/software}.

\bibitem{Garrappa:2015}
Roberto Garrappa.
\newblock Numerical evaluation of two and three parameter {M}ittag-{L}effler
  functions.
\newblock {\em SIAM J. Numer. Anal.}, 53(3):1350--1369, 2015.

\bibitem{GarrappaPopolizio:2018}
Roberto Garrappa and Marina Popolizio.
\newblock Computing the matrix {M}ittag-{L}effler function with applications to
  fractional calculus.
\newblock {\em J. Sci. Comput.}, 77(1):129--153, 2018.

\bibitem{GLS90}
G.~Gripenberg, S.-O. Londen, and O.~J. Staffans.
\newblock {\em Volterra Integral and Functional Equations}.
\newblock Encyclopedia of Mathematics and its Applications. Cambridge
  University Press, 1990.

\bibitem{HatanoNakagawaWangYamamoto:2013}
Yuko Hatano, Junichi Nakagawa, Shenghang Wang, and Masahiro Yamamoto.
\newblock Determination of order in fractional diffusion equation.
\newblock {\em J. Math. Industry}, 5(A):51--57, 2013.

\bibitem{JinKian:2021}
Bangti Jin and Yavar Kian.
\newblock Recovering multiple fractional orders in time-fractional diffusion in
  an unknown medium.
\newblock {\em Proceedings of the Royal Society A: Mathematical, Physical and
  Engineering Sciences}, 2021.
\newblock in press; see also arXiv:2106.02554 [math.NA].

\bibitem{JinRundell:2015}
Bangti Jin and William Rundell.
\newblock A tutorial on inverse problems for anomalous diffusion processes.
\newblock {\em Inverse Problems}, 31(3):035003, 40, 2015.

\bibitem{fracJMGT}
Barbara Kaltenbacher and Vanja Nikoli\'c.
\newblock {Time-fractional Moore-Gibson-Thompson equations}.
\newblock {\em Mathematical Models and Methods in the Applied Sciences M3AS},
  2022.
\newblock to appear; see also arXiv:2104.13967 [math.AP].

\bibitem{KaltenbacherRundell:2021b}
Barbara Kaltenbacher and William Rundell.
\newblock Some inverse problems for wave equations with fractional derivative
  attenuation.
\newblock {\em Inverse Problems}, 2021.

\bibitem{BBB}
Barbara Kaltenbacher and William Rundell.
\newblock {\em Inverse Problems for Fractional Partial Differential Equations}.
\newblock AMS, 2022.

\bibitem{KubicaRyszewskaYamamoto:2020}
Adam Kubica, Katarzyna Ryszewska, and Masahiro Yamamoto.
\newblock {\em Time-fractional Differential Equations: A Theoretical
  Introduction}.
\newblock Springer, 2020.

\bibitem{LiZhangJiaYamamoto:2013}
Gongsheng Li, Dali Zhang, Xianzheng Jia, and Masahiro Yamamoto.
\newblock Simultaneous inversion for the space-dependent diffusion coefficient
  and the fractional order in the time-fractional diffusion equation.
\newblock {\em Inverse Problems}, 29(6):065014, 36, 2013.

\bibitem{LiYamamoto:2015}
Zhiyuan Li and Masahiro Yamamoto.
\newblock Uniqueness for inverse problems of determining orders of multi-term
  time-fractional derivatives of diffusion equation.
\newblock {\em Appl. Anal.}, 94(3):570--579, 2015.

\bibitem{LuchkoGorenflo:1999}
Yurii Luchko and Rudolf Gorenflo.
\newblock An operational method for solving fractional differential equations
  with the {C}aputo derivatives.
\newblock {\em Acta Math. Vietnam.}, 24(2):207--233, 1999.

\bibitem{MainardiGorenflo:2000}
Francesco Mainardi and Rudolf Gorenflo.
\newblock On {M}ittag-{L}effler-type functions in fractional evolution
  processes.
\newblock {\em J. Comput. Appl. Math.}, 118(1-2):283--299, 2000.

\bibitem{Popolizio:2018}
Marina Popolizio.
\newblock Numerical solution of multiterm fractional differential equations
  using the matrix mittag-leffler functions.
\newblock {\em Mathematics}, 1(6), 2018.

\bibitem{RundellSacks:1992b}
William Rundell and Paul~E. Sacks.
\newblock The reconstruction of {S}turm-{L}iouville operators.
\newblock {\em Inverse Problems}, 8(3):457--482, 1992.

\bibitem{RundellSacks:1992a}
William Rundell and Paul~E. Sacks.
\newblock Reconstruction techniques for classical inverse {S}turm-{L}iouville
  problems.
\newblock {\em Math. Comp.}, 58(197):161--183, 1992.

\bibitem{SakamotoYamamoto:2011a}
Kenichi Sakamoto and Masahiro Yamamoto.
\newblock Initial value/boundary value problems for fractional diffusion-wave
  equations and applications to some inverse problems.
\newblock {\em J. Math. Anal. Appl.}, 382(1):426--447, 2011.

\bibitem{SamkoKilbasMarichev:1993}
Stefan~G. Samko, Anatoly~A. Kilbas, and Oleg~I. Marichev.
\newblock {\em Fractional {I}ntegrals and {D}erivatives}.
\newblock Gordon and Breach Science Publishers, Yverdon, 1993.

\bibitem{schmidt2002finite}
Andr{\'e} Schmidt and Lothar Gaul.
\newblock Finite element formulation of viscoelastic constitutive equations
  using fractional time derivatives.
\newblock {\em Nonlinear Dynamics}, 29(1):37--55, 2002.

\bibitem{SunLiZhang:2021}
L.~L. Sun, Y.~S. Li, and Y.~Zhang.
\newblock Simultaneous inversion of the potential term and the fractional
  orders in a multi-term time-fractional diffusion equation.
\newblock {\em Inverse Problems}, 37(5):Paper No. 055007, 26, 2021.

\bibitem{VoegeliNedaiaslSauter:2016}
Urs V\"ogeli, Khadijeh Nedaiasl, and Stefan Sauter.
\newblock A fully discrete {G}alerkin method for {A}bel-type integral
  equations.
\newblock {\em Advances in Computational Mathematics}, 12 2016.

\bibitem{Yamamoto:2021}
M.~Yamamoto.
\newblock Uniqueness in determining fractional orders of derivatives and
  initial values.
\newblock {\em Inverse Problems}, 37(9):Paper No. 095006, 34, 2021.

\end{thebibliography}
\end{document}
