\subsection{Numerical solution of the forward problem}

There are several methods available for solving multi-term
fractional ordinary differential equations.
For our situation we require a solver that is accurate over the entire
time interval $[0,\infty)$ since one problem we consider
is the recovery of the components of the operator from large time values only.
Our method of choice here is to convert the system with multiple
fractional derivatives to a single 
{\sc ode}
of the form  $D_t^\gamma u = A u$
where $A$ is a square matrix.
The seminal starting point here is the paper by Diethelm and Ford,
\cite{DiethelmFord:2004} which allows one to consider the equation
$D^{\alpha_0} y(t) = f\bigl(t,y(t),D^{\alpha_1},\;\ldots\;,D^{\alpha_n}\bigr)$
subject to $y^{(k)}(0) = y_0^k$ for $k=0,\,1,\;\ldots\;\lceil\alpha_0\rceil-1$,
and its conversion to the form $D^\gamma Y(t) = g\bigl(t,Y(t)\bigr)$,
with $Y(0) = Y_0$.
Existence and uniquness results are obtained and a numerical method for
the solution formulated.
This was later refined by Garrappa and Popolizio,
\cite{GarrappaPopolizio:2018} in the case of linear systems
into a solver whose accuracy approaches machine precision.
This is based on using the Mittag-Leffler function with a matrix argument $A$
that uses different approaches depending of the location of the
eigenvalues of $A$ in the complex plane and combined into an algorithm that
works for matrices with any eigenvalue locations.
See also \cite{Popolizio:2018}.
We describe this above approach briefly since it comes with a certain
restriction that should be clarified.

The following result is proven in \cite{Popolizio:2018}:
\begin{theorem}
Consider the initial value problem
\begin{equation}\label{eqn:ode_ivp}
D^{\alpha_0} = f\bigl(t,y(t),D^{\alpha_1}y(t),\,\ldots\,
D^{\alpha_{n-1}}y(t)\bigr),\qquad
y^{(j)}(0) = y_0{(j)}, j = 0,\;\ldots\,,\,[\alpha_0]-1
\end{equation}
where $\alpha_0> \alpha_1 >\, \ldots\, \alpha_{k-1}$ and $0<\alpha_{k-1}<1$.
Assume that each $\alpha_j\in \mathbb{Q}$ and let $M$ 
be the least
common denominator of $\alpha_0,\,\ldots,\alpha_{k-1}$.
Set $\gamma=1/M$ and $N=M\alpha_0$.
Then the initial value problem \eqref{eqn:ode_system} is equivalent to
the system of equations
\begin{equation}\label{eqn:ode_system}
D^\gamma y_0(t) = y_1(t),\ D^\gamma y_1(t) = y_2(t), \ 
	D^\gamma y_{N-1}(t) = f(t,y_0(t),y_{\alpha_1/\gamma}(t),\ldots
	\,y_{\alpha_{k-1}/\gamma}(t)
\end{equation}
together with the initial conditions
\begin{equation}\label{eqn:ode_system_init_conditions}
	y_j(0) = y_0^{(j/M)} \quad \mbox{if } j/M \in \mathbb{Z}_0,
	\quad \mbox{else }\ 0.
\end{equation}
\end{theorem}
As a result of the above theorem the linear system can be reformulated to
the form
\begin{equation}\label{eqn:ode_matrix_system}
D^\gamma Y(t) = A Y(t) + 
e_N\,f(t),\qquad Y(0)=Y_0,
\quad e_N = (0,0,\ldots,1)^T\in \mathbb{R}^N.
\end{equation}
where the coefficient matrix $A\in \mathbb{R}^{N\times N}$ is of 
companion type.

Then it is possible to express the solution to \eqref{eqn:ode_matrix_system}
in terms of Mittag-Leffler functions with matrix arguments as
\begin{equation}\label{eqn:ode_matrix_ML}
Y(t) = E_{\alpha,1}(t^\gamma A) Y_0 
+ \int_0^t (t-s)^{\gamma-1} E_{\gamma,\gamma}\bigl((t-s)^\gamma A\bigr)
	e_N\,f(s)\,ds.
\end{equation}
For general matrix functions the Schur-Parlett algorithm is the method of
choice and to this end the final component needed is an accurate evaluation
of the matrix Mittag-Leffler function and its derivatives.
This is both nontrivial and quite technical and we simply refer to the above
references, \cite{GarrappaPopolizio:2018,Popolizio:2018},
and also to \cite{Garrappa:2015} for the details.
Code to implement what is needed for this step is available from
Roberto Garrappa's homepage \cite{Garrappa}.

Note that in our case we have $\alpha_0=2$ and also the requirement that
each of the exponents $\alpha_j = q_j/p_j$ must be rational numbers.
The above restrictions can lead to a quite large system of size
$\mbox{lcm}(p_1,\,\ldots,p_{k-1})$ and hence a small value of $\gamma$.
However, we use this solver only for the purpose of providing simulated data
and our inversion techniques are independent of its use.

\revision{
Since we are using asymptotic formulas it is essential to use a reliable and accurate solver that is capable to cover a wide range of time values. The code from \cite{Garrappa:2015,GarrappaPopolizio:2018,Popolizio:2018} provably fulfills these requirements and our numerical experiments confirmed this.
}
