% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
\usepackage{authblk}
\usepackage{EMNLP2023}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}

\input{macros}

\title{Let Me Teach You: \\ Pedagogical Foundations of Feedback for Language Models}

\author[1]{\textbf{Beatriz Borges}}
\author[2]{\textbf{Niket Tandon}}
\author[1]{\textbf{Tanja Käser}}
\author[1]{\textbf{Antoine Bosselut}}
\affil{EPFL \:\:\: $^2$Allen Institute for Artificial Intelligence}
\affil[ ]{\texttt{\{beatriz.borges, antoine.bosselut\}@epfl.ch}}


\begin{document}
\maketitle
\begin{abstract}
Natural Language Feedback (NLF) is an increasingly popular avenue to align Large Language Models (LLMs) to human preferences. Despite the richness and diversity of the information it can convey, NLF is often hand-designed and arbitrary. In a different world, research in pedagogy has long established several effective feedback models. 
In this opinion piece, we compile ideas from pedagogy to introduce \ours, a feedback framework for LLMs that outlines the various characteristics of the feedback space, and a feedback content taxonomy based on these variables. 
Our taxonomy offers both a general mapping of the feedback space, as well as pedagogy-established discrete categories, allowing us to empirically demonstrate the impact of different feedback types on revised generations. In addition to streamlining existing NLF designs, \ours also brings out new, unexplored directions for research in NLF. We make our taxonomy available to the community, providing guides and examples for mapping our categorizations to future resources.
\end{abstract}

\input{01_introduction}
\input{02_background}
\input{03_framework}
\input{04_taxonomy}
\input{05_case_study}
\input{06_conclusion}

\newpage
\section*{Limitations}
\ours, our proposed framework to capture the full feedback ecosystem, is theorectically grounded and fairly unexplored. Some aspects, like the impact of timing, need to be reassessed for LLMs.

Our previous NLP research mapping (presented in Table \ref{tab:nlp_feedback_space}) was restricted to only the nine feedback content categories. Though they are cleanly delineated and encapsulate the main feedback types that emerged in pedagogical research, they do not encompass all the feedback space captured by the 10 general axes in the taxonomy.

Our case study was conducted exclusively in English. Models trained on other languages, especially lower-resource ones, might react to feedback differently, and it might have a weaker impact on revised generations. 

Additionally, we used GPT-4, a paid and closed-source LLM, whose details about architecture and training remain unknown.



\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\appendix
\include{appendix_a}
\include{appendix_b}
\include{appendix_c}
\include{appendix_d}

\end{document}
