\begin{thebibliography}{}

\bibliographystyle{IEEEtran}

\bibitem{iskander}
    Z. Yun and M. F. Iskander, "Ray Tracing for Radio Propagation Modeling: Principles and Applications," \textit{IEEE Access}, Vol. 3, pp. 1089-1100, 2015.
\bibitem{fuschini2019}
    F. Fuschini, M. Zoli, E.M. Vitucci, M. Barbiroli and V. Degli-Esposti, “A Study on Mm-wave Multi-User Directional Beamforming Based on Measurements and Ray Tracing Simulations,” \textit{IEEE Trans. Antennas Propag.}, Vol 67, No. 4, pp 2633-2644, Apr. 2019.
\bibitem{Bhat2018}
    A. Bhat, S. Aoki and R. Rajkumar, "Tools and Methodologies for Autonomous Driving Systems," \textit{Proc. IEEE}, Vol. 106, No. 9, pp. 1700-1716, Sep. 2018.
\bibitem{boban1}
    R. He et al., "Propagation Channels of 5G Millimeter-Wave Vehicle-to-Vehicle Communications: Recent Advances and Future Challenges," \textit{IEEE Veh. Technol. Mag.}, Vol. 15, No. 1, pp. 16-26, Mar 2020.
\bibitem{Xing2020}
    Y. Xing, C. Lv and D. Cao, "Personalized Vehicle Trajectory Prediction Based on Joint Time-Series Modeling for Connected Vehicles," \textit{IEEE Trans. Veh. Technol.}, Vol. 69, No. 2, pp. 1341-1352, Feb. 2020.
\bibitem{VDE2021}
    V. Degli-Esposti, “Ray tracing: techniques, applications and prospect,” in Proc. of 2020 International Symposium on Antennas and Propagation, Osaka, Japan, pp. 1-2, January 25-28, 2021.
\bibitem{he2019}
    D. He, B. Ai, K. Guan, L. Wang, Z. Zhong and T. Kürner, "The Design and Applications of High-Performance Ray-Tracing Simulation Platform for 5G and Beyond Wireless Communications: A Tutorial," \textit{IEEE Commun. Surv. Tutor.}, Vol. 21, No. 1, pp. 10-27, Firstquarter 2019.
\bibitem{hussain2019}
    S. Hussain and C. Brennan, “Efficient preprocessed ray tracing for 5G mobile transmitter scenarios in urban microcellular environments,” \textit{IEEE Trans. Antennas Propag.}, Vol. 67, No. 5, pp. 3323–3333, May 2019.
\bibitem{nuckelt2015}
    J. Nuckelt, M. Schack, and T. Kürner, “Geometry-based path interpolation for rapid ray-optical modeling of vehicular channels,” in Proc. of 9th Eur. Conference on Antennas and Propagation (EUCAP), 2015, pp. 1–5, Lisbon, Portugal, Apr. 12-17, 2015.
\bibitem{azpilicueta}    
    L. Azpilicueta, C. Vargas-Rosales and F. Falcone, "Intelligent Vehicle Communication: Deterministic Propagation Prediction in Transportation Systems," \textit{IEEE Veh. Technol. Mag.}, Vol. 11, No. 3, pp. 29-37, Sep. 2016.
\bibitem{bilibashi}
    D. Bilibashi, E. M. Vitucci and V. Degli-Esposti, "Dynamic Ray Tracing: Introduction and Concept," in Proc. of 2020 14th European Conference on Antennas and Propagation (EuCAP), 2020, pp. 1-5.
\bibitem{bilibashi2}
    D. Bilibashi, E. M. Vitucci and V. Degli-Esposti, "Dynamic Ray Tracing: A 3D Formulation," in Proc. of 2020 International Symposium on Antennas and Propagation (ISAP), 2021, pp. 279-280.
\bibitem{qua}
    F. Quatresooz, S. Demey and C. Oestges, ”Tracking of Interaction Points for Improved Dynamic Ray Tracing,” \textit{IEEE Trans. Veh. Technol.}, Vol. 70, No. 7, pp. 6291-6301, Jul. 2021.
\bibitem{Martin1968}
    G. H. Martin, Kinematics and Dynamics of Machines, McGraw-Hill, 1968.
\bibitem{taylor2005}
    J. R. Taylor, Classical mechanics, University Science Books, 2005.
\bibitem{fuschini2015}
    F. Fuschini, E. M. Vitucci, M. Barbiroli, G. Falciasecca and V. Degli-Esposti, "Ray tracing propagation modeling for future small-cell and indoor applications: A review of current techniques," \textit {Radio Science}, Vol. 50, No. 6, pp. 469-485, Jun. 2015.
\bibitem{vitucci2019}
    E. M. Vitucci, J. Chen, V. Degli-Esposti, J. S. Lu, H. L. Bertoni, X. Yin, "Analyzing Radio Scattering Caused by Various Building Elements Using Millimeter-Wave Scale Model Measurements and Ray Tracing," \textit{IEEE Trans. Antennas Propag.}, Vol. 67, No. 1, pp. 665-669, Jan. 2019.
\bibitem{UTD} 
    R.G. Kouyoumjian, P. H. Pathak, "A uniform geometrical theory of diffraction for an edge in a perfectly conducting surface", \textit{Proc. IEEE}, vol. 62, No. 11, pp. 1448-1461, Nov. 1974. 
\bibitem{Keller} 
    J. B. Keller, “Geometrical theory of diffraction,” \textit{J. Opt. Soc. Amer.}, vol. 52, pp. 116-130, 1962.
\bibitem{abbas}
    T. Abbas, J. Nuckelt, T. Kürner, T. Zemen, C. F. Mecklenbräuker and F. Tufvesson, "Simulation and Measurement-Based Vehicle-to-Vehicle Channel Characterization: Accuracy and Constraint Analysis," \textit{IEEE Trans. Antennas Propag.}, Vol. 63, No. 7, pp. 3208-3218, Jul. 2015.
\bibitem{paier2010}
    A. Paier, L. Bernadó, J. Karedal, O. Klemp and A. Kwoczek, "Overview of Vehicle-to-Vehicle Radio Channel Measurements for Collision Avoidance Applications," \textit{IEEE 71st Vehicular Technology Conference,} 2010, pp. 1-5.
\bibitem{Kuerner2018}
    R. Alieiev, T. Hehn, A. Kwoczek and T. Kürner, “Predictive Communication and its Application to Vehicular Environments: Doppler-Shift Compensation,” \textit{IEEE Trans. Veh. Technol.}, Vol. 67, No. 8, pp. 7380-7393, Aug. 2018.
\bibitem{DiTaranto2014}
    R. Di Taranto, S. Muppirisetty, R. Raulefs, D.T.M. Slock, T. Svensson, H. Wymeersch, “Location-Aware Communications for 5G Networks”, IEEE Signal Proc. Magazine, vol. 31, no. 6, pp. 102-112, November 2014
\bibitem{Witrisal2016}
    K. Witrisal, P. Meissner, E. Leitinger, Y. Shen, C. Gustafson, F. Tufvesson, K. Haneda, D. Dardari, A. Molisch, A. Conti, and M. Z. Win, “High-accuracy localization for assisted living: 5G systems will turn multipath channels from foe to friend,” \textit{IEEE Signal Process. Mag.}, vol. 33, no. 2, pp. 59–70, Mar. 2016.
\bibitem{Koivisto2017}
    M. Koivisto, A. Hakkarainen, M. Costa, P.Kela, K. Leppanen, M. Valkama, “High-Efficiency Device Positioning and Location Aware Communications in Dense 5G Networks”, \textit{IEEE Comm. Mag.}, vol. 55, no. 8, pp. 188-195, Aug. 2017.
\bibitem{Thomae2018}
    M. N. de Sousa, R. S. Thomä,  “Enhancement of Localization Systems in NLOS Urban Scenario with Multipath Ray Tracing Fingerprints and Machine Learning,” \textit{Sensors}, Vol. 18, No. 11, 4073, 2018.
\bibitem{ChenDoppler} 
    V. C. Chen, The Micro-Doppler Effect in Radar, 2nd Edition, Artech House, 2019.









    

    

    








    
\end{thebibliography}