

%\documentclass{sig-alternate-05-2015}
\documentclass[10 pt, conference]{IEEEtran}

\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}

\usepackage{pdfpages}
\usepackage{subfigure,graphicx}
\usepackage{amsmath,epsfig}
\usepackage{color}
\usepackage{algpseudocode}
\usepackage{epstopdf}
\newtheorem{observation}{Observation}

%\def\x{{\mathbf x}}
%\def\L{{\cal L}}

\newtheorem{myDef}{\textbf{Definition}}
\newtheorem{myTheo}{\textbf{Theorem}}
\newtheorem{myPro}{\textbf{Proposition}}
\newtheorem{myLem}{\textbf{Lemma}}

\newtheorem{cor}{\textbf{Corollary}}

\newcommand{\rev}[1]{{\color{black}#1}}
\newcommand{\com}[1]{\textbf{\color{red} (Comment: #1) }}

\newcommand{\pht}[1]{{\color{black}#1}}

\usepackage{cite}
\usepackage{amsmath}

\interdisplaylinepenalty=2500

\addtolength{\topmargin}{.1in}
\setlength{\columnsep}{.28in}
\vspace{-4mm}

%\usepackage[cmintegrals]{newtxmath}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}


\title{When Data Sponsoring Meets Edge Caching: \\ A Game-Theoretic Analysis}


\IEEEoverridecommandlockouts

\author{
\IEEEauthorblockN{Haitian Pang\IEEEauthorrefmark{1},
Lin Gao\IEEEauthorrefmark{2},
Qinghua Ding\IEEEauthorrefmark{1},
Lifeng Sun\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Tsinghua National Laboratory for Information Science and Technology, and
\\
Department of Computer Science and Technology, Tsinghua University, Beijing, China}
\IEEEauthorblockA{\IEEEauthorrefmark{2}
School of Electronic and Information Engineering, Harbin Institute of Technology, Shenzhen, China}
\IEEEauthorblockA{Email: \{pht14@mails., dqh14@mails., sunlf@\}tsinghua.edu.cn, gaol@hit.edu.cn}
\thanks{This work is supported by the National Natural Science Foundation of China (Grant No. 61771162, 61472204, and 61521002), Shenzhen Science and Technology Plan (Grant No. CXZZ20150323151850088), and Beijing Key Laboratory of Networked Multimedia (Grant No. Z161100005016051).}
\vspace{-8mm}
}



\maketitle

\begin{abstract}
\emph{Data sponsoring} is a widely-used incentive method in today's cellular networks, where video content providers (CPs) cover part or all of the cellular data cost for mobile users so as to attract more video users and increase data traffic.
In the forthcoming 5G cellular networks, \emph{edge caching} is emerging as a promising technique to deliver videos with lower cost and higher quality. The key idea is to cache video contents on edge networks (e.g., femtocells and WiFi access points) in advance and deliver the cached contents to local video users directly (without involving cellular data cost for users).
In this work, we aim to study how the edge caching will affect the CP's data sponsoring strategy as well as the users' behaviors and the data market.
Specifically, we consider a single CP who offers both the edge caching service and the data sponsoring service to a set of heterogeneous mobile video users (with different mobility and video request patterns).
We formulate the interactions of the CP and the users as a two-stage Stackelberg game, where the CP (leader) determines the budgets (efforts) for both services in Stage I, and the users (followers) decide whether and which service(s) they would like to subscribe to.
We analyze the sub-game perfect equilibrium (SPE) of the proposed game systematically.
Our analysis and experimental results show that by introducing the edge caching, the CP can increase his revenue by $105\%$.
\end{abstract}

%\begin{IEEEkeywords}
%Data Sponsoring, Edge Caching, Content Delivery Networks, Stackelberg Game.
%\end{IEEEkeywords}

\input{Section_introduction}

%\input{Section_measurement}

\input{Section_system_model}

\input{Section_equilibrium}

\input{Section_numerical_result}

%\input{Section_literature_review}

\section{Conclusion}

%This work study the joint optimization of data sponsor scheme, \emph{i.e.}, cellular data and edge caching sponsoring through a two-stage Stackelberg game. We characterize the equilibrium of user membership selection game in Stage II and CP budget game in Stage I. We also develop an algorithm to compute the equilibria in Stage I. The simulation results show that edge caching is a promising scheme to attract mobile users for the CP. Joint optimization can promote the CP's revenue by $71\%$ compared to the pure cellular sponsoring.


In this work, we studied how the edge caching will affect the CP's data sponsoring strategy as well as the users' behaviors and the data market.
Specifically, we considered a single CP who offers both the edge caching service and the data sponsoring service to heterogeneous mobile video users.
We formulated the interactions of the CP and the users as a two-stage Stackelberg game, with the CP as leader and the users as followers, and analyzed the sub-game perfect equilibrium (SPE) systematically.
Numerical results showed that by introducing the edge caching, the CP can increase his revenue up to $105\%$.


\input{Section_bibliography}

%\clearpage
%\input{Section_appendix}
\end{document}
