Since the fifth Painlev\'e equation is a second-order ordinary differential equation, solutions are locally defined by two initial values. Therefore, the space of initial values is two complex-dimensional. However, standard existence and uniqueness theorems only cover values of $y$ that are not arbitrarily close to $0$, $1$ or infinity (where the second derivative given by $\PV$ becomes ill-defined). In this section, we explain how to construct a regularized, compactified space of all possible initial values that overcomes these issues.

We start by formulating $\PV$ as an equivalent system of equations in Section \ref{sec:system} and describing its autonomous limiting form obtained as $x\to0$ in Section \ref{sec:auto}. The mathematical construction of the space of initial values is then given in Section \ref{sec:okamoto}. Where $y$ is arbitrarily close to the singular values $0$, $1$, $\infty$, the solutions have singular power series expansions, which become regularized Taylor expansions in corresponding domains of the initial value space. These regular expansions are provided in Section \ref{sec:poles}.

\subsection{A system equivalent to $\PV$}\label{sec:system}

With the change of the independent variable $t=\log x$, Equation (\ref{eq:PV}) becomes:
\begin{equation}\label{eq:PVlog}
\begin{split}
\frac{d^2y}{dt^2}=%&
\left(\frac{1}{2y}+\frac{1}{y-1}\right) \left(\frac{dy}{dt}\right)^2+(y-1)^2\left(\alpha y+\frac{\beta}{y}\right)
%\\&\qquad 
+e^t\gamma y +e^{2t}\frac{\delta y(y+1)}{y-1}.
\end{split}
\end{equation}
We rewrite Equation (\ref{eq:PVlog}) in the following way:
\begin{equation}\label{eq:PVlog-system}
\begin{split}
\frac{dy}{dt}=&
 2 y (y-1)^2z-(\theta_0+\eta)y^2+(2\theta_0+\eta-\theta_1 e^t)y-\theta_0,
\\
\frac{dz}{dt}=&-
(y-1)(3y-1)z^2+\big(2(\theta_0+\eta)y-2\theta_0-\eta+\theta_1 e^t\big)z
%\\&\qquad 
-\frac12\epsilon(\theta_0+\eta-\theta_{\infty}),
\end{split}
\end{equation}
where
$\theta_{\infty}^2=2\alpha$,
$\theta_0^2=-2\beta$,
$\theta_1^2=-2\delta$ $(\theta_1\neq0)$,
$\eta=-\frac{\gamma}{\theta_1}-1$, and
$\epsilon=\frac12(\theta_0+\theta_{\infty}+\eta)$.

\begin{remark}
Here, we assumed that $\delta\neq0$, which is a generic case of the fifth Painlev\'e equation.
When $\delta=0$, the $\PV$ is equivalent to the third Painlev\'e equation \cite{OO2006}.
\end{remark}

The system (\ref{eq:PVlog-system}) is Hamiltonian:
$$
\frac{dy}{dt}=\frac{\partial H}{\partial z},
\qquad
\frac{dz}{dt}=-\frac{\partial H}{\partial y},
$$
with Hamiltonian function:
\begin{equation}\label{eq:H}
H=y(y-1)^2z^2-(\theta_0+\eta)y^2z+(2\theta_0+\eta-\theta_1 e^t)yz-\theta_0z+\frac12\epsilon(\theta_0+\eta-\theta_{\infty})y.
\end{equation}


\subsection{The autonomous equation}
\label{sec:auto}

The autonomous equation corresponding to (\ref{eq:PVlog}) is:
\begin{equation}\label{eq:PVlog-auto}
\frac{d^2y}{dt^2}=\left(\frac{1}{2y}+\frac{1}{y-1}\right) \left(\frac{dy}{dt}\right)^2+(y-1)^2\left(\alpha y+\frac{\beta}{y}\right),
\end{equation}
which is equivalent to the autonomous version of (\ref{eq:PVlog-system}):
\begin{equation}\label{eq:PVlog-system-auto}
\begin{aligned}
&\frac{dy}{dt}=
(y-1)^2(2yz-\theta_0)+\eta y(y-1),
\\
&\frac{dz}{dt}=
(y-1)z(2\eta+2\theta_0+z-3yz)+\eta z-\frac12\epsilon(\theta_0+\eta-\theta_{\infty}).
\end{aligned}
\end{equation}
System (\ref{eq:PVlog-system-auto}) is also Hamiltonian:
$$
\frac{dy}{dt}=\frac{\partial E}{\partial z},
\qquad
\frac{dz}{dt}=-\frac{\partial E}{\partial y},
$$
with Hamiltonian:
\begin{equation}\label{eq:E}
E=y(y-1)^2z^2-(\theta_0+\eta)y^2z+(2\theta_0+\eta)yz-\theta_0z+\frac12\epsilon(\theta_0+\eta-\theta_{\infty})y.
\end{equation}

Using the first equation of (\ref{eq:PVlog-system-auto}) to express $z$, and using the fact that $E$ is constant along solutions, we get:
$$
\left(\frac{dy}{dt}\right)^2=(y-1)^2(4 C y + \theta_0^2 - 2 \theta_0 (\eta + \theta_0) y  + \theta_{\infty}^2  y^2 ),
\qquad
C=\const.
$$

It is worth observing that the constant function $y\equiv1$ is the only solution of this equation taking the value $1$.
From (\ref{eq:PVlog-system-auto}), the corresponding function $z$ is the solution of
$$
\frac{dz}{dt}=
\eta z-\frac12\epsilon(\theta_0+\eta-\theta_{\infty}).
$$
That is, we have
$$
z=c_1 e^{\eta t}+\frac{\epsilon(\theta_0+\eta-\theta_{\infty})}{2\eta},
$$
where $c_1$ is a constant.

The flow (\ref{eq:PVlog-system-auto}) has four fixed points: 
\begin{equation*}
(y, z)=
  \begin{cases}
   \left(1, \dfrac{\epsilon(\theta_0+\eta-\theta_{\infty})}{2\eta}\right)\\
   \\
   \left(Y_i, \dfrac{\theta_0}{2Y_i}+\dfrac{\eta}{2(1-Y_i)}\right), i\in\{1,2,3\},
  \end{cases}
\end{equation*}
where $Y_1$, $Y_2$, $Y_3$ are the roots of the following cubic polynomial in $Y$:
\[
  \left(-\theta_{\infty}^2 -   6 \eta^2 + 8 \eta \theta_0 + 2\theta_0^2\right) Y^3
 %\\&\qquad 
 +\left( 2 \eta^2 - 12 \eta \theta_0 - 2\theta_0^2+\theta_{\infty}^2 \right) Y^2 
+\theta_0 (4 \eta - \theta_0) Y
+\theta_0^2.
\]

%\subsection{Fibration associated to a differential equation}\label{sec:fibration}
%\input{2-space/fibration}


\subsection{Resolution of singularities}\label{sec:okamoto}
\input{2-space/okamoto}

\subsection{Movable singularities in Okamoto's space}\label{sec:poles}
\input{2-space/poles}


