
\documentclass[final]{cvpr}
\usepackage{float}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage[font=small,skip=5pt]{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}

\usepackage{pifont}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[table,dvipsnames,svgnames,x11names]{xcolor}
\usepackage{booktabs}
\definecolor{dgreen}{rgb}{0.04,0.7,0.13}
\newcommand{\cmark}{{\color{red}\ding{51}}}
\newcommand{\xmark}{{\color{dgreen}\ding{55}}}
\newcommand{\ncmark}{{\ding{51}}}
\newcommand{\nxmark}{{\ding{55}}}
\newcolumntype{x}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\usepackage{overpic} 

\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}


\def\cvprPaperID{3521} %
\def\confYear{CVPR 2021}


\begin{document}
\title{Reconstructing 3D Human Pose by Watching Humans in the Mirror}

\author{Qi Fang\thanks{Equal Contribution. $^\dag$Corresponding author.}
\quad Qing Shuai$^{*}$
\quad Junting Dong
\quad Hujun Bao
\quad Xiaowei Zhou$^{\dag}$
\\[1.5mm]
State Key Lab of CAD\&CG, Zhejiang University 
}


\maketitle
\pagestyle{empty}
\thispagestyle{empty}

\begin{abstract}
In this paper, we introduce the new task of reconstructing 3D human pose from a single image in which we can see the person and the person's image through a mirror. Compared to general scenarios of 3D pose estimation from a single view, the mirror reflection provides an additional view for resolving the depth ambiguity.
We develop an optimization-based approach that exploits mirror symmetry constraints for accurate 3D pose reconstruction. We also provide a method to estimate the surface normal of the mirror from vanishing points in the single image. 
To validate the proposed approach, we collect a large-scale dataset named Mirrored-Human, which covers a large variety of human subjects, poses and backgrounds. The experiments demonstrate that, when trained on Mirrored-Human with our reconstructed 3D poses as pseudo ground-truth, the accuracy and generalizability of existing single-view 3D pose estimators can be largely improved. The code and dataset are available at \url{https://zju3dv.github.io/Mirrored-Human/}.

\end{abstract}

\section{Introduction}
\input{src/01_introduction}

\section{Related work}
\input{src/02_relatedwork}

\section{Methods}
\input{src/03_method}

\input{src/04-1_evaulation}
\input{src/05-1_learning}

\input{src/06_conclusion}


\newpage
{\small
\bibliographystyle{ieee_fullname}
\bibliography{cvpr}
}

\end{document}
