Thanks to 
the students of the BSc course titled “High Level Programming Languages” at the University of Debrecen, 
to the members of the NEMESPOR mailing lists \url{https://groups.google.com/forum/#!members/nemespor}, 
to the members of the UDPROG Facebook community \url{https://www.facebook.com/groups/udprog}
and to the members of the DEAC-Hackers esport department \url{http://deac.hu/szakosztalyok/esport}
for their interest and for performing the BrainB Test Series 6.
Special thanks 
to Ren\'at\'o Besenczi for pretesting the Windows release of the BrainB program,
to Roland Paszerbovics, Gerg\H o Hajzer and P\'eter Rozsos for their interest and support
and to N\'andor Benj\'amin B\'atfai for performing the BrainB Test Series 6 on several occasions.

Finally, our thanks go to Dr. P\'eter Jeszenszky for reading the manuscript and suggesting improvements.

Author contributions were the following: 
N. B.\footnote{\label{efop363}This work was supported by the construction EFOP-3.6.3-VEKOP-16-2017-00002. The project was co-financed by the Hungarian Government and the European Social Fund.} 
conceived the idea, developed the benchmark program, collected the data from the UDPROG community and analyzed the measurements. 
D. P.\footnote{The work/publication is supported by the GINOP-2.3.2-15-2016-00062 project.} 
wrote the section \enquote{Psychological Background}. 
G. B.\textsuperscript{\ref{efop363}} wrote the section \enquote{Choosing colors}. 
R. B.\textsuperscript{\ref{efop363}} wrote the section \enquote{ Informatics Background} and collected the data from the DEAC-Hackers.
D. V.\textsuperscript{\ref{efop363}} wrote the  section \enquote{Losing the Character}.
All authors edited and reviewed the final version of the manuscript.

%League of Legends is a trademark of Riot Games, Inc.
%Clash of Clans and Clash Royale are trademars of Supercell. 
%Heroes of the Storm and World of Warcraft are trademarks of Blizzard Entertainment, Inc.
%DOTA2 is a trademark of Valve Corporation.
