\documentclass[twocolumn]{autart}  % Comment this line out
                                                          % if you need a4paper
\usepackage{color}
\usepackage{graphicx}

\usepackage{hyperref}
\usepackage{amsmath,amsfonts, amssymb}
\usepackage{multirow}
\usepackage{natbib}
%\bibliographysyle{agsm}
\begin{document}

\begin{frontmatter}
\title{A Moving-Horizon Hybrid Stochastic Game for Secure Control of Cyber-Physical Systems\thanksref{footnoteinfo}} % Title, preferably not more 
                                                % than 10 words.

\thanks[footnoteinfo]{This material is based on research sponsored by DARPA under agreement number FA8750-12-2-0247.  The U.S. Government is authorized to reproduce and distribute reprints for Governmental purposes notwithstanding any copyright notation thereon.  The views and conclusions contained herein are those of the authors and should not be interpreted as necessarily representing the official policies or endorsements, either expressed or implied, of DARPA or the U.S. Government. This work was also supported in part by NSF CNS-1505701, CNS-1505799 grants, and the Intel-NSF Partnership for Cyber-Physical Systems Security and Privacy. This paper was not presented at any IFAC meeting. Part of the results in this work appeared at the 52nd Conference of Decision and Control, Florence, Italy, December 2013~\cite{cdc_replay} and the 53rd Conference of Decision and Control, Los Angeles, CA, USA, December 2014~\cite{game_cdc14}. Corresponding author F.~Miao. Tel. 2154216608.}

\author[Uconn]{Fei Miao}\ead{fei.miao@uconn.edu},  % Add the 
\author[NYU]{Quanyan Zhu}\ead{quanyan.zhu@nyu.edu},               % e-mail address 
\author[Duke]{Miroslav Pajic}\ead{miroslav.pajic@duke.edu},  % (ead) as shown
\author[Upenn]{George J. Pappas}\ead{pappasg@seas.upenn.edu}

\address[Uconn]{ University of Connecticut, Storrs, CT, USA}
\address[Upenn]{ University of Pennsylvania, Philadelphia, PA, USA}  % Please supply                                              
\address[NYU]{ New York University, Brooklyn, NY, USA}             % full addresses
\address[Duke]{Duke University, Durham, NC, USA}
%\address[Pappas]{ University of Pennsylvania, Philadelphia, PA, USA}

\begin{keyword}
Stochastic Game, Secure Control, Saddle-Point Equilibrium
\end{keyword}
%\maketitle

\begin{abstract}
\label{abstract}
 In this paper, we establish a zero-sum, hybrid state stochastic game model for designing defense policies for cyber-physical systems against different types of attacks. With the increasingly integrated properties of cyber-physical systems (CPS) today, security is a challenge for critical infrastructures. Though resilient control and detecting techniques for a  specific model of attack have been proposed, to analyze and design detection and defense mechanisms against multiple types of attacks for CPSs requires new system frameworks. Besides security, other requirements such as optimal control cost also need to be considered. The hybrid game model we propose contains physical states that are described by the system dynamics, and a cyber state that represents the detection mode of the system composed by a set of subsystems. A strategy means selecting a subsystem by combining one controller, one estimator and one detector among a finite set of candidate components at each state. Based on the game model, we propose a suboptimal value iteration algorithm for a finite horizon game, and prove that the algorithm results an upper bound for the value of the finite horizon game. A moving-horizon approach is also developed in order to provide a scalable and real-time computation of the switching strategies. Both algorithms aims at obtaining a saddle-point equilibrium policy for balancing the system's security overhead and control cost. 
%This approach leads to a real-time algorithm that yields a sequence of Nash equilibrium strategies which can be shown to converge. 
The paper illustrates these concepts using numerical examples, and we compare the results with previously system designs that only equipped with one type of controller. 
\end{abstract}

\end{frontmatter}

\input{introduction}

\input{model_attack}

\input{game_form}

\input{algorithm_finite}

\input{algorithm}

\input{simulation}

\input{conclusion}

\bibliographystyle{agsm}        
{  \small 
\bibliography{gamejs}
}

%\input{bio_coding}
\end{document}