%  ========================================================================
%  Copyright (c) 1985 The University of Washington
%
%  Licensed under the Apache License, Version 2.0 (the "License");
%  you may not use this file except in compliance with the License.
%  You may obtain a copy of the License at
%
%      http://www.apache.org/licenses/LICENSE-2.0
%
%  Unless required by applicable law or agreed to in writing, software
%  distributed under the License is distributed on an "AS IS" BASIS,
%  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%  See the License for the specific language governing permissions and
%  limitations under the License.
%  ========================================================================
%

% Documentation for University of Washington thesis LaTeX document class
% by Jim Fox
% fox@washington.edu
%
%    Revised for version 2015/03/03 of uwthesis.cls
%    Revised, 2016/11/22, for cleanup of sample copyright and title pages
%
%    This document is contained in a single file ONLY because
%    I wanted to be able to distribute it easily.  A real thesis ought
%    to be contained on many files (e.g., one for each chapter, at least).
%
%    To help you identify the files and sections in this large file
%    I use the string '==========' to identify new files.
%
%    To help you ignore the unusual things I do with this sample document
%    I try to use the notation
%       
%    % --- sample stuff only -----
%    special stuff for my document, but you don't need it in your thesis
%    % --- end-of-sample-stuff ---


%    Printed in twoside style now that that's allowed
%
 
\documentclass [11pt, proquest] {uwthesis}[2017/05/05]
 
%
% The following line would print the thesis in a postscript font 

% \usepackage{natbib}
% \def\bibpreamble{\protect\addcontentsline{toc}{chapter}{Bibliography}}

\setcounter{tocdepth}{1}  % Print the chapter and sections to the toc
 

% ==========   Local defs and mods
%

% --- sample stuff only -----
% These format the sample code in this document

\usepackage{alltt}  % 
\newenvironment{demo}
  {\begin{alltt}\leftskip3em
     \def\\{\ttfamily\char`\\}%
     \def\{{\ttfamily\char`\{}%
     \def\}{\ttfamily\char`\}}}
  {\end{alltt}}
 
% metafont font.  If logo not available, use the second form
%
% \font\mffont=logosl10 scaled\magstep1
\let\mffont=\sf
% --- end-of-sample-stuff ---


\usepackage{hyperref,amssymb,amsmath,graphicx,xcolor}
\usepackage{bm}
\usepackage{mathtools}

\newcommand{\gsim}{\raisebox{-0.7ex}{$\stackrel{\textstyle >}{\sim}$ }}
\newcommand{\lsim}{\raisebox{-0.7ex}{$\stackrel{\textstyle <}{\sim}$ }}

\def\si{^1 \hskip -0.03in S _0}
\def\siii{^3 \hskip -0.025in S _1}
\def\diii{^3 \hskip -0.03in D _1}

\def\Dslash{D\hskip-0.65em /}
\def\pislash{{\pi\hskip-0.55em /}}

\newcommand{\ket}[1]{\left| #1 \right>} % for Dirac bras
\newcommand{\bra}[1]{\left< #1 \right|} % for Dirac kets
\newcommand{\braket}[2]{\left< #1 \vphantom{#2} \right|
 \left. #2 \vphantom{#1} \right>} % for Dirac brackets
\newcommand{\mbraket}[3]{\left< #1 \vphantom{#2#3} \right|
 #2 \left| #3 \vphantom{#1#2} \right>} % for Dirac matrix elements
\newcommand{\grad}[1]{\gv{\nabla} #1} % for gradient
\let\divsymb=\div % rename builtin command \div to \divsymb
\renewcommand{\div}[1]{\gv{\nabla} \cdot #1} % for divergence
\newcommand{\curl}[1]{\gv{\nabla} \times #1} % for curl
\newcommand{\tr}{\text{Tr}} % trac:
\let\bar=\smallbar % rename builtin \bar{} to \smallbar{}
\newcommand{\bar}[1]{\overline{#1}} % default to large bar
\newcommand{\fs}[1]{\slashed{#1}} % shorter slashed{}
\let\tilde=\widetilde

\usepackage{amssymb,latexsym}
\usepackage{amsmath,amsbsy,bbm}
%\usepackage{epsfig,bm} 
%\usepackage{graphicx,comment}
%\usepackage{bm,comment}
%\unitlength=1mm
%\usepackage{epstopdf} \usepackage{color}
\usepackage{subfigure}
\usepackage{slashed,array,mathtools,amsfonts,multirow,hyperref}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{~}

\newcommand{\hook}{\mathbin{\rule[-.2ex]{.7em}{.03em}\rule[-.2ex]{.03em}{1.4ex}}}
\let\vaccent=\v % rename builtin command \v{} to \vaccent{}
\renewcommand{\v}[1]{\ensuremath{\mathbf{#1}}} % for vectors
\newcommand{\gv}[1]{\ensuremath{\mbox{\boldmath$ #1 $}}} 

\newcommand{\uv}[1]{\ensuremath{\mathbf{\hat{#1}}}} % for unit vector
\newcommand{\abs}[1]{\left| #1 \right|} % for absolute value
\newcommand{\avg}[1]{\left< #1 \right>} % for average
\let\underdot=\d % rename builtin command \d{} to \underdot{}
\renewcommand{\d}[2]{\frac{d #1}{d #2}} % for derivatives
\newcommand{\dd}[2]{\frac{d^2 #1}{d #2^2}} % for double derivatives
\newcommand{\p}{\partial}
\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}} 

\newcommand{\pdd}[2]{\frac{\partial^2 #1}{\partial #2^2}} 

\newcommand{\pdc}[3]{\left( \frac{\partial #1}{\partial #2}
 \right)_{#3}} % for thermodynamic partial derivatives
\newcommand{\fd}[2]{\frac{\delta #1}{\delta #2}} %functional derivative
\newcommand{\ifd}[1]{\frac{\delta}{i\delta #1}} %for QFT correlations
\newcommand{\ifdad}[1]{\frac{i\delta}{\delta #1}} %for adjoint QFT correlations
\newcommand{\ifdp}[1]{\frac{(2\pi)^4\delta}{i\delta #1}} %for QFT correlations
\newcommand{\ifdadp}[1]{\frac{i(2\pi)^4\delta}{\delta #1}} %for adjoint QFT correlations




\begin{document}
 
% ==========   Preliminary pages
%
% ( revised 2012 for electronic submission )
%

\prelimpages
 
%
% ----- copyright and title pages
%
\Title{Statistical Angles on the Lattice QCD Signal-to-Noise Problem}
\Author{Michael L. Wagman}
\Year{2017}
\Program{Physics}

\Chair{Martin J. Savage}{Prof.}{Physics}
\Signature{Silas R. Beane}
\Signature{David B. Kaplan}

\copyrightpage

\titlepage  

 
%
% ----- signature and quoteslip are gone
%

%
% ----- abstract
%


\setcounter{page}{-1}
\abstract{%
  The theory of quantum chromodynamics (QCD) encodes the strong interactions that bind quarks and gluons into nucleons and that bind nucleons into nuclei.
  Predictive control of QCD would allow nuclear structure and reactions as well as properties of supernovae and neutron stars to be theoretically studied from first principles.
  Lattice QCD (LQCD) can represent generic QCD predictions in terms of well-defined path integrals,
  but the sign and signal-to-noise problems have obstructed LQCD calculations of large nuclei and nuclear matter in practice.
  This thesis presents a statistical study of LQCD correlation functions, with a 
  particular focus on characterizing the structure of the noise associated with quantum fluctuations.
  The signal-to-noise problem in baryon correlation functions is demonstrated to arise from a sign problem associated with Monte Carlo sampling of complex correlation functions.
  Properties of circular statistics are used to understand the emergence of a large time noise region where standard energy measurements are unreliable.
  Power-law tails in the distribution of baryon correlation functions, associated with stable distributions and L{\'e}vy flights,
  are found to play a central role in their time evolution.

  Building on these observations, a
  new statistical analysis technique called phase reweighting is introduced
  that allow energy levels to be extracted from large-time correlation functions with time-independent signal-to-noise ratios.
  Phase reweighting effectively includes dynamical refinement of source magnitudes
  but introduces a bias
  associated with the phase.
  This bias can be removed
  by performing 
  an extrapolation,
  but at the expense of
  re-introducing a signal-to-noise problem.
  Lattice QCD calculations 
  of the $\rho^+$ and nucleon masses and of the $\Xi\Xi(\si)$ binding energy
  show consistency between standard results obtained using smaller-time correlation functions and
  phase-reweighted results using large-time correlation functions inaccessible to standard statistical analysis methods.
  A detailed study of the statistics and phase reweighting of isovector meson correlation functions demonstrates that phase reweighting applies to real but non-positive correlation functions and can be used to predict ground-state energies of correlation functions that are too noisy to be analyzed by other methods. 
  The relative precision of phase reweighting compared to standard methods is expected to be increased on 
  lattices with larger time directions than those considered in this thesis, 
  and these preliminary studies suggest phase reweighting of noisy nuclear correlation functions 
  should be investigated on larger lattices. 
  The results of this thesis suggest 
  that phase reweighting may be applicable more broadly to real but non-positive correlation functions in quantum Monte Carlo simulations of particle, nuclear, and condensed matter physics systems as well as to complex correlation functions describing multi-baryon systems in LQCD.
}

 
%
% ----- contents & etc.
%
\tableofcontents
%\listoftables  % I have no tables
 
%
% ----- glossary 
%
%\chapter*{Glossary}      % starred form omits the `chapter x'
%\addcontentsline{toc}{chapter}{Glossary}
%\thispagestyle{plain}
%%
%\begin{glossary}
%\item[argument] replacement text which customizes a \LaTeX\ macro for
%each particular usage.
% 
%\end{glossary}
 
%
% ----- acknowledgments

\acknowledgments{% \vskip2pc 
 {\narrower\noindent
   An old proverb says that it takes a village to raise a child.
   In my experience, raising a graduate student all the way through twenty-first grade requires not just one but several villages.
   
   First and foremost, I am grateful to my advisor Prof. Martin Savage
   for teaching by example how to
   always stay curious about the physical world,
   turn fuzzy questions into crisp ideas,
   and push through whatever unexpected obstacles arise to
   finish a worthwhile project in however long it takes.
   Martin's focus, commitment, and sense of justice have been inspirational to me,
   and his training has given me a much deeper understanding of
   both how to calculate anything
   and how to assess what is actually worth calculating in order to learn more about nature.

   My earliest teachers were my parents Kathy and Ed and my sister Nicole.
   Their encouragement and
   willingness to keep answering ``why?''
   built the foundation of my education,
   and the worlds of spaceships and superheros that I first explored with Nicole
   taught me to think of science as exciting and anything as possible.

   A number of other teachers have played essential roles in my education.
   I am forever grateful to my middle school teacher Mrs. Graham,
   who opened my eyes to the wonders of mathematics
   and taught me to think critically and independently about every subject from math to literature.
   I am likewise grateful to the high school teachers who nurtured my passion for learning,
   especially Ms. Hawthorn, Mr. Young, Mr. Davis, Mr. Goldsborough,
   and my AP physics teacher Mr. Rowe for confusing and de-confusing me about what an electric field is
   and sharing an infectious enthusiasm for physics.
   I would also like to wholeheartedly thank my classmates,
   especially my friends from Mrs. Graham's class, my collaborators in TSA, and my band mates,
   for making learning a fun collaborative project
   and pondering life's big philosophical questions with me as if we could solve them all.

   My time at Brown University was full of lessons from great teachers.
   I am particularly grateful to Prof. James Valles for
   his encouragement and mentoring
   and thank him, Ilyong Jung, and Shawna Hollen for introducing me to the world of research.
   I am also grateful to Prof. Jan Hesthaven and Scott Field for
   nurturing my interests in theoretical and computational physics research.
   I learned many lessons about life and about physics
   from my friends and roommates at Brown,
   and I cannot thank them enough for their love and support as well as countless stimulating discussions. 
   In particular I thank Matt Dodelson for convincing me to take any math course that looked interesting
   regardless of the prerequisites
   and thank him, Adam Coogan, and Tom Iadecola for helping me survive the ensuing all-nighters.

   During graduate school, I benefited greatly from the teachings of
   Profs. Silas Beane, David Kaplan, Andreas Karch, Gerald Miller, Ann Nelson, Sanjay Reddy, Martin Savage, Steve Sharpe, and Larry Yaffe.
   Much of my learning was done alongside my physics-life-buddy Dorota Grabowska,
   with whom I look forward to many more dinner table conversations about the foundations of quantum field theory,
   and many dear friends from my graduate-school cohort and fellow residents of Physics House.
   I am deeply grateful to the other members of the NPLQCD collaboration:
   Silas Beane, Emmanuel Chang, Zohreh Davoudi, Will Detmold, Kostas Orginos, Assumpta Parre{\~n}o, Martin Savage, Phiala Shanahan, Brian Tiburzi, and Frank Winter
   for welcoming me into an inspirational family of collaborators.
   I thank Michael Buchoff for the countless hours we spent following half of ``shut up and calculate''
   and for guiding me through the early stages of entering the physics community.
   I also thank Ra{\'u}l Brice{\~n}o, Aleksey Cherman, Max Hansen, Natalie Klco, and Alessandro Roggero
   for their guidance and collaboration and for the positive energy that they bring to the world.
   I am also grateful for my opportunities to meet friends and collaborators outside UW,
   in particular Sri Sen and my TASI cohort.
   The research presented in this thesis has also benefited from conversations with
   Tanmony Bhattacharya, Joe Carlson, Tom DeGrand, Leonardo Giusti, Rajan Gupta, Dean Lee, Alessandro Lovato, Steve Peiper, Daniel Trewartha, and Bob Wiringa,
   and would not have been possible without inspiration from David Kaplan to dive into learning about the signal-to-noise problem.

   Last but far from least, I thank my partner Kelly Buckley for her support during the highs and the lows of research,
   for helping me find big picture explanations,
   and for joining me on our next adventure.
 \par}
}

%
% ----- dedication

\dedication{\begin{center}To teachers who can explain quantum field theory and to students who find it beautiful. \end{center}}


% end of the preliminary pages
 
\listoffigures
 
 
%
% ==========      Text pages
%

\textpages
 
% ========== Chapter 1 (Introduction)

\include{MW_intro}
\include{MW_chap1a}
\include{MW_chap1b}
\include{MW_chap1c}
 
% ========== Chapter 2
 
\include{MW_chap2}
 
% ========== Chapter 3

\include{MW_chap3}

% ========== Chapter 4

\include{MW_chap4}

% ========== Conclusion

\include{MW_conclusion}

% ==========   Bibliography
%
\nocite{*}   % include everything in the uwthesis.bib file
\bibliographystyle{plain}
\bibliography{MW_bib}
%
% ==========   Appendices
%
\appendix
\raggedbottom\sloppy
 
% ========== Appendix A
 

%\vita{Michael Wagman grew up outside Harrisburg, Pennsylvania.
%  
%  
%  Jim Fox is a Software Engineer with IT Infrastructure Division at the University of Washington.
%His duties do not include maintaining this package.  That is rather
%an avocation which he enjoys as time and circumstance allow.
%
%He welcomes your comments to {\tt fox@uw.edu}.
%}



\end{document}
