\documentclass[a4paper, amsfonts, amssymb, amsmath, reprint, showkeys, nofootinbib, twoside]{revtex4-1}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[colorinlistoftodos, color=green!40, prependcaption]{todonotes}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}

\input{preamble}
\usepackage[pdftex, pdftitle={Article}, pdfauthor={Author}]{hyperref} % For hyperlinks in the PDF
%\setlength{\marginparwidth}{2.5cm}
\bibliographystyle{apsrev4-1}
\begin{document}
\title{Ancilla-Assisted Process Tomography with Bipartite Mixed Separable States}

\author{Zhuoran Bao, Daniel F. V. James}
    \email[Correspondence email address: ]{zhuoran.bao@mail.utoronto.ca\\
    dfvj@physics.utoronto.ca}% Your name
    \affiliation{Dept. of Physics, University of Toronto, Toronto, M5S 1A7, Ontario, Canada}

\date{to be submitted to PRA} 

\begin{abstract}
It has been shown that the entanglement between the system state and the ancillary state is not a strict requirement for performing ancilla-assisted process tomography(AAPT). Instead, it only requires that the system-ancilla state to be faithful, which is equivalent to the invertibility of a certain matrix representing the state. However, it is difficult to distinguish between a faithful state that brings small error amplification and one that produces larger error amplification. Restricted to two-qubit system-ancilla states, we present a theoretical analysis to connect the invertibility problem to the concept of sinisterness, which classifies the correlation of two qubits. Using sinisterness, we provide a way of constructing all two qubits faithful mixed separable states with the smallest error amplification. We show that the maximally entangled states provided the smallest error amplification, while the separable Werner states produced an uneven error amplification larger than the maximally entangled state. Nevertheless, the error amplification due to inverting the separable Werner states or isotropic states is the best any mixed separable state can do.
\end{abstract}

\keywords{ancilla-assisted process tomography, bipartite mixed-separable states, sinisterness}


\maketitle

\input{sections/section01.tex}
\input{sections/section02.tex}
\input{sections/section03.tex}
\input{sections/section04.tex}
\input{sections/conclusion.tex}
%\input{sections/acknowledgements.tex}

\begin{thebibliography}{}
\bibitem{Chuang}
I. L. Chuang, M. A. Nielsen, J. Mod. Opt. 44, 2455–2467 (1997).

\bibitem{Poyatos}
J. F. Poyatos, J. I. Cirac, and P. Zoller, Phys. Rev. Lett. 78, 390 (1997).

\bibitem{Pryde}
O'Brien, J. L. and Pryde, G. J. and Gilchrist, A. and James, D. F. V. and Langford, N. K. and Ralph, T. C. and White, A. G., “Quantum Process Tomography of a Controlled-NOT Gate,” Phys. Rev. Lett. 93(10), 080502 (2004).

\bibitem{Mohseni2006}
M. Mohseni and D. A. Lidar, Phys. Rev. Lett. 97, 170501
(2006)

\bibitem{Mohseni2007}
M. Mohseni and D. A. Lidar, Phys. Rev. A 75, 062331 (2007)

\bibitem{Mohseni2008}
M. Mohseni, A. T. Rezakhani, and D. A. Lidar, Phys. Rev. A, 77, 032322 (2008).

\bibitem{Altepeter}
J. B. Altepeter, D. Branning, E. Jeffrey, T. C. Wei, P. G. Kwiat, R. T. Thew, J. L. O’Brien, M. A. Nielsen, and A. G. White, Phys. Rev. Lett. 90, 193601 (2003).

\bibitem{Ariano}
G. M. D’Ariano and P. Lo Presti, Phys. Rev. Let. 86, 4195 (2001)

\bibitem{James}
D. F. V. James, Journal of the Optical Society of America A, Vol. 39, Issue 12, pp. C86-C97 (2022).

\bibitem{DiVincenzo}
D.P. DiVincenzo, B.M. Terhal, and A.V. Thapliyal, “Optimal decomposition of barely separable states,” J. Mod. Opt. 47, 377-385 (2000).

\bibitem{Wootters}
W. K. Wootters, “Entanglement of Formation of an Arbitrary State of Two Qubits,” Phys. Rev. Lett. 80(10),
2245-2248 (1998).

\bibitem{fang}
Y. Fang, K. A. Loparo and Xiangbo Feng, "Inequalities for the trace of matrix product," in IEEE Transactions on Automatic Control, vol. 39, no. 12, pp. 2489-2490, Dec. 1994, doi: 10.1109/9.362841.

\bibitem{sedrakyan}
Sedrakyan, H., Sedrakyan, N. (2018). The HM-GM-AM-QM Inequalities. In: Algebraic Inequalities. Problem Books in Mathematics. Springer, Cham. https://doi.org/10.1007/978-3-319-77836-5\_3
\end{thebibliography}

\end{document}
