\documentclass[11pt]{article}
%------------------------------------------------------------------
%\pdfoutput=1
\usepackage{amsthm,amsmath,amssymb}
\usepackage{amsfonts}%
\usepackage{graphicx}%
\pagestyle{myheadings} %
\usepackage{url}%
\usepackage{color}
\usepackage{a4wide}
\usepackage{algorithmic,algorithm,float}
%------------------------------------------------------------------
\setlength{\textwidth}{17cm}
\setlength{\textheight}{23.5cm}
\setlength{\oddsidemargin}{0cm}
\nonstopmode
\setlength{\evensidemargin}{0cm}
\setlength{\footskip}{40pt}
%\setlength{\oddsidemargin}{0.2in}%
%\setlength{\textwidth}{5.9in}%
%\setlength{\textheight}{9.9in}%702.566pt
%\setlength{\hoffset}{0pt}%
%\setlength{\voffset}{-10pt}%
\setlength{\topmargin}{-1.3cm}%35pt
\setlength{\headheight}{+0.0cm}%15pt
\setlength{\headsep}{+0.75cm}%21.13pt
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}
\newtheorem{problem}{Problem}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}
%------------------------------------------------------------------
\newcommand{\codim}{{\rm codim}}
\newcommand{\Range}{{\rm Range}}
\newcommand{ \Null}{{\rm Null}}
\newcommand{\spann}{{\rm span}}
\newcommand{\eop}{\hfill  $\Box$}
%------------------------------------------------------------------
\renewcommand{\Re}{\mathop{\mathrm{Re}}}
\renewcommand{\Im}{\mathop{\mathrm{Im}}}
\newcommand{\Pv}{\mathop{\mathrm{PV}}}
\newcommand{\ind}{\mathrm{ind}}
\renewcommand{\i}{\mathrm{i}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\bB}{{\bf B}}
\newcommand{\bC}{{\bf C}}
\newcommand{\CC}{{\mathbb C}}
\newcommand{\RR}{{\mathbb R}}
\newcommand{\bI}{{\bf I}}
\newcommand{\bK}{{\bf K}}
\newcommand{\bM}{{\bf M}}
\newcommand{\bN}{{\bf N}}
\newcommand{\bP}{{\bf P}}
\newcommand{\bQ}{{\bf Q}}
\newcommand{\bL}{{\bf L}}
\newcommand{\bs}{{\bf s}}
\newcommand{\bJ}{{\bf J}}
\newcommand{\bR}{{\bf R}}
\newcommand{\bT}{{\bf T}}
\newcommand{\bn}{{\bf n}}
\newcommand{\bh}{{\bf h}}
\newcommand{\bx}{{\bf x}}
\newcommand{\by}{{\bf y}}
%------------------------------------------------------------------


%------------------------------------------------------------------
\begin{document}







\title{Towards computing the harmonic-measure distribution function for the middle-thirds Cantor set}

\author{Christopher C. Green \& Mohamed M. S. Nasser}

\date{}
\maketitle

\vskip-0.8cm %
\centerline{Wichita State University, Department of Mathematics, Statistics \& Physics,} %
\centerline{Wichita KS 67260, USA}%
\centerline{\tt christopher.green@wichita.edu, mms.nasser@wichita.edu}
%

\begin{abstract}
The harmonic-measure distribution function, or $h$-function for short, associated with a particular planar domain, describes the hitting probability of a Brownian walker released from some point with the boundary of the domain. 
In this paper, we present a fast and accurate boundary integral method for the numerical computation of the $h$-functions for symmetric multiply connected slit domains with high connectivity.
In view of the fact that the middle-thirds Cantor set $\mathcal{C}$ is a special limiting case of these slit domains, the proposed method is used to approximate the $h$-function for the set $\mathcal{C}$. 
\end{abstract}


\begin{center}
	\begin{quotation}
		{\noindent {{\bf Keywords}.\;\; 
				Harmonic-measure distribution function; multiply connected slit domain; middle-thirds Cantor set; conformal mapping; boundary integral equation; Neumann kernel.}%
		}%
	\end{quotation}
\end{center}

\begin{center}
	\begin{quotation}
		{\noindent {{\bf MSC 2020}.\;\; 
				65E05; 30C85; 30E25; 45B05.}%
		}%
	\end{quotation}
\end{center}


% \linenumbers

\input{sec1.tex}

\input{sec2.tex}

\input{sec3.tex}

\input{sec4.tex}

\input{sec5.tex}

\input{sec6.tex}



\begin{thebibliography}{10}
	
	\bibitem{asww}
	J.~Aar{\~a}o, M.A. Snipes, B.L. Walden, and L.A. Ward.
	\newblock {\em Four ways to calculate harmonic measure in a doubly connected
		domain}, in preparation.
	
	\bibitem{AST13}
	N.~Aoyama, T.~Sakajo, and H.~Tanaka.
	\newblock A computational theory for spiral point vortices in multiply
	connected domains with slit boundaries.
	\newblock {\em Japan J. Indust. Appl. Math.}, 30:485--509, 2013.
	
	\bibitem{Atk97}
	K.E. Atkinson.
	\newblock {\em The Numerical Solution of Integral Equations of the Second
		Kind}.
	\newblock Cambridge University Press, Cambridge, 1997.
	
	\bibitem{bawa14}
	A.~Barton and L.A. Ward.
	\newblock A new class of harmonic measure distribution functions.
	\newblock {\em J. Geom. Anal.}, 24(4):2035--2071, 2014.
	
	\bibitem{beso03}
	D.~Betsakos and A.~Solynin.
	\newblock On the distribution of harmonic measure on simply connected planar
	domains.
	\newblock {\em J. Aust. Math. Soc.}, 75:145--151, 2003.
	
	\bibitem{bh89}
	D.A. Brannan and W.K. Hayman.
	\newblock Research problems in complex analysis.
	\newblock {\em Bull. London Math. Soc.}, 21:1--35, 1989.
	
	\bibitem{CrowdyBook}
	Darren Crowdy.
	\newblock {\em Solving Problems in Multiply Connected Domains}.
	\newblock SIAM, 2020.
	
	\bibitem{ckgn}
	D.G. Crowdy, E.H. Kropf, C.C. Green, and M.M.S. Nasser.
	\newblock The {S}chottky-{K}lein prime function: a theoretical and
	computational tool for applications.
	\newblock {\em IMA J. App. Math.}, 81:589--628, 2016.
	
	\bibitem{Del-harm}
	Thomas~K DeLillo and John~A Pfaltzgraff.
	\newblock Extremal distance, harmonic measure and numerical conformal mapping.
	\newblock {\em J. Comput. Appl. Math.}, 46(1-2):103--113, 1993.
	
	\bibitem{Tre-Gre}
	Mark Embree and Lloyd~N Trefethen.
	\newblock Green's functions for multiply connected domains via conformal
	mapping.
	\newblock {\em SIAM Rev.}, 41(4):745--761, 1999.
	
	\bibitem{Gak}
	F.D. Gakhov.
	\newblock {\em Boundary Value Problems}.
	\newblock Pergamon Press, Oxford, 1966.
	
	\bibitem{garmar}
	J.B. Garnett and D.E. Marshall.
	\newblock {\em Harmonic Measure}.
	\newblock Cambridge University Press, Cambridge, 2008.
	
	\bibitem{gswc}
	C.C. Green, M.A. Snipes, L.A. Ward, and D.G. Crowdy.
	\newblock Harmonic-measure distribution functions for a class of multiply
	connected symmetrical slit domains.
	\newblock {\em Proceedings of the Royal Society A}, 478(2259):20210832, 2022.
	
	\bibitem{Gre-Gim12}
	L.~Greengard and Z.~Gimbutas.
	\newblock {\em {FMMLIB2D}: A {MATLAB} toolbox for fast multipole method in two
		dimensions}, version 1.2. edition, 2012.
	\newblock \url{http://www.cims.nyu.edu/cmcl/fmm2dlib/fmm2dlib.html}. Accessed
	17 Nov 2022.
	
	\bibitem{ka44}
	S.~Kakutani.
	\newblock Two-dimensional {B}rownian motion and harmonic functions.
	\newblock {\em Proc. Imp. Acad. Tokyo}, 20:706--714, 1944.
	
	\bibitem{ka45}
	Shizuo Kakutani.
	\newblock Two-dimensional {B}rownian motion and the type problem of {R}iemann
	surfaces.
	\newblock {\em Proceedings of the Japan Academy}, 21:138--140, 1945.
	
	\bibitem{bookBM}
	Ioannis Karatzas and Steven Shreve.
	\newblock {\em Brownian Motion and Stochastic Calculus}.
	\newblock Springer Science \& Business Media, 2nd edition, 2012.
	
	\bibitem{LSN17}
	J.~Liesen, O.~S{\'e}te, and M.M.S. Nasser.
	\newblock Fast and accurate computation of the logarithmic capacity of compact
	sets.
	\newblock {\em Comput. Methods Funct. Theory}, 17:689--713, 2017.
	
	\bibitem{ArMa}
	A.~Mahenthiram.
	\newblock {\em Harmonic-measure distribution functions, and related functions,
		for simply connected and multiply connected two-dimensional regions}.
	\newblock PhD thesis (submitted), University of South Australia, 2022.
	
	\bibitem{Nas-Siam1}
	M.M.S. Nasser.
	\newblock Numerical conformal mapping via a boundary integral equation with the
	generalized {N}eumann kernel.
	\newblock {\em SIAM J. Sci. Comput.}, 31:1695--1715, 2009.
	
	\bibitem{Nas-ETNA}
	M.M.S. Nasser.
	\newblock Fast solution of boundary integral equations with the generalized
	{N}eumann kernel.
	\newblock {\em Electron. Trans. Numer. Anal.}, 44:189--229, 2015.
	
	\bibitem{NG18}
	M.M.S. Nasser and C.C. Green.
	\newblock A fast numerical method for ideal fluid flow in domains with multiple
	stirrers.
	\newblock {\em Nonlinearity}, 31:815--837, 2018.
	
	\bibitem{NK}
	M.M.S. Nasser and E.~Kalmoun.
	\newblock Application of integral equations to simulating local fields in
	carbon nanotube reinforced composites.
	\newblock In R.~McPhedran, S.~Gluzman, V.~Mityushev, and N.~Rylko, editors,
	{\em 2D and Quasi-2D Composite and Nanocomposite Materials}, pages 233--248.
	Elsevier, 2020.
	
	\bibitem{Nvm}
	M.M.S Nasser and M.~Vuorinen.
	\newblock Numerical computation of the capacity of generalized condensers.
	\newblock {\em J. Comput. Appl. Math.}, 377:112865, 2020.
	
	\bibitem{SnipWard05}
	M.A. Snipes and L.A. Ward.
	\newblock Realizing step functions as harmonic measure distributions of planar
	domains.
	\newblock {\em Ann. Acad. Sci. Fenn. Math.}, 30(2):353--360, 2005.
	
	\bibitem{SnipWard08}
	M.A. Snipes and L.A. Ward.
	\newblock Convergence properties of harmonic measure distributions for planar
	domains.
	\newblock {\em Complex Var. Elliptic Equ.}, 53(10):897--913, 2008.
	
	\bibitem{SnipWard16}
	M.A. Snipes and L.A. Ward.
	\newblock Harmonic measure distribution functions of planar domains: A survey.
	\newblock {\em J. Anal.}, 24:293--330, 2016.
	
	\bibitem{Tre-Ser}
	Lloyd~N Trefethen.
	\newblock Series solution of {L}aplace problems.
	\newblock {\em ANZIAM J.}, 60(1):1--26, 2018.
	
	\bibitem{wawa96}
	B.L. Walden and L.A. Ward.
	\newblock Distributions of harmonic measure for planar domains.
	\newblock In I.~Laine and O.~Martio, editors, {\em Proceedings of 16th
		Nevanlinna Colloquium, {J}oensuu}, pages 289--299. Walter de Gruyter, Berlin,
	1996.
	
	\bibitem{wawa01}
	B.L. Walden and L.A. Ward.
	\newblock Asymptotic behaviour of distributions of harmonic measure for planar
	domains.
	\newblock {\em Complex Variables: Theory and Applications}, 46(2):157--177,
	2001.
	
	\bibitem{wawa07}
	B.L. Walden and L.A. Ward.
	\newblock A harmonic measure interpretation of the arithmetic--geometric mean.
	\newblock {\em Amer. Math. Monthly}, 114(7):610--622, 2007.
	
	\bibitem{Weg-Nas}
	R.~Wegmann and M.M.S. Nasser.
	\newblock The {R}iemann-{H}ilbert problem and the generalized {N}eumann kernel
	on multiply connected regions.
	\newblock {\em J. Comput. Appl. Math.}, 214:36--57, 2008.
	
\end{thebibliography}


\end{document}

%\endinput
%%
%% End of file `elsarticle-template-num-names.tex'.
