\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\input{preamble}
\begin{document}

\title{Towards machine learning guided by best practices}

\author{\IEEEauthorblockN{Anamaria Mojica-Hanke}
\IEEEauthorblockA{\textit{University of Passau} \\
Passau, Germany}
\IEEEauthorblockA{\textit{Universidad de los Andes} \\
	Bogota, Colombia\\
	ai.mojica10@uniandes.edu.co}

}

\maketitle

\begin{abstract}


Nowadays, machine learning (ML) is being used in software systems with multiple application fields, from medicine to software engineering (SE). On the one hand, the popularity of ML in the industry can be seen in the statistics showing its growth and adoption.  On the other hand, its popularity can also be seen in research, particularly  in SE, where multiple studies related to the use of Machine Learning in Software Engineering have been published in conferences and journals.  At the same time, researchers and practitioners have shown that machine learning has some particular challenges and pitfalls. In particular, research has shown that ML-enabled systems  have a different development process than traditional software, which also describes  some of the challenges of ML applications.  In order to mitigate some of the identified challenges and pitfalls, white and gray literature has proposed a set of recommendations based on their own experiences  and focused on their domain (\eg biomechanics), but for the best of our knowledge, there is no guideline focused on the SE community. %This thesis aims to reduce this gap by answering research questions that help to understand the practices used and discussed by practitioners and researchers in the SE community. As a result we will present a set of best practices with a focus on SE. 
This thesis aims to reduce the gap of not having clear guidelines in the SE community by using  possible sources of practices such as question-and-answer communities and also previous research studies. As a result, we will  present a set of practices with an SE perspective, for researchers and practitioners, including a tool for searching them. 

\end{abstract}

\begin{IEEEkeywords}
Machine learning, good practices, software engineering
\end{IEEEkeywords}

\input{secs/motivation}
\input{secs/related_work}
\input{secs/research_q}
\input{secs/contributions_result_so_far}
\input{secs/timeline}




\balance
\bibliographystyle{IEEEtran}
\bibliography{local}

\end{document}
