%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, journal, twoside]{IEEEtran}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

%\overrideIEEEmargins                                      % Needed to meet printer requirements.

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed



\newcommand*{\M}{\mathbf}
\newcommand*{\V}{\mathbf}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}


\usepackage{changepage} % for adjustwidth
\usepackage{pstool}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{array}
%\usepackage{xcolor}
\usepackage[dvipsnames]{xcolor}
%\usepackage{breakurl}
\usepackage{hyperref} % for link footnote
\usepackage[capitalize]{cleveref}
\usepackage{algpseudocode}
\usepackage[]{algorithm2e}
\usepackage{multirow}
\usepackage{units}
\definecolor{magenta1}{rgb}{0.761, 0.428, 0.627}
\usepackage{epstopdf}
\usepackage{booktabs} 

%FIXED "aside from" or "alongside"
\title{
  Online Learning of Neural Surface Light Fields\\ alongside Real-time Incremental 3D Reconstruction
}
\author{Yijun Yuan and Andreas N\"uchter% <-this % stops a space
  %\thanks{*This work was supported by \# organization}% <-this % stops a space
  \thanks{Manuscript received: January, 24, 2023; Revised March, 29, 2023; Accepted April, 28, 2023.}%Use only for final RAL version
  \thanks{This paper was recommended for publication by Editor Civera Javier upon evaluation of the Associate Editor and Reviewers' comments.}
  \thanks{All authors are with Informatics XVII : Robotics, Julius-Maximilians-Universit\"at W\"urzburg, Germany.
    {\tt\footnotesize \{yijun.yuan|andreas. nuechter\}@uni-wuerzburg.de }}%
}

\begin{document}

\maketitle
%\thispagestyle{empty}
%\pagestyle{empty}
\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted April, 2023}
{Yuan \MakeLowercase{\textit{et al.}}: Neural Surface Light Fields alongside Reconstruction} 


\begin{abstract}

Immersive novel view generation is an important technology in the field of graphics and has recently also received attention for operator-based human-robot interaction. 
However, the involved training is time-consuming, and thus the current test scope is majorly on object capturing.
This limits the usage of related models in the robotics community for 3D reconstruction since robots (1) usually only capture a very small range of view directions to surfaces that cause arbitrary predictions on unseen, novel direction, (2) requires real-time algorithms, and (3) work with growing scenes, e.g., in robotic exploration.
The paper proposes a novel Neural Surface Light Fields model that copes with the small range of view directions while producing a good result in unseen directions.
Exploiting recent encoding techniques, the training of our model is highly efficient.

In addition, we design Multiple Asynchronous Neural Agents (MANA), a universal framework to learn each small region in parallel for large-scale growing scenes.
Our model learns online the Neural Surface Light Fields (NSLF) aside from real-time 3D reconstruction with a sequential data stream as the shared input.
In addition to online training, our model also provides real-time rendering after completing the data stream for visualization.
We implement experiments using well-known RGBD indoor datasets, showing the high flexibility to embed our model into real-time 3D reconstruction and demonstrating high-fidelity view synthesis for these scenes. The code is available on github\footnote{\url{https://jarrome.github.io/NSLF-OL}}.
\end{abstract}
\begin{IEEEkeywords}
	Mapping; SLAM
\end{IEEEkeywords}
\vspace{-.3cm}
\input{tex/intro}

\input{tex/related}

\input{tex/method}

\input{tex/exp}

\vspace{-.2cm}
\section{Conclusion}
In this paper, we have proposed an online learning method for neural surface light fields during real-time incremental 3D reconstruction on large scenes.

We have proposed a novel Neural Surface Light Fields model to address the challenge that in a SLAM and reconstruction scenario the captured surface directions are very limited, the learned model easily produces arbitrary predictions from unseen directions.

For online learning in growing scenes where we do not pre-know the boundaries in advance, we have designed Multiple Asynchronous Neural Agents to work alongside real-time incremental 3D reconstruction.

The performance of the proposed method has been demonstrated in our experiments.
Our implementation achieves real-time learning of Neural Surface Light Fields alongside real-time incremental reconstruction.

{\small
	\bibliographystyle{IEEEtran.bst}
	\bibliography{ref}
}

\end{document}
