% File tacl2021v1.tex
% Dec. 15, 2021

% The English content of this file was modified from various *ACL instructions
% by Lillian Lee and Kristina Toutanova
%
% LaTeXery is mostly all adapted from acl2018.sty.

\documentclass[11pt,a4paper]{article}
\usepackage{times,latexsym}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage{bbm}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{bigstrut}
\usepackage{subfigure}
\usepackage{diagbox}
\usepackage{footnote}
\usepackage{mathtools}
\usepackage{epstopdf}
\usepackage[dvipsnames,table,xcdraw]{xcolor}

%% Package options:
%% Short version: "hyperref" and "submission" are the defaults.
%% More verbose version:
%% Most compact command to produce a submission version with hyperref enabled
%%    \usepackage[]{tacl2021v1}
%% Most compact command to produce a "camera-ready" version
%%    \usepackage[acceptedWithA]{tacl2021v1}
%% Most compact command to produce a double-spaced copy-editor's version
%%    \usepackage[acceptedWithA,copyedit]{tacl2021v1}
%
%% If you need to disable hyperref in any of the above settings (see Section
%% "LaTeX files") in the TACL instructions), add ",nohyperref" in the square
%% brackets. (The comma is a delimiter in case there are multiple options specified.)

\usepackage[acceptedWithA]{tacl2021v1}
% \setlength\titlebox{10cm} % <- for Option 2 below

%%%% Material in this block is specific to generating TACL instructions
\usepackage{xspace,mfirstuc,tabulary}
\usepackage{subfigure}
\usepackage{graphicx}
\newcommand{\dateOfLastUpdate}{Dec. 15, 2021}
\newcommand{\styleFileVersion}{tacl2021v1}

\newcommand{\ex}[1]{{\sf #1}}

\newif\iftaclinstructions
\taclinstructionsfalse % AUTHORS: do NOT set this to true
\iftaclinstructions
\renewcommand{\confidential}{}
\renewcommand{\anonsubtext}{(No author info supplied here, for consistency with
TACL-submission anonymization requirements)}
\newcommand{\instr}
\fi

%
\iftaclpubformat % this "if" is set by the choice of options
\newcommand{\taclpaper}{final version\xspace}
\newcommand{\taclpapers}{final versions\xspace}
\newcommand{\Taclpaper}{Final version\xspace}
\newcommand{\Taclpapers}{Final versions\xspace}
\newcommand{\TaclPapers}{Final Versions\xspace}
\else
\newcommand{\taclpaper}{submission\xspace}
\newcommand{\taclpapers}{{\taclpaper}s\xspace}
\newcommand{\Taclpaper}{Submission\xspace}
\newcommand{\Taclpapers}{{\Taclpaper}s\xspace}
\newcommand{\TaclPapers}{Submissions\xspace}
\fi

\newcommand{\NAME}[0]{\textsc{RR}}
%%%% End TACL-instructions-specific macro block
%%%%

\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{Rethinking with Retrieval: Faithful Large Language Model Inference}

% Author information does not appear in the pdf unless the "acceptedWithA" option is given

% The author block may be formatted in one of two ways:

% Option 1. Author’s address is underneath each name, centered.
\iffalse
\author{
  Template Author1\Thanks{The {\em actual} contributors to this instruction
    document and corresponding template file are given in Section
    \ref{sec:contributors}.} 
  \\
  Template Affiliation1/Address Line 1
  \\
  Template Affiliation1/Address Line 2
  \\
  Template Affiliation1/Address Line 2
  \\
  \texttt{template.email1example.com}
  \And
  Template Author2 
  \\
  Template Affiliation2/Address Line 1
  \\
  Template Affiliation2/Address Line 2
  \\
  Template Affiliation2/Address Line 2
  \\
  \texttt{template.email2@example.com}
}
\fi

\author{Hangfeng He$^\dag$\thanks{\, Part of this work was done while the author was at the University of Pennsylvania.}\qquad Hongming Zhang$^\ddagger$ \qquad Dan Roth$^\mathsection$ \\
  $^\dag$University of Rochester\qquad
  $^\ddagger$Tencent AI Lab, Seattle \qquad
  $^\mathsection$University of Pennsylvania\\
\texttt{hanfeng.he@rochester.edu}, \texttt{hongmzhang@global.tencent.com} \\ \texttt{danroth@seas.upenn.edu}
}

% % Option 2.  Author’s address is linked with superscript
% % characters to its name, author names are grouped, centered.

% \author{
%   Template Author1\Thanks{The {\em actual} contributors to this instruction
%     document and corresponding template file are given in Section
%     \ref{sec:contributors}.}$^\diamond$ 
%   \and
%   Template Author2$^\dagger$
%   \\
%   \ \\
%   $^\diamond$Template Affiliation1/Address Line 1
%   \\
%   Template Affiliation1/Address Line 2
%   \\
%   Template Affiliation1/Address Line 2
%   \\
%   \texttt{template.email1example.com}
%   \\
%   \ \\
%   \\
%   $^\dagger$Template Affiliation2/Address Line 1
%   \\
%   Template Affiliation2/Address Line 2
%   \\
%   Template Affiliation2/Address Line 2
%   \\
%   \texttt{template.email2@example.com}
% }

\date{}

\begin{document}
\maketitle
\begin{abstract}
Despite the success of large language models (LLMs) in various natural language processing (NLP) tasks, the stored knowledge in these models may inevitably be incomplete, out-of-date, or incorrect. This motivates the need to utilize external knowledge to assist LLMs. Unfortunately, current methods for incorporating external knowledge often require additional training or fine-tuning, which can be costly and may not be feasible for LLMs. To address this issue, we propose a novel post-processing approach, \textit{rethinking with retrieval} (\NAME{}), which retrieves relevant external knowledge based on the decomposed reasoning steps obtained from the chain-of-thought (CoT) prompting. This lightweight approach does not require additional training or fine-tuning and is not limited by the input length of LLMs. We evaluate the effectiveness of \NAME{} through extensive experiments with GPT-3 on three complex reasoning tasks: commonsense reasoning, temporal reasoning, and tabular reasoning. Our results show that \NAME{} can produce more faithful explanations and improve the performance of LLMs.\footnote{Our code is publicly available at \url{https://github.com/HornHehhf/RR}.}

\end{abstract}

\input{01-introduction}
\input{02-related-work}
\input{03-framework}
\input{04-experiments}
\input{05-analysis}
\input{06-conclusion}

\clearpage
\bibliography{new}
\bibliographystyle{acl_natbib}

\clearpage
\appendix
\input{07-appendix.tex}

\end{document}


