\documentclass[12pt]{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
\usepackage[slovak]{babel}
% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{natbib}
\usepackage{fancyhdr}
\usepackage{unicode}
%\title{Your Paper}
%\author{You}


\linespread{0.99}

\pagestyle{fancy}
\fancyhf{}
\setlength{\headsep}{15pt}


% redefine the plain page style
\fancypagestyle{plain}{%
  \renewcommand{\headrulewidth}{0pt}% no rule above!
  \fancyhf{}\fancyfoot[R]{Page \thepage}%
}



%definition of journal abbreviations (MZ)
\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\pasp}{PASP}
\newcommand{\mnras}{MNRAS}
\newcommand{\aj}{AJ}
\newcommand{\nat}{Nature}
\newcommand{\nar}{NewAR}
\newcommand{\na}{NewA}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\icarus}{Icar}
\newcommand{\araa}{ARA\&A}
\newcommand{\aapr}{A\&ARv}
\newcommand{\aplett}{Astrophysical Letters}
\newcommand{\physrep}{Physics Reports}
\newcommand{\actaa}{Acta Astronomica}
\newcommand{\rmxaa}{RMxAA}

\begin{document}
%\maketitle

%\begin{abstract}
%Your abstract.
%\end{abstract}

\section*{\textcolor{blue}{Reply to the referee MNRAS: MN-21-4483-MJ.R2}}

\textcolor{blue}{We thank the referee for reading our manuscript and the suggestion. We implemented it in our draft and address it below.}\\

\textit{Comments to the Author:}\\
The authors have addressed almost all of my concerns. Their answers are generally reasonable. However, the answer to my Point 3 should be added into the manuscript rather than only in the response. Please append to the manuscript your comparison (in the response) between the results using the original cosmological parameters and those given in your paper. In addition, please add several sentences in the main text to state that the incorrectness can be negligible and the results will not be influenced.\\

\textcolor{blue}{\textit{Reply:}}\\
\textcolor{blue}{We agree with the referee. The comparison of the flat-$\Lambda$CDM cosmological parameters between the two 118 H$\beta$ datasets (the one using the original cosmological parameters and the other generally used in the paper with slighly different cosmological parameters) is now in \textbf{Footnote 12}. The differences are insignificant as explained in the previous reply. This is now also stressed in the first paragraph of Section 3 (``Data''). We hope that this explanation and justification in the footnote is now sufficient. A more elaborate comparison in the main text would likely significantly extend the 20 free-page limit. We thank the referee for understanding in advance.}





\end{document}