% Template for ICASSP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{multirow}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{amssymb}
\usepackage{times,amsmath,epsfig}
\usepackage{amsmath,graphicx,latexsym}
\usepackage{algorithm,algorithmic}
\usepackage{amssymb}
\usepackage{url}
\usepackage{times,amsmath,epsfig,changebar}
\usepackage[tight]{subfigure}

\newcommand{\comment}[1]{}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{Privacy Preserving and Collusion Resistant Energy Sharing}
%
% Single address.
% ---------------

\name{Yuan Hong, Han Wang, Shangyu Xie, Bingyu Liu}

\address{Department of Computer Science\\Illinois Institute of Technology\\10 W 31st Street, Chicago, IL 60616\\yuan.hong@iit.edu}


%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}


Energy has been increasingly generated or collected by different entities on the power grid (e.g., universities, hospitals and householdes) via solar panels, wind turbines or local generators in the past decade. With local energy, such electricity consumers can be considered as ``microgrids'' which can simulataneously generate and consume energy. Some microgrids may have excessive energy that can be shared to other power consumers on the grid. To this end,  all the entities have to share their local private information (e.g., their local demand, local supply and power quality data) to each other or a third-party to find and implement the optimal energy sharing solution. However, such process is constrained by privacy concerns raised by the microgrids. In this paper, we propose a privacy preserving scheme for all the microgrids which can securely implement their energy sharing against both semi-honest and colluding adversaries. The proposed approach includes two secure communication protocols that can ensure quantified privacy leakage and handle collusions.


\end{abstract}
%
%\begin{keywords}
%Smart Grid, Privacy, Security
%\end{keywords}
%

\section{Introduction}
\label{sec:intro}
\input{intro}

\section{Related Work}
\label{sec:related}
\input{related}

\section{Preliminaries}
\label{sec:pre}
\input{pre}

\section{Extended Transformation}
\label{sec:ext}
\input{ext}

\section{Experiments}
\label{sec:exp}
\input{exp}


\section{Conclusion and Future work}
In this paper, we have extended the secure transformation and solution reconstruction in \cite{HongIJER15} to ensure provable security for securely solving the energy sharing optimization problem and implementing the optimal solution on the power transmission network. Novel secure communication protocols were proposed for all the parties to jointly transform their individual shares of the optimization problem, and jointly reconstruct their own shares in the optimal solution of the original problem. In the meanwhile, collusions can be handled with the secure communication protocols. In case that some parties disclose information to each other so as to learn other parties' private information, they cannot learn the actual transformation and reconstruction as long as at least one party is not colluding with them.

In the future, we will investigate other privacy preserving cooperative models among entities with local energy (viz. microgrids) on the power grid. For instance, global and local load balancing can be manipulated and further optimized via the cooperation among microgrids (e.g., scheduling \cite{HongEnergies17,liuscheduling17}). We intend to propose a privacy preserving cooperative model for them to jointly improving the global and local performance of the power generation, supply, storage and consumption.  

\subsection*{Acknowledgments}
This work is partially supported by the National Science Foundation under Grants No. CNS-1618221/1745894.

%\bibliography{ref} 
%\bibliographystyle{string,refs}
\bibliographystyle{abbrv}

\begin{thebibliography}{10}
	
	\bibitem{ArboleyaGCFMSBP15}
	P.~Arboleya, C.~Gonzalez{-}Moran, M.~Coto, M.~C. Falvo, L.~Martirano,
	D.~Sbordone, I.~Bertini, and B.~D. Pietra.
	\newblock Efficient energy management in smart micro-grids: {ZERO} grid impact
	buildings.
	\newblock {\em {IEEE} Trans. Smart Grid}, 6(2):1055--1063, 2015.
	
	\bibitem{DuanD09}
	R.~Duan and G.~Deconinck.
	\newblock Multi-agent coordination in market environment for future electricity
	infrastructure based on microgrids.
	\newblock In {\em SMC}, pages 3959--3964, 2009.
	
	\bibitem{SGSBook}
	S.~Goel and Y.~Hong.
	\newblock Security challenges in smart grid implementation.
	\newblock {\em SpringerBriefs in Cybersecurity}, pages 1--39, 2015.
	
	\bibitem{Goldreich87}
	O.~Goldreich, S.~Micali, and A.~Wigderson.
	\newblock How to play any mental game - a completeness theorem for protocols
	with honest majority.
	\newblock In {\em Proceedings of the 19th {ACM} Symposium on the Theory of
		Computing}, pages 218--229, New York, NY, 1987. ACM.
	
	\bibitem{HongThesis}
	Y.~Hong.
	\newblock {\em Privacy-preserving Collaborative Optimization}.
	\newblock PhD thesis, Rutgers University, Newark, NJ, 2013.
	
	\bibitem{HongIJER15}
	Y.~Hong, S.~Goel, and W.~M. Liu.
	\newblock An efficient and privacy-preserving scheme for p2p energy exchange
	among smart microgrids.
	\newblock {\em International Journal of Energy Research}, 40(3):313--331, 2016.
	
	\bibitem{HongTIFS17}
	Y.~Hong, W.~M. Liu, and L.~Wang.
	\newblock Privacy preserving smart meter streaming against information leakage
	of appliance status.
	\newblock {\em {IEEE} Trans. Information Forensics and Security},
	12(9):2227--2241, 2017.
	
	\bibitem{HongOpt13}
	Y.~Hong and J.~Vaidya.
	\newblock An inference-proof approach to privacy-preserving horizontally
	partitioned linear programs.
	\newblock {\em Optimization Letters}, 8(1):267--277, 2014.
	
	\bibitem{HongDBsec}
	Y.~Hong, J.~Vaidya, and H.~Lu.
	\newblock Efficient distributed linear programming with limited disclosure.
	\newblock In {\em DBSec}, pages 170--185, 2011.
	
	\bibitem{HongJCS12}
	Y.~Hong, J.~Vaidya, and H.~Lu.
	\newblock Secure and efficient distributed linear programming.
	\newblock {\em Journal of Computer Security}, 20(5):583--634, 2012.
	
	\bibitem{HongTDSC15}
	Y.~Hong, J.~Vaidya, H.~Lu, P.~Karras, and S.~Goel.
	\newblock Collaborative search log sanitization: Toward differential privacy
	and boosted utility.
	\newblock {\em {IEEE} Trans. Dependable Sec. Comput.}, 12(5):504--518, 2015.
	
	\bibitem{HongDBSEC14}
	Y.~Hong, J.~Vaidya, H.~Lu, and L.~Wang.
	\newblock Collaboratively solving the traveling salesman problem with limited
	disclosure.
	\newblock In {\em DBSec}, pages 179--194, 2014.
	
	\bibitem{HongJIS14}
	Y.~Hong, J.~Vaidya, and S.~Wang.
	\newblock A survey of privacy-aware supply chain collaboration: From theory to
	applications.
	\newblock {\em Journal of Information Systems}, 28(1):243--268, 2014.
	
	\bibitem{HongEnergies17}
	Y.~Hong, S.~Wang, and Z.~Huang.
	\newblock Efficient energy consumption scheduling: Towards effective load
	leveling.
	\newblock {\em Energies}, 10(1), 2017.
	
	\bibitem{liuscheduling17}
	F.~Liu, S.~Wang, Y.~Hong, and X.~Yue.
	\newblock On the robust and stable flowshop scheduling under stochastic and
	dynamic disruptions.
	\newblock {\em IEEE Transactions on Engineering Management}, PP(99):1--15,
	2017.
	
	\bibitem{MaityR10}
	I.~Maity and S.~Rao.
	\newblock Simulation and pricing mechanism analysis of a solar-powered
	electrical microgrid.
	\newblock {\em IEEE Systems Journal}, 4(3):275--284, 2010.
	
	\bibitem{McLaughlinMA11}
	S.~E. McLaughlin, P.~McDaniel, and W.~Aiello.
	\newblock Protecting consumer privacy from electric load monitoring.
	\newblock In {\em ACM Conference on Computer and Communications Security},
	pages 87--98, 2011.
	
	\bibitem{Paillier99}
	P.~Paillier.
	\newblock Public key cryptosystems based on composite degree residuosity
	classes.
	\newblock In {\em Advances in Cryptology - Eurocrypt '99 Proceedings, LNCS
		1592}, pages 223--238, 1999.
	
	\bibitem{RottondiVC13}
	C.~Rottondi, G.~Verticale, and A.~Capone.
	\newblock Privacy-preserving smart metering with multiple data consumers.
	\newblock {\em Computer Networks}, 57(7):1699--1713, 2013.
	
	\bibitem{SaadHPB12}
	W.~Saad, Z.~Han, H.~V. Poor, and T.~Basar.
	\newblock Game-theoretic methods for the smart grid: An overview of microgrid
	systems, demand-side management, and smart grid communications.
	\newblock {\em IEEE Signal Process. Mag.}, 29(5):86--105, 2012.
	
	\bibitem{SankarRMP13}
	L.~Sankar, S.~R. Rajagopalan, S.~Mohajer, and H.~V. Poor.
	\newblock Smart meter privacy: A theoretical framework.
	\newblock {\em IEEE Trans. Smart Grid}, 4(2):837--846, 2013.
	
	\bibitem{YangLQQMM12}
	W.~Yang, N.~Li, Y.~Qi, W.~H. Qardaji, S.~E. McLaughlin, and P.~McDaniel.
	\newblock Minimizing private data disclosures in the smart grid.
	\newblock In {\em ACM Conference on Computer and Communications Security},
	pages 415--427, 2012.
	
	\bibitem{Yao86}
	A.~C. Yao.
	\newblock How to generate and exchange secrets.
	\newblock In {\em Proceedings of the 27th {IEEE} Symposium on Foundations of
		Computer Science}, pages 162--167, Los Alamitos, CA, USA, 1986. IEEE, IEEE
	Computer Society.
	
	\bibitem{ZhuHSSIMMS13}
	T.~Zhu, Z.~Huang, A.~Sharma, J.~Su, D.~E. Irwin, A.~K. Mishra, D.~S.
	Menasch{\'{e}}, and P.~J. Shenoy.
	\newblock Sharing renewable energy in smart microgrids.
	\newblock In {\em {ACM/IEEE} 4th International Conference on Cyber-Physical
		Systems}, pages 219--228, 2013.
	
	\bibitem{ZhuXPTG11}
	T.~Zhu, S.~Xiao, Y.~Ping, D.~Towsley, and W.~Gong.
	\newblock A secure energy routing mechanism for sharing renewable energy in
	smart microgrid.
	\newblock In {\em SmartGridComm}, pages 143--148, 2011.
	
\end{thebibliography}


\end{document}
