\documentclass[letterpaper, 10pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts

\usepackage[noend, boxruled, linesnumbered] {algorithm2e}
\SetAlCapSkip{1em}
\makeatletter
\renewcommand{\algorithmcfname}{Alg.}
\renewcommand{\fnum@algocf}{\AlCapSty{\AlCapFnt\algorithmcfname\nobreakspace\thealgocf}}
\makeatother

\usepackage{svg}
\usepackage{float}
\usepackage{amsmath, array}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{dsfont}
\usepackage{amssymb}
\usepackage[labelfont=bf]{caption}
\usepackage[noadjust]{cite}
\usepackage{filecontents}
\usepackage{url}

\newlength{\bibitemsep}\setlength{\bibitemsep}{0\baselineskip plus .01\baselineskip minus .05\baselineskip}
\newlength{\bibparskip}\setlength{\bibparskip}{0pt}
\let\oldthebibliography\thebibliography
\renewcommand\thebibliography[1]{%
	\oldthebibliography{#1}%
	\setlength{\parskip}{\bibitemsep}%
	\setlength{\itemsep}{\bibparskip}%
}

%\usepackage{flushend}

\renewcommand{\citedash}{--}

\newcommand{\simplicity}[1]{\textcolor{orange}{#1}}
\newcommand{\impedance}[1]{\textcolor{blue}{#1}}
\newcommand{\grasping}[1]{\textcolor{cyan}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

\newcommand{\vdeltaL}{\delta_{\text{l}}}

\newcommand{\vf}{f(t)}
\newcommand{\vfEst}{d(t)}
\newcommand{\vdfEst}{\dot{d}_{\text{p}}(t)}
\newcommand{\vfP}{d_{\text{p}}(t)}
\newcommand{\vfF}{f_F (t)}
\newcommand{\vdn}{d_n (t)}

\newcommand{\vt}{\tau(t)}

\newcommand{\vvR}{v_{\text{r}}(t)}
\newcommand{\vvRn}{v_{\text{r}_n}(t)}
\newcommand{\vkV}{k_{\text{v}}(t)}

\newcommand{\vc}{c(t)}
\newcommand{\vcP}{c_{\text{p}}(t)}

\newcommand{\veP}{e_{\text{p}}(t)}
\newcommand{\veD}{e_{\text{d}}(t)}
\newcommand{\vdeD}{\dot{e}_{\text{d}}(t)}

\newcommand{\vkP}{k_{\text{p}}}
\newcommand{\vkD}{k_{\text{d}}}

\newcommand{\vx}{x(t)}
\newcommand{\vddx}{\ddot{x}(t)}

\newcommand{\vw}{\omega(t)}
\newcommand{\vdw}{\dot{\omega}(t)}

\newcommand{\vp}{p}
\newcommand{\vpO}{p_{\text{O}}(t)}

\newcommand{\vA}{\text{A}}
\newcommand{\vB}{\text{B}}

\newcommand{\vlA}{l_{\text{A}}}
\newcommand{\vlB}{l_{\text{B}}}
\newcommand{\vnlA}{n_{l_{\text{A}}}}

\newcommand{\vthetaO}{\theta_1 (t)}
\newcommand{\vthetaT}{\theta_2 (t)}
\newcommand{\vdthetaO}{\dot{\theta}_1 (t)}
\newcommand{\vdthetaT}{\dot{\theta}_2 (t)}
\newcommand{\vddthetaO}{\ddot{\theta}_1 (t)}
\newcommand{\vddthetaT}{\ddot{\theta}_2 (t)}
\newcommand{\vdeltaTheta}{\Delta\theta(t)}

\def\sec#1{Section \ref{sec:#1}}
\def\fig#1{Figure \ref{fig:#1}}
\def\alg#1{Alg. \ref{alg:#1}}
\def\eqn#1{(\ref{eq:#1})}

\title{\LARGE \bf Penalty-based Numerical Representation of Rigid Body Interactions with Applications to Simulation of Robotic Grasping}


\author{Michael Zechmair, Yannick Morel%
	\thanks{Michael and Yannick are with the Faculty of Psychology and Neuroscience,
		Bonnefantenstraat 2, 6211 KL Maastricht, Netherlands,
		{\tt\scriptsize \{m.zechmair, y.morel\}@maastrichtuniversity.nl}.}%
	\thanks{This research has received funding from the European Union's Horizon 2020 Framework Programme for Research and Innovation under the Specific Grant Agreement No. 785907 (Human Brain Project SGA3).}%
}

\setlength{\textfloatsep}{10pt}
\setlength{\belowdisplayskip}{3pt}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowcaptionskip}{-5pt}

%
\begin{document}
	\maketitle
	\thispagestyle{empty}
	\pagestyle{empty}
	
	%
	\noindent\begin{abstract}
		This paper presents a novel approach to numerically describe the interactions between rigid bodies, with a special focus on robotic grasping. Some of the more common approaches used to address such issues rely on satisfaction of a set of strict constraints, descriptive of the expected physical reality of such interactions in practice. However, application of constraint-based methods in a numerical setting may lead to problematic configurations in which, for instance, volumes occupied by distinct bodies may overlap. Such situations lying beyond the range of admissible configurations for constraint-based methods, their occurrence typically results in non-meaningful simulation outcomes. We propose a method which acknowledges the possibility of such occurrences while demoting their occurrence. This is pursued through the use of a penalty-based approach, and draws on notions of mechanical impedance to infer apposite reaction forces. Results of numerical simulations illustrate efficacy of the proposed approach.
	\end{abstract}
	%
	\input{sections/introduction.tex}
	\input{sections/approach_general_overview.tex}
	\input{sections/approach_pd_control_law.tex}
	\input{sections/numerical_results_overview.tex}
	\input{sections/numerical_results_bullet_comparison.tex}
	\input{sections/shadow_robot_hand.tex}
	\input{sections/conclusion.tex}
	
	\section{REFERENCES}
	\bibliographystyle{adaptive}
	\begingroup
	\renewcommand{\section}[2]{}%
	\bibliography{IEEEabrv,IEEEexample}
	\endgroup
	
\end{document}
% 