\documentclass[sigconf]{acmart}
\renewcommand\footnotetextcopyrightpermission[1]{}
\settopmatter{printacmref=false}
\pdfminorversion=4
\usepackage{booktabs} % For formal tables
\usepackage{balance} 

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


%Conference
\copyrightyear{2017} 
\acmYear{2017} 
\setcopyright{acmcopyright}
%Conference
\acmConference[VAMS'17]{ACM VAMS Workshop}{August 2017}{Como, Italy} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{15.00}

\begin{document}

\title{Multiple Stakeholders in Music Recommender Systems}

\author{Himan Abdollahpouri}
\affiliation{%
  \institution{DePaul University}
  \country{USA}
}

\email{habdolla@depaul.edu}
\author{Steve Essinger}
\affiliation{%
  \institution{Pandora Media, Inc.}
  \country{USA} 
}
\email{sessinger@pandora.com}



\begin{abstract}
    Music recommendation services collectively spin billions of songs for millions of listeners on a daily basis. Users can typically listen to a variety of songs tailored to their personal tastes and preferences. Music is not the only type of content encountered in these services, however. Advertisements are generally interspersed throughout the music stream to generate revenue for the business. Additional content may include artist messaging, ticketing, sports, news and weather. In this paper, we discuss issues that arise when multiple content providers are stakeholders in the recommendation process. These stakeholders each have their own objectives and must work in concert to sustain a healthy music recommendation service.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

\keywords{}


\maketitle

\input{mainBody}

%\bibliographystyle{ACM-Reference-Format}
%\balance
%\bibliography{sigproc} 


\balance
\begin{thebibliography}{99}
 
\bibitem{reciprocal} Luiz Pizzato, Tomek Rej, Thomas Chung, Irena Koprinska, and Judy Kay. 2010. RECON: a reciprocal recommender for online dating. In Proceedings of the fourth
ACM conference on Recommender systems. ACM, 207-214.
 
\bibitem{jugovac2017efficient} Michael Jugovac, Dietmar Jannach, and Lukas Lerche. 2017. Efficient optimization of multiple recommendation quality factors according to individual user tendencies. Expert Systems with Applications 81 (2017), 321-331
 
\bibitem{biasRecSys2017} Himan Abdollahpouri, Robin Burke, and Bamshad Mobasher. 2017. Controlling
Popularity Bias in Learning to Rank Recommendation. In Proceedings of the 11th
ACM conference on Recommender systems. ACM.
  
\bibitem{jambor2010optimizing} Tamas Jambor and Jun Wang. 2010. Optimizing multiple objectives in collaborative
filtering. In Proceedings of the fourth ACM conference on Recommender
systems. ACM, 55-62

\bibitem{umapHimanMS} Himan Abdollahpouri, Robin Burke, and Mobasher Bamshad. 2017. Recommender systems as multi-stakeholder environments. In Proceedings of the 25th
Conference on User Modeling, Adaptation and Personalization (UMAP2017). ACM.

\bibitem{DBLP:conf/um/BurkeAMG16} Robin D. Burke, Himan Abdollahpouri, Bamshad Mobasher, and Trinadh Gupta. 2016. Towards Multi-Stakeholder Utility Evaluation of Recommender Systems.
In Workshop on Surprise, Opposition, and Obstruction in Adaptive and Personalized
Systems, UMAP 2016

\bibitem{vamsBurkeHiman} Robin Burke and Himan Abdollahpouri. 2017. Patterns of Multistakeholder Recommendation.
In 1st International Workshop on Value-Aware and Multistakeholder
Recommendation at RecSys 2017

\bibitem{burke2016educational} Robin Burke and Himan Abdollahpouri. 2016. Educational Recommendation with Multiple Stakeholders. In Web Intelligence Workshops (WIW), IEEE/WIC/ACM
International Conference on. IEEE, 62-63

\bibitem{lee2014fairness} Eric L Lee, Jing-Kai Lou, Wei-Ming Chen, Yen-Chi Chen, Shou-De Lin, YenSheng Chiang, and Kuan-Ta Chen. 2014. Fairness-aware loan recommendation
for microfinance services. In Proceedings of the 2014 International Conference on
Social Computing. ACM, 3.

\end{thebibliography}  


\end{document}
