\documentclass[format=acmsmall, review=false, screen=true]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{multirow}
\usepackage{bm}
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


% Metadata Information
\acmJournal{TOIS}
\acmVolume{1}
\acmNumber{1}
\acmArticle{11}
\acmYear{2018}
\acmMonth{4}
\copyrightyear{2018}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2018}
% \received[revised]{March 2018}
% \received[accepted]{June 2018}


% Document starts
\begin{document}
% Title portion. Note the short title for running heads 
\title[Memory-augmented Dialogue Management for Task-oriented Dialogue Systems]{Memory-augmented Dialogue Management for Task-oriented Dialogue Systems}
\thanks{This work was partly supported by the National Basic Research Program (973 Program) under grant No. 2013CB329403, and the National Science Foundation of China under grant No. 61272227/61332007.}
\author{Zheng Zhang}
\author{Minlie Huang}
\authornote{Corresponding author}
\affiliation{%
  \institution{Tsinghua University}
  \department{Department of Computer Science and Technology}
  \city{Beijing}
  \postcode{100084}}
\email{zhangz.goal@gmail.com}
\email{aihuang@tsinghua.edu.cn}

\author{Zhongzhou Zhao}
\author{Feng Ji}
\author{Haiqing Chen}
\affiliation{%
  \institution{Alibaba Group}
  \city{Hangzhou}
  \state{Zhejiang}
  \postcode{311121}}
\email{zhongzhou.zhaozz@alibaba-inc.com}
\email{zhongxiu.jf@alibaba-inc.com}
\email{haiqing.chenhq@alibaba-inc.com}

\author{Xiaoyan Zhu}
\affiliation{%
  \institution{Tsinghua University}
  \department{Department of Computer Science and Technology}
  \city{Beijing}
  \postcode{100084}}
\email{zxy-dcs@tsinghua.edu.cn}


\begin{abstract}
Dialogue management (DM) decides the next action of a dialogue system according to the current dialogue state, and thus plays a central role in task-oriented dialogue systems. 
Since dialogue management requires to have access to not only local utterances, but also the global semantics of the entire dialogue session, modeling the long-range history information is a critical issue. To this end, we propose a novel Memory-Augmented Dialogue management model (MAD) which employs a memory controller and two additional memory structures, i.e., a slot-value memory and an external memory. The slot-value memory tracks the dialogue state by memorizing and updating the values of semantic slots (for instance, {\it cuisine, price, and location }), and the external memory augments the representation of hidden states of traditional recurrent neural networks through storing more context information. To update the dialogue state efficiently, we also propose slot-level attention on user utterances to extract specific semantic information for each slot.
Experiments show that our model can obtain state-of-the-art performance and outperforms existing baselines.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010178.10010179.10010181</concept_id>
<concept_desc>Computing methodologies~Discourse, dialogue and pragmatics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257.10010293.10010294</concept_id>
<concept_desc>Computing methodologies~Neural networks</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011039.10011311</concept_id>
<concept_desc>Software and its engineering~Semantics</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Discourse, dialogue and pragmatics}
\ccsdesc[500]{Computing methodologies~Neural networks}
\ccsdesc[300]{Software and its engineering~Semantics}

%
% End generated code
%


\keywords{Dialogue Management, Attention, Dialogue State, Memory Network,
          Neural Network}




\maketitle

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Z. Zhang et al.}

\input{samplebody-journals}


\end{document}
