% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
% \usepackage[review]{acl}
\usepackage{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}
% \usepackage{authblk}

\usepackage{booktabs, multirow} % for borders and merged ranges
\usepackage{soul}% for underlines
% \usepackage[table]{xcolor} % for cell colors
\usepackage{changepage,threeparttable} % for wide tables

\usepackage{amsfonts, amsmath, amssymb}
\usepackage{xcolor}
\usepackage{calc}
\usepackage{ifthen}
\usepackage{tikz}
\usepackage{url} 
\usepackage{tabularx}
\usepackage{float}
\usepackage{rotating,booktabs,multirow}
\usepackage{adjustbox}
\usepackage{xcolor}
\newcommand{\jjcomment}[1]{\textcolor{magenta}{[~Jing:#1~]}}
\newcommand{\jjadd}[1]{\textcolor{magenta}{#1}}
\newcommand{\mhcomment}[1]{\textcolor{cyan}{[~明环:#1~]}}
\newcommand{\mhadd}[1]{\textcolor{cyan}{#1}}
\usepackage{makecell}

% \renewcommand{\paragraph}[1]{
%      \textbf{#1.} 
% }

\usepackage[caption=false]{subfig}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Exploring and Adapting Chinese GPT to  Pinyin Input Method}
% \title{A GPT-based Pinyin Input Method}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{
Minghuan Tan$^1$\thanks{~~Work done during internship at Tencent AI Lab. ~~~~* indicates equal contribution.} \and
Yong Dai$^{2*}$\and
Duyu Tang$^2$\thanks{~~Corresponding author.}\and
Zhangyin Feng$^2$ \\
\bf{Guoping Huang}$^2$ \and 
\bf{Jing Jiang}$^1$ \and
Jiwei Li$^3$  \and
Shuming Shi$^2$
\\ \\
$^1$ Singapore Management University.
$^2$ Tencent AI Lab.
$^3$  Zhejiang University.\\
mhtan.2017@phdcs.smu.edu.sg, jingjiang@smu.edu.sg \\
\{yongdai,duyutang,aifeng,donkeyhuang,shumingshi\}@tencent.com,  
jiwei\_li@zju.edu.cn
}

\begin{document}

\maketitle
\begin{CJK*}{UTF8}{gbsn}

\begin{abstract}
While GPT has become the de-facto method for text generation tasks, its application to pinyin input method remains unexplored.
In this work, we make the first exploration to leverage Chinese GPT for pinyin input method.
We find that a frozen GPT achieves state-of-the-art performance on perfect pinyin.
However, the performance drops dramatically when the input includes abbreviated pinyin.
A reason is that an abbreviated pinyin can be mapped to many perfect pinyin, which links to even larger amount of Chinese characters.
We mitigate this issue with two strategies,
including enriching the context with pinyin and optimizing the training process to help distinguish homophones. 
To further facilitate the evaluation of pinyin input method, we create a dataset consisting of 270K instances from 15 domains.
Results show that our approach improves the performance on abbreviated pinyin across all domains.
Model analysis demonstrates that both strategies
contribute to the performance boost.
\end{abstract}

\vspace{0.01cm}

\input{introduction}
\input{task}
% \input{frozen-gpt}
% \input{pinyingpt}
\input{models}
\input{experiment}
\input{related}
\input{conclusion}

% Entries for the entire Anthology, followed by custom entries
\bibliography{anthology,custom}
\bibliographystyle{acl_natbib}

\appendix
\input{appendix}

\end{CJK*}

\end{document}
