Since the observation of a Higgs boson ($H$) by the ATLAS and CMS 
collaborations~\cite{atlas-higgs, cms-higgs}, its properties have been measured and
presented in subsequent publications. Its mass was determined
to be $\mH = 125.09 \pm 0.21\mathrm{(stat)} \pm 0.11\mathrm{(syst)}$~\GeV~\cite{higgs-mass}.
The couplings to Standard Model (SM) elementary particles were measured and confirmed to be consistent with 
the predictions for a SM Higgs boson within the present 
uncertainties~\cite{atlas-couplings,cms-couplings,atlas-cms-combined}, 
and alternative spin and $CP$ hypotheses were rejected in favour of the SM 
hypothesis~\cite{atlas-spin,Aad:2015mxa,cms-spin,cms-higgsprop}. 

In the SM, the \Zg decay proceeds through loop diagrams similar to the \htogg decay. 
The branching ratio for
the Higgs boson decay to $Z\gamma$ is predicted by the SM to be $\brhzg = (1.54\pm0.09)\times 10^{-3}$ at $\mH = 125.09$~\GeV,
which is
comparable with the branching ratio of the Higgs boson decay to a photon pair, $\brhgg = (2.27 \pm 0.05)\times 10^{-3}$. However, the number of reconstructed events is significantly smaller if 
$Z$ boson
decays into electron or muon pairs are considered ($B(Z\to ee)=(3.363\pm 0.004)\%$
and $B(Z\to\mu\mu)=(3.366\pm 0.007)\%$~\cite{Olive:2016xmw}).
A $H\to Z\gamma$ branching ratio different from the SM prediction would be expected if $H$ were
a neutral scalar of different
origin~\cite{low, low2}, or a composite state~\cite{azatov}, or in
models with additional colourless charged scalars, leptons or
vector bosons coupled to the Higgs boson and exchanged in the
\htoZg~loop~\cite{extensions, Chen:2013vi, carena}.

The $H\to Z(\to\ell\ell)\gamma$ decay ($\ell= e$ or $\mu$) 
has been searched for by the ATLAS and CMS
collaborations using the full data sets collected at $\sqrt{s}=7$ and 
8~\TeV~\cite{atlas-lowmass,cms-lowmass}. 
No significant excess over the expected background was observed. 
The ATLAS Collaboration reported an observed (expected) upper limit at the 95\% 
confidence level (CL) of 11 (9) times the SM prediction for a Higgs boson mass of 
$\mH = 125.5$~\GeV. 
The observed (expected) limit from the 
CMS Collaboration is 9.5 (10) times the SM prediction for a 125~\GeV\ Higgs boson.

Many models of physics beyond the SM introduce new heavy bosons $(X)$ through extensions of the Higgs
sector or as additional gauge fields. 
Searches for heavy $Z\gamma$ resonances were carried out by the D0 Collaboration at the 
Tevatron and by the ATLAS and CMS collaborations. 
The D0 Collaboration set upper limits on $\sigma(p\bar{p}\to X) \cdot B(X\to Z\gamma)$ ranging from 
2.5 (3.1)~pb  for a scalar (vector) $X$ mass of 140~\GeV\ to 0.19 (0.20)~pb for a mass of 
600~\GeV~\cite{d0-highmass-2}
using about 1~fb$^{-1}$ of $p\bar{p}$ collision data recorded
at $\sqrt{s} = 1.96$~\TeV.
The ATLAS Collaboration excluded technimesons decaying to $Z\gamma$ for
technimeson masses between 200 and 700~\GeV\ and between 750 and 890~\GeV, and composite spin-0
resonances decaying to $Z\gamma$
for most of the resonance mass range between 
200~\GeV\ and 1.18~\TeV\ for certain model parameters using $pp$ collision data recorded at
\sqes~\cite{atlas-highmass2}. Using 3.2~\invfb\ of $pp$ collision data recorded at \sqtt, the
ATLAS Collaboration set limits on $\sigxbr$ between 295~fb and 8.2~fb
for spin-0 resonances produced in gluon--gluon fusion for a $X$ mass range from 250~\GeV\ to 
2.75~\TeV\ using leptonic and hadronic $Z$ boson decays~\cite{Aaboud:2016trl}. 
The CMS Collaboration set upper limits on $\sigxbr$ between about 300~fb
and about 2.5~fb for spin-0 resonances produced in gluon--gluon fusion for a mass range of 200~\GeV\ to
3~\TeV\ using leptonic and hadronic $Z$ decays and $pp$ collision data taken at $\sqrt{s}=8$ and 
13~\TeV~\cite{cms-highmass2}.

This article presents improved searches for decays of the Higgs boson to $Z\gamma$ as well as 
for narrow high-mass resonances decaying to $Z\gamma$
using $Z$ boson decays to electron or muon pairs. 
The $Z(\to\ell\ell)\gamma$ final state can be reconstructed completely and with high
efficiency, good invariant mass resolution, and relatively small backgrounds. 
It is therefore a powerful experimental signature.
The main background is the non-resonant production of $Z$ bosons in 
conjunction with
photons, which is modelled using samples of simulated events. A smaller contribution 
arises from $Z$ boson production together with hadronic jets when a jet is misidentified
as a photon. This background is studied with a dedicated selection of the photon candidate.  
Both searches are based on $pp$ collision data recorded at
\sqtt~with the ATLAS detector at the LHC during 2015 and 2016, corresponding to a total
integrated luminosity of \lumithirteentev~\invfb.
The search for decays of the Higgs boson to $Z\gamma$ benefits from the increased
Higgs production cross section due to the increased centre-of-mass energy and also from the
larger data set compared to the previous search~\cite{atlas-lowmass}. In addition, the
event categorisation now includes a category sensitive to Higgs boson production 
via vector-boson fusion. The search is optimised based on the expected production
processes and kinematics for a SM Higgs boson.
The search for high-mass resonances uses a 
significantly larger data set than the previous search~\cite{Aaboud:2016trl}
and is extended to spin-2 resonance production.
 
