\thispagestyle{empty}

\chapter*{Words of Thanks}
%\begin{center}
%{\huge {\bf Words of thanks}}
%\end{center}
\addcontentsline{toc}{chapter}{Word of thanks}


It is always hard to thanks everyone that might helped me to reach this point of my career or
helped me to finish this thesis. Much probably some important person will be forgotten,
and for those (unfairly) forgotten people I promptly apologize.

At first place, I would like to thank my advisor Silvio~P.~Sorella. Thank you, Silvio. You did
inspire me to work in QFT and to always go as deep as possible in the world of non-perturbative
QCD. Thank you for the very long, fruitful and exciting meetings in your office (if it would
have a title, it would be ``The endless river''), and for the coffees after all. 

Dear Professor Dr. David~Dudal, thank you for everything you have made for me (and my wife) once
we have been in Belgium. You spared no efforts to make us feel at home: that was a marvelous
time, professionally and personally. Actually, it is really tough to separate the advisor
from the friend. I wish all the possible happiness to you and your family.

Thank you Prof. Marcio~Capri for have accepted be my co-advisor, for always be
accessible to discuss with me and for trying to teach me the art of Algebraic
Renormalization (yes, it is not a technique, it is an art) --- sorry, I will never reach your
high level of expertise. Thank you Prof. Marcelo Guimar\~aes, Prof. Bruno Mintz and Prof.
Leticia Palhares, which are not my officially advisors, but (lucky me!) were always there to
advise me and to have enlightening discussions with me. Thank you, each one of you, for making
pleasant our long meetings: not everyone is lucky enough to work with friends, as I was.

And talking about friends, thank you Luiz Gustavo, Gustavo Vicente, Ricardo Rodrigues (``o
Tol'') for turning easier, funnier and enjoyable those four years I did spend at UERJ. There
is no doubt that times of joy are fundamental for performing a good work. Equally, I would like
to thank Thomas Mertens. I know it was not easy for him to bear two Brazilian colleagues at
the same time in his office, at UGhent (it is not a fair thing to do with any Belgian). And
finally, to my great friend Diego R. Granado, thank you so much. We did start it together, we
will finish it together. Thank you.

I would like to thank CAPES for financially supporting me during these four years. It may not
seems to be, but physicists also need to eat.

\`A minha fam\'ilia, minha m\~ae, minha irm\~a e meu irm\~ao, agrade\c{c}o do fundo do meu
cora\c{c}\~ao, por voc\^es estarem sempre ao meu lado me dando suporte e muito carinho. Amo
todos voc\^es.

Por final, agrade\c{c}o \`a minha neguinha, Juliana V. Ford. Sem ela nada disso seria
poss\'ivel, ou mesmo faria sentido. Dedico a voc\^e esta tese.

Greetings,\\
\indent Igor F. Justo

\thispagestyle{empty}

\newpage

\thispagestyle{empty}
\ 
