%++++++++++++++++
%.IDENTIFICATION $Id$
%.PURPOSE		Gaia DR1 CU9 scientific validation
%.AUTHOR        F.A. + CU9 validation group
%.TYPE          text
%.LANGUAGE      LaTeX
%.KEYWORDS      Gaia, DPAC, CU9
%----------------
% to be called after the documentclass definition
\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{xcolor}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%

%\usepackage{pdflscape}
\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{}{,} %% natbib format for A&A and ApJ

\input{macros}

\begin{document} 

   \title{Gaia Data Release 1}

   \subtitle{Catalogue validation 
   }

   \input{authors}

   \date{ }

 
\abstract
  % context heading (optional)
{
Before the publication of the {\gaia} Catalogue, the contents of the first data release have 
undergone multiple dedicated validation tests. 
}
  % aims heading (mandatory)
{
These tests aim at analysing in-depth the Catalogue content to detect anomalies, 
individual problems in specific objects or in overall statistical properties, 
either to filter them before the public release, or to describe the different caveats of the 
release for an optimal exploitation of the data.
}
  % methods heading (mandatory)
{
Dedicated methods using either Gaia internal data, external catalogues or models have been 
developed for the validation processes. 
They are testing normal stars as well as various populations like open or globular 
clusters, double stars, variable stars, quasars. 
Properties of coverage, accuracy and precision of the data are provided by the numerous 
tests presented here and jointly analysed to assess the data release content.
}
  % results heading (mandatory)
{
This independent validation confirms the quality of the published data, {\GDR1} being the 
most precise all-sky astrometric and photometric catalogue to-date. However, several 
limitations in terms of completeness, astrometric and photometric quality are identified
and described. Figures describing the relevant properties of the release are shown
and the testing activities carried out validating the user interfaces are also described. 
A particular emphasis is made on the statistical use of the data in scientific exploitation.
}
  % conclusions heading (optional), leave it empty if necessary 
{}

   \keywords{astrometry --
                parallaxes --
                proper motions --
                methods: data analysis --
                Surveys --
                Catalogs -- 
               }
   
   \titlerunning{Gaia Data Release 1 -- Catalogue validation} 
   \authorrunning{F. Arenou et al.}

   \maketitle

%
%________________________________________________________________

%\textcolor{red}{\Large Article reorganised. Texts missing shown with TODO.}

\input{introduction}

\input{data-and-models}

\input{erroneous-duplicate}

\input{completeness}

\input{angular-resolution}

\input{statistical-methods}

\input{parallax-accuracy}

\input{astrometric-precision}

\input{other-astrometry}

\input{quality-correlations}

\input{photometry}

\input{conclusions}

\input{acknowledgements}

\bibliographystyle{aa} % style aa.bst
\bibliography{dpac,biblio} % your references refs.bib

\appendix
%\input{appendix-models} 

\input{archive-validation}

\input{acronyms}

\input{statistics}

\end{document}
