%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

% Comment this line out if you need a4paper
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  
\documentclass[letterpaper, 10 pt, journal, twoside]{IEEEtran} 

% Use this line for a4 paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      

% This command is only needed if 
% you want to use the \thanks command
\IEEEoverridecommandlockouts                              

% Needed to meet printer requirements.
%\overrideIEEEmargins                                      

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document


%%XXX: Packages
\usepackage[normalem]{ulem}
\usepackage[table,usenames,dvipsnames]{xcolor}
\usepackage{extarrows}
\let\labelindent\relax
\usepackage[inline]{enumitem}
\usepackage{cite}

% Math
\usepackage{amsmath,amssymb,amsfonts,dsfont} % math
\usepackage{mathtools, bm}
\usepackage{algorithm,algorithmicx,listings}
\usepackage[noend]{algpseudocode}

% New command for R
\newcommand{\RR}{\mathbb{R}}

% Figures
\usepackage{graphicx}
\usepackage{tabularx}
%\usepackage{multirow,multicol,rotating,diagbox}
%\usepackage{booktabs}
%\usepackage{makecell}
\usepackage[font={small}]{caption}   %onehalfspacing
\usepackage{subcaption}
%\usepackage[font={small}]{subcaption}
%\setlength{\belowcaptionskip}{-3.5pt}
%\setlength{\abovecaptionskip}{3pt}
\captionsetup[algorithm]{font=small}
\usepackage[breaklinks=true, colorlinks, bookmarks=true, citecolor=Black, urlcolor=Violet,linkcolor=Black]{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%XXX: Commands
\def\liminf{\mathop{\lim\inf}\limits}	% EXAMPLE: \liminf_n A_n
\def\limsup{\mathop{\lim\sup}\limits}	%
\def\argmin{\mathop{\arg\min}\limits}	%
\def\argmax{\mathop{\arg\max}\limits}	%
% Write above and below equal sign
\newcommand{\longeq}[2]{\xlongequal[\!#2\!]{\!#1\!}}
% #1 = top; #2 = bottom; #3 = inequality (<,>,\leq,\geq)
\newcommand{\longineq}[3]{\overset{#1}{\underset{#2}{#3}}}
\newcommand{\indicator}{\mathds{1}}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\per}{\mathbf{per}}
\def\deg{^{\circ}}
\def\negquad{\mkern-18mu}             % negative quad space
\def\negqquad{\mkern-36mu}            % negative qquad space
\newcommand{\txbx}[1]{\boxed{\text{#1}}}
\newcommand{\TODO}[1]{{\color{red}#1}}
\newcommand{\prl}[1]{\mathopen{}\left(#1\right)\mathclose{}}
\newcommand{\brl}[1]{\mathopen{}\left[#1\right]\mathclose{}}
\newcommand{\crl}[1]{\mathopen{}\left\{#1\right\}\mathclose{}}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
%\newtheorem*{assumption*}{Assumption}
\newtheorem{remark}{Remark}
%\newtheorem*{problem*}{Problem}
\newtheorem{problem}{Problem}
\newtheorem{lemma}{Lemma}


\title{
Robust Stereo Visual Inertial Odometry for Fast Autonomous Flight
}


\author{Ke Sun, Kartik Mohta, Bernd Pfrommer, Michael Watterson, Sikang Liu, \\
Yash Mulgaonkar, Camillo J. Taylor, and Vijay Kumar*
\thanks{Manuscript received: September, 10, 2017; Revised December, 1, 2017; Accepted December, 27, 2017. This paper was recommended for publication by Editor Cyrill Stachniss upon evaluation of the Associate Editor and Reviewers' comments. This work was supported in part by DARPA grants HR001151626 and HR0011516850, ARL grant W911NF-08-2-0004, and a NASA Space Technology Research Fellowship awarded to Michael Watterson.}%Use only for final RAL version
\thanks{*The authors are with GRASP Lab, University of Pennsylvania, Philadelphia, PA 19104, USA, {\tt\small\{sunke, kmohta, pfrommer, wami, sikang, yashm, cjtaylor, kumar\}@seas.upenn.edu}.}
\thanks{Digital Object Identifier (DOI): see top of this page.}
}


\begin{document}

\maketitle
%\thispagestyle{empty}
%\pagestyle{empty}
% Paper headers 
\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted December, 2017}
{Sun \MakeLowercase{\textit{et al.}}: Robust Stereo Visual Inertial Odometry for Fast Autonomous Flight}  



\begin{abstract}
In recent years, vision-aided inertial odometry for state estimation has matured significantly. However, we still encounter challenges in terms of improving the computational efficiency and robustness of the underlying algorithms for applications in autonomous flight with micro aerial vehicles in which it is difficult to use high quality sensors and powerful processors because of constraints on size and weight. In this paper, we present a filter-based stereo visual inertial odometry that uses the Multi-State Constraint Kalman Filter (MSCKF)~\cite{mourikis2007multi}. Previous work on stereo visual inertial odometry has resulted in solutions that are computationally expensive. We demonstrate that our Stereo Multi-State Constraint Kalman Filter (S-MSCKF) is comparable to state-of-art monocular solutions in terms of computational cost, while providing significantly greater robustness. We evaluate our S-MSCKF algorithm and compare it with state-of-art methods including OKVIS, ROVIO, and VINS-MONO on both the EuRoC dataset, and our own experimental datasets demonstrating fast autonomous flight with maximum speed of $17.5$m/s in indoor and outdoor environments. Our implementation of the S-MSCKF is available at \url{https://github.com/KumarRobotics/msckf_vio}.
\end{abstract}
\begin{IEEEkeywords}
Localization; Aerial Systems: Perception and Autonomy; SLAM
\end{IEEEkeywords}


\input{tex/Introduction.tex}
\input{tex/RelatedWork.tex}
\input{tex/FilterDescription.tex}
\input{tex/Experiments.tex}
\input{tex/Conclusion.tex}

% This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.
%\addtolength{\textheight}{-12cm}   



\section*{APPENDIX}
\appendices
\input{tex/Appendices}



%\section*{ACKNOWLEDGMENT}

% Bibliography
%==================================================================%
\bibliographystyle{IEEEtran}
\bibliography{ref}
%==================================================================%


\end{document}
