\documentclass[format=acmsmall, review=false, screen=true]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{soul}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


% Metadata Information
\acmJournal{TWEB}
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2017}
\acmMonth{0}
\copyrightyear{2017}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2017}
%\received[revised]{March 2009}
%\received[accepted]{June 2009}

% Document starts
\begin{document}
% Title portion. Note the short title for running heads 
\title[When Simpler Data Does Not Imply Less Information]{When Simpler Data Does Not Imply Less Information: A Study of User Profiling Scenarios with Constrained View of Mobile HTTP(S) Traffic}  
\author{Souneil Park}
%\orcid{1234-5678-9012-3456} 
\affiliation{%
  \institution{Telefonica Research}
  \streetaddress{Torre Telefónica Diagonal 00 Plaza de Ernest Lluch i Martín, 5}
  \city{Barcelona}
%  \state{VA}
  \postcode{08019}
  \country{Spain}}
\author{Aleksandar Matic}
\affiliation{%
  \institution{Telefonica Alpha}
  \streetaddress{Torre Telefónica Diagonal 00 Plaza de Ernest Lluch i Martín 5}
  \city{Barcelona}
%  \state{VA}
  \postcode{08019}
  \country{Spain}}
\author{Kamini Garg}
\affiliation{%
  \institution{University of Applied Sciences and Arts of Southern Switzerland $\dagger$}
  \department{Informatics}
  \city{Lugano}
%  \state{VA}
%  \postcode{08019}
  \country{Switzerland}}
 \author{Nuria Oliver}
\affiliation{%
  \institution{Telefonica Research $\ddagger$}
  \streetaddress{}
  \city{London}
%  \state{VA}
  \postcode{}
  \country{United Kingdom}}
  
\begin{abstract}
The exponential growth in smartphone adoption is contributing to the availability of vast amounts of human behavioral data. This data enables the development of increasingly accurate data-driven user models that facilitate the delivery of personalized services which are often free in exchange for the use of its customers' data. Although such usage conventions have raised many privacy concerns, the increasing value of personal data is motivating diverse entities to aggressively collect and exploit the data. In this paper, we unfold profiling scenarios around mobile HTTP(S) traffic, focusing on those that have limited but meaningful segments of the data. The capability of the scenarios to profile personal information is examined with real user data, collected in-the-wild from 61 mobile phone users for a minimum of 30 days. Our study attempts to model heterogeneous user traits and interests, including personality, boredom proneness, demographics, and shopping interests. Based on our modeling results, we discuss various implications to personalization, privacy, and personal data rights.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Human Computer Interaction ~User Models}

%
% End generated code
%

% We no longer use \terms command
%\terms{Design, Algorithms, Performance}

\keywords{Mobile computing, personalized services, user modeling}

\thanks{
$\dagger$  Work carried out as part of her Ph.D. research. Currently in UPC Switzerland.

$\ddagger$ Currently in Vodafone Research.
}

\maketitle

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Park et al.}

\input{v1_1_introduction}
\input{v1_2_related_work}
\input{v1_3_data_constraints}
\input{v1_4_study_design}
\input{v1_5_feature_ext}
\input{v1_6_data_results}
\input{v1_7_discussion}
\input{v1_8_implications}
\input{v1_9_conclusion_refs}

\end{document}
