\documentclass[12pt, reqno, a4paper]{amsart}
%\documentclass[12pt, reqno, a4paper, draft]{amsart}
\usepackage{amsthm, amsmath, amssymb, amscd,latexsym}
\setlength\topmargin{-4mm}
\setlength\oddsidemargin{0mm}
\setlength\evensidemargin{0mm}
\setlength\textwidth{160mm}
\setlength\textheight{239mm}
\usepackage{enumerate}
\usepackage{latexsym}
\usepackage{graphicx, color}
\def\C{\mathbb C}
\def\Ch{\widehat{\mathbb C}}
\def\D{\mathbb D}
\def\H{\mathbb H}
\def\K{\mathbb K}
\def\N{\mathbb N}
\def\Q{\mathbb Q}
\def\R{\mathbb R}
\def\Z{\mathbb Z}
\def\disp{\displaystyle}
\def\wt{\widetilde}
\def\mod{{\rm mod} \ }
\def\const{{\rm const}}
\def\mod{{\rm mod} \ }
\def\noin{\noindent}
\def\dist{{\rm dist}}
\def\diam{{\rm diam}}
\def\Leb{{\rm Leb}}
\def\Lebh{\widehat{\rm Leb}}
\def\ord{{\rm ord}}
\def\vep{\varepsilon}
\def\exist{{}^\exists}
\def\fall{{}^\forall}
\def\Re{\text{\rm Re }}
\def\pt{\partial}


\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}

\newtheorem*{thmA*}{Theorem A}
\newtheorem*{thmA'*}{Theorem A'}
\newtheorem*{corA'*}{Corollary A'}
\newtheorem*{thmB*}{Theorem B}
\newtheorem*{thmC*}{Theorem C}
\newtheorem*{corC*}{Corollary C}
\newtheorem*{corD*}{Corollary D}
\newtheorem*{thmD*}{Theorem D}
\newtheorem*{thmE*}{Theorem E}
\newtheorem*{thmF*}{Theorem F}
\newtheorem*{conj*}{Conjecture}
\newtheorem*{thm*}{Theorem}

\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\newtheorem{rem}[thm]{Remark}
\newtheorem{notn}[thm]{Notation}
\newtheorem{ex}[thm]{Example}
\newtheorem{Assumption}[thm]{Assumption}
\newtheorem{Problem}[thm]{Problem}
\newtheorem{Convention}[thm]{Convention}
\newtheorem{Question*}[thm]{Question}
\newtheorem*{defn*}{Definition}
\newtheorem*{rem*}{Remark}


\makeatletter
\@addtoreset{equation}{section} \def\theequation{\thesection.\arabic{equation}}
\makeatother


%
%----------------------------------------
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\Bar}{\overline}
%----------------------------parenthesis
%|A|
\newcommand{\norm}[1]{{\left\| #1 \right\|}}
%||A||
\newcommand{\abs}[1]{{\left| #1 \right|}}
%(A)
\newcommand{\kakko}[1]{{\left( #1 \right)}}
\newcommand{\paren}[1]{{\left( #1 \right)}}
%{A}
\newcommand{\skakko}[1]{{\left\{ #1 \right\}}}
\newcommand{\braces}[1]{{\left\{ #1 \right\}}}
%----------------------------------------
\newcommand{\al}{\alpha}
\newcommand{\e}{\varepsilon}
\newcommand{\lam}{\lambda}
\newcommand{\cM}{{\mathcal{M}}}
\newcommand{\cN}{{\mathcal{N}}}
\newcommand{\cK}{{\mathcal{K}}}
\newcommand{\cc}{\circ}
\newcommand{\st}{\ | \ }
\newcommand{\QED}{\hfill $\blacksquare$}
\renewcommand{\Im}{{\mathrm{Im}\,}}
\newcommand{\sminus}{\smallsetminus}
\newcommand{\sig}{\sigma}
%----------------------------------------


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\parindent=5mm
\baselineskip=15pt
\parskip=3pt




\title{Julia sets appear quasiconformally in the Mandelbrot set}


\author{Tomoki Kawahira and Masashi Kisaka}
\setcounter{footnote}{-1}
\thanks{
2020 {\it Mathematics Subject Classification.} Primary 37F46;
Secondary 37F25, 37F31.
\\
\hskip 5truemm 
{\it Key words and phrases.} quadratic family, Mandelbrot-like family.
}

\address{
Graduate School of Economics\\
Hitotsubashi University\\
Tokyo 186-8601 \\
Japan}
\email{t.kawahira@r.hit-u.ac.jp}

\address{
Department of Mathematical Sciences \\
Graduate School of Human and Environmental Studies \\
Kyoto University \\
Kyoto 606-8501 \\
Japan }
\email{kisaka@math.h.kyoto-u.ac.jp}
%\keywords{complex dynamics, quadratic family, Mandelbrot set, Julia set, 
%Mandelbrot-like family, quasiconformal map}
%\subjclass{Primary 58F23; Secondary 30D05}
%\subjclass[2010]{Primary: 30D05, 37F10, 37F31; Secondary: 30D20}






\begin{abstract}
In this paper we prove the following: 
Take any \lq\lq small Mandelbrot set" and zoom in a neighborhood of a
parabolic or Misiurewicz parameter in it, then we can see a quasiconformal
image of a Cantor Julia set which is a perturbation of a  parabolic
or Misiurewicz Julia set. Furthermore,  zoom in its middle part, then we can
see a certain nested structure (\lq\lq decoration") and finally another 
\lq\lq smaller Mandelbrot set" appears. A similar nested 
structure exists in the Julia set for any parameter in the \lq\lq smaller 
Mandelbrot set". We can also find images of a Julia sets by quasiconformal
maps with dilatation arbitrarily close to 1. This answers a question by
Adrian Douady. All the parameters belonging to 
these images are semihyperbolic and this leads to the fact that the set of
semihyperbolic but non-Misiurewicz and non-hyperbolic parameters is dense 
with Hausdorff dimension 2 in the boundary of the Mandelbrot set.




\end{abstract}

\maketitle



\input{20211218_1-5_arXiv_v2.tex}
\input{20211218_6-8_arXiv_v2.tex}
\input{20211218_9-10_arXiv_v2.tex}







\begin{thebibliography}{99}

\parskip=3pt

\bibitem[{\bf A}]{Ahlfors 1978}
L.V.~Ahlfors, 
{\it Complex Analysis, third ed.},
McGraw-Hill Book Co., New York, 1978.

\bibitem[\bf B\rm]{Beardon 1991}
A.F.~Beardon, \it
Iteration of Rational Functions\rm, 
Springer Verlag, New York, Berlin and Heidelberg, 1991.


\bibitem[\bf BH\rm]{Buff-Henriksen 2001}
X.~Buff and C.~Henriksen, Julia sets in parameter spaces, \it 
Comm. Math. Phys. \rm {\bf 220} (2001), no. 2, 333--375.


\bibitem[\bf BR\rm]{Bers-Royden 1986} 
L.~Bers and H.L.~Royden,
Holomorphic families of injections, 
{\it Acta Math.} {\bf 157} (1986), 259--286.




\bibitem[\bf CJY\rm]{Carleson-Jones-Yoccoz 1994}
L.~Carleson, P.W.~Jones and J.-C.~Yoccoz, 
Julia and John, \it
Bol. Soc. Brasil. Mat. (N.S.) {\bf 25} \rm (1994), no. 1, 1--30. 




\bibitem[\bf CRY\rm]{Cornell-Rojas-Yampolsky 2017}
D.~Cornell, C.~Rojas and M.~Yampolsky, 
Non computable Mandelbrot-like set for a one-parameter complex family, \it
%\verb|arXiv:1703.04668|, 2017.
Inform. and Comput. {\bf 262} \rm (2018), part 1, 110--122. 


\bibitem[\bf CT\rm]{Cui-Tan 2018}
G.~Cui and L.~Tan, 
Hyperbolic-parabolic deformations of rational maps, \it
Science China Math. {\bf 61} \rm (2018) 2157--2220.


\bibitem[{\bf D}]{D 1983} 
P.L. Duren,
{\it Univalent Functions}, 
Springer-Verlag, 1983.


\bibitem[\bf D-BDS\rm]{Douady 2000}
A. Douady, X. Buff, R. Devaney and P. Sentenac, 
Baby Mandelbrot sets are born in cauliflowers, 
in\it \ The Mandelbrot set, theme and variations\rm, London Math. Soc. Lecture 
Note Ser. {\bf 274}, Cambridge Univ. Press, Cambridge (2000), 19--36.


\bibitem[{\bf DH1}]{DH Orsay}
A. Douady and J. H. Hubbard, 
Etude dynamique des polyn\^omes complexes I \& II, 
{\it Publ. Math. Orsay, Universit\'e de Paris-Sud}, 
D\'epartement de Math\'ematiques, Orsay, 
1984/85, 84-2, 85-4.


\bibitem[\bf DH2\rm]{Douady-Hubbard 1985}
A. Douady and J. Hubbard, 
On the dynamics of polynomial-like mappings, \it
Ann. Sci. \'Ecole Norm. Sup. \rm {\bf 18} (1985), 287--343.


\bibitem[{\bf DSZ}]{DSZ 1997} 
A. Douady, P. Sentenac and M. Zinsmeister,
Implosion parabolique et dimension de Hausdorff,
{\it Compte Rendu Acad. Sci., S\'er I}, 
{\bf 325} (1997), 765--772.


\bibitem[{\bf G}]{Gaidashev 2007}
D.~Gaidashev, 
Cylinder renormalization for Siegel discs and 
a constructive measurable Riemann mapping theorem, 
{\it Nonlinearity} {\bf 20} (2007), 713--741.


\bibitem[\bf H\rm]{Haissinsky 2000}
P. Ha\"{\i}ssinsky, 
Modulation dans l'ensemble de Mandelbrot, 
in\it \ The Mandelbrot set, theme and variations\rm, London Math. Soc. Lecture 
Note Ser. {\bf 274}, Cambridge Univ. Press, Cambridge (2000), 37--66.


\bibitem[{\bf IT}]{IT Book}
Y. Imayoshi and M. Taniguchi, 
{\it An Introduction to Teichm\" uller Spaces}. 
Springer, 1992.


\bibitem[{\bf J}]{Jung 2015}
W. Jung, personal communication, 2015. See 
\verb|http://www.mndynamics.com/indexp.html| (his web page)
and also
\verb|http://www.mrob.com/pub/muency/embeddedjuliaset.html|.


\bibitem[{\bf K1}]{Kawahira 2009} 
T.~Kawahira, 
Tessellation and Lyubich-Minsky laminations 
associated with quadratic maps, I: pinching semiconjugacies, 
{\it Ergod. Th. \& Dynam. Sys.} {\bf 29} (2009), 
579--612.


\bibitem[{\bf K2}]{Kawahira 2014} 
T.~Kawahira, 
Quatre applications du lemme de Zalcman \`a la dynamique complexe, 
{\it J. Anal. Math.} {\bf 124} (2014), 309--336.


\bibitem[{\bf La}]{Lavaurs 1989} 
P.~Lavaurs, 
Syst\`emes dynamiques holomorphes, 
explosion de points p\'eriodiques paraboliques,
{\it Th\`ese de doctorat}, Universit\'e Paris-Sud in Orsay, 1989.


\bibitem[{\bf Ly1}]{Lyubich 1991} 
M. Lyubich, 
On the Lebesgue measure of the Julia set of a quadratic
polynomial, {\it Preprint} IMS at Stony Brook, \#1991/10.



\bibitem[{\bf Ly2}]{Lyubich 1999} 
M. Lyubich, 
Feigenbaum-Coullet-Tresser universality and Milnor's hairiness conjecture,
{\it Ann. of Math.} (2) {\bf 149} (1999), no. 2, 319--420.


\bibitem[{\bf Ly3}]{Lyubich Book}
M. Lyubich,
{\it 
Conformal Geometry and Dynamics of Quadratic Polynomials, vol I--II.
} Available in his web page 
(\verb|http://www.math.stonybrook.edu/~mlyubich/book.pdf|).



\bibitem[{\bf LyMin}]{Lyubich-Minsky 1997}
M.~Lyubich and Y.~Minsky, Laminations in holomorphic dynamics,
{\it J. Differential Geom.} {\bf 47} (1997), no. 1, 17--94. 






\bibitem[{\bf Ma}]{Mane 1993}
R. Ma\~n\'e, 
On a theorem of Fatou, \it
Bol. Soc. Brasil. Mat. (N.S.) \bf 24 \rm No.1 (1993), 1--11.





\bibitem[{\bf Mc1}]{McMullen 1994}
C.T. McMullen, \it
Renormalization and complex dynamics\rm, 
Ann. of Math. Studies {\bf 135}, Princeton Univ. Press, 1994. 



\bibitem[{\bf Mc2}]{McMullen 2000}
C.T. McMullen, 
The Mandelbrot set is universal, 
in\it \ The Mandelbrot set, theme and variations\rm, London Math. Soc. 
Lecture Note Ser. {\bf 274}, Cambridge Univ. Press, Cambridge (2000), 
1--17.


\bibitem[\bf Mil1\rm]{Milnor 2000}
J. Milnor, 
Periodic orbits, externals rays and the Mandelbrot set: an expository account, 
\it G\'eom\'etrie complexe et syst\`emes dynamiques \rm(Orsay, 1995), 
Ast\'erisque \bf 261 \rm (2000), xiii, 277--333.


\bibitem[\bf Mil2\rm]{Milnor 2006}
J. Milnor, \it
Dynamics in one complex variable, third ed.\rm, 
Annals of Mathematics Studies, vol. {\bf 160}, Princeton University Press,
Princeton, NJ, 2006.


\bibitem[\bf MNTU\rm]{MNTU 2000}
S. Morosawa, Y. Nishimura, M. Taniguchi and T. Ueda, \it 
Holomorphic dynamics, \rm Translated from the 1995 Japanese original 
and revised by the authors. Cambridge Studies in Advanced Mathematics 
{\bf 66}, Cambridge University Press, Cambridge, 2000.


\bibitem[\bf MTU\rm]{MTU 1995}
S. Morosawa, M. Taniguchi and T. Ueda, 
\it Holomorphic dynamics \rm (in Japanese), 
Baifuukan (publisher), 1995.


\bibitem[{\bf PS}]{Peitgen-Saupe 1988} 
H.-O.~Peitgen and D.~Saupe (eds.), 
\it The science of fractal images\rm, 
Springer-Verlag, New York, 1988.



\bibitem[{\bf Ric}]{Rickman 1969} 
S.~Rickmann,
Removability theorems for quasiconformal mappings, 
{\it Ann. Acad. Sci. Fenn. } {\bf 449} (1969), 
1--8.

\bibitem[\bf Riv\rm]{Rivera-Letelier 2001}
J. Rivera-Letelier, On the continuity of Hausdorff dimension of Julia sets and 
similarity between the Mandelbrot set and Julia sets, \it Fund. Math. \rm 
{\bf 170} (2001), no. 3, 287--317.


\bibitem[\bf S\rm]{Shishikura 1998}
M. Shishikura, 
The Hausdorff dimension of the boundary of the Mandelbrot set and Julia sets,
\it Ann. of Math. \rm (2) {\bf 147} (1998), no. 2, 225--267.


\bibitem[{\bf S\l}]{Slodkowski 1991}
Z. S\l odkowski, 
{\rm Holomorphic motions and polynomial hulls}, \it
Proc. Amer. Math. Soc. {\bf 111} \rm (2) (1991), 347--355.


\bibitem[\bf T1\rm]{Tan Lei 1990}
%Tan~L., 
L. Tan, 
Similarity between the Mandelbrot set and Julia sets, 
\it Comm. Math. Phys. 
{\bf 134} \rm (1990), no. 3, 587--617.


\bibitem[{\bf T2}]{Tan Lei 2000} 
%Tan~L., 
L. Tan, 
Local properties of the Mandelbrot set at parabolic points,
in\it \ The Mandelbrot set, theme and variations\rm, London Math. Soc. Lecture 
Note Ser. {\bf 274}, Cambridge Univ. Press, Cambridge (2000), 133--160.


\end{thebibliography}



\end{document}
