

%
\section{Related Surveys}
\label{exis_surveys}
In this section we mention the existing surveys relevant to SDN and WLAN.


A comprehensive study of software-defined wireless cellular, sensor, mesh, and home networks is presented in \cite{wSDN1}. 
This work classifies the existing contributions based on their objective and architecture.
%
A survey of data plane and control plane programmability approaches is given in \cite{macedo2015programmable}, where the authors review the components of programmable wired and wireless networks, as well as control plane architectures and virtualization tools.
%
\cite{richart2016resource} presents a survey of virtualization and its challenges in wireless networks. 
%This paper reviews resource allocation and isolation as the two main challenges of virtualization.
%
A survey of OpenFlow concepts, abstractions and its potential applications in wired and wireless networks is given in \cite{hu2014survey}.
\cite{NextGen-WiFi-Survey-2016} and \cite{NGwlans-survey-2016} review the 802.11 standards for high-throughput applications, TV white spaces and machine-to-machine communications. 
\cite{S1-energy-MAC} surveys energy-efficient MAC protocols for WLANs.
A survey of cellular to WLAN offloading mechanisms is given in \cite{Offloading-survey-2016}.

Channel assignment strategies are reviewed in \cite{Channel-assignment-survey-2010}, and the dynamics of channel assignment in dense WLANS are investigated in \cite{S9-Channel}. 
QoS support in dense WLANs through layer-1 and layer-2 protocols are surveyed in \cite{S2-QoS,S3-QoS,S4-QoS}. 
Client-based association mechanisms and AP placement strategies are surveyed in \cite{Association-DenseWLANs-2014}.
Distributed load-balancing mechanisms are reviewed in \cite{S5-LB}.
%
\cite{S6-Intf} provides a survey on spectrum occupancy measurement techniques in order to generate interference maps in WLANs. 
In \cite{S7-ax}, the future demands of WLANs and the potential new features of ongoing 802.11ax standard are investigated and reviewed. 
A review of wireless virtualization mechanisms is given in \cite{liang2015wireless}.
This work also presents the business models, enabling technologies, and performance metrics of wireless virtual networks.
%
%\cite{claise2012overview} presents a review of network management standards, including CAPWAP, SNMP and Netconf.
%

Our review of existing surveys shows that there is no study of WLANs from a SDN point of view.
Therefore, the main motivation for conducting this study was the lack of a comprehensive survey on SDWLAN architectures and essential centralized network control mechanisms. 

%To the best of our knowledge, this is the first effort on reviewing, investigating and qualitative comparison of existing SDWLAN architectures and centralized network control mechanisms.
%
