\section{Conclusions and Future Work}
\label{sec:conclu}

In this paper, we propose a learning framework based on deep matching networks to leverage external knowledge for response ranking in information-seeking conversation systems. We incorporate external knowledge into deep neural models with pseudo-relevance feedback and QA correspondence knowledge distillation. Extensive experiments %with information-seeking conversation data sets including both 
on both open benchmarks and commercial data show our methods outperform various baselines including the state-of-the-art methods. %on response selection in multi-turn conversations. 
We also perform analysis on different response types and model variations to provide insights on model applications. For future work, we plan to model user intent in information-seeking conversations and learn meaningful patterns from user intent dynamics to help response selection. Incorporating both structured and unstructured knowledge into deep matching networks for response ranking is also interesting to explore. %an interesting direction to explore. % in conversations.

%\ylcomment{Try to finish a complete version soon before 22:00 pm,  01/24 and send the draft to JF/Bruce for comments and revising.}

\section{Acknowledgments}
This work was supported in part by the Center for Intelligent Information Retrieval and in part by NSF grant \#IIS-1419693. Any opinions, findings and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect those of the sponsor.




