

\documentclass[11pt,a4paper]{article}
\usepackage{times,latexsym}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage[acceptedWithA]{tacl2021v1}


\input{math_commands.tex}
\usepackage{times}
\usepackage{xspace,mfirstuc,tabulary}
\usepackage{latexsym}
\usepackage{linguex}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow, makecell}
\usepackage{color, colortbl}
\renewcommand{\UrlFont}{\ttfamily}
\usepackage{etoolbox}
\usepackage{numprint}
\patchcmd{\quote}{\rightmargin}{\leftmargin 1em \rightmargin}{}{}
\usepackage{multirow}
\usepackage{microtype}
\usepackage{tikz}
\usepackage{amssymb}
\usepackage{mdframed}
\usepackage{cuted}
\usepackage{subfigure}


\definecolor{gray}{rgb}{.95, .95, .95}
\definecolor{highlight}{rgb}{1.0, 1.0, 0.89}
\definecolor{aquamarine}{rgb}{0.5, 1.0, 0.83}
\definecolor{asparagus}{rgb}{0.53, 0.66, 0.42}
\definecolor{emerald}{rgb}{0.31, 0.78, 0.47}
\definecolor{gainsboro}{rgb}{0.86, 0.86, 0.86}
\definecolor{gold(web)(golden)}{rgb}{1.0, 0.84, 0.0}

\theoremstyle{remark}
\newtheorem{remark}{\textbf{Observation}}


\newcommand{\CTRL}{\textsc{CTRL-Dialog}}

\newcommand{\note}[1]{{#1}}
\newcommand{\nouha}[1]{\textcolor{red}{Nouha: #1}}
\newcommand{\hannah}[1]{\textcolor{blue}{Hannah: #1}}

\newcommand{\BEGIN}{\textsc{Begin}}
\newcommand{\begindata}{\BEGIN}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\title{Evaluating Attribution in Dialogue Systems: The BEGIN Benchmark
}
 \author{
  Nouha Dziri\hspace*{.4mm}\Thanks{Equal Contribution.}\hspace*{.4mm}\ \Thanks{Work done while at Google Research.}\hspace*{.2mm} $^{\diamondsuit}$ \quad Hannah Rashkin$^{*\hspace*{.1mm}\S}$ \quad Tal Linzen$^{\S\hspace*{.15mm}\clubsuit}$ \quad David Reitter$^\S$
   \\
  $^\diamondsuit$University of Alberta, Canada \quad $^\S$Google Research, USA \quad $^\clubsuit$New York University, USA  \\
  \texttt{dziri@cs.ualberta.ca} \quad
  { \tt \{hrashkin,linzen,reitter\}@google.com} 
 }

\date{}

\begin{document}

\setlength{\textfloatsep}{10pt plus 2.0pt minus 4.0pt}

\setlength{\Extopsep}{0.2\baselineskip}
\setlength{\Exredux}{0\baselineskip}
\setlength{\Exlabelwidth}{1em}%



\maketitle
\begin{abstract}
Knowledge-grounded dialogue systems powered by large language models often generate responses that, while fluent, are not \textit{attributable} to a relevant source of information. Progress towards models that do not exhibit this issue requires evaluation metrics that can quantify its prevalence. To this end, we introduce the Benchmark for Evaluation of Grounded INteraction (\begindata), comprised of 12k dialogue turns generated by neural dialogue systems trained on three knowledge-grounded dialogue corpora. We collect human annotations assessing the extent to which the models' responses can be attributed to the given background information. We then use \begindata\ to analyze eight evaluation metrics. We find that these metrics rely on spurious correlations, do not reliably distinguish attributable abstractive responses from unattributable ones, and perform substantially worse when the knowledge source is longer. Our findings underscore the need for more sophisticated and robust evaluation metrics for knowledge-grounded dialogue. We make \begindata \ publicly available at \url{https://github.com/google/BEGIN-dataset}. 






\end{abstract}






\input{1_introduction}
\input{2_setup}
\input{4_begin}
\input{5_experiments}
\input{6_related_work}
\input{7_conclusion}
\input{8_appendix}
\clearpage









    
\bibliography{grounded_dialog_metric,anthology}
\bibliographystyle{acl_natbib}



\end{document}
