\begin{abstract}
Deep learning powered object detection method is the key of environment perception for autonomous driving and smart traffic in Cooperative Intelligent Transportation Systems (C-ITS). 
However, the performance of the detection is strongly dependent on the data volume in model training, which is usually not sufficient due to the limited data collected by specific testing vehicles. 
Meanwhile, all intelligent traffic participants can generate a large number of data timely, which can not be used directly, because of privacy issue.
In this paper, we introduce a two-tier federated learning framework, which can notable enhance OEM pre-trained deep learning model by exploiting data from connected public traffic agents in vehicular networks without affecting the user data privacy. 
Through coordinating existing traffic infrastructure, including roadside units and traffic cloud, the model parameters are disseminated by V2X communication and aggregated hierarchically.
With consideration of individual heterogeneity of data distribution and computation ability across traffic agents, we employ a novel method that addresses the fairness problem in different layers of framework architecture, i.e. traffic agent- and roadside unit layer.
Finally, We show the model enhancement in real traffic scenarios by running deep learning methods in federated fashion and demonstrate our proposal of federated object detection in with traffic image data. The simulation results show that the perception accuracy is on average improved by around \Crs{xx\%} with \Crs{xx\%} less communication time.
\end{abstract}

%\begin{IEEEkeywords}
%federated learning, deep learning model enhancement, cooperative intelligent transportation system, traffic object detection, image processing
%\end{IEEEkeywords}