\begin{abstract}

Deep learning is a key approach for object detection in the environment perception function of Cooperative Intelligent Transportation Systems (C-ITS) with autonomous vehicles and a smart traffic infrastructure. %
The performance of the object detection strongly depends on the data volume in the model training, which is usually not sufficient due to the limited data collected by a typically small fleet of test vehicles. %
In today's C-ITS, smart traffic participants are capable to timely generate and transmit a large amount of data. However, these data can not be used for model training directly due to privacy constraints. %
In this paper, we introduce a Hierarchical Heterogeneity-tolerated federated learning (HHt-Fed) framework, which can notably enhance the conventional %OEM 
pre-trained deep learning model. The framework exploits data from connected public traffic agents in vehicular networks without affecting the user data privacy. 
Through coordinating existing traffic infrastructure, including roadside units and traffic clouds, the model parameters are efficiently disseminated by vehicular communications and hierarchically aggregated.
Considering the individual heterogeneity of data distribution, computational capabilities across traffic agents, we employ a novel method that addresses the fairness problem at different layers of the framework architecture, i.e., the traffic agent layer and the roadside unit layer.
Finally, we show the model enhancement in real traffic scenarios by running deep learning methods in a federated fashion and demonstrate our proposal of federated object detection with traffic image data. The simulation results show that the perception accuracy is improved on average by around \Crs{xx\%} after only \Crs{xx} communication rounds.
\end{abstract}

\begin{IEEEkeywords}
federated learning, deep learning model enhancement, cooperative intelligent transportation system, traffic object detection, image processing
\end{IEEEkeywords}