%---------------------------------------------------------------------------------------------------------------
% documentclass
%---------------------------------------------------------------------------------------------------------------
\documentclass[10pt,twocolumn,romanappendices,final]{IEEEtran}
\pdfoutput=0

%---------------------------------------------------------------------------------------------------------------
% style packages
%---------------------------------------------------------------------------------------------------------------
\usepackage{styles/rnd_fields_cs}

%---------------------------------------------------------------------------------------------------------------
% file with bibliography
%---------------------------------------------------------------------------------------------------------------
%\addbibresource{../cs_us_imaging/cs_us_imaging.bib}

%---------------------------------------------------------------------------------------------------------------
% list of symbols and acronyms
%---------------------------------------------------------------------------------------------------------------
\input{0_acronyms.tex}
\acresetall

%---------------------------------------------------------------------------------------------------------------
% opening
%---------------------------------------------------------------------------------------------------------------
\title{Random Incident Waves for Fast Compressed Pulse-Echo Ultrasound Imaging}
\author{%
Martin~F.~Schiffner%
\thanks{M.~F.~Schiffner is with the Lehrstuhl für Medizintechnik, Ruhr-Universität Bochum, D-44801 Bochum, Germany (e-mail: martin.schiffner@rub.de).}%
}

% highlight bad boxes
\overfullrule=1mm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% abstract: less than 200 words and index terms
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  \boldmath
  \input{abstract.tex}
\end{abstract}
\acresetall

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% keywords
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{IEEEkeywords}
  random incident waves,
  inverse scattering,
  compressed sensing,
  sparse regularization,
  ultrafast ultrasound imaging,
  computational ultrasound imaging,
  fast multipole method,
  \acs{GPU} computing
\end{IEEEkeywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 1.) introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}
\input{introduction/introduction.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2.) compressed sensing in a nutshell
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compressed Sensing in a Nutshell}
\label{sec:compressed_sensing}
\input{compressed_sensing/compressed_sensing.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3.) linear physical model for the pulse-echo measurement process
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Linear Physical Model for the Pulse-Echo Measurement Process}
\label{sec:linear_model}
\input{linear_model/linear_model.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4.) syntheses of the incident waves
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Syntheses of the Incident Waves}
\label{sec:syn_p_in}
\input{syntheses_incident_waves/syntheses_incident_waves.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5.) image recovery based on compressed sensing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Image Recovery Based on Compressed Sensing}
\label{sec:recovery}
\input{recovery/recovery.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 6.) implementation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}
\label{sec:implementation}
\input{implementation/implementation.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 7.) simulation study
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation Study}
\label{sec:simulation_study}
\input{simulation_study/simulation_study.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 8.) experimental validation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Experimental Validation}
%\label{sec:experimental_validation}
%\input{experimental_validation/experimental_validation.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 9.) results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
\input{results/results.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 10.) discussion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}
\input{discussion/discussion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 11.) conclusion and outlook
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Outlook}
\label{sec:conclusion_outlook}
\input{conclusion/conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% acknowledgment
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgment}
\input{acknowledgment.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% appendices
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendices
%\appendix

%---------------------------------------------------------------------------------------------------------------
% Appendix A: The EBVP for the Helmholtz Equation, Green's Functions, and Their Angular Spectra
%---------------------------------------------------------------------------------------------------------------
\section{}
\label{app:helmholtz_green}
\input{appendix/app_helmholtz_green.tex}

%textwidth: \the\textwidth\par
%columnwidth: \the\columnwidth

%---------------------------------------------------------------------------------------------------------------
% Appendix B: adjoint sensing matrix
%---------------------------------------------------------------------------------------------------------------
\section{}
\label{app:adjoint}
\input{appendix/app_adjoint.tex}

% include bibliography
\bibliographystyle{ieeetr}
\begin{thebibliography}{100}

\bibitem{book:Szabo2013}
T.~L. Szabo.
\newblock {\em Diagnostic Ultrasound Imaging: Inside Out}.
\newblock Elsevier Academic Press, 2nd edition, Dec. 2013.

\bibitem{article:BierigJDMS2009}
S.~M. Bierig and A.~Jones.
\newblock Accuracy and cost comparison of ultrasound versus alternative imaging
  modalities, including {CT}, {MR}, {PET}, and angiography.
\newblock {\em J. Diagn. Med. Sonog.}, 25(3):138--144, May 2009.

\bibitem{book:Bushberg2011}
J.~T. Bushberg, J.~A. Seibert, E.~M. {Leidholdt Jr.}, and J.~M. Boone.
\newblock {\em The Essential Physics of Medical Imaging}.
\newblock Lippincott Williams \& Wilkins, 3rd (north america) edition, Dec.
  2011.

\bibitem{article:JensenProgBMB2007}
J.~A. Jensen.
\newblock Medical ultrasound imaging.
\newblock {\em Prog. Biophys. Mol. Bio.}, 93(1--3):153--165, Jan.--Apr. 2007.

\bibitem{article:WellsPMB2006}
P.~N.~T. Wells.
\newblock Ultrasound imaging.
\newblock {\em Phys. Med. Biol.}, 51(13):R83--R98, Jul. 2006.

\bibitem{article:MontaldoITUFFC2009}
G.~Montaldo, M.~Tanter, J.~Bercoff, N.~Benech, and M.~Fink.
\newblock Coherent plane-wave compounding for very high frame rate
  ultrasonography and transient elastography.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  56(3):489--506, Mar. 2009.

\bibitem{article:MoghimiradITUFFC2016}
E.~Moghimirad, C.~A. {Villagómez Hoyos}, A.~Mahloojifar, B.~{Mohammadzadeh
  Asl}, and J.~A. Jensen.
\newblock Synthetic aperture ultrasound {F}ourier beamformation using virtual
  sources.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  63(12):2018--2030, Dec. 2016.

\bibitem{article:JensenUlt2006}
J.~A. Jensen, S.~I. Nikolov, K.~L. Gammelmark, and M.~H. Pedersen.
\newblock Synthetic aperture ultrasound imaging.
\newblock {\em Ultrasonics}, 44, Supplement:e5--e15, Dec. 2006.

\bibitem{article:ChengITUFFC2006}
J.~Cheng and J.~y.~Lu.
\newblock Extended high-frame rate imaging method with limited-diffraction
  beams.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  53(5):880--899, May 2006.

\bibitem{article:LuITUFFC1997}
J.~y.~Lu.
\newblock {2D} and {3D} high frame rate imaging with limited diffraction beams.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  44(4):839--856, Jul. 1997.

\bibitem{article:TanterITUFFC2014}
M.~Tanter and M.~Fink.
\newblock Ultrafast imaging in biomedical ultrasound.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  61(1):102--119, Jan. 2014.

\bibitem{article:BercoffITUFFC2004}
J.~Bercoff, M.~Tanter, and M.~Fink.
\newblock Supersonic shear imaging: {A} new technique for soft tissue
  elasticity mapping.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  51(4):396--409, Apr. 2004.

\bibitem{article:BercoffITUFFC2011}
J.~Bercoff, G.~Montaldo, T.~Loupas, D.~Savery, F.~Meziere, M.~Fink, and
  M.~Tanter.
\newblock Ultrafast compound {D}oppler imaging: {P}roviding full blood flow
  characterization.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  58(1):134--147, Jan. 2011.

\bibitem{article:PapadacciITUFFC2014}
C.~Papadacci, M.~Pernot, M.~Couade, M.~Fink, and M.~Tanter.
\newblock High-contrast ultrafast imaging of the heart.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  61(2):288--301, Feb. 2014.

\bibitem{article:MaceITUFFC2013}
E.~Mace, G.~Montaldo, B.~Osmanski, I.~Cohen, M.~Fink, and M.~Tanter.
\newblock Functional ultrasound imaging of the brain: {T}heory and basic
  principles.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  60(3):492--506, Mar. 2013.

\bibitem{article:ProvostPMB2014}
J.~Provost, C.~Papadacci, J.~E. Arango, M.~Imbault, M.~Fink, J.-L. Gennisson,
  M.~Tanter, and M.~Pernot.
\newblock {3D} ultrafast ultrasound imaging in vivo.
\newblock {\em Phys. Med. Biol.}, 59(19):L1--L13, Oct. 2014.

\bibitem{article:GarciaITUFFC2013}
D.~Garcia, L.~L. Tarnec, S.~Muth, E.~Montagnon, J.~Porée, and G.~Cloutier.
\newblock {S}tolt's {$f$}-{$k$} migration for plane wave ultrasound imaging.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  60(9):1853--1867, Sep. 2013.

\bibitem{article:ZhangITUFFC2016}
M.~Zhang, F.~Varray, A.~Besson, R.~E. Carrillo, M.~Viallon, D.~Garcia, J.-P.
  Thiran, D.~Friboulet, H.~Liebgott, and O.~Bernard.
\newblock Extension of {F}ourier-based techniques for ultrafast imaging in
  ultrasound with diverging waves.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  63(12):2125--2137, Dec. 2016.

\bibitem{article:KruizingaITUFFC2012}
P.~Kruizinga, F.~Mastik, N.~de~Jong, A.~F.~W. van~der Steen, and G.~van Soest.
\newblock Plane-wave ultrasound beamforming using a nonuniform fast {F}ourier
  transform.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  59(12):2684--2691, Dec. 2012.

\bibitem{proc:SchiffnerAI2012}
M.~F. Schiffner and G.~Schmitz.
\newblock Plane wave pulse-echo ultrasound diffraction tomography with a fixed
  linear transducer array.
\newblock In A.~Nowicki, J.~Litniewski, and T.~Kujawska, editors, {\em Acoust.
  Imaging}, volume~31 of {\em Acoust. Imaging}, pages 19--30. Springer
  Netherlands, 2012.

\bibitem{book:Devaney2012}
A.~J. Devaney.
\newblock {\em Mathematical Foundations of Imaging, Tomography and Wavefield
  Inversion}.
\newblock Cambridge University Press, 1st edition, Jul. 2012.

\bibitem{book:Natterer2001}
F.~Natterer and F.~Wübbeling.
\newblock {\em Mathematical Methods in Image Reconstruction}.
\newblock Mathematical Modeling and Computation. Society for Industrial and
  Applied Mathematics (SIAM), 2001.

\bibitem{book:Kak2001}
A.~C. Kak and M.~Slaney.
\newblock {\em Principles of Computerized Tomographic Imaging}.
\newblock Classics in Applied Mathematics. Society for Industrial and Applied
  Mathematics (SIAM), 2001.

\bibitem{article:OzkanITUFFC2018}
E.~Ozkan, V.~Vishnevsky, and O.~Goksel.
\newblock Inverse problem of ultrasound beamforming with sparsity constraints
  and regularization.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  65(3):356--365, Mar. 2018.

\bibitem{article:BessonITUFFC2018}
A.~Besson, D.~Perdios, F.~Martinez, Z.~Chen, R.~E. Carrillo, M.~Arditi,
  Y.~Wiaux, and J.-P. Thiran.
\newblock Ultrafast ultrasound imaging as an inverse problem: {M}atrix-free
  sparse image reconstruction.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  65(3):339--355, Mar. 2018.

\bibitem{article:BerthonPMB2018}
B.~Berthon, P.~Morichau-Beauchant, J.~Porée, A.~Garofalakis, B.~Tavitian,
  M.~Tanter, and J.~Provost.
\newblock Spatiotemporal matrix image formation for programmable ultrasound
  scanners.
\newblock {\em Phys. Med. Biol.}, 63(3):03NT03, Feb. 2018.

\bibitem{article:BessonITUFFC2016}
A.~Besson, M.~Zhang, F.~Varray, H.~Liebgott, D.~Friboulet, Y.~Wiaux, J.-P.
  Thiran, R.~E. Carrillo, and O.~Bernard.
\newblock A sparse reconstruction framework for {F}ourier-based plane-wave
  imaging.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  63(12):2092--2106, Dec. 2016.

\bibitem{article:DavidJASA2015}
G.~David, J.~l.~Robert, B.~Zhang, and A.~F. Laine.
\newblock Time domain compressive beam forming of ultrasound signals.
\newblock {\em J. Acoust. Soc. Am.}, 137(5):2773--2784, May 2015.

\bibitem{article:ZhangUlt2013}
Q.~Zhang, B.~Li, and M.~Shen.
\newblock A measurement-domain adaptive beamforming approach for ultrasound
  instrument based on distributed compressed sensing: {I}nitial development.
\newblock {\em Ultrasonics}, 53(1):255--264, Jan. 2013.

\bibitem{proc:SchiffnerIUS2013a}
M.~F. Schiffner and G.~Schmitz.
\newblock Compensating the combined effects of absorption and dispersion in
  plane wave pulse-echo ultrasound imaging using sparse recovery.
\newblock In {\em 2013 IEEE Int. Ultrasonics Symp. (IUS)}, pages 573--576, Jul.
  2013.

\bibitem{proc:SchiffnerIUS2013b}
M.~F. Schiffner and G.~Schmitz.
\newblock The separate recovery of spatial fluctuations in compressibility and
  mass density in plane wave pulse-echo ultrasound imaging.
\newblock In {\em 2013 IEEE Int. Ultrasonics Symp. (IUS)}, pages 577--580, Jul.
  2013.

\bibitem{proc:SchiffnerIUS2012}
M.~F. Schiffner and G.~Schmitz.
\newblock Fast image acquisition in pulse-echo ultrasound imaging using
  compressed sensing.
\newblock In {\em 2012 IEEE Int. Ultrasonics Symp. (IUS)}, pages 1944--1947,
  Oct. 2012.

\bibitem{article:SchiffnerBMT2012}
M.~F. Schiffner, T.~Jansen, and G.~Schmitz.
\newblock Compressed sensing for fast image acquisition in pulse-echo
  ultrasound.
\newblock {\em Biomed. Tech.}, 57(SI-1 Track-B):192--195, Aug. 2012.

\bibitem{proc:SchiffnerIUS2011}
M.~F. Schiffner and G.~Schmitz.
\newblock Fast pulse-echo ultrasound imaging employing compressive sensing.
\newblock In {\em 2011 IEEE Int. Ultrasonics Symp. (IUS)}, pages 688--691, Oct.
  2011.

\bibitem{book:Foucart2013}
S.~Foucart and H.~Rauhut.
\newblock {\em A Mathematical Introduction to Compressive Sensing}.
\newblock Applied and Numerical Harmonic Analysis. Springer, 1st edition, Aug.
  2013.

\bibitem{article:KutyniokGAMM2013}
G.~Kutyniok.
\newblock Theory and applications of compressed sensing.
\newblock {\em GAMM-Mit\-teil\-ung\-en}, 36(1):79--101, Aug. 2013.

\bibitem{article:BaraniukSPM2007}
R.~G. Baraniuk.
\newblock Compressive sensing [lecture notes].
\newblock {\em IEEE Signal Process. Mag.}, 24(4):118--121, Jul. 2007.

\bibitem{article:CandesSPM2008}
E.~J. Candes and M.~B. Wakin.
\newblock An introduction to compressive sampling.
\newblock {\em IEEE Signal Process. Mag.}, 25(2):21--30, Mar. 2008.

\bibitem{article:ProvostITMI2009}
J.~Provost and F.~Lesage.
\newblock The application of compressed sensing for photo-acoustic tomography.
\newblock {\em IEEE Trans. Med. Imag.}, 28(4):585--594, Apr. 2009.

\bibitem{article:ChenMedPhys2008}
G.-H. Chen, J.~Tang, and S.~Leng.
\newblock Prior image constrained compressed sensing ({PICCS}): {A} method to
  accurately reconstruct dynamic {CT} images from highly undersampled
  projection data sets.
\newblock {\em Med. Phys.}, 35(2):660--663, Feb. 2008.

\bibitem{article:LustigMRM2007}
M.~Lustig, D.~Donoho, and J.~M. Pauly.
\newblock Sparse {MRI}: {T}he application of compressed sensing for rapid {MR}
  imaging.
\newblock {\em Magnet. Reson. Med.}, 58(6):1182--1195, Dec. 2007.

\bibitem{article:FoucartACHA2009}
S.~Foucart and M.-J. Lai.
\newblock Sparsest solutions of underdetermined linear systems via
  {$\ell_{q}$}-minimization for {$0 < q \leq 1$}.
\newblock {\em Appl. Comput. Harmon. A.}, 26(3):395--407, May 2009.

\bibitem{proc:ChartrandICASSP2008}
R.~Chartrand and W.~Yin.
\newblock Iteratively reweighted algorithms for compressive sensing.
\newblock In {\em 2008 IEEE Int. Conf. Acoustics, Speech and Signal Processing
  (ICASSP)}, pages 3869--3872, Mar.--Apr. 2008.

\bibitem{article:ChartrandISPL2007}
R.~Chartrand.
\newblock Exact reconstruction of sparse signals via nonconvex minimization.
\newblock {\em IEEE Signal Process. Lett.}, 14(10):707--710, Oct. 2007.

\bibitem{article:MontaldoITUFFC2005}
G.~Montaldo, D.~Palacio, M.~Tanter, and M.~Fink.
\newblock Building three-dimensional images using a time-reversal chaotic
  cavity.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  52(9):1489--1497, Sep. 2005.

\bibitem{article:FromentezeOptExp2017}
T.~Fromenteze, O.~Yurduseven, M.~Boyarsky, J.~Gollub, D.~L. Marks, and D.~R.
  Smith.
\newblock Computational polarimetric microwave imaging.
\newblock {\em Opt. Express}, 25(22):27488--27505, Oct. 2017.

\bibitem{article:GollubSciRep2017}
J.~N. Gollub, O.~Yurduseven, K.~P. Trofatter, D.~Arnitz, M.~F. Imani,
  T.~Sleasman, M.~Boyarsky, A.~Rose, A.~Pedross-Engel, H.~Odabasi,
  T.~Zvolensky, G.~Lipworth, D.~Brady, D.~L. Marks, M.~S. Reynolds, and D.~R.
  Smith.
\newblock Large metasurface aperture for millimeter wave computational imaging
  at the human-scale.
\newblock {\em Sci. Rep.}, 7:42650, Feb. 2017.

\bibitem{article:FromentezeApplPhysLett2015}
T.~Fromenteze, O.~Yurduseven, M.~F. Imani, J.~Gollub, C.~Decroze, D.~Carsenat,
  and D.~R. Smith.
\newblock Computational imaging using a mode-mixing cavity at microwave
  frequencies.
\newblock {\em Appl. Phys. Lett.}, 106(19):194104--1--194104--5, May 2015.

\bibitem{article:LipworthJOSAA2013}
G.~Lipworth, A.~Mrozack, J.~Hunt, D.~L. Marks, T.~Driscoll, D.~Brady, and D.~R.
  Smith.
\newblock Metamaterial apertures for coherent computational imaging on the
  physical layer.
\newblock {\em J. Opt. Soc. Am. A}, 30(8):1603--1612, Aug. 2013.

\bibitem{article:HuntScience2013}
J.~Hunt, T.~Driscoll, A.~Mrozack, G.~Lipworth, M.~Reynolds, D.~Brady, and D.~R.
  Smith.
\newblock Metamaterial apertures for computational imaging.
\newblock {\em Science}, 339(6117):310--313, Jan. 2013.

\bibitem{proc:BessonICIP2016}
A.~Besson, R.~E. Carrillo, O.~Bernard, Y.~Wiaux, and J.-P. Thiran.
\newblock Compressed delay-and-sum beamforming for ultrafast ultrasound
  imaging.
\newblock In {\em 2016 IEEE Int. Conf. Image Processing (ICIP)}, pages
  2509--2513, Sep. 2016.

\bibitem{article:LiutkusSciRep2014}
A.~Liutkus, D.~Martina, S.~Popoff, G.~Chardon, O.~Katz, G.~Lerosey, S.~Gigan,
  L.~Daudet, and I.~Carron.
\newblock Imaging with nature: {C}ompressive imaging using a multiply
  scattering medium.
\newblock {\em Sci. Rep.}, 4:5552, Jul. 2014.

\bibitem{article:KruizingaSciAdv2017}
P.~Kruizinga, P.~van~der Meulen, A.~Fedjajevs, F.~Mastik, G.~Springeling,
  N.~de~Jong, J.~G. Bosch, and G.~Leus.
\newblock Compressive {3D} ultrasound imaging using a single sensor.
\newblock {\em Sci. Adv.}, 3(12), Dec. 2017.

\bibitem{article:Ghanbarzadeh-DagheyanSensors2018}
A.~Ghanbarzadeh-Dagheyan, C.~Liu, A.~Molaei, J.~Heredia, and J.~Martinez
  Lorenzo.
\newblock Holey-cavity-based compressive sensing for ultrasound imaging.
\newblock {\em Sensors}, 18(6), 2018.

\bibitem{letter:VanSlounITBME2015}
R.~{van Sloun}, A.~Pandharipande, M.~Mischi, and L.~Demi.
\newblock Compressed sensing for ultrasound computed tomography.
\newblock {\em IEEE Trans. Biomed. Eng.}, 62(6):1660--1664, Jun. 2015.

\bibitem{article:LiuITUFFC2018}
J.~Liu, Q.~He, and J.~Luo.
\newblock Compressed sensing based synthetic transmit aperture imaging:
  {V}alidation in a convex array configuration.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  65(3):300--315, Mar. 2018.

\bibitem{article:LiuITMI2017}
J.~Liu, Q.~He, and J.~Luo.
\newblock A compressed sensing strategy for synthetic transmit aperture
  ultrasound imaging.
\newblock {\em IEEE Trans. Med. Imag.}, 36(4):878--891, Apr. 2017.

\bibitem{proc:SchiffnerIUS2017}
M.~Schiffner and G.~Schmitz.
\newblock Random incident sound waves for fast compressed pulse-echo ultrasound
  imaging.
\newblock In {\em 2017 IEEE Int. Ultrasonics Symp. (IUS)}, page~1, Sept. 2017.

\bibitem{article:SchiffnerJASA2017}
M.~F. Schiffner and G.~Schmitz.
\newblock Fast compressive pulse-echo ultrasound imaging using random incident
  sound fields.
\newblock {\em J. Acoust. Soc. Am.}, 141(5):3611, May 2017.

\bibitem{article:TroppPIEEE2010}
J.~A. Tropp and S.~J. Wright.
\newblock Computational methods for sparse solution of linear inverse problems.
\newblock {\em Proc. IEEE}, 98(6):948--958, Jun. 2010.

\bibitem{book:Hansen2010}
P.~C. Hansen.
\newblock {\em Discrete Inverse Problems: Insight and Algorithms}.
\newblock Fundamentals of Algorithms. Society for Industrial and Applied
  Mathematics (SIAM), Jan. 2010.

\bibitem{book:Hansen1998}
P.~C. Hansen.
\newblock {\em Rank-Deficient and Discrete Ill-Posed Problems: Numerical
  Aspects of Linear Inversion}.
\newblock Mathematical Modeling and Computation. Society for Industrial and
  Applied Mathematics (SIAM), Jan. 1998.

\bibitem{book:Eldar2012}
Y.~C. Eldar and G.~Kutyniok, editors.
\newblock {\em Compressed Sensing: Theory and Applications}.
\newblock Cambridge University Press, 1st edition, May 2012.

\bibitem{article:FoucartACHA2010}
S.~Foucart.
\newblock A note on guaranteed sparse recovery via {$\ell_{1}$}-minimization.
\newblock {\em Appl. Comput. Harmon. A.}, 29(1):97--103, Jul. 2010.

\bibitem{article:CandesCRAS2008}
E.~J. Candès.
\newblock The restricted isometry property and its implications for compressed
  sensing.
\newblock {\em C. R. Acad. Sci. Paris, Ser. I}, 346(9--10):589--592, May 2008.

\bibitem{article:TillmannITIT2014}
A.~M. Tillmann and M.~E. Pfetsch.
\newblock The computational complexity of the restricted isometry property, the
  nullspace property, and related concepts in compressed sensing.
\newblock {\em IEEE Trans. Inf. Theory}, 60(2):1248--1259, Feb. 2014.

\bibitem{article:BaraniukCA2008}
R.~Baraniuk, M.~Davenport, R.~DeVore, and M.~Wakin.
\newblock A simple proof of the restricted isometry property for random
  matrices.
\newblock {\em Constr. Approx.}, 28(3):253--263, Dec. 2008.

\bibitem{coll:Fornasier2015}
M.~Fornasier and H.~Rauhut.
\newblock Compressive sensing.
\newblock In O.~Scherzer, editor, {\em Handbook of Mathematical Methods in
  Imaging}, pages 205--256. Springer, 2nd edition, 2015.

\bibitem{article:RudelsonCPAM2008}
M.~Rudelson and R.~Vershynin.
\newblock On sparse reconstruction from {F}ourier and {G}aussian measurements.
\newblock {\em Commun. Pur. Appl. Math.}, 61(8):1025--1045, Aug. 2008.

\bibitem{article:ChernyakovaITUFFC2018}
T.~Chernyakova, R.~Cohen, R.~Mulayoff, Y.~Sde-Chen, C.~Fraschini, J.~Bercoff,
  and Y.~C. Eldar.
\newblock {F}ourier-domain beamforming and structure-based reconstruction for
  plane-wave imaging.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  65(10):1810--1821, Oct. 2018.

\bibitem{proc:SchiffnerIUS2016a}
M.~F. Schiffner and G.~Schmitz.
\newblock A low-rate parallel {F}ourier domain beamforming method for ultrafast
  pulse-echo imaging.
\newblock In {\em 2016 IEEE Int. Ultrasonics Symp. (IUS)}, pages 1--4, Sep.
  2016.

\bibitem{article:BurshteinITUFFC2016}
A.~Burshtein, M.~Birk, T.~Chernyakova, A.~Eilam, A.~Kempinski, and Y.~C. Eldar.
\newblock Sub-{N}yquist sampling and {F}ourier domain beamforming in volumetric
  ultrasound imaging.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  63(5):703--716, May 2016.

\bibitem{article:ChernyakovaITUFFC2014}
T.~Chernyakova and Y.~C. Eldar.
\newblock {F}ourier-domain beamforming: {T}he path to compressed ultrasound
  imaging.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  61(8):1252--1267, Aug. 2014.

\bibitem{article:WagnerITSP2012}
N.~Wagner, Y.~C. Eldar, and Z.~Friedman.
\newblock Compressed beamforming in ultrasound imaging.
\newblock {\em IEEE Trans. Signal Process.}, 60(9):4643--4657, Sep. 2012.

\bibitem{book:Manolakis2005}
D.~G. Manolakis, V.~K. Ingle, and S.~M. Kogon.
\newblock {\em Statistical and Adaptive Signal Processing: Spectral Estimation,
  Signal Modeling, Adaptive Filtering, and Array Processing}.
\newblock Artech House Signal Processing Library. Artech House, Inc., 2005.

\bibitem{book:Briggs1995}
W.~L. Briggs and V.~E. Henson.
\newblock {\em The DFT: An Owner's Manual for the Discrete Fourier Transform}.
\newblock Other Titles in Applied Mathematics. Society for Industrial and
  Applied Mathematics (SIAM), 1995.

\bibitem{website:NCIDictionary2017}
{National Cancer Institute ({NCI}) at the National Institutes of Health ({NIH})}.
\newblock {{NCI} Dictionary of Cancer Terms}, May 2017.
\newblock {\url{https://www.cancer.gov/publications/dictionaries/cancer-terms/def/soft-tissue}}

\bibitem{article:NgITUFFC2006}
J.~Ng, R.~Prager, N.~Kingsbury, G.~Treece, and A.~Gee.
\newblock Modeling ultrasound imaging as a linear, shift-variant system.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  53(3):549--563, Mar. 2006.

\bibitem{coll:Jensen2002}
J.~A. Jensen.
\newblock Ultrasound imaging and its modeling.
\newblock In M.~Fink, W.~A. Kuperman, J.-P. Montagner, and A.~Tourin, editors,
  {\em Imaging of Complex Media with Acoustic and Seismic Waves}, volume~84 of
  {\em Topics in Applied Physics}, pages 135--166. Springer, 1st edition, 2002.

\bibitem{article:JensenJASA1991}
J.~A. Jensen.
\newblock A model for the propagation and scattering of ultrasound in tissue.
\newblock {\em J. Acoust. Soc. Am.}, 89(1):182--190, Jan. 1991.

\bibitem{article:GorePMB1977a}
J.~C. Gore and S.~Leeman.
\newblock Ultrasonic backscattering from human tissue: {A} realistic model.
\newblock {\em Phys. Med. Biol.}, 22(2):317--326, Mar. 1977.

\bibitem{book:Duck1990}
F.~A. Duck.
\newblock {\em Physical Properties of Tissue - A Comprehensive Reference Book}.
\newblock Academic Press Limited, 1990.

\bibitem{article:WellsUMB1975}
P.~N.~T. Wells.
\newblock Absorption and dispersion of ultrasound in biological tissue.
\newblock {\em Ultrasound Med. Biol.}, 1(1):369 -- 376, Mar. 1975.

\bibitem{article:KellyJASA2008b}
J.~F. Kelly, R.~J. McGough, and M.~M. Meerschaert.
\newblock Analytical time-domain {G}reen's functions for power-law media.
\newblock {\em J. Acoust. Soc. Am.}, 124(5):2861--2872, Nov. 2008.

\bibitem{article:WatersITUFFC2005}
K.~R. Waters, J.~Mobley, and J.~G. Miller.
\newblock Causality-imposed ({K}ramers-{K}ronig) relationships between
  attenuation and dispersion.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  52(5):822--833, May 2005.

\bibitem{article:SzaboJASA1995}
T.~L. Szabo.
\newblock Causal theories and data for acoustic attenuation obeying a frequency
  power law.
\newblock {\em J. Acoust. Soc. Am.}, 97(1):14--24, Jan. 1995.

\bibitem{book:Schmerr2015}
L.~W. {Schmerr Jr.}
\newblock {\em Fundamentals of Ultrasonic Phased Arrays}, volume 215 of {\em
  Solid Mechanics and Its Applications}.
\newblock Springer International Publishing, 1st edition, 2015.

\bibitem{article:LabyedITUFFC2014}
Y.~Labyed and L.~Huang.
\newblock {TR-MUSIC} inversion of the density and compressibility contrasts of
  point scatterers.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  61(1):16--24, Jan. 2014.

\bibitem{book:Born1999}
M.~Born and E.~Wolf.
\newblock {\em Principles of Optics: Electromagnetic Theory of Propagation,
  Interference and Diffraction of Light}.
\newblock Cambridge University Press, 7th (expanded) edition, Oct. 1999.

\bibitem{article:LiPIER2010}
J.~Li, X.~Wang, and T.~Wang.
\newblock On the validity of {B}orn approximation.
\newblock {\em Prog. Electromagn. Res.}, 107:219--237, 2010.

\bibitem{article:ChewITAP1997}
W.~C. Chew, J.-M. Jin, C.-C. Lu, E.~Michielssen, and J.~M. Song.
\newblock Fast solution methods in electromagnetics.
\newblock {\em IEEE Trans. Antennas Propag.}, 45(3):533--543, Mar. 1997.

\bibitem{article:RokhlinJCP1990}
V.~Rokhlin.
\newblock Rapid solution of integral equations of scattering theory in two
  dimensions.
\newblock {\em J. Comput. Phys.}, 86(2):414--439, Feb. 1990.

\bibitem{book:Mallat2009}
S.~Mallat.
\newblock {\em A Wavelet Tour of Signal Processing: The Sparse Way}.
\newblock Academic Press, 3rd edition, 2009.

\bibitem{article:VanDenBergSIAMJSC2009}
E.~van~den Berg and M.~P. Friedlander.
\newblock Probing the pareto frontier for basis pursuit solutions.
\newblock {\em SIAM J. Sci. Comput.}, 31(2):890--912, 2009.

\bibitem{book:Gibson2014}
W.~C. Gibson.
\newblock {\em The Method of Moments in Electromagnetics}.
\newblock CRC Press, 2nd edition, Aug. 2014.

\bibitem{article:CoifmanIAPM1993}
R.~Coifman, V.~Rokhlin, and S.~Wandzura.
\newblock The fast multipole method for the wave equation: A pedestrian
  prescription.
\newblock {\em IEEE Antennas Propag. Mag.}, 35(3):7--12, Jun. 1993.

\bibitem{article:DemanetACHA2007}
L.~Demanet and L.~Ying.
\newblock Wave atoms and sparsity of oscillatory patterns.
\newblock {\em Appl. Comput. Harmon. A.}, 23(3):368--387, Nov. 2007.

\bibitem{article:WangISPM2009}
Z.~Wang and A.~C. Bovik.
\newblock Mean squared error: {L}ove it or leave it? {A} new look at {S}ignal
  {F}idelity {M}easures.
\newblock {\em IEEE Signal Process. Mag.}, 26(1):98--117, Jan. 2009.

\bibitem{article:CandesJFAA2008}
E.~J. Candès, M.~B. Wakin, and S.~P. Boyd.
\newblock Enhancing sparsity by reweighted {$\ell_{1}$} minimization.
\newblock {\em J. Fourier Anal. Appl.}, 14(5--6):877--905, Dec. 2008.

\bibitem{article:AchimITCI2015}
A.~Achim, A.~Basarab, G.~Tzagkarakis, P.~Tsakalides, and D.~Kouamé.
\newblock Reconstruction of ultrasound {RF} echoes modeled as stable random
  variables.
\newblock {\em IEEE Trans. Comput. Imag.}, 1(2):86--95, Jun. 2015.

\bibitem{proc:SchiffnerIUS2014}
M.~F. Schiffner and G.~Schmitz.
\newblock Pulse-echo ultrasound imaging combining compressed sensing and the
  fast multipole method.
\newblock In {\em 2014 IEEE Int. Ultrasonics Symp. (IUS)}, pages 2205--2208,
  Sep. 2014.

\bibitem{article:ChaillatJCP2012}
S.~Chaillat and G.~Biros.
\newblock {F}a{IMS}: {A} fast algorithm for the inverse medium problem with
  multiple frequencies and multiple sources for the scalar {H}elmholtz
  equation.
\newblock {\em J. Comput. Phys.}, 231(12):4403--4421, Jun. 2012.

\bibitem{article:ZhaoITEC2005}
K.~Zhao, M.~N. Vouvakis, and J.-F. Lee.
\newblock The adaptive cross approximation algorithm for accelerated method of
  moments computations of {EMC} problems.
\newblock {\em IEEE Trans. Electromagn. Compat.}, 47(4):763--773, Nov. 2005.

\bibitem{article:DemanetFCompMath2010}
L.~Demanet and L.~Ying.
\newblock Scattering in flatland: {E}fficient representations via wave atoms.
\newblock {\em Found. Comput. Math.}, 10(5):569--613, Oct. 2010.

\bibitem{article:BluISPM2008}
T.~Blu, P.-L. Dragotti, M.~Vetterli, P.~Marziliano, and L.~Coulot.
\newblock Sparse sampling of signal innovations.
\newblock {\em IEEE Signal Process. Mag.}, 25(2):31--40, Mar. 2008.

\bibitem{article:VetterliITSP2002}
M.~Vetterli, P.~Marziliano, and T.~Blu.
\newblock Sampling signals with finite rate of innovation.
\newblock {\em IEEE Trans. Signal Process.}, 50(6):1417--1428, Jun. 2002.

\bibitem{proc:SchiffnerIUS2016b}
M.~F. Schiffner and G.~Schmitz.
\newblock Ultrafast image acquisition in pulse-echo ultrasound imaging using
  compressed sensing.
\newblock In {\em 2016 IEEE Int. Ultrasonics Symp. (IUS)}, pages 1--3, Sep.
  2016.

\bibitem{article:MisaridisITUFFC2005}
T.~Misaridis and J.~A. Jensen.
\newblock Use of modulated excitation signals in medical ultrasound. {P}art
  {III}: {H}igh frame rate imaging.
\newblock {\em IEEE Trans. Ultrason., Ferroelectr., Freq. Control},
  52(2):208--219, Feb. 2005.

\enlargethispage{-203mm}

\bibitem{article:IlovitshNatComBio2018}
T.~Ilovitsh, A.~Ilovitsh, J.~Foiret, B.~Z. Fite, and K.~W. Ferrara.
\newblock Acoustical structured illumination for super-resolution ultrasound
  imaging.
\newblock {\em Nat. Commun. Biol.}, 1(1):3, Jan. 2018.

\bibitem{article:CandesACHA2011}
E.~J. Candes, Y.~C. Eldar, D.~Needell, and P.~Randall.
\newblock Compressed sensing with coherent and redundant dictionaries.
\newblock {\em Appl. Comput. Harmon. A.}, 31(1):59--73, Jul. 2011.

\bibitem{article:LorintiuITMI2015}
O.~Lorintiu, H.~Liebgott, M.~Alessandrini, O.~Bernard, and D.~Friboulet.
\newblock Compressed sensing reconstruction of {3D} ultrasound data using
  dictionary learning and line-wise subsampling.
\newblock {\em IEEE Trans. Med. Imag.}, 34(12):2467--2477, Dec. 2015.

\bibitem{book:OlverNHMF2010}
F.~W.~J. Olver, D.~W. Lozier, R.~F. Boisvert, and C.~W. Clark, editors.
\newblock {\em NIST Handbook of Mathematical Functions}.
\newblock Cambridge University Press, 2010.

\end{thebibliography}

\end{document}
