\documentclass[pmlr,twocolumn,10pt]{jmlr}% new name PMLR (Proceedings of Machine Learning)


\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usepackage{url}
\usepackage{multicol}

% for todo notes:
\usepackage[draft,inline,nomargin,index]{fixme}
\fxsetup{theme=colorsig,mode=multiuser,inlineface=\itshape,envface=\itshape}
\FXRegisterAuthor{rp}{arp}{Richard}
\FXRegisterAuthor{sf}{asf}{Sorelle}

\usepackage{fancyvrb}


\usepackage{amsmath} %, amsthm, amssymb}

\usepackage{multicol}

\newcommand{\mypara}[1]{\paragraph{#1}}

\usepackage[export]{adjustbox}% http://ctan.org/pkg/adjustbox

\usepackage[hyphenbreaks]{breakurl}
\def\UrlBreaks{\do\/\do-} % a bit of magic from https://norwied.wordpress.com/2012/07/10/how-to-break-long-urls-in-bibtex/


%Conference
\jmlrvolume{81}
\jmlryear{2018}
\jmlrworkshop{Conference on Fairness, Accountability, and Transparency}

\title{Interpretable Active Learning\titletag{\thanks{This research was funded in part by the NSF under grants IIS-1633387, DMR-1709351, and DMR-1307801 and by the Arnold and Mabel Beckman Foundation.}\thanks{\url{https://github.com/rlphilli/InterpretableActiveLearning}}}}
\author{\Name{Richard L. Phillips} \Email{rlphillips@haverford.edu}\\
            \addr Haverford College
            \AND
            \Name{Kyu Hyun Chang} \Email{kyuhyun217@gmail.com}\\
            \addr Google Inc.\thanks{Work done while the author was a student at Haverford College.}
            \AND
            \Name{Sorelle A. Friedler} \Email{sorelle@cs.haverford.edu}\\
            \addr Haverford College
}


\begin{document}

\maketitle
 
\begin{abstract}
\looseness-1 Active learning has long been a topic of study in machine learning. However, as increasingly complex and opaque models have become standard practice, the process of active learning, too, has become more opaque. There has been little investigation into interpreting what specific trends and patterns an active learning strategy may be exploring. This work expands on the Local Interpretable Model-agnostic Explanations framework (LIME) to provide explanations for active learning recommendations. We demonstrate how LIME can be used to generate locally faithful explanations for an active learning strategy, and how these explanations can be used to understand how different models and datasets explore a problem space over time. 

In order to quantify the per-subgroup differences in how an active learning strategy queries spatial regions, we introduce a notion of uncertainty bias (based on disparate impact) to measure the discrepancy in the confidence for a model's predictions between one subgroup and another.  Using the uncertainty bias measure, we show that our query explanations accurately reflect the subgroup focus of the active learning queries, allowing for an interpretable explanation of what is being learned as points with similar sources of uncertainty have their uncertainty bias resolved.  We demonstrate that this technique can be applied to track uncertainty bias over user-defined clusters or automatically generated clusters based on the source of uncertainty.
\end{abstract}

\begin{keywords}
Interpretability; Active learning.
\end{keywords}


\input{body}


\bibliography{bibliography} 

\end{document}

