In this work, we study the effect of competition in prophet settings.
%
We show that under both random and ranked tie-breaking rules, agents have simple strategies that grant them high guarantees, ones that are tight even with respect to equilibrium profiles under some distributions.

Under the ranked tie-breaking rule, we show an interesting correspondence between the equilibrium strategies of the $k$ competing agents and the optimal strategy of a single decision maker that can select up to $k$ rewards. 
It would be interesting to study whether this phenomenon applies more generally, and what are the conditions under which it holds.
 



Below we list some future directions that we find particularly natural. 
\begin{itemize}
	\item Study competition in additional problems related to optimal stopping theory, such as Pandora's box \cite{weitzman1979optimal}.% and game of Googol \cite{gnedin1994solution} settings.
	\item Study competition in prophet (and secretary) settings under additional tie-breaking rules, such as random tie breaking with non-uniform distribution, and tie-breaking rules that allow to split rewards among agents.
	\item Study competition in  scenarios where agents can choose multiple rewards, under some feasibility constraints (such as matroid or downward-closed feasibility constraints). 
	\item Consider prophet settings with the objective of outperforming the other agents, as in \cite{immorlica2011dueling}, or different agents' objectives.
	\item Consider competition settings with non-immediate decision making, as in \cite{ezra2020competitive}.
\end{itemize}

