%%
%% This is file `sample-acmsmall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `acmsmall')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-acmsmall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[acmsmall]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you

\usepackage{graphicx, url}
%\usepackage[noadjust]{cite}
\usepackage{balance}
\usepackage{subfigure,captcont,wrapfig, setspace}
\usepackage{comment, ragged2e}
\usepackage{subfigure, color, colortbl}
\usepackage{amsmath}
\usepackage[linesnumbered, ruled, vlined]{algorithm2e}


%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{0000001.0000001}


%%
%% These commands are for a JOURNAL article.
\acmJournal{TECS}
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmMonth{8}

\definecolor{blue}{rgb}{0.0,0.0,1}
\newcommand*{\revise}{\textcolor{blue}}

\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand*{\edit}{\textcolor{red}}
\newcommand{\code}[1]{\texttt{#1}}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{LPWAN in the TV White Spaces: A Practical Implementation and Deployment Experiences}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Mahbubur Rahman}
\orcid{0000-0003-2353-6687}
\affiliation{%
  \institution{City University of New York}
  \streetaddress{Queens College Science Building, 65-30 Kissena Boulevard}
  \city{Flushing}
  \state{NY}
  \postcode{11367}
  \country{USA}}
\email{mdmahbubur.rahman@qc.cuny.edu}

\author{Dali Ismail}
\affiliation{%
 \institution{Wayne State University}
  \streetaddress{5057 Woodward Avenue, Suite 3010}
  \city{Detroit}
  \state{MI}
  \postcode{48202}
  \country{USA}}
\email{dali.ismail@wayne.edu}

\author{Venkata P. Modekurthy}
\affiliation{%
 \institution{Wayne State University}
  \streetaddress{5057 Woodward Avenue, Suite 3010}
  \city{Detroit}
  \state{MI}
  \postcode{48202}
  \country{USA}}
\email{modekurthy@wayne.edu}

\author{Abusayeed Saifullah}
\affiliation{%
 \institution{Wayne State University}
  \streetaddress{5057 Woodward Avenue, Suite 3010}
  \city{Detroit}
  \state{MI}
  \postcode{48202}
  \country{USA}}
\email{saifullah@wayne.edu}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Low-Power Wide-Area Network (LPWAN) is an enabling Internet-of-Things (IoT) technology that supports long-range, low-power, and low-cost connectivity to numerous devices. To avoid the crowd in the limited ISM band (where most LPWANs operate) and cost of licensed band, the recently proposed SNOW (Sensor Network over White Spaces) is a promising LPWAN platform that operates over the TV white spaces. As it is a very recent technology and is still in its infancy, the current SNOW implementation uses the USRP devices as LPWAN nodes, which has high costs ($\approx$ \$750 USD per device) and large form-factors, hindering its applicability in practical deployment. In this paper, we implement SNOW using low-cost, low form-factor, low-power, and widely available commercial off-the-shelf (COTS) devices to enable its practical and large-scale deployment. Our choice of the COTS device (TI CC13x0: CC1310 or CC1350) consequently brings down the cost and form-factor of a SNOW node by 25x and 10x, respectively. Such implementation of SNOW on the CC13x0 devices, however, faces a number of challenges to enable link reliability and communication range. Our implementation addresses these challenges by handling peak-to-average power ratio problem, channel state information estimation, carrier frequency offset estimation, and near-far power problem. Our deployment in the city of Detroit, Michigan demonstrates that CC13x0-based SNOW can achieve uplink and downlink throughputs of 11.2kbps and 4.8kbps per node, respectively, over a distance of 1km. Also, the overall throughput in the uplink increases linearly with the increase in the number of SNOW nodes.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003034</concept_id>
<concept_desc>Networks~Network architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003079</concept_id>
<concept_desc>Networks~Network performance evaluation</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003083.10003097</concept_id>
<concept_desc>Networks~Network mobility</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003039.10003040</concept_id>
<concept_desc>Networks~Network protocol design</concept_desc>
<concept_significance>100</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010553.10003238</concept_id>
<concept_desc>Computer systems organization~Sensor networks</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Networks~Network architectures}
\ccsdesc[500]{Networks~Network performance evaluation}
\ccsdesc[300]{Networks~Network mobility}
\ccsdesc[100]{Networks~Network protocol design}
\ccsdesc[300]{Computer systems organization~Sensor networks}


\keywords{LPWAN, SNOW, White spaces, OFDM}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\renewcommand{\shortauthors}{Rahman, M. et al.}

\input{introduction}
\input{snow_overview}
\input{technical}
\input{deployment}
\input{evaluation}
\input{related}

\section{Conclusions}\label{sec:conclusion}
The recently proposed LPWAN technology -- SNOW -- has the potential to enable connectivity to numerous IoT devices over long distances. However, the high cost and the large form-factor of the USRP-based SNOW nodes hinder its practical deployments. In this paper, we have implemented SNOW for practical deployments using the CC13x0 devices as SNOW nodes. Our CC13x0-based SNOW implementation decreases the cost and the form-factor of a single SNOW node by 25x and 10x, respectively. 
We have also addressed several practical deployment challenges that include PAPR reduction, CSI estimation, CFO estimation, and near-far power problem. 
We have deployed our CC13x0-based SNOW in the city of Detroit, Michigan and achieved per node uplink and downlink throughputs of 11.2kbps and 4.8kbps, respectively, over a distance of 1km. 
%Additionally, our overall uplink throughput at the BS have increased linearly with the increase in the number of nodes. 
Our experiments also show that SNOW can achieve throughput several times higher than LoRaWAN under typical settings.
Finally, our extensive experiments have demonstrated the CC13x0-based SNOW as a feasible LPWAN technology that can be deployed practically at low-cost and in large-scale for future IoT applications.
%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
This work was supported by NSF through grants CAREER-1846126 and CNS-2006467.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{whitespacebib}


\end{document}
\endinput
%%
%% End of file `sample-acmsmall.tex'.
