\documentclass[]{ceurart}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[export]{adjustbox}
\usepackage{algorithm2e}
\usepackage{booktabs}
\usepackage{balance}
\usepackage{comment}
\usepackage{colortbl}
\usepackage{color,soul}
\usepackage{calc}
\usepackage{enumitem}
\usepackage{float}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{mdwlist}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xspace} 
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{times}


\newcommand{\proposed}{APAE}
\definecolor{magicmint}{rgb}{0.67, 0.94, 0.82}
\definecolor{melon}{rgb}{0.99, 0.74, 0.71}
\newcommand{\lmjm}{LMJM}
\newcommand{\lmdr}{LMDir}
\newcommand{\nores}{\cellcolor{lightgray}}
\newcommand\defas{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
\newcommand{\para}[1]{\paragraph{\textnormal{\textbf{#1}.}}}
\newcommand{\uls}{\begin{itemize}}
\newcommand{\ule}{\end{itemize}}
\newcommand{\ols}{\begin{enumerate}}
\newcommand{\ole}{\end{enumerate}}
\newcommand{\li}{\item}
\newcommand{\RQ}[1]{\textbf{RQ{#1}}}
\newcommand{\pws}{\eta(\Psi_\mu)}
\newcommand{\pwu}{\eta(\mathcal{M})}
\newcommand{\pwua}[1]{\eta_#1(\mathcal{M})}
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.25\hsize}X}

\begin{document}

\copyrightyear{2023}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

\conference{QPP++ 2023: Query Performance Prediction and Its Evaluation in New Tasks, co-located with 45th European Conference on Information Retrieval (ECIR) from the 2nd to the 6th of April 2023 in Dublin, Ireland}

\title{On the Feasibility and Robustness of Pointwise Evaluation of Query Performance Prediction}

\author[1]{Suchana Datta}[%
orcid=0000-0001-9220-6652,
email=suchana.datta@ucdconnect.ie,
]

\author[2]{Debasis Ganguly}[%
orcid=0000-0003-0050-7138,
email=debasis.ganguly@glasgow.ac.uk,
url=https://gdebasis.github.io/,
]

\author[3]{Derek Greene}[%
orcid=0000-0001-8065-5418,
email=derek.greene@ucd.ie,
url=http://derekgreene.com/,
]

\author[4]{Mandar Mitra}[%
orcid=0000-0001-9045-9971,
email=mandar@isical.ac.in,
url=https://www.isical.ac.in/mandar-mitra,
]

\address[1]{University College Dublin, Ireland}
\address[2]{University of Glasgow, UK}
\address[3]{University College Dublin, Ireland}
\address[4]{Indian Statistical Institute, Kolkata, India}

\begin{abstract}
\input Despite the retrieval effectiveness of queries being mutually independent of one another, the evaluation of query performance prediction (QPP) systems has been carried out by measuring rank correlation over an entire set of queries. 
Such a listwise approach has a number of disadvantages, notably that it does not support the common requirement of assessing QPP for individual queries.
In this paper, we propose a pointwise QPP framework that allows us to evaluate the quality of a QPP system for individual queries by measuring the deviations between each prediction versus the corresponding true value, and then aggregating the results over a set of queries.
Our experiments demonstrate that this new approach leads to smaller variances in QPP evaluations across a range of different target metrics and retrieval models.
\end{abstract}

\maketitle

\section{Introduction}
\input{src/intro.tex}

\section{A Framework for Pointwise QPP Evaluation}
\input{src/proposed}

\section{Experiments}
\input{src/exp}

\section{Concluding Remarks}
\input{src/conclusion}

\para{\textbf{Acknowledgement.}} \small The first and the third authors were supported by the Science Foundation Ireland (SFI) grant number SFI/12/RC/2289\_P2.

\bibliography{refs_reduced}

\end{document}
