\documentclass{llncs}

\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{hyphenat}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{algorithmicx}
\usepackage{xspace}
\usepackage{array}
\usepackage{todonotes}

\newcommand{\NP}{{$\mathsf{NP}$}\xspace}
\newcommand{\coNP}{${\mathsf{co}\text{-}\mathsf{NP}}$\xspace}
\newcommand{\PP}{{$\mathsf{P}$}\xspace} 
\newcommand{\SKA}{{\em SKA}\xspace}
\newcommand{\NSKA}{{\em NSKA}\xspace}
\newcommand{\NISKA}{{\em (N)SKA}\xspace}
\newcommand{\SST}{{$SST$}\xspace}
\newcommand{\SMST}{{$SMST$}\xspace}
\newcommand{\OISMST}{{$01\text{-}SMST$}\xspace}
\newcommand{\POISMST}{{$\cap\text{-}01\text{-}SMST$}\xspace}

\newtheorem{prop}[theorem]{Proposition}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{fact}[theorem]{Fact}


\newcommand{\R}{\mathbb{R}}   % množina reálnách čísel
\newcommand{\Z}{\mathbb{Z}}   % množina celých čísel
\newcommand{\N}{\mathbb{N}}   % množina přirozených čísel




\begin{document}

\title{On the Simultaneous Minimum Spanning Trees Problem}

\author{
Mat\v ej Kone\v cn\'y,
Stanislav Ku\v cera,
Jana Novotn\'a, 
Jakub Pek\'{a}rek, 
Martin Smol\'ik,
Jakub T\v etek,
Martin T\"opfer}
\institute{Department of Applied Mathematics, Faculty of Mathematics and Physics, Charles
University, Prague, Czech Republic,\\
\email{matejkon@gmail.com, stanislav.kucera@outlook.com, janca@kam.mff.cuni.cz,
edalegos@gmail.com,
smolik.ma@gmail.com,
j.tetek@gmail.com,
mtopfer@gmail.com}
}
\maketitle

\begin{abstract}

%\todo{abstrakt by měl být delší}
%\todo{prodloužil jsem}

Simultaneous Embedding with Fixed Edges (SEFE) \cite{b:sefe} is a problem where given $k$ planar graphs we ask whether they can be simultaneously embedded so that the embedding of each graph is planar and common edges are drawn the same. Problems of SEFE type have inspired questions of Simultaneous Geometrical Representations and further derivations. Based on this motivation we investigate the generalization of the simultaneous paradigm on the classical combinatorial problem of minimum spanning trees. Given $k$ graphs with weighted edges, such that they have a common intersection, are there minimum spanning trees of the respective graphs such that they agree on the intersection? We show that the unweighted case is polynomial-time solvable while the weighted case is only polynomial-time solvable for $k=2$ and it is \NP-complete for $k\geq 3$. 


%As the polynomial algorithm for $k=2$ uses some heavy machinery, we also give a simple combinatorial algorithm for the case when the intersection is a clique. \todo{No we don't}

%In the second part, we discuss a similar problem of simultaneous perfect matchings and show that it is \NP-complete for $k\geq 3$. \todo{No we don't}
\end{abstract}


\input{01-introduction}
\input{02-kruskal}
\input{03-reductions}
\input{04-NP}
\input{05-P}
%\include{06-Conclusion}

\section{Acknowledgements}

This paper is the output of the 2017 Problem~Seminar of Charles University. At this seminar undergraduate students attempt to solve open problems and learn to do research. We would like to thank Jan~Kratochv\'{i}l and Pavel~Valtr for their guidance, help and tea. 

The work was supported by the grant SVV--2017--260452 and grant CE-ITI P202/12/G061 of GA \v{C}R 






\begin{thebibliography}{9}
\bibitem{b:sefe}
Thomas Bläsius, Stephen G. Kobourov, Ignaz Rutter. "Simultaneous Embedding of Planar Graphs" arxiv.org:1204.5853 or arxiv.org:1204.5853v3 (2015).

\bibitem{b:boruvka}
Borůvka, Otakar. "O jistém problému minimílním (About a certain minimal problem)", Práce mor. přírodověd. spol. v Brně III (3) (1926) 37–58 (Czech, German summary).

\bibitem{b:jarnik}
Jarník, Vojtěch: "O jistém problému minimálním", Práce Moravské Přírodovědecké Společnosti, 6, 1930, pp. 57-63.

\bibitem{b:prim}
Prim, Robert Clay. "Shortest connection networks and some generalizations." Bell Labs Technical Journal 36.6 (1957): 1389-1401.

\bibitem{b:kruskal}
Kruskal, Joseph B. "On the shortest spanning subtree of a graph and the traveling salesman problem." Proceedings of the American Mathematical society 7.1 (1956): 48-50.

\bibitem{b:mst}
Graham, Ronald L., and Pavol Hell. "On the history of the minimum spanning tree problem." Annals of the History of Computing 7.1 (1985): 43-57.

\bibitem{b:mstopt}
Pettie, Seth, and Vijaya Ramachandran. "An optimal minimum spanning tree algorithm." Journal of the ACM (JACM) 49.1 (2002): 16-34.

\bibitem{b:karp}
Karp, Richard M. "Reducibility among combinatorial problems." Complexity of computer computations. springer US, 1972. 85-103.

\bibitem{b:edmonds}
Edmonds, Jack. "Submodular functions, matroids, and certain polyhedra." Combinatorial Structures and Their Applications (Gordon and Breach, New York, 1970) 68-87. 

\bibitem{b:graphicintersection}
Gabow, Harold N., and Matthias Stallmann. "Efficient algorithms for graphic matroid intersection and parity." International Colloquium on Automata, Languages, and Programming. Springer Berlin Heidelberg, 1985.
\end{thebibliography}






\end{document}

