\section{ChEMBL SQL query}
A locally-downloaded MySQL instance of the ChEMBL27 database~\cite{mendez2019chembl} (version 8.0.19) was queried~\cite{mysql}. Our data extraction procedure is performed in two steps: First, a list of biological targets was extracted. Second, compounds for which a specific activity towards any of these targets was annotated were extracted. Both steps are described in the following. 

\subsection{Extraction of targets}
"Single-protein" targets were selected, for which \texttt{activity.standard\_types} were reported either as $\mathrm{IC}_{50}$, $\mathrm{EC}_{50}$, $K_i$, $K$, $K_b$, $K_a$, $K_d$, $K_e$, or $K_m$ and in units of nM, or as a set of other \texttt{activity.standard\_types} (\textit{e.g.,} $-\log K$) and without units. The following types of annotations were excluded: Annotations with an \texttt{assay.relationship\_type} other than "homologous" or "direct", annotations with an \texttt{assay.} \texttt{confidence\_score} below $7$, annotations with assay descriptions for mutant species, annotations for potential activity duplicates, annotations with assay data validity comments other than "Manually validated" or "null", and  annotations with \texttt{activity.activity\_comments} indicating missing data such as "Not Determined" or "Not tested". Only targets which had annotations for $10$ or more unique compounds (as identified by their \texttt{activity.molregno} identifier) after this data extraction process were kept. 

\subsection{Extraction of compounds}
For each of the targets extracted in the previous steps, we queried the SQL database for activity annotations. Annotations for which the \texttt{activity.standard\_value} or the \texttt{activity.standard\_unit} was missing were discarded. All \texttt{activity.standard\_values} for annotations were converted to negative decadic logarithm scales (p$X$) and values below -3 on this scale were corrected to their absolute value. The  \texttt{activity.standard\_values} for annotations with activity comments denoting inactivity were set to $3$ on this log-scale. Annotations where the converted \texttt{activity.standard\_value} lay outside the range of $3$-$12$ were excluded. For each of the compounds that remained, we extracted the ChEMBL-ID and the canonical SMILES. 







