The following theorem relating Rademacher complexity and pseudo-dimension is well-known, though we work out the precise constants for completeness.

\pseudimerad*

\begin{proof} To prove this theorem, we will use the notion of a \emph{covering number.}
\begin{definition}[Covering number]
Let $A \subset \R^N$ be a set of vectors. We define $N_p(\beta,A)$ to be the cardinality of the smallest set $A' \subset \R^N$ such that for all $a \in A$, there exists $a' \in A'$ such that $\sqrt[p]{\frac{1}{N}\sum_{i = 1}^N (a_i - a_i')^p} \leq \beta$. We say that such an $A'$ $\beta$-covers $A$ in the $p$-norm and that $N_p(\beta,A)$ is the $L_p$-norm covering number.
\end{definition}
 We can relate the above definition to a mechanism class $\pazocal{M}$ over a set of samples $\sample = \left\{\vec{v}^1, \dots, \vec{v}^N\right\}$ by bounding $N_p(\beta, \pazocal{M}|_{\sample})$, where $\pazocal{M}|_{\sample}$ is the set of vectors \[\pazocal{M}|_{\sample} = \left\{\left(\profit_M\left(\vec{v}^1\right), \profit_M\left(\vec{v}^2\right), \dots, \profit_M\left(\vec{v}^N\right)\right) \ | \ M \in \pazocal{M}\right\}.\] To finish the proof, we will need a few more theorems and lemmas, which we translate into the language of mechanism design.

\begin{theorem}[\cite{Anthony09:Neural}]\label{thm:pdim_covering}
Let $\pazocal{M}$ be a mechanism class with finite pseudo-dimension $Pdim(\pazocal{M})$ such that for any $M \in \pazocal{M}$ and any valuation vector $\vec{v}$ in the support of $\dist$, $\profit_M(\vec{v}) \in [0,1]$. Then for any set $\sample$, $N_2(\beta, \pazocal{M}|_{\sample}) \leq 2\left(\frac{4e}{\beta^2}\right)^{Pdim(\pazocal{M})}$.
\end{theorem}

\begin{theorem}[\cite{Dudley87:Universal}]\label{thm:dudley}
Let $\pazocal{M}$ be a mechanism class. For any set $\sample$, \[\epsilon_{\pazocal{M}}(N, \delta) \leq 12 \int_0^{\infty} \sqrt{\frac{\log N_2(\beta, \pazocal{M}|_{\sample})}{N}} \, d\beta.\]
\end{theorem}

\begin{lemma}\label{lemma:scale}
For any set of vectors $A \subseteq \R^N$, scalar $c > 0$, and vector $\vec{a}_0 \in \R^N$, we have that $\forall \beta > 0$, $N_p(\beta, \left\{c\vec{a} + \vec{a}_0 : \vec{a} \in A\right\}) \leq N_p(\beta/c, A)$.
\end{lemma}
\begin{proof}
Suppose that $A'$ is a $\beta$-cover of $\left\{c\vec{a} + \vec{a}_0 : \vec{a} \in A\right\}$ in the $L_p$-norm. Then for all $\vec{a} \in A$, there exists $\vec{a}' \in A'$ such that \[\sqrt[p]{\frac{1}{m}\sum_{i = 1}^m (ca_i + a_{0,i} - a_i')^p} \leq \beta.\] Therefore, \begin{align*}\sqrt[p]{\frac{1}{m}\sum_{i = 1}^m (ca_i + a_{0,i} - a_i')^p} &= \sqrt[p]{\frac{1}{m}\sum_{i = 1}^m c^p\left(a_i + \frac{1}{c}(a_{0,i} - a_i')\right)^p}\\
&= c\sqrt[p]{\frac{1}{m}\sum_{i = 1}^m \left(a_i - \frac{1}{c}(a_i' - a_{0,i})\right)^p} \leq \beta. \end{align*} This means that the set $\left\{\frac{1}{c}(\vec{a}' - \vec{a}_0) : \vec{a}' \in A'\right\}$ is a $\frac{\beta}{c}$-cover of $A$.
\end{proof}

We are now ready to bound $\epsilon_{\pazocal{M}}(N, \delta)$ in terms of the pseudo-dimension of $\pazocal{M}$.
Let $\pazocal{M}'|_{\sample} \subseteq [0,1]^N$ be the set of vectors $\pazocal{M}'|_{\sample} = \left\{\frac{1}{U}\vec{w} \ | \ \vec{w} \in \pazocal{M}|_{\sample}\right\}$. The theorem follows from the following chain of inequalities:
\begin{align}
\epsilon_{\pazocal{M}}(N, \delta) &\leq 12 \int_0^{\infty} \sqrt{\frac{\log N_2 \left(\beta, \pazocal{M}|_{\sample}\right)}{N}} \, d\beta \label{ineq:dudley}\\
&\leq \frac{12}{\sqrt{N}} \int_0^{\infty} \sqrt{\log N_2 \left(\frac{\beta}{U}, \pazocal{M}'|_{\sample}\right)} \, d\beta \label{ineq:scale}\\
&\leq \frac{12}{\sqrt{N}} \int_0^{U} \sqrt{\log N_2 \left(\frac{\beta}{U}, \pazocal{M}'|_{\sample}\right)} \, d\beta \label{ineq:int}\\
&\leq \frac{12}{\sqrt{N}} \int_0^{U} \sqrt{\log 2 + Pdim(\pazocal{M})\log\frac{4e}{(\beta/U)^2}} \, d\beta\label{ineq:pdim}\\
&= \frac{12}{\sqrt{N}} \int_0^{U} \sqrt{1 + Pdim(\pazocal{M})\log\frac{4U^2e}{\beta^2}} \, d\beta\\
&\leq \frac{12}{\sqrt{N}}\left(U + \sqrt{Pdim(\pazocal{M})}\int_0^{U} \sqrt{\log\frac{4U^2e}{\beta^2}} \, d\beta\right)\\
&= \frac{12}{\sqrt{N}}\left(U + \sqrt{Pdim(\pazocal{M})}\int_0^{U} \sqrt{\log (4e) + \log\frac{U^2}{\beta^2}} \, d\beta\right)\\
&\leq \frac{12}{\sqrt{N}}\left(U\left(1 + \sqrt{Pdim(\pazocal{M})\log (4e)}\right) + \sqrt{Pdim(\pazocal{M})}\int_0^{U} \sqrt{\log\frac{U^2}{\beta^2}} \, d\beta\right)\\
&= \frac{12}{\sqrt{N}}\left(U\left(1 + \sqrt{Pdim(\pazocal{M})}\left(\sqrt{\log (4e)} +\sqrt{\frac{\pi}{\ln 4}}\right)\right)\right)\\
&\leq \frac{12 U}{\sqrt{N}} \left(1 + 4\sqrt{Pdim(\pazocal{M})}\right)\\
&\leq \frac{12\cdot 5 U}{\sqrt{N}} \sqrt{Pdim(\pazocal{M})}= \frac{60 U}{\sqrt{N}} \sqrt{Pdim(\pazocal{M})},
\end{align} as claimed. Inequality~\eqref{ineq:dudley} follows from Theorem~\ref{thm:dudley}. Inequality~\eqref{ineq:scale} follows from Lemma~\ref{lemma:scale}. Inequality~\eqref{ineq:int} follows from the fact that $\pazocal{M}'|_{\sample} \subseteq [0,1]^N$ which means that  the set $\{\vec{0}\}$ is a $\beta$-cover of $\pazocal{M}'|_{\sample}$ for $\beta \geq 1$, so $\log N_2(\beta, \pazocal{M}|_{\sample}) = 0$. Therefore, we only need to extend the integral to $U$. Inequality~\eqref{ineq:pdim} follows from Theorem~\ref{thm:pdim_covering}. The remaining equalities and inequalities follow from simple algebraic manipulations.
\end{proof}

