\vspace{-5pt}
\subsection*{Gold Standard Dataset Tables}
\vspace{-2pt}
%\noindent \textbf{Gold standard dataset tables}: 
We curated a manual gold standard evaluation dataset to measure the quality of the automatically derived annotations in the Chest ImaGenome dataset and for model benchmarking. Here we describe the three gold standard ground truth files in the ``gold\_dataset'' directory. They are in tabular format for ease of comparison purposes.

$\bullet$  \textit{\textbf{gold\_attributes\_relations\_500pts\_500studies1st.txt}} is the ground truth file which contains 21,594 object-to-attribute relations manually annotated for 3,042 sentences from the \textit{first} CXR study for 500 unique patients. The notebook `object-attribute-relation\_evaluation.ipynb' explains in detail how we it to calculate the performance of object-to-attribute relation extraction.

$\bullet$  \textit{\textbf{gold\_comparison\_relations\_500pts\_500studies2nd.txt}} is the ground truth file which contains 5,156 object-object (per attribute) comparison relations for 638 sentences from the \textit{second} CXR study for the same 500 unique patients. The notebook `object-object-comparison-relation\_evaluation.ipynb' uses it to calculate the performance for object-to-object-comparison relation extraction.

$\bullet$  The four \textit{\textbf{bbox\_coordinate\_annotations*.csv}} files contain the manually annotated bounding box coordinates for the objects on the corresponding 1,000 unique CXR images. The notebook `object-bbox-coordinates\_evaluation.ipynb' calculates the bounding box object detection performance using these ground truth files.

$\bullet$ Lastly, \textit{\textbf{final\_merging\_report\_and\_bbox\_ground\_truth.ipynb}} combines the manual text and anatomical bbox annotations as \textit{\textbf{gold\_object\_attribute\_with\_coordinates.txt}} and \textit{\textbf{gold\_object\_comparison\_with\_coordinates.txt}}.

Additional supporting files for measuring the performance of the silver dataset against the gold standard are described in Supplementary (Section \ref{gold_supp}):

% % Can also put this in supplementary material
% \noindent \textbf{gold\_all\_sentences\_500pts\_1000studies.txt} contains all the sentences tokenized from the original MIMIC-CXR reports that were used to create the gold standard dataset. We include this file because sentences with no relevant object, attribute or relation descriptions did not make it into the gold standard dataset. We renamed `subject\_id' from MIMIC-CXR dataset to `patient\_id' in Chest ImaGenome dataset to avoid confusion with field names for relationships in the scene graphs. Otherwise, the ids are unchanged. Sentences in the tokenized file are assigned to `history', `prelimread', or `finalreport' in the `section' column. The `sent\_loc' column contains the order of the sentences as in the original report. Minimal tokenization has been done to the sentences.

% \noindent \textbf{gold\_bbox\_scaling\_factors\_original\_to\_224x224.csv} contains the scaling `ratio' and the paddings (`left', `right', `top', and `bottom') added to square the image after resizing the original MIMIC-CXR dicoms to 224x224 sizes. These ratios were used to rescale the annotated coordinates for 224x224 images back to the original CXR image sizes.

% \noindent \textbf{auto\_bbox\_pipeline\_coordinates\_1000\_images.txt'} contains the bounding box coordinates that were automatically extracted by the Bbox pipeline for the different objects for images in the gold standard dataset. It is in tabular format like with the ground truth for easier evaluation purposes.
