\section{Conclusion and Future Work}
\label{Sec:conclusion}
In this paper, we study a novel problem of learning robust GNNs on noisy graphs with limited labeled nodes. We demonstrate that noisy edges and limited labeled nodes would largely impair the performance of GNNs. A novel RS-GNN is proposed to mitigate these issues. More specially, we adopt the edges in the noisy graph as supervision to obtain a denoised and densified graph to facilitate the message passing for predictions of unlabeled nodes. Moreover, we also utilize the supervision from the generated graph to explicitly involve unlabeled nodes. Extensive experiments on real-world datasets demonstrate the robustness of the proposed framework on noisy graphs with limited labeled nodes. There are several directions requiring further investigation. First, we focus on structural noise in this paper. However, for some applications, such as social networks, users may provide fake attributes for privacy. Thus, we will extend it to graphs with structural noise as well as attribute noise under the setting of limited labeled nodes. Second, the labels may also contain noise which may degrade the performance of GNNs due to the message passing. Therefore, we will also explore methods that handle noisy graphs with limited and noisy labels. 

\section{Acknowledgement}
This material is based upon work supported by, or in part by, the National Science Foundation (NSF) under grant \#IIS1955851, and Army Research Office (ARO) under grant \#W911NF-21-1-0198. The findings and conclusions in this paper do not necessarily reflect the view of the funding agency. 
