\documentclass[runningheads]{llncs}

\usepackage{amsmath}
\usepackage{oz}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{tikz-cd}
\usepackage{caption}
\usepackage{framed}
\usepackage{subcaption}
\captionsetup{compatibility=false}

\usepackage[utf8x]{inputenc}
\usepackage{amssymb, upgreek}

\usepackage{color}

\usepackage{rotating}

% Lean preamble
\definecolor{keywordcolor}{rgb}{0.7, 0.1, 0.1}   % red
\definecolor{commentcolor}{rgb}{0.4, 0.4, 0.4}   % grey
\definecolor{symbolcolor}{rgb}{0.0, 0.1, 0.6}    % blue
\definecolor{sortcolor}{rgb}{0.1, 0.5, 0.1}      % green
\definecolor{errorcolor}{rgb}{1, 0, 0}           % bright red
\definecolor{stringcolor}{rgb}{0.5, 0.3, 0.2}    % brown

\usepackage{listings}
\usepackage{chngcntr}
\def\lstlanguagefiles{lstlean.tex}
\lstset{
	language=lean,
	abovecaptionskip=\smallskipamount,
	belowcaptionskip=\smallskipamount,
	belowskip=-2em,
	basicstyle=\small
	}
\lstdefinestyle{lean}{
	float=t,
	%floatplacement=tp,
	%aboveskip=3pt,
	%belowskip=-3pt,
	numbers=left
}

%\captionsetup[lstlisting]{numberbychapter=false}

\input{macros}
\input{macros_spl}
\begin{document}
\counterwithout{lstlisting}{chapter}

\title{Towards Certified Analysis of Software Product Line Safety Cases}
\author{Ramy Shahin\inst{1} \and
	Sahar Kokaly\inst{2} \and
	Marsha Chechik\inst{1}}
\institute{University of Toronto, Toronto, Canada\\
	\email{\{rshahin,chechik\}@cs.toronto.edu} \and
	General Motors, Canada\\
	\email{sahar.kokaly@gm.com}}
\maketitle

\vspace{-0.2in}
\begin{abstract}
	Safety-critical software systems are in many cases designed and implemented as families of products, usually referred to as Software Product Lines (SPLs). Products within an SPL vary from each other in terms of which features they include. Applying existing analysis techniques to SPLs and their safety cases is usually challenging because of the potentially exponential number of products with respect to the number of supported features.
	In this paper, we present a methodology and infrastructure for certified \emph{lifting} of existing single-product safety analyses to product lines. To ensure certified safety of our infrastructure, we implement it in an interactive theorem prover, including formal definitions, lemmas, correctness criteria theorems, and proofs.
	%Modifying a software system might impact its safety case in many ways.  algorithms identify how local changes to specific system elements affect safety case elements, given traceability links between the two. Those algorithms can only work on the artifacts of a single software product at a time. However, in many cases a family of software products is developed together in the form of a Software Product Line (SPL), with artifacts potentially shared between different product variants. In this paper, we present lifting of a CIA algorithm to Software Product Lines aimed at supporting the input of feature-specific modifications, and potentially returning feature-specific safety case annotations. 
	
	We apply this infrastructure to formalize and lift a Change Impact Assessment (CIA) algorithm. We present a formal definition of the lifted algorithm, outline its correctness proof (with the full machine-checked proof available online), and discuss its implementation within a model management framework. 
\keywords{Safety cases, Product lines, Lean, Certified analysis.}
\end{abstract}
\vspace{-0.2in}

\input{intro}
\input{background}
\input{methodology}
\input{cia}
\input{impl}
\input{related}
\input{conclusion}

\bibliographystyle{splncs04}
\bibliography{spl,modeling,pl,safety}
\end{document}