\documentclass{article}
\input{defspack}
\newcommand \blue[1]        {{\color{blue}#1}}
\ninept
\title{Sampling and Reconstruction of Graph Signals via  Weak Submodularity and Semidefinite Relaxation}
%Sampling and Reconstruction of Graph Signals via Weak Submodular and Convex Optimization
\name{Abolfazl Hashemi$^\dagger$, Rasoul Shafipour$^\ddagger$, Haris Vikalo$^\dagger$, and Gonzalo Mateos$^\ddagger$}
\address{$^\dagger$Dept. of Electrical and Computer Engineering, University of Texas at Austin, Austin, TX, USA\\
$^\ddagger$Dept. of Electrical and Computer Engineering, University of Rochester, Rochester, NY, USA}
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
We study the problem of sampling a bandlimited graph signal in the presence of noise, where the objective is to 
select a node subset of prescribed cardinality that minimizes the signal reconstruction mean squared error (MSE). 
To that end, we formulate the task at hand as the minimization of MSE subject to binary constraints, and 
approximate the resulting NP-hard problem via semidefinite programming (SDP) relaxation. Moreover, we provide 
an alternative  formulation based on maximizing a monotone weak submodular function and propose a randomized-greedy 
algorithm to find a sub-optimal subset. We then derive a worst-case performance guarantee on the MSE returned 
by the randomized greedy algorithm for general non-stationary graph signals. The efficacy of the proposed 
methods is illustrated through numerical simulations on synthetic and real-world graphs. Notably, the randomized greedy 
algorithm yields an order-of-magnitude speedup over state-of-the-art greedy sampling schemes, while incurring 
only a marginal MSE performance loss.
\end{abstract}
%
\begin{keywords}
graph signal processing, sampling, weak submodularity, semidefinite programming, randomized algorithms \vspace{-0.2cm}
\end{keywords}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\input{Secintro}
\vspace{-0.25cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries and Problem Statement}\label{sec:pre}
\input{Secpre}
\vspace{-0.2cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{New Schemes for Sampling Graph Signals}\label{sec:alg}
\input{Secalg}
\vspace{-0.55cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Simulations}\label{sec:sim}
\input{Secsim}
\vspace{-0.2cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion} \label{sec:concl}
We considered the problem of sampling a bandlimited graph signal in the presence of noise, where the goal is to select a subset of graph nodes of prescribed cardinality to minimize the mean square signal reconstruction error. First, we developed an SDP relaxation method to find an approximate solution to the NP-hard sample-set selection task. 
Then  the problem was reformulated as the maximization of a monotone weak submodular function, and a novel randomized-greedy algorithm was proposed to find a near-optimal sample subset. In addition, we analyzed the performance of the randomized greedy algorithm, and showed that the resulting MSE is a constant factor away from the optimal MSE. Unlike prior work, our guarantees do not require stationarity of the graph signal. Simulations studies showed that the proposed sampling algorithms compare favorably to competing alternatives in terms of accuracy and runtime.

% As part of the future work, it is valuable to theoretically study the performance of the SDP relaxation method proposed in this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\newpage
\bibliographystyle{IEEEbib}
%\bibliographystyle{ieeetr}\footnotesize
\bibliography{refs}
\end{document}
