\documentclass[10pt, onecolumn]{IEEEtran}
\usepackage{array}
\usepackage{subfigure}
\usepackage{xcolor, colortbl}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs, tabularx, colortbl,threeparttable}
\usepackage{multirow,amsmath,mathrsfs,verbatim, bbm}
\usepackage{graphicx}
\usepackage{authblk}
\definecolor{mygray}{gray}{.7}
\usepackage{listings}
\usepackage{xspace}
\usepackage{caption2}

\newcommand{\nickName}{AppStarscream\xspace}

\renewcommand{\figurename}{Figure}

%\renewcommand{\baselinestretch}{0.98}
\begin{document}
\bibliographystyle{abbrv}

\title{Flexible Installability of Android Apps with App-level Virtualization based Decomposition}


\author{Yi Liu}
\author{Yun Ma}
\author{Xuanzhe Liu}
\affil{}
\renewcommand\Authfont{\fontsize{10}{11.4}\selectfont}
\renewcommand\Affilfont{\fontsize{9}{10.8}\itshape}


\maketitle


\begin{abstract}
With the popularity of smartphones, users are heavily dependent on mobile applications for daily work and entertainments. However, mobile apps are becoming more and more complicated with more features and increasing size, part of which may be redundant to users. Due to the limitation of current installation mechanism, users have to download full-size applications instead of enjoy only the wanted features. Such full-size apps may consume more resources, including CPU, memory, and energy, which may hurt users' enthusiasm for further installation. We first conduct an empirical study to characterize used features when users interact with mobile applications, and find that users only consume a small set features of target apps. To address this problem, we present \nickName{}, which offers to decompose and run Android apps with app-level virtualization. With \nickName{}, developers can decompose an existing app into multiple bundles, including a base bundle with frequently used pages and feature bundles with inactive pages. Then, end users can just download base bundle for daily use, and visit uninstalled pages on demand. We have implemented a prototype system and evaluated it with real-world apps showing that \nickName{} is efficient and practical.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010575.10010755</concept_id>
%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
%  <concept_significance>300</concept_significance>
% </concept>
% <concept>
%  <concept_id>10010520.10010553.10010554</concept_id>
%  <concept_desc>Computer systems organization~Robotics</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
% <concept>
%  <concept_id>10003033.10003083.10003095</concept_id>
%  <concept_desc>Networks~Network reliability</concept_desc>
%  <concept_significance>100</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}


\begin{IEEEkeywords}
	App decomposition, App-level virtualization, On-demand installation
\end{IEEEkeywords}


\IEEEpeerreviewmaketitle


\input{section/introduction}
\input{section/motivation}
\input{section/design_principle_challenges}
\input{section/approach}
\input{section/implementation}
\input{section/evaluation}
\input{section/discussion}
\input{section/relatedwork}
\input{section/conclusion}

\bibliography{ref}

\end{document}
