\subsection{Measurement Model}
\label{subsec: measurement model}
Consider the case of a single feature $f_j$ observed by the stereo cameras with pose $\left({}^{C_i}_G\mathbf{q}, {}^G\mathbf{p}_{C_i}\right)$. Note that the stereo cameras have different poses, represented as $\left({}^{C_{i,1}}_G\mathbf{q}, {}^G\mathbf{p}_{C_{i,1}}\right)$ and $\left({}^{C_{i,2}}_G\mathbf{q}, {}^G\mathbf{p}_{C_{i,2}}\right)$ for left and right cameras respectively, at the same time instance. Although the state vector only contains the pose of the left camera, the pose of the right camera can be easily obtained using the extrinsic parameters from the calibration. The stereo measurement, $\mathbf{z}_i^j$, is represented as,
\begin{equation}
\mathbf{z}_i^j = 
\begin{pmatrix}
u_{i, 1}^j \\ v_{i, 1}^j \\ 
u_{i, 2}^j \\ v_{i, 2}^j
\end{pmatrix} 
= 
\begin{pmatrix}
\frac{1}{{}^{C_{i, 1}}Z_j} & \mathbf{0}_{2\times 2} \\
\mathbf{0}_{2\times 2} & \frac{1}{{}^{C_{i, 2}}Z_j}
\end{pmatrix}
\begin{pmatrix}
{}^{C_{i, 1}}X_j \\ {}^{C_{i, 1}}Y_j \\
{}^{C_{i, 2}}X_j \\ {}^{C_{i, 2}}Y_j
\end{pmatrix}
\label{eq: stereo measurement}
\end{equation}
Note that the dimension of $\mathbf{z}_i^j$ can be reduced to $\mathbb{R}^3$ assuming the stereo images are properly rectified. However, by representing $\mathbf{z}_i^j$ in $\mathbb{R}^4$, it is no longer required that the observations of the same feature on the stereo images are on the same image plane, which removes the necessity for stereo rectification. In Eq.~\eqref{eq: stereo measurement}, $\left({}^{C_{i, k}}X_j\  {}^{C_{i, k}}Y_j\  {}^{C_{i, k}}Z_j \right)^\top$, $k\in\{1, 2\}$, are the positions of the feature, $f_j$, in the left and right camera frame, $C_{i, 1}$ and $C_{i, 2}$, which are related to the camera pose by,
\begin{equation*}
\begin{gathered}
{}^{C_{i, 1}}\mathbf{p}_j = 
\begin{pmatrix}
{}^{C_{i, 1}}X_j \\ {}^{C_{i, 1}}Y_j \\ {}^{C_{i, 1}}Z_j
\end{pmatrix} = 
C\left({}^{C_{i, 1}}_G\mathbf{q}\right)
\left({}^G\mathbf{p}_j-{}^G\mathbf{p}_{C_{i, 1}}\right) \\
\begin{aligned}
{}^{C_{i, 2}}\mathbf{p}_j &= 
\begin{pmatrix}
{}^{C_{i, 2}}X_j \\ {}^{C_{i, 2}}Y_j \\ {}^{C_{i, 2}}Z_j
\end{pmatrix} = 
C\left({}^{C_{i, 2}}_G\mathbf{q}\right)
\left({}^G\mathbf{p}_j-{}^G\mathbf{p}_{C_{i, 2}}\right) \\
&= C\left({}^{C_{i, 2}}_{C_{i, 1}}\mathbf{q}\right)
\left({}^{C_{i, 1}}\mathbf{p}_j - 
{}^{C_{i, 1}}\mathbf{p}_{C_{i, 2}}\right)
\end{aligned}
\end{gathered}
\end{equation*} 
The position of the feature in the world frame, ${}^G\mathbf{p}_j$, is 
computed using the least square method given in~\cite{mourikis2007multi} based on the current estimated camera poses. Linearizing the measurement model at the current estimate, the residual of the measurement can be approximated as,
\begin{equation}
\label{eq: error measurement model}
\mathbf{r}^j_i = 
\mathbf{z}_i^j - \hat{\mathbf{z}}_i^j = 
\mathbf{H}_{C_i}^j\tilde{\mathbf{x}}_{C_i} + 
\mathbf{H}_{f_i}^j{}^G\tilde{\mathbf{p}}_{j} + 
\mathbf{n}_i^j
\end{equation}
where $\mathbf{n}_i^j$ is the noise of the measurement. The measurement Jacobian $\mathbf{H}_{C_i}^j$ and $\mathbf{H}_{f_i}^j$ are shown in Appendix~\ref{sec: measurement jacobian}.

By stacking multiple observations of the same feature $f_j$, we have,
\begin{equation*}
%\label{eq: stacked error measurement model}
\mathbf{r}^j = 
\mathbf{H}_{\mathbf{x}}^j\tilde{\mathbf{x}} + 
\mathbf{H}_f^j {}^G\tilde{\mathbf{p}}_j + 
\mathbf{n}^j
\end{equation*}
As pointed out in~\cite{mourikis2007multi}, since ${}^G\mathbf{p}_j$ is computed using the camera poses, the uncertainty of ${}^G\mathbf{p}_j$ is, therefore, correlated with the camera poses in the state. In order to ensure the uncertainty of ${}^G\mathbf{p}_j$ does not affect the residual, the residual in Eq.~\eqref{eq: error measurement model} is projected to the null space, $\mathbf{V}$, of $\mathbf{H}_f^j$ , i.e.
\begin{equation}
\label{eq: null space error measurement model}
\mathbf{r}^j_o 
= \mathbf{V}^\top \mathbf{r}^j
= \mathbf{V}^\top \mathbf{H}_{\mathbf{x}}^j\tilde{\mathbf{x}} +
\mathbf{V}^\top \mathbf{n}^j
= \mathbf{H}_{\mathbf{x}, o}^j\tilde{\mathbf{x}} + 
\mathbf{n}^j_o
\end{equation}
Based on Eq.~\eqref{eq: null space error measurement model}, the update step of the EKF can be carried out in a standard way.
















