\section{Recovery for $k$-cardinality constraint $(2-\tfrac{1}{k})$-stable system}
A special case of submodular maximization on $p$-extendible systems is when we have a uniform matroid constraint where the only feasible solutions are those that have cardinality $k \ge 1$ ($\I=\{S: |S|\le k\}$). For this special case, recall that greedy is a $(1-\tfrac{1}{e})$-approximation (in fact, $1-(1-\tfrac{1}{k})^k$) and that this is tight \cite{feige1998threshold}. Regarding stability, we may as well hope that a stronger recovery result is true, i.e. that greedy recovers $\gamma$-stable instances for $\gamma<p+1$. This is indeed true.

\begin{theorem}
For submodular maximization under a uniform matroid ($\I=\{S: |S|\le k\},k\ge 1$), greedy recovers $(2-\tfrac{1}{k})$-stable instances.
\end{theorem}

\begin{proof}
Suppose $f$ is monotone submodular, the optimum solution is $S^*$ (with $S^*=k$) and that greedy selects $S=\{e_1,\dots,e_k\}$ (with that order). We can assume without loss of generality that $f(S^*)=1$ and that the first element $e_1 \in S\sm S^*$. By the greedy criterion we have: $f(e_1)\ge \max_{e\in S^*}f(e)\ge \tfrac{1}{k}$ and by the approximation guarantee for greedy: $f(S)\ge 1-(1-\tfrac{1}{k})^k$. We can already compute some (pessimistic) estimate for the stability factor $\gamma$ needed for recovery. In order to favour the value of the greedy solution $S$ over the optimum $S^*$, we could perturb just the marginal value of $e_1\in S\sm S^*$:
\[
\tilde{f}(e_1)=\gamma f(e_1), \tilde{f}(S)=\gamma f(e_1) + f_{\{e_1\}}(e_2)+f_{\{e_1,e_2\}}(e_3)+\dots+f_{\{e_1,e_2,\dots,e_{k-1}\}}(e_k)=
\]
\[
=(\gamma-1) f(e_1)+f(S)\ge (\gamma-1)\tfrac{1}{k}+1-(1-\tfrac{1}{k})^k
\]
To ensure $\tilde{f}(S)\ge \tilde{f}(S^*) \iff (\gamma-1)\tfrac{1}{k}+1-(1-\tfrac{1}{k})^k\ge 1$, we need to have $\gamma\ge k(1-\tfrac{1}{k})^k+1$. Since $e^x\ge1+x, \forall x\in \RR$ we can deduce that if the instance is $(\tfrac{k}{e}+1)$-stable then greedy recovers the optimum $S^*$. Below we see how to bring this factor down to $(2-\tfrac{1}{k})$. We make two important observations regarding the perturbation factor $\gamma$ needed for recovery.

Recall that $f(e_1)\ge \tfrac{1}{k}$. Let $S_i=\{e_1,\dots,e_i\}$. The first important observation is that $\gamma$ will need to be the largest when $f(e_1) = \tfrac{1}{k}$ and all elements of $S^*$ contribute the same to the greedy, i.e. for any $i$: $f_{S_i}(e_j)=f_{S_i}(e_{j'})$, where $e_j,e_{j'}\in S^*$. This follows by the greedy criterion since otherwise greedy would pick the best among $e \in S^*$ and be better off (see figure PUT FIGURE). 

The second observation is that $\gamma$ will need to be the largest when only $e_1 \notin S^*$ and $e_i\in S^*, \forall i \in \{2,\dots,k\}$ (recall perturbations in favour of greedy can only affect elements $e\in S\sm S^*$). To see this, let's compare two cases:
\begin{itemize}
\item $S\sm S^*=\{e_1\}$ and $S\cap S^*=\{e_2,\dots,e_k\}$: Suppose $\gamma_1$ perturbation is needed so that $\tilde{f}(S)\ge \tilde{f}(S^*)=f(S^*)=1$. Then $\tilde{f}(S)=\gamma_1 f(e_1)+ f_{\{e_1\}}(e_2)+f_{\{e_1,e_2\}}(e_3)+\dots+f_{\{e_1,e_2,\dots,e_{k-1}\}}(e_k)=\gamma_1\tfrac{1}{k}+(k-1)f_{\{e_1\}}(e_2)=\gamma_1\tfrac{1}{k}+(k-1)\left(\tfrac{1}{k}(1-\tfrac{1}{k})\right)$ and $\tilde{f}(S)\ge1\iff \gamma_1\ge 2-\tfrac{1}{k}$.
\item $S\sm S^*=\{e_1,e_2\}$ and $S\cap S^*=\{e_3,\dots,e_k\}$: Suppose $\gamma_2$ perturbation is needed so that $\tilde{f}(S)\ge \tilde{f}(S^*)=f(S^*)=1$. Then $\tilde{f}(S)=\gamma_2 f(e_1)+\gamma_2 f_{\{e_1\}}(e_2)+ f_{\{e_1,e_2\}}(e_3)+\dots+f_{\{e_1,e_2,\dots,e_{k-1}\}}(e_k)=\gamma_2\tfrac{1}{k}+\gamma_2\left(\tfrac{1}{k}(1-\tfrac{1}{k})\right)+(k-2)f_{\{e_1,e_2\}}(e_3)=\gamma_2\tfrac{1}{k}+\gamma_2\left(\tfrac{1}{k}(1-\tfrac{1}{k})\right)+(k-2)\left(\tfrac{1}{k}(1-\tfrac{1}{k})^2\right)$ and $\tilde{f}(S)\ge1\iff \gamma_2\ge \tfrac{4k^2-5k+2}{2k^2-k}$.
\end{itemize}
We check that $2-\tfrac{1}{k}\ge \tfrac{4k^2-5k+2}{2k^2-k} \iff k\ge1$ and thus in the first case the perturbation factor needed for recovery is larger and $(2-\tfrac{1}{k})$-stability is sufficient for exact recovery since otherwise $S\sm S^*\neq \emptyset $ and perturbing as in the first case above we would get $\tilde{f}(S)\ge \tilde{f}(S^*)$, contradicting the stability of the given instance. This $(2-\tfrac{1}{k})$ threshold is also tight (see figure PUT FIGURE).
\end{proof}

