\section{Conclusion and Further Research}\label{sec:conclusion}
Many well-studied problems like Matching, Independent Set or Asymmetric TSP belong to the family of $p$-extendible systems. In this paper, we established some connections between $p$-systems and $p$-extendible systems with the notion of Bilu-Linial stability of meaningful solutions that is observed in real world data. We proved some positive recovery results for the Greedy algorithm and for Local Search and we also gave tight counter-examples for our algorithms. Finally, we extended the notion of Bilu-Linial stability to submodular functions, proving similar recovery results in that setting and we also gave another characterization of $p$-extendible systems. As far as \textit{worst-case} approximation is concerned, we showed that Local Search is a $p^2$-approximation for $p$-extendible systems ($p^2+1$ for the submodular case) and that it fails for $p$-systems, improving on an old result by Fisher et al~\cite{nemhauser1978analysis, fisher1978analysis, korte1978analysis}.

Some interesting questions we leave open is to understand the deeper connections between approximation and recovery of stable solutions. What is the relation between the approximation and the recovery thresholds? When is an approximation algorithm going to recover stable solutions? Proving general lower bounds for recovery in the spirit of \cite{balcan2015k}, which showed that recovering symmetric $k$-center on $(2- \epsilon)$-stable instances is hard unless $NP = RP$, is also another direction we want to explore. Finally, which of the approximation algorithms we already know, have the more refined guarantee discussed in \hyperref[sec:approx-stability]{Section \ref{sec:approx-stability}} and thus directly yield recovery results?