\chapter{Acknowledgements}
\label{chap:ack}

% PhD advisors
First, my heartfelt thanks to my PhD advisor Prof. Peter Gehler without whom
this thesis work would not have materialized. His suggestions helped me work
on very interesting research problems in computer vision and machine learning
whereas stimulating discussions with him helped me propose compelling techniques
for those problems. He also taught me how to be critical about various aspects of
a research project. I thank Dr. Sebastian Nowozin for being a co-advisor in my
first PhD research project and teaching me how to be rigorous in research.

% Inspiration and help
Thanks to Prof.~Michael Black for allowing me to be a part of his vibrant research
group in T\"ubingen, where I conducted my PhD research. Special thanks to
Prof. Bipin Indurkhya for teaching me how to be mature in our reasoning and thinking
while doing research.~Thanks to my masters advisor Prof.~Jayanthi Sivaswamy for her
guidance during the start of my research career. Thanks to Dr. Pushmeet Kohli,
Dr. Ali Eslami, Dr. John Winn and Dr. Daniel Tarlow for giving me a great internship
opportunity at Microsoft Research that helped me getting a broader perspective over
the fields of computer vision and machine learning.
Thanks to Prof. Jan Kautz for giving me a wonderful opportunity at Nvidia
to further pursue my research interests after my PhD.

% Thesis committe and reviewers
I am thankful to Prof. Hendrik Lensch, Prof. Peter Gehler, Prof. Felix Wichmann and
Prof. Matthias Bethge for being a part of my thesis committee and
thanks to Prof. Hendrik Lensch and Prof. Peter Gehler for providing reviews to
this thesis work. Special thanks to Dr. Iasonas Kokkinos for providing an additional
review for this thesis.
Thanks to Thomas Nestmeyer, Dr. Laura Sevilla, Angjoo Kanazawa,
Fatma G\"uney, Jonas Wulff and Christoph Lassner for their helpful feedback
and comments on this thesis manuscript.

% Collaborators
I am fortunate to have collaborated with several great researchers during my
PhD: Dr. Martin Kiefel, Raghudeep Gadde, Dr. Sebastian Nowozin, Dr. Ali Eslami,
Dr. John Winn, Dr. Pushmeet Kohli, Dr. Matthew Loper, Prof. Michael Black,
Dr. Laura Sevilla, Dr. Deqing Sun, Daniel Kappler, Dr. Renaud Marlet and Dr. Daniel Tarlow.
I am very grateful to them.
Special thanks to Raghudeep Gadde and Dr. Laura Sevilla for trusting me and
letting me be a part of their research projects. I am highly thankful to Raghudeep Gadde
for the countless hours we spent together on brainstorming various research questions
and techniques.

% Tuebingen group
I want to express my gratitude to my wonderful colleagues at Max-Planck Institute
Thomas Nestmeyer, Raghudeep Gadde, Abhilash Srikantha, Dr. Laura Sevilla, Dr. Silvia Zuffi, Jonas Wulff,
Fatma G\"uney, Dr. Martin Kiefel,
Dr. Andreas Lehrmann, Christoph Lassner, Sergey Prokudin, Dr.~Osman Ulusoy,
Dr. Federica Bogo, Daniel Kappler, Prof. Michael Black,
Dr. Andreas Geiger, Prof. J\"urgen Gall, Dr. Chaohui Wang, Dr. Javier Romero,
Dr. Hueihan Jhuang, Dr. Dimitris Tzionas, Dr. Gerard Pons-Moll,
Dr. Cristina Cifuentes, Dr. Naejin Kong, Naureen Mohamed, Angjoo Kanazawa,
Dr. Ijaz Akhter, Dr. S{\o}ren Hauberg, Dr. Matthew Loper, Dr. Aggeliki Tsoli,
Dr. Sergi Pujades, Siyu Tang, Dr. Si Yong Yeo, Joel Janai, Yiyi Liao and others
for their insightful discussions, technical and non-technical conversations and making my
road to obtaining my PhD less bumpy. Thanks to Melanie Feldhofer, Jon Anning
and Nicole Overbaugh for their great support in administrative matters.

% Friends
I am highly indebted to my friends Srikar Ravulapalli, Srujan Sunkoju, Srinivas Sunkara,
Vamshi Velagapuri, Chandrasekhar Varkala, Sunil Soni, Rohit Gernapudi, Raghudeep Gadde,
Seetharamakrishna Madamsetti, Tenzin Bety, Tsering Bhuti, Phurbu Thackchoe, Varsha Eluri
and Dharani Kodali for always supporting, helping and encouraging me in the times of need.
Thanks to Dr. Sowmya Vajjala and Dr. Lorenzo Ducci
for the fun times we had in and around T\"ubingen and also patiently listening to my
ravings about both research and life in general.

% Family
Finally, I would like to thank my family members who have given me great freedom and support
to pursue my interests. I am very thankful to my parents
Dr. Chandrasekhar Jampani and Sudharani Kodali, my brother Prasanth Jampani, my sister-in-law Neelima Kamani,
my grandmother Krishnakumari Kodali for their great support during all these years.
Special thanks to my late grandfather and my favorite person Anjaneyulu Kodali for
understanding me so well and encouraging me in different aspects of life. He will always
be in my heart. Lastly, but importantly, I am very grateful to my wife
Dr. Yuyu Liu for her love and continued support over the last few years and for sharing
the ups and downs of my life.
