
\section{List of Figures}\label{sec:list_of_figures}
\begin{itemize}
    \item Schematic of Telescope, with vents and angles highlighted: \textbf{half a page?}
    \item \textbf{1 full page}, final network:
    \begin{itemize}
        \item Sliced Wasserstein AutoEncoder (SWAE) + Imputation block
        \item Tabnet block (modify from \cite{tabnet}
        \item Speed as a Supervisor (SaaS) block (modify from \cite{saas2})
        \item Mixture Density Network (MDN)
    \end{itemize}
    \item \textbf{1x1}: Show convergence of imputation (\S\ref{sec:DL_imputation})
    \item Exploratory Data Analysis (EDA) plots from Billy's work:
    \begin{itemize}
        \item divide features into groups. temperature, temperature difference, (insert more here). for each group, identify the top two feature with strongest correlations with mpiq, and show two figures with two plots each--mpiq $\ge$ mkamiq, with vents open and closed, repeat for mpiq $<$ mkamiq. for each group, a total of 4 subplots (2 per feature), arranged in \textbf{2x2} fashion. for a total of \textbf{k} such plots, for k groups.
        \item anything else?
    \end{itemize}
    \item EDA plots from Racine's work. still need to finalize.
    \item Probability Calibration (\S\ref{sec:DL_probability_calibration}), Errors (\S\ref{sec:DL_errors}).
    \begin{itemize}
        \item \textbf{1x3}, or \textbf{1x2 + 1x1}. point predictions, aleatoric errors + epistemic errors, aleatoric+epistemic WITH probability calibration. in each plot, jot down all the metrics from \S\ref{sec:DL_metrics}.
    \end{itemize}
    \item Benefit of MDN (\S\ref{sec:DL_MDN}):
    \begin{itemize}
        \item \textbf{2x2} plot: for gaussian:for the two cases of with and without mdn, joint plot of median predictions vs ground truth. repeat the same for beta.
        \item \textbf{1x1} plot: histogram of mpiq fitted with gaussian and fitted with beta, to demonstrate the superiority of the latter.
    \end{itemize}
    \item Feature Importance
    \begin{itemize}
        \item \textbf{1x1} summary plot with positive and negative correlations. \textbf{need to write code to combine the two}
        \item \textbf{1x2} Evolution of Feature Importance with time, with clustering. \textbf{need to write code for this}.
    \end{itemize}
    \item SSL (\S\ref{sec:DL_SSL}): \textbf{1x2} pred v/s true (calibrated). for both, jot down all metrics. SSL should show improved results.
    \item \textbf{1x2}: Compare performance to NGBoost + Shap
\end{itemize}
