\pdfoutput=1 
\documentclass[a4paper,11pt]{article}
%% uncomment the following for journal submission
\pdfoutput=1
\usepackage[english]{babel}
\usepackage{jheppub}
\usepackage{subfigure}
%\usepackage{subfig}
\usepackage{xspace}
\usepackage{amsmath,amssymb,textcomp,enumerate,alltt,xspace,multirow}
\usepackage{tensor}
\usepackage{slashed}
\usepackage{bbm}
\usepackage{multicol}

%% graphics
\usepackage{graphicx}
\usepackage{relsize}
\usepackage{pstricks}
\usepackage{color}
\usepackage{xcolor}
%\usepackage{showlabels}
\graphicspath{fig}

\bibliographystyle{JHEP}

\makeatletter
\g@addto@macro\bfseries{\boldmath}
\makeatother


\input texmacros.tex

\newcommand{\LT}[1]{{\bf \textcolor{blue}{[LT: #1]}}}
\newcommand{\GG}[1]{{\bf \textcolor{red}{[GG: #1]}}}


%%%%%%%%%
\preprint{
\begin{flushright}
MSUHEP-21-016 \\
OUTP-21-20P   \\
\end{flushright}
}
%%%%%%%%%
%%%%%%%%%

\title{Three-loop helicity amplitudes for four-quark scattering in massless QCD}

\author[a,c]{Fabrizio Caola,}
\author[b]{Amlan Chakraborty,}
\author[a,d]{Giulio Gambuti,}
\author[b]{Andreas von Manteuffel,}
\author[a]{Lorenzo Tancredi}
\emailAdd{fabrizio.caola@physics.ox.ac.uk}
\emailAdd{chakra69@msu.edu }
\emailAdd{giulio.gambuti@physics.ox.ac.uk}
\emailAdd{vmante@msu.edu}
\emailAdd{lorenzo.tancredi@physics.ox.ac.uk}

\affiliation[a]{
Rudolf Peierls Centre for Theoretical Physics, University of Oxford,\\
Clarendon Laboratory, Parks Road, Oxford OX1 3PU
}


\affiliation[b]{
Department  of  Physics  and  Astronomy,  Michigan  State  University,\\
East  Lansing,  Michigan  48824,  USA
}

\affiliation[c]{
Wadham College, University of Oxford, Parks Road, Oxford OX1 3PN, UK
}

\affiliation[d]{
New College, University of Oxford, Holywell Street, Oxford OX1 3BN, UK
}

\abstract{
%
We compute the three-loop corrections to the helicity amplitudes for $q\bar{q}\to Q\bar{Q}$ scattering in massless QCD.
In the Lorentz decomposition of the scattering amplitude we avoid evanescent  Lorentz structures and map the corresponding form factors directly to the physical helicity amplitudes.
We reduce the amplitudes to master integrals and express them in terms of harmonic polylogarithms.
The renormalised amplitudes exhibit infrared divergences of dipole and quadrupole type, as predicted by previous work on the infrared structure of multileg scattering amplitudes.
We derive the finite remainders and present explicit results for all relevant partonic channels, both for equal and different quark flavours.
%
}

\keywords{QCD, Collider Physics, N3LO calculations}

\allowdisplaybreaks[1]

\begin{document}
\maketitle

\input{1-intro}
\input{2-notation}
\input{3-amplitude}
\input{4-computation}
\input{5-subtraction}
\input{6-results}
\input{7-other_processes}
\input{8-conclusions}


\section*{Acknowledgments}
LT is grateful to T.\ Peraro for
collaboration on a related project on 
the tensor decomposition in the 't Hooft-Veltman scheme used
in this paper. We thank F. Buccioni for his assistance in comparing our one-loop results to \texttt{OpenLoops}.
The research of FC is
partially supported by the ERC Starting Grant 804394
HipQCD. AvM is supported in part by the National Science Foundation through Grant 2013859.
LT and GG are supported by the Royal Society through Grant
URF/R1/191125.
\appendix

\input{9-appA}
\input{10-appB}
\input{11-appC}

\bibliography{biblio}

\end{document}
