\RequirePackage{fix-cm}
\RequirePackage{amsmath}
\documentclass[smallextended]{svjour3}
\smartqed 
\usepackage{balance}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tcolorbox}
\usepackage{url}
\usepackage{xspace}

\usepackage{tikz}
\usetikzlibrary{automata,arrows,positioning,calc}
\everymath{\displaystyle}

\usepackage{pgfplots}
\pgfplotsset{compat=1.15}

% \usepackage{comment}
% \usepackage{fancybox}
% \usepackage{hyperref}
%\usepackage{mathtools}
% \usepackage{pdflscape}
% \usepackage{subfigure}

% ------------------------------------------------------------------------------
\newcommand{\hypobox}[1]{\begin{center}%
   \noindent\thicklines\setlength{\fboxsep}{8pt}%
    \cornersize{0.2}\Ovalbox{\begin{minipage}{3.0in}%
        \textit{#1}\end{minipage}} \end{center}}
% -----------------------------------------------------------------------------

\renewcommand{\paragraph}[1]{\noindent\textbf{\textsf{#1}:}}

\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\etc}{\emph{etc.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}

%\newcommand{\foutse}[1]{\textcolor{blue}{{\it [Foutse says: #1]}}}
%\newcommand{\Saidur}[1]{\textcolor{green}{{\it [SR: #1]}}}
%\newcommand{\Azadeh}[1]{\textcolor{orange}{{\it [AZ: #1]}}}
%\newcommand{\TODO}[1]{\textcolor{cyan}{{\it [TODO: #1]}}}
%\newcommand{\newtext}[1]{\textcolor{purple}{{[#1]}}}
%\newcommand{\YANN}[1]{\textcolor{cyan}{{\it [YANN: #1]}}}

\newcommand{\RQOne}{Do design patterns and--or design anti-patterns mutate during software evolution and what is the probability of the mutations?}

\newcommand{\RQTwo}{What types of changes lead to  mutations between design patterns and design anti-patterns?}

\newcommand{\RQThree}{What is the fault-proneness of mutated design patterns and anti-patterns and what transitions lead to more fault-prone mutations?}

\newcommand{\RQFour}{Do specific types of changes lead to increased fault-proneness during mutations?}



\begin{document}

\title{Investigating Design Anti-pattern and Design Pattern Mutations and Their Change- and Fault-proneness}

\titlerunning{Design Anti-pattern and Design Pattern Mutations}

\author{Zeinab (Azadeh) Kermansaravi \and
        Md Saidur Rahman \and
        Foutse Khomh 		\and
        Fehmi Jaafar \and
        Yann-Ga\"{e}l Gu\'{e}h\'{e}neuc
}
\institute{Zeinab Kermansaravi \at
            SWAT Lab, Ptidej Team, DGIGL, Polytechnique Montr\'{e}al, Montr\'{e}al, QC, Canada\\
		    \email{zeinab.kermansaravi@polymtl.ca}
	    \and
 		    Md Saidur Rahman \at
            SWAT Lab, DGIGL, Polytechnique Montr\'{e}al, Montr\'{e}al, QC, Canada\\
            \email{saidur.rahman@polymtl.ca}
    	\and
 		    Foutse Khomh \at
            SWAT Lab, DGIGL, Polytechnique Montr\'{e}al, Montr\'{e}al, QC, Canada\\
           	\email{foutse.khomh@polymtl.ca}
        \and
	    	Fehmi Jaafar \at
            Computer Research Institute of Montr\'{e}al, Montr\'{e}al, QC, Canada\\
            \email{fehmi.jaafar@crim.ca}
        \and	
            Yann-Ga\"{e}l Gu\'{e}h\'{e}neuc \at
            Ptidej Team, CSSE, Concordia University, Montr\'{e}al, QC, Canada\\
            \email{yann-gael.gueheneuc@concordia.ca}
}
\date{Received: date / Accepted: date}
\maketitle

\begin{abstract}
During software evolution, inexperienced developers may introduce design anti-patterns when they modify their software systems to fix bugs or to add new functionalities based on changes in requirements. Developers may also use design patterns to promote software quality or as a possible cure for some design anti-patterns. Thus, design patterns and design anti-patterns are introduced, removed, and mutated from one another by developers.

Many studies investigated the evolution of design patterns and design anti-patterns and their impact on software development. However, they investigated design patterns or design anti-patterns in isolation and did not consider their mutations and the impact of these mutations on software quality. Therefore, we report our study of bidirectional mutations between design patterns and design anti-patterns and the impacts of these mutations on software change- and fault-proneness. 

We analyzed snapshots of seven Java software systems with diverse sizes, evolution histories, and application domains. We built Markov models to capture the probability of occurrences of the different design patterns and design anti-patterns mutations. Results from our study show that (1) design patterns and design anti-patterns mutate into other design patterns and--or design anti-patterns. They also show that (2) some change types primarily trigger mutations of design patterns and design anti-patterns (renaming and changes to comments, declarations, and operators), and (3) some mutations of design anti-patterns and design patterns are  more faulty in specific contexts.

These results provide important insights into the evolution of design patterns and design anti-patterns and its impact on the change- and fault-proneness of software systems.

\keywords{Design smells \and Design patterns \and Anti-patterns \and Fault-proneness \and Change-proneness \and Markov Chain}
\end{abstract}

\input{sections/Introduction}
\input{sections/RelatedWork}
\input{sections/Methodology}
\input{sections/StudyDesign}
\input{sections/StudyResults}
\input{sections/Discussion}
\input{sections/TreatsToValidity}
\input{sections/Conclusion}



\balance
\newcommand{\student}[1]{#1}
\newcommand{\uml}{UML}
\bibliographystyle{IEEEtran} \scriptsize
\def\IEEEbibitemsep{0pt}
\bibliography{BibiTex}

\end{document}