% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
%\usepackage{ruler}
\usepackage{color}
\usepackage{times}
\usepackage{epsfig}
\usepackage{gensymb}
\usepackage{amsfonts}
\usepackage{booktabs}


\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

%\newcommand{\KGthree}{\textcolor{magenta}}
%\newcommand{\KG}{\textcolor{black}}
%\newcommand{\KGtwo}{\textcolor{black}}
%\newcommand{\cc}{\textcolor{green}}
%\newcommand{\BX}{\textcolor{black}}
%\newcommand{\bx}{\textcolor{blue}}
%\newcommand{\bo}{\textcolor{red}}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\KGthree}{\textcolor{black}}
\newcommand{\KG}{\textcolor{black}}
\newcommand{\KGtwo}{\textcolor{black}}
\newcommand{\cc}{\textcolor{black}}
\newcommand{\BX}{\textcolor{black}}
\newcommand{\bx}{\textcolor{black}}
\newcommand{\bo}{\textcolor{black}}
\newcommand{\boc}{\textcolor{black}}
\DeclareMathOperator*{\argmin}{argmin}





\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
%\pagestyle{headings}
%\mainmatter
%\def\ECCV18SubNumber{88}  % Insert your submission number here

\title{Snap Angle Prediction for 360$^{\circ}$ Panoramas} % Replace with your title

\titlerunning{Snap Angle Prediction for 360$^{\circ}$ Panorama}

\authorrunning{B. Xiong and K. Grauman}

\author{Bo Xiong\inst{1} \and Kristen Grauman\inst{2}}
\institute{University of Texas at Austin \\
\and  Facebook AI Research \\
\email{bxiong@cs.utexas.edu,grauman@fb.com}\footnote[1]{\emph{On leave from University of Texas at Austin (grauman@cs.utexas.edu).}}}




\maketitle

\begin{abstract}
360$^{\circ}$ panoramas are a rich medium, yet notoriously difficult to visualize in the 2D image plane.  We explore how intelligent rotations of a spherical image may enable content-aware projection with fewer perceptible distortions.  Whereas existing approaches assume the viewpoint is fixed, intuitively some viewing angles within the sphere preserve high-level objects better than others.  To discover the relationship between these optimal \emph{snap angles} and the spherical panorama's content, we develop a reinforcement learning approach for the cubemap projection model.  Implemented as a deep recurrent neural network, our method selects a sequence of rotation actions and receives reward for avoiding cube boundaries that overlap with important foreground objects. \boc{ We show our approach creates more visually pleasing panoramas while using 5x less computation than the baseline.}
% Our results demonstrate the impact both qualitatively and quantitatively. 
 

\keywords{\KGthree{360$^{\circ}$ panoramas, content-aware projection, foreground objects}}
\end{abstract}





\input{introduction}
\input{related_work}
\input{approach}
\input{results}
\input{conclusions}

\vspace{-5pt}
\paragraph{Acknowledgements} \boc{This research is supported in part by NSF IIS-1514118 and a Google Faculty Research Award. We also gratefully acknowledge a GPU donation from Facebook.}

\clearpage





\bibliographystyle{splncs}
\bibliography{snapAngle}





\input{main_supp}




\end{document}
