\section{Discussion}
\label{sec:Discussion}

Figure \ref{fig:Accuracy} shows that TF-IDF $n$-gram based support vector classifier with radial basis function (SVC-RBF) achieves the highest classification accuracy of 0.813031. We also note that regardless of whether the text vectorization is sparse (TF-IDF $n$-grams) or dense (doc2vec), SVC-RBF and random forest classifiers achieve high accuracy in the neighborhood of approximately 0.8. 

Figures \ref{fig:Accuracy}, \ref{fig:Recall}, and \ref{fig:f1} further indicate that TF-IDF $n$-gram based SVC-RBF achieves the highest cross validation scores with respect to accuracy, recall, and f1 score. However, Figure \ref{fig:Precision} shows doc2vec based random forest achieves the highest precision score.

These results demonstrate that while support vector classifiers with radial basis functions and random forest classifiers are suitable models for SOC code prediction, the choice of representation (sparse vs.~dense) may depend on the metric of highest importance.

Figure \ref{fig:TrainingTime} shows that the high accuracy of TF-IDF $n$-gram based SVC-RBF comes at the cost of high training time, which is significantly greater than all the other models considered in this study. On the other hand, doc2vec based SVC-RBF requires much lower training time and yet achieves comparable accuracy. We note that the dimensionality of the sparse vectors is 858 while that of the dense vectors is 100, which is likely a contributing factor to this disparity in training time. We further observe that random forest classifiers, whether based on sparse or dense vectors, can be trained even more quickly while still achieving comparable accuracy.

Therefore, in a real world deployment, the choice of model may be dependent on the trade-off between training time and accuracy. Let us consider a scenario where once an initial model has been deployed, more accurate models are trained in the background as more training data become available over time, allowing the web service to switch to such models when they are substantially more accurate. If there are time constraints associated with the initial deployment, random forest or doc2vec based SVC-RBF would provide a highly accurate model more quickly. Subsequently, if there are no time constraints on switching to newer models, then TF-IDF $n$-gram based SVC-RBF may be preferable for later deployments. The next section concludes the paper. 

