\documentclass[twoside]{amsart}

\numberwithin{equation}{section}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,amsthm,latexsym,psfrag}
\usepackage[mathscr]{euscript}
\usepackage{graphicx,color,epic,eepic,bbold,enumerate}
\usepackage[all]{xy}
\usepackage{hyperref}

\theoremstyle{plain}
        \newtheorem{theorem}{Theorem}[section]
        \newtheorem{lemma}[theorem]{Lemma}
        \newtheorem{proposition}[theorem]{Proposition}
        \newtheorem{corollary}[theorem]{Corollary}
               
\theoremstyle{definition}
        \newtheorem{definition}[theorem]{Definition}
        \newtheorem{remark}[theorem]{Remark}
        \newtheorem{example}[theorem]{Example}

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\W}{\mathbb{W}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\calA}{\mathcal{A}}
\newcommand{\calB}{\mathcal{B}}
\newcommand{\calW}{\mathcal{W}}
\newcommand{\calV}{\mathcal{V}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\calK}{\mathcal{K}}
\newcommand{\calL}{\mathcal{L}}
\newcommand{\calM}{\mathcal{M}}
\newcommand{\calN}{\mathcal{N}}
\newcommand{\calO}{\mathcal{O}}
\newcommand{\calQ}{\mathcal{Q}}
\newcommand{\calP}{\mathcal{P}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calJ}{\mathcal{J}}
\newcommand{\calS}{\mathcal{S}}
\newcommand{\calT}{\mathcal{T}}
\newcommand{\calU}{\mathcal{U}}
\newcommand{\calZ}{\mathcal{Z}}
\newcommand{\scrL}{\mathscr{L}}
\newcommand{\scrA}{\mathscr{A}}
\newcommand{\scrC}{\mathscr{C}}
\newcommand{\scrD}{\mathscr{D}}
\newcommand{\scrE}{\mathscr{E}}
\newcommand{\scrQ}{\mathscr{Q}}
\newcommand{\scrJ}{\mathscr{J}}
\newcommand{\scrP}{\mathscr{P}}
\newcommand{\scrX}{\mathscr{X}}
\newcommand{\sfe}{\mathsf{e}}
\newcommand{\sfE}{\mathsf{E}}
\newcommand{\sfJ}{\mathsf{J}}
\newcommand{\sfR}{\mathsf{R}}
\newcommand{\sfT}{\mathsf{T}}
\newcommand{\sfW}{\mathsf{W}}
\newcommand{\frg}{\mathfrak{g}}
\newcommand {\cc} [1] {\overline {{#1}}}
\newcommand {\id} {\operatorname{id}}
\newcommand {\Kern} {\operatorname{ker}}
\newcommand {\Bild} {\operatorname{im}}
\newcommand {\conv} {\operatorname{conv}}
\newcommand {\ad} {\operatorname{ad}}
\newcommand {\res} {\operatorname{res}}
\newcommand {\qres} {\widetilde{\operatorname{res}}}
\newcommand {\qkos} {\widetilde{\partial}}
\newcommand {\prol} {\operatorname{ext}}
\newcommand {\Hm} {\operatorname{H}}
\newcommand {\fnu} {[\![\nu]\!]}
\newcommand {\ii} {\operatorname{i}}
\newcommand {\ee} {\operatorname{e}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\xra}{\xrightarrow}
\newcommand{\ov}{\overline}
\def\connsum{\mathop{\#}\limits}

\setcounter{section}{0}

\begin{document}
\title{Invariant Whitney Functions}

\author{Hans-Christian~Herbig and Markus Pflaum}
\address{Hans-Christian~Herbig\newline\indent
        Universidade Federal de Rio de Janeiro,
        Departamento de Matem\'atica Aplicada\newline\indent
        CEP 21941-909 - Rio de Janeiro, Brazil}
\email{herbighc@gmail.com} 
\address{Markus J. Pflaum\newline\indent
         Department of Mathematics, University of Colorado, 
         Boulder, CO 80309-0395, USA}   
\email{markus.pflaum@colorado.edu}

\keywords{compact transformation groups, stratifications, Whitney functions}
\subjclass[2010]{57S15, 58A35}
\begin{abstract} 
A theorem of Gerald Schwarz \cite[Thm.~1]{SchwaSFIACLG} says that for a linear action of a compact Lie group $G$ on a finite dimensional real vector space $V$ any smooth $G$-invariant function on $V$ can be written as a composite with the Hilbert map. We prove a similar statement for the case of Whitney functions along a subanalytic set $Z\subset V$ fulfilling some regularity assumptions. In order to deal with the case when $Z$ is not $G$-stable we use the language of groupoids.
\end{abstract}
\maketitle
\tableofcontents
\bibliographystyle{amsplain}
\input{introwhitney}
{\bf Acknowledgements.}
The authors express their gratitude to Edward Bierstone for clarifications 
concerning  Gabrielov regularity. They thank the Instituto de Matem\'atica 
Pura e Aplicada (IMPA) in Rio de Janeiro and the Center for the Quantum
Geometry of Moduli Spaces (QGM) at Aarhus University for hospitality.
The research of MP has been supported by the National Science Foundation 
under DMS-1105670 and by Simons Foundation collaboration grant number 359389.
The research of HCH has received support from QGM which is funded by the Danish 
National Research Foundation. Moreover, he received support from the
Brazilian National Council for Scientific and Technological Development CNPq,
the Austrian Ministry of Science and Research BMWF, Start-Prize Y377, and from
the Eduard {\v C}ech Institute through the grant GA CR P201/12/G028.
HCH also gratefully acknowledges hospitality by the University of Colorado. 
\input{prelimwhitney}
\input{orbittypestratification}
\input{invwhitney}%hans
%\input{orb} %hans
%\input{grpd}%markus
%\input{example}%hans
\begin{appendix}
\input{faadibruno}%hans
\input{realalgebraic}%markus
%\input{appgrpd}   
\end{appendix}
\bibliography{HerPflHHASFOS}
\end{document}