% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{soul, color, xcolor}
\usepackage{graphicx}
\usepackage{CJKutf8}
\usepackage{CJK}
\usepackage{graphicx}
\usepackage{float}%提供float浮动环境
\usepackage{hyperref}
\hypersetup{hypertex=true,
            colorlinks=true,
            linkcolor=blue,
            anchorcolor=blue,
            citecolor=blue}
\usepackage{booktabs}%提供命令\toprule、\midrule、\bottomrule
\usepackage{multirow}%提供跨列命令\multicolumn{}{}{}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{biblatex}
%\usepackage{changes}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{bbding}

% \usepackage[backend=biber,style=gb7714-2015,seconds=true,gbnamefmt=lowercase,gbpub=false]{biblatex}

\newcommand{\ie}{\textit{i.e.,}\xspace}
\newcommand{\aka}{\textit{a.k.a.,}\xspace}
\newcommand{\eg}{\textit{e.g.,}\xspace}
\newcommand{\wrt}{\textit{w.r.t.}\xspace}
\newcommand{\wo}{\textit{w/o}\xspace}
\newcommand{\w}{\textit{w/}\xspace}
\newcommand{\etc}{\textit{etc}}
\newcommand{\ignore}[1]{}

\renewcommand{\labelitemi}{\textbullet}
\renewcommand{\labelitemii}{-}

\addbibresource{ref.bib}

\begin{document}
%
%\title{Erya: A Suite for Translation between Ancient Chinese and Modern Chinese}
\title{Towards Effective Ancient Chinese Translation: Dataset, Model, and Evaluation}
%
\titlerunning{Towards Effective Ancient Chinese Translation}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Geyang Guo$^1$ \and
Jiarong Yang$^1$ \and
Fengyuan Lu$^1$ \and
Jiaxin Qin$^1$ \and
\\Tianyi Tang$^1$ \and
Wayne Xin Zhao$^{1,2}$\thanks{Corresponding author.}}
%
\authorrunning{G. Guo et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{$^1$Gaoling School of Artificial Intelligence, Renmin University of China\\
$^2$Beijing Key Laboratory of Big Data Management and Analysis Methods\\
\email{\{guogeyang,yangjiarong001,lufengyuan,2020201476\}@ruc.edu.cn,\\steventianyitang@outlook.com,batmanfly@gmail.com}}
%
\maketitle              % typeset the header of the contribution
%
\input{abstract}
%
%
%

\input{intro}

\input{relatedwork}

\input{dataset}

\input{framework}

\input{experiment}

\section{Conclusion}
In this paper, we introduce Erya for ancient Chinese translation consisting of Erya dataset, model, and benchmark.
Erya dataset is currently the largest ancient Chinese corpora collection including both monolingual corpus and ancient-modern parallel data. 
We further propose a multi-task learning combining DAS and DMLM 
 to train Erya model. 
Finally, we conduct comprehensive evaluation using Erya benchmark. Extensive experiments have validated the superior capability of Erya model under both zero-shot and fine-tuning settings. 
% We will release all the above-mentioned resources to facilitate the research on ancient Chinese.

%we devise a new word alignment method called disyllabic word alignment, with which we propose a multi-task training method combining DAS and DMLM.

\section*{Acknowledgments}
This work was partially supported by National Natural Science Foundation of China under Grant No. 62222215, Beijing Natural Science Foundation under Grant No. 4222027, and Beijing Outstanding Young Scientist Program under Grant No. BJJWZYJH012019100020098. Xin Zhao is the corresponding author. Special thanks to Manman Wang for the advice on ancient Chinese.


\printbibliography

\end{document}
