% -*- TeX:SE -*-
%
% main.tex

 
  
%\documentclass[conference]{IEEEtran}
\documentclass[journal]{IEEEtran}
 
%\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{times}
%\usepackage{natbib} %IEEEtrans bibliography doesn't like natbib apparently
\usepackage{dcolumn}
\usepackage{endnotes}
\usepackage{graphics}
%\usepackage{subfigure}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{amssymb,amsmath}
\usepackage{balance}

\usepackage{listings}
\usepackage[]{algorithm2e}
\usepackage{flushend}
\usepackage{color,soul}
%\usepackage[hyphenbreaks]{breakurl}
%\usepackage[hyphens]{url}
%\usepackage{hyperref}
%\def\UrlBreaks{\do\/\do-}
%\usepackage{url}
%\usepackage[hyphens]{url}
\usepackage{hyperref}
%For making to do notes
\usepackage[dvipsnames]{xcolor}
\usepackage{todonotes}

\usepackage{siunitx}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

%For hl command
\soulregister\cite7
\soulregister\ref7
\soulregister\pageref7

%\usepackage[hyphenbreaks]{breakurl}
\def\UrlBreaks{\do\/\do-}

%\usepackage[colorlinks,urlcolor=blue]{hyperref}

%\usepackage[color=yellow,textsize=footnotesize]{todonotes}
%{\color{red} highlighted}


%\bibliographystyle{unsrt}
\bibliographystyle{IEEEtran} % IEEEtrans for @Patent
\urlstyle{sf}

\begin{document}

%\title{Integer Echo State Networks: Hyperdimensional Reservoir Computing}
\title{Integer Echo State Networks: Efficient Reservoir Computing for Digital Hardware}

% Approach for distributed representation and processing of a sensory data based on principles of hyper-dimensional computing


\author{Denis~Kleyko,
        E.~Paxon~Frady,
        Mansour~Kheffache,
        and~Evgeny~Osipov % <-this % stops a space
\thanks{%Manuscript received on May 1, 2019; 
This work  was  supported in part  by the Swedish Research Council (grant No. 2015-04677). 
The work of DK was supported by the European Union’s Horizon 2020 Research and Innovation Programme under the Marie Skłodowska-Curie Individual Fellowship Grant Agreement 839179 and in part by the DARPA’s VIP (Super-HD Project) and AIE (HyDDENN Project) programs.
%revised May 3, 2018; accepted May 3, 2018. Date of publication May 3, 2018; date of current version May 3, 2018.}
%\thanks{This work was supported by the Swedish Research Council (grant no. 2015-04677) and Systems on Nanoscale Information fabriCs (SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA. DK also acknowledges Stiftelsen Seth M Kempes Stipendiefond for partially funding his research visit to UC Berkeley.
}
\thanks{\mbox{*}D. Kleyko is with the Redwood Center for Theoretical Neuroscience at the University of California, Berkeley, CA 94720, USA and also with Intelligent Systems Lab at Research Institutes of Sweden, 164 40 Kista, Sweden. \mbox{E-mail}: \mbox{denis.kleyko@ri.se}}% <-this % stops a space 
%\thanks{E. P. Frady is with Neuromorphic Computing Lab, Intel Labs and also with the Redwood Center for Theoretical Neuroscience at the University of California, Berkeley, CA 94720, USA. \mbox{E-mail}: \mbox{epaxon@berkeley.edu}
\thanks{E. P. Frady is with the Redwood Center for Theoretical Neuroscience at the University of California, Berkeley, CA 94720, USA. \mbox{E-mail}: \mbox{epaxon@berkeley.edu}
}% <-this % stops a space
\thanks{M. Kheffache is with Netlight Consulting AB, 111 53 Stockholm, Sweden. \mbox{E-mail}: \mbox{mansour.kheffache@netlight.com}}% <-this % stops a space 
\thanks{E. Osipov is with the Department of Computer  Science Electrical and Space Engineering, Lule\aa{} University of Technology, 971 87 Lule\aa{}, Sweden. \mbox{E-mail}: \mbox{evgeny.osipov@ltu.se} }% <-this % stops a space
 }% <-this % stops a space







\markboth{}%
{Kleyko \MakeLowercase{\textit{et al.}}: Integer Echo State Networks}


\maketitle

% I would change the first sentence (the rest is fine) to:
%
\begin{abstract}

%We propose an integer approximation of Echo State Networks (ESN) based on the
%mathematics of hyperdimensional computing.
%The reservoir of the proposed Integer Echo State Network (intESN) contains only \textit{n}-bits integers and replaces the recurrent matrix multiply %with an efficient cyclic shift operation. Such an architecture results in dramatic improvements in memory footprint and computational efficiency, with minimal performance loss.
%Our architecture naturally supports the usage of the trained reservoir in  symbolic processing tasks of analogy making and logical inference. 

We propose an approximation of Echo State Networks (ESN) that can be efficiently implemented on digital hardware based on the mathematics of hyperdimensional computing. The reservoir of the proposed integer Echo State Network (intESN) is a vector containing only n-bits integers (where n<8 is normally sufficient for a satisfactory performance). The recurrent matrix multiplication is replaced with an efficient cyclic shift operation. The proposed intESN approach is verified with typical tasks in reservoir computing: memorizing of a sequence of inputs; classifying time-series; learning dynamic processes. Such architecture results in dramatic improvements in memory footprint and computational efficiency, with minimal performance loss. 
%{\color{red}
The experiments on a field-programmable gate array confirm that the proposed intESN approach is much more energy efficient than the conventional ESN.
%}
\end{abstract}

\begin{IEEEkeywords}
reservoir computing, echo state networks, vector symbolic architectures, hyperdimensional computing, memory capacity, time-series classification, dynamic systems modelling
 \end{IEEEkeywords}


\input{tex/introduction} 
\input{tex/Related}
\input{tex/intESN}
\input{tex/performance_evaluation}
\input{tex/fpga}
\input{tex/Discussion}
\input{tex/Conclusions}



\bibliography{bica}

\end{document}
