\section{Additive Agents\protect\footnote{We have created a website at \href{https://www.cs.umd.edu/\~saeedrez/fair.html}{https://www.cs.umd.edu/$\sim$saeedrez/fair.html} for the implemented algorithm and all related materials.}}}\label{additive}
In this section we study the fair allocation problem in the additive setting. We present a proof to the existence of a $3/4$-$\MMS$ allocation when the agents are additive. This improves upon the work of \procacciafirst ~\cite{Procaccia:first} wherein the authors prove a $2/3$-$\MMS$ allocation exists for any combination of additive agents.  As we show, our proof is constructive; given an algorithm that determines the $\MMS$ of an additive set function within a factor $\alpha$, we can implement an algorithm that finds a $3/(4 \alpha)$-$\MMS$ allocation in polynomial time. This married with the PTAS algorithm of \epsteinefficient ~\cite{epstein2014efficient} for finding the $\MMS$ values, results is an algorithm that finds a $3/(4+\epsilon)$-$\MMS$ allocation in polynomial time.

The main idea behind the $3/4$-$\MMS$ allocation is \textit{clustering} the agents. Roughly speaking, we categorize the agents into three clusters, namely $\cone$, $\ctwo$, and $\cthree$. We show that the valuation functions of the agents within each cluster show similar behaviors. Along the clustering process, we allocate the heavy items (the items that have a valuation of at least $1/4$ to some agents) to the agents. By Observation \ref{reducibility}, proving a $3/4$-$\MMS$ guarantee can be narrowed down to only $3/4$-irreducible instances. The $3/4$-irreducibility of the problem guarantees that after the clustering process, the remaining items are light. This enables us to run a $\bagfilling$ process to satisfy the agents. In order to prove the correctness of the algorithm, we take advantage of the properties of each cluster separately.

The organization of this section is summarized in the following: we start by a brief and abstract explanation of the ideas in Section \ref{overview}. In Section \ref{additive:observations} we study the properties of the additive setting and state the main observations that later imply the correctness of our algorithm. Next, in Section \ref{additive:clusters} we discuss a method for clustering the agents and in Section \ref{additive:allocation} we show how we allocate the items to the agents of each cluster to ensure a $3/4$-$\MMS$ guarantee. Finally, in Section \ref{additive:algorithm} we explain the implementation details and prove a polynomial running time for the proposed algorithm.

Throughout this section, we assume $\MMS_i = 1$ for all agents $\agent_i \in \agents$. This is without loss of generality for the existential proof since one can scale the valuation functions to impose this constraint. However, the computational complexity of the allocation will be affected by this assumption since determining the $\MMS$ of an additive function is NP-hard~\cite{epstein2014efficient}. That said, we show in Section \ref{additive:algorithm} that this challenge can be overcome by incurring an additional $1+\epsilon$ factor to the approximation guarantee.  

For brevity, we defer the proofs of Sections \ref{additive:observations}, \ref{additive:clusters}, \ref{additive:allocation}, and \ref{additiveproofs} to Appendices \ref{additiveobservationsproof},\ref{clusteringappendix},\ref{clustering2appendix}, and \ref{additiveproofappendix}, respectively.
\input{overview}
\input{additiveobservations}
\input{additiveclusters}
\input{additiveallocation}
\input{additivealgorithm}
