\section{Generating Opinion Graphs} \label{sec:graph}

Based on mined explanations and canonicalized opinions from Sections~\ref{sec:exp} and \ref{sec:cluster}, the final step for generating an opinion  graph is to predict edges between nodes. In theory, when using perfectly accurate explanations and opinion clusters, generating such edges is trivial. Intuitively, when an opinion phrase explains another opinion phrase, opinion phrases that are paraphrases of the first phrase should also explain phrases that paraphrase the latter one. In other words, given a set of explanations $E$ and two groups of opinion phrases, $n_i$ and $n_j$, there should be an edge from $n_i$ to $n_j$ if there exists an edge between two opinion phrases in $n_i$ and $n_j$ respectively:

\vspace{-1mm}
\[e=(n_i\rightarrow n_j) \text{~is~true}, \text{if~} \exists \, e=(p\rightarrow p')\in E|  p\in n_i, p'\in n_j\]
\vspace{-1mm}

For example, when we know that \asop{``close to the beach''} $\rightarrow$ \asop{``good location''}, we are able to conclude (\asop{``close to the beach''}, \asop{``near the beach''}, \asop{``walking distance to the beach''})  $\rightarrow$ (\asop{``good location''}, \asop{``great location''}, \asop{``awesome location''}).

However, in practice, our obtained explanations and nodes are not perfect. Thus, we may get a lot of false positive edges based on the above criteria. To minimize the false positives, we use a simple heuristic to further prune the edges, which is based on the observation that two groups of opinions seldom explain each other at the same time. 
\vspace{-1mm}
\[e=(n_i\rightarrow n_j) \text{~is~true}, \text{if~} \sum_{e\in E_{ij}} \mathrm{p}_e - \sum_{e'\in E_{ji}} \mathrm{p}_e' > 0\, ,\]
where $E_{ij} = \{e=(p_i\rightarrow p_j) \mid p_i\in n_i, p_j\in n_j\}$ and $E_{ji} = \{e=(p_j\rightarrow p_i) \mid p_i\in n_i, p_j\in n_j\}$ are the explanations from $n_i$ to $n_j$ and $n_j$ to $n_i$ respectively; and $\mathrm{p}_e$ and $\mathrm{p}_e'$ are the explanation probabilities obtained from our explanation mining classifier. 

Deriving edges between canonicalized opinions is a difficult problem in general. There are many ways to optimize this step further, and we leave this as part of our future work.
