% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

\usepackage{amsmath,amssymb}    % Advanced maths commands

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
\usepackage{mathptmx}
%\usepackage{txfonts}


% Jeroen: The below is a patch to fix the annoying pdf generation errors related to hyperref
% spreading links on two pages. I have no clue what it does but it works :)
% Source: https://github.com/ho-tex/hyperref/issues/19
\usepackage{etoolbox}
\makeatletter
\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
   \errmessage{\noexpand\@combinedblfloats could not be patched}%
}%
\makeatother



% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}   % Including figure files
\usepackage{amssymb}    % Extra maths symbols


\usepackage{natbib, aas_macros}
\usepackage{graphicx, color, url}
\usepackage{grffile} 
%\usepackage[a4paper]{geometry}


% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\newcommand{\kms}{\mathrm{km\ s^{-1}}\,}

\def\JB#1{{\bf {\color{red}[#1 -- Jeroen]}}}
\def\MF#1{{\bf {\color{blue}[#1 -- Michiko]}}}
\def\simon#1{{\bf {\color{green}[#1 -- SPZ]}}}
\def\Simon#1{{\bf {\color{green}[#1 -- SPZ]}}}
\def\SPZ#1{{\bf {\color{green}[#1 -- SPZ]}}}
\def\JNB#1{{\bf {\color{orange}[#1 -- Junichi]}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[The dynamics of stellar disks in live halos]{The dynamics of stellar disks in live dark-matter halos}
\author[M. S. Fujii et al.]{M. S. Fujii$^{1}$\thanks{E-mail:
fujii@astron.s.u-tokyo.ac.jp (MSF)}, J. B\'edorf$^{2}$, J. Baba$^{3}$, and S. Portegies Zwart$^{2}$\\
$^{1}$Department of Astronomy, Graduate School of Science, The University of Tokyo, 7-3-1 Hongo, Bunkyo-ku, Tokyo, 113-0033, Japan\\
$^{2}$Leiden Observatory, Leiden University, NL-2300RA Leiden, The Netherlands\\
$^{3}$National Astronomical Observatory of Japan, Mitaka-shi, Tokyo 181-8588, Japan}

\date{Accepted . Received ; in original form }

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2002}
\maketitle



\begin{abstract}

Recent developments in computer hardware and software enable
researchers to simulate the self-gravitating evolution of galaxies at
a resolution comparable to the actual number of stars.  Here we
present the results of a series of such simulations.  We performed
$N$-body simulations of disk galaxies with between 100 and 500 million
particles over a wide range of initial conditions.  Our calculations
include a live bulge, disk, and dark matter halo, each of which is
represented by self-gravitating particles in the $N$-body code.  The
simulations are performed using the gravitational $N$-body tree-code
{\tt Bonsai} running on the Piz Daint supercomputer.
We find that the time scale over which the bar forms increases
exponentially with decreasing disk-mass fraction and that the bar formation
epoch exceeds a Hubble time when the disk-mass fraction is $\sim0.35$.
These results can be explained with the swing-amplification theory.
The condition
for the formation of $m=2$ spirals is consistent with that for the
formation of the bar, which is also an $m=2$ phenomenon.  We further argue
that the non-barred grand-design spiral galaxies
are transitional, and that they evolve to barred
galaxies on a dynamical timescale.
We also confirm that the disk-mass fraction and shear rate
are important parameters for the morphology of disk galaxies.
The former affects the number of spiral arms and the bar formation
epoch, and the latter determines the pitch angle of the spiral arms.


\end{abstract}

\begin{keywords}
galaxies: kinematics and dynamics --- galaxies: spiral --- galaxies: structure ---
galaxies: evolution --- methods: numerical
\end{keywords}


\input{introduction}
\input{n_body_simulations}
\input{results}
\input{discussion}
\input{summary}



%\bsp
\section*{Acknowledgments}

We thank the anonymous referee for the very helpful comments.
This work was supported by JSPS KAKENHI Grant Number 26800108, 
HPCI Strategic Program Field 5 'The origin of matter and the universe,' 
and the Netherlands Research School for Astronomy (NOVA).
Simulations are performed using GPU clusters, HA-PACS at the
University of Tsukuba, Piz Daint at CSCS and Little Green Machine II
(621.016.701). Initial development has been done using the Titan
computer Oak Ridge National Laboratory.  This work was supported by a
grant from the Swiss National Supercomputing Centre (CSCS) under
project ID s548 and s716.  This research used resources of the Oak Ridge
Leadership Computing Facility at the Oak Ridge National Laboratory,
which is supported by the Office of Science of the U.S. Department of
Energy under Contract No. DE-AC05-00OR22725 and by the European
Union's Horizon 2020 research and innovation programme under grant
agreement No 671564 (COMPAT project).
\appendix

\input{appendixA}
\input{appendixB}
\input{appendixC}


\bibliographystyle{mnras}
\bibliography{reference}


\label{lastpage}
\end{document}
