%\documentclass[preprint,12pt]{elsarticle}
%\include{begin}

\section{Shell script files for setup and postprocessing}
%
A Shell file is prepared for the integrated run throughout from the Lagrange, conversion and Euler codes. However, each code can be also run manually one by one.
%
After finishing all the simulation process, users may need to visualize the simulation data. Some of the data computed are visualized by the following shell scripts. All shell files require gnuplot 4.6 or later.

%
\subsection{Calculation set up shell}
\begin{enumerate}
\item{\bf setup\_fusion.h}
The shell file remove the calculation output date and makes the output file.
%\item{\bf remove\_all.sh}
%The shell file remove the calculation output date.
\end{enumerate}
%

\subsection{Visualization for the Lagrange code data}
All the visualized data images are stored in the "pic\_La" directory. 
\begin{enumerate}
\item{\bf adiabat.sh}\\
The visualized graph for the time history of the adiabat $\alpha$ calculated in "Insulation.cpp" in the Lagrangian code. 

\item{\bf Animation\_Ti\_MODE.sh}\\
The shell file visualizes the mode analysis results of the ion temperature calculated by "Legendre.cpp" in the Lagrangian code. 

\item{\bf ImplosionVelocity.sh}\\
The shell plots the time histories of the implosion speed averaged over the azimuthal direction for the DT inner surface, the DT outer surface and the averaged DT speed. 
\item{\bf RMSoutput.sh}\\
The shell file plots the time histories of the root-mean-square (RMS) for the ion temperature and the mass density in the DT layer and Al layer. The RMS data is calculated by "RMS.cpp" in the Lagrangian code. 
\item{\bf SLC\_t\_r.sh}\\
The shell file outputs the images of the $r-t$ diagrams representing the time history of the Lagrangian meshes at $\theta =$30, 60, 120 and 150 degrees and at $\phi =$10, 100, 190 and 280 degrees. To execute the shell file, users need to specify the boundary mesh number of each material in the Lagrangian code. 
\end{enumerate}

\subsection{Visualization for the Euler code data}
All visualized data files are stored in the "pic\_Eu" directory. 
\begin{enumerate}
\item{\bf Animation\_atomic\_XY.sh}\\
The shell file visualizes the distributions of the atomic number on the XY plane for each output data in the Euler code. 
\item{\bf Animation\_atomic\_YZ.sh}\\
The shell file visualizes the distributions of the atomic number on the YZ plane for each output data in the Euler code. 
\item{\bf Animation\_rho\_XY.sh}\\
The shell file visualizes the distributions of the mass density on the XY plane for each output data in the Euler code.  
\item{\bf Animation\_rho\_YZ.sh}\\
The shell file visualizes the distributions of the mass density on the YZ plane for each output data in the Euler code.  
\if0
\item{\bf Animation\_Ti\_MODE.sh} \\
The shell file visualizes the mode analysis results for the ion temperature distribution calculated in the "Legendre.cpp" in Euler code. 
\fi
\item{\bf Animation\_Ti\_XY.sh}\\
The shell file visualizes the distributions of the ion temperature on the XY plane for each output data in the Euler code. 
\item{\bf Animation\_Ti\_YZ.sh}\\
The shell file visualizes the distributions of the ion temperature on the YZ plane for each output data in the Euler code. 
\item{\bf Fusiongain.sh}\\
The shell file plots the history of the fusion energy gain. 
\item{\bf rhoR.sh}\\
The shell file plots the history of the $\rho R$. 
\end{enumerate}
%\include{end}