\documentclass[acmsmall]{acmart}

\usepackage[hyphens]{url}
\usepackage{hyperref}

\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{xspace}
\usepackage{subcaption}
\settopmatter{printfolios=true}

%Comment commands
\newcommand{\nj}[1]{{\color{purple}{[nj: #1]}}}
\newcommand{\mt}[1]{{\color{red}{[mt: #1]}}}
\newcommand{\mm}[1]{{\color{blue}{[mm: #1]}}}
\newcommand{\lv}[1]{{\color{green}{[lv: #1]}}}
\newcommand{\TOOL}{{\emph{Priv-Accept}}\xspace}
\newcommand{\BEFORE}{{\emph{Before-Visit}}\xspace}
\newcommand{\AFTER}{{\emph{After-Visit}}\xspace}
\newcommand{\INTERNAL}{{\emph{Additional-Visits}}\xspace}

%Conference Info
\acmYear{2021}
\copyrightyear{2021}
\setcopyright{acmcopyright}
\acmJournal{TWEB}



\begin{document}
\title[The Internet with Privacy Policies]{The Internet with Privacy Policies: Measuring The Web Upon Consent}

%\author{Nikhil Jha, Martino Trevisan, Luca Vassio, Marco Mellia}
\author{Nikhil Jha}
\affiliation{
\institution{Politecnico di Torino}
\streetaddress{Corso Duca degli Abruzzi, 24}
\city{Torino}
\postcode{10129}
\country{Italy}}
\email{nikhil.jha@polito.it}

\author{Martino Trevisan}
\affiliation{
\institution{Politecnico di Torino}
\streetaddress{Corso Duca degli Abruzzi, 24}
\city{Torino}
\postcode{10129}
\country{Italy}}
\email{martino.trevisan@polito.it}

\author{Luca Vassio}
\affiliation{
\institution{Politecnico di Torino}
\streetaddress{Corso Duca degli Abruzzi, 24}
\city{Torino}
\postcode{10129}
\country{Italy}}
\email{luca.vassio@polito.it}

\author{Marco Mellia}
\affiliation{
\institution{Politecnico di Torino}
\streetaddress{Corso Duca degli Abruzzi, 24}
\city{Torino}
\postcode{10129}
\country{Italy}}
\email{marco.mellia@polito.it}

\begin{abstract}
To protect users' privacy, legislators have regulated the usage of tracking technologies, mandating the acquisition of users' consent before collecting data. Consequently, websites started showing more and more consent management modules -- i.e., Privacy Banners -- the visitors have to interact with to access the website content. They challenge the automatic collection of Web measurements, primarily to monitor the extensiveness of tracking technologies but also to measure Web performance in the wild. Privacy Banners, in fact, limit crawlers from observing the actual website content.

In this paper, we present a thorough measurement campaign focusing on popular websites in Europe and the US, visiting both landing and internal pages from different countries around the world. We engineer \TOOL, a Web crawler able to accept the privacy policies, as most users would do in practice. It lets us compare how webpages change before and after. Our results show that all measurements performed not dealing with the Privacy Banners offer a very biased and partial view of the Web. After accepting the privacy policies, web tracking is abundantly more pervasive, and webpages are larger and slower.
\end{abstract}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003033.10003079.10011704</concept_id>
       <concept_desc>Networks~Network measurement</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10002978.10003029</concept_id>
       <concept_desc>Security and privacy~Human and societal aspects of security and privacy</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Networks~Network measurement}
\ccsdesc[500]{Security and privacy~Human and societal aspects of security and privacy}

\ccsdesc[500]{Networks~Network measurement}

\keywords{Web Measurements, Crawling, Privacy Banner, GDPR}

\maketitle

\input{1_introduction}
\input{3_history}
\input{4_cookie_accept}
\input{5_results}
\input{6_conclusions}

\section*{Acknowledgments}
The research leading to these results has been funded by the European Union's Horizon 2020 research and innovation program under grant agreement No. 871370 (PIMCity project) and the SmartData@PoliTO center for Data Science technologies.

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\input{7_appendix}

\end{document}