\section{Proofs for Section~\ref{sec:exact_sub}}\label{app:exact_sub}
\begin{proof}[Proof of Theorem~\ref{thm:bad_sdp}]
	We first show that the SDP admits exactly one feasible point. Indeed, let $X \succeq 0$ be feasible for the SDP. Then, constraints $n$ and $n+1$ imply $\ip{A_{n+1} - A_{n}}{X} = 0$. That is, the trace of the principal submatrix of size $n-1$ of $X$ is zero. Since this submatrix is also positive semidefinite, it is zero. Constraints 1 to $n-1$ further show that all entries but $X_{nn}$ are zero. Finally, constraints $n$ and ${n+1}$ force $X_{nn} = \frac{5(n-1)}{3}$. This $X$ has rank~1 and is necessarily optimal.
	
	We now show that the proposed $\bar U$ is suboptimal for $L$. To this end, build $\tilde U \in \Rnk$ with the last row having squared 2-norm equal to $\frac{5(n-1)}{3}$, and all other rows are zero. Clearly, $\tilde U\tilde U^T$ is feasible for the SDP, so that $L(\tilde U) = 0$: this is optimal. On the other hand, $L(\bar U) = \frac{5}{18}(n-1)^2\eps^2 > L(\tilde U)$.
	
	Finally, we check stationarity of $\bar U$. Let $\calA \colon \Snn \to \R^m$ be the linear operator such that $\calA(X)_i = \ip{A_i}{X}$, and define the residue function $\vr(U) = \calA(UU^T) - b$. The cost function and its derivatives take the following forms:
	\begin{align*}
		L(U) & = \frac{1}{2} \|\vr(U)\|_2^2, \\
		\nabla L(U) & = 2\calA^*(\vr(U))U, \\
		\nabla^2 L(U)[\dot U] & = 2\calA^*(\vr(U))\dot U + 2\calA^*(\calA(U\dot U^T + \dot U U^T))U.
	\end{align*}
	Simple computations show that $\calA(\bar U \bar U^T) = (0, \ldots, 0, (n-1)\eps, 2(n-1)\eps)^T$, so that $\calA^*(\vr(\bar U)) = -\frac{n-1}{3} \eps^2 \cdot e_n^{} e_n^T$: only the bottom-right entry is non-zero. Consequently, $\nabla L(\bar U) = 0$: $\bar U$ is an FOSP To show second-order stationarity, we must also show that $\nabla^2 L(\bar U)$ is positive semidefinite.
	That is, we must show the inequalities:
	\begin{align*}
		0 \leq \ip{\dot U}{\nabla^2 L(U)[\dot U]} & = 2\ip{\dot U \dot U^T}{\calA^*(\vr(U))} + \left\|\calA(U \dot U^T + \dot U U^T)\right\|_2^2
	\end{align*}
	for all $\dot U \in \Rnk$. Let
	\begin{align*}
		\dot U & = \begin{bmatrix}
			\textrm{---} &\dot u_1^T & \textrm{---} \\ & \vdots&  \\ \textrm{---} &\dot u_n^T& \textrm{---}
		\end{bmatrix}, \quad \textrm{ with } \quad \dot u_1, \ldots, \dot u_n \in \Rk \textrm{ arbitrary.}
	\end{align*}
	Then, $\calA(\bar U\dot U^T + \dot U\bar U^T) = (2\dot u_n^T, q_1, q_2)^T$ for some values $q_1, q_2$, so that:
	\begin{align*}
		\ip{\dot U}{\nabla^2 L(\bar U)[\dot U]} & = -2\frac{n-1}{3} \eps^2 \|\dot u_n\|_2^2 + 4 \|\dot u_n\|_2^2 + q_1^2 + q_2^2 \geq \left(4-2\frac{n-1}{3} \eps^2 \right) \|\dot u_n\|_2^2.
	\end{align*}
	Under our condition on $\eps$, this is indeed always nonnegative: $\bar U$ is an SOSP.
\end{proof}

