\section{Reddit administrative actions come loss}
Content moderation is seen a commodity rather than a necessity provided by the social media for its platform. It helps to maintain a welcoming and civil platform for new users to join. Moderation also creates a platform favourable for advertisers and investors. There are cases where \note{Cite YouTube apocalypse, sleeping giants, twitter (for inversters)} advertisers and investors withdrew their interest from a platform entirely because of the bad image of the platform due to inappropriate content and lack of content moderation. The lack of initiative in moderation from Reddit is apparent in how its content policy grew over the years, driven mainly by criticism from media and users. We hypothesize the delay or lack of urgency in performing administrative actions is caused by the cost of the interventions. In their work, et al. show how platforms profit greatly from toxicity and extremist ideologies. Following this pattern, we aim to measure the revenue these communities bring and the revenue lost from closing these communities. Establishing a high cost to administrative actions will enable us understand would enable us to understand the lack of moderation in newer platforms and the inconsistencies in Reddit’s moderation.

\subsection{Revenue Streams}
As a social media hosting user-generated content, platforms Reddit’s primary source of revenue is advertisement and then paid memberships. Advertisers can place their ad on Reddits sidebar or in the middle of feed. Being the 7th most popular website in the US Reddit sees a lot of traffic with 330 million monthly active users \note{cite}. Valued at \$6 billion with a revenue of \$226 million for 2021 \note{cite} Reddit’s ARPU (Average Revenue per User) is estimated to be around \$0.68. Compared to \$7 and \$9 ARPU of Facebook and Twitter Reddit’s is still growing its business model to catch up. Apart from advertising, a smaller part of Reddit’s revenue comes from selling in-site currency: \textit{Gold}, \textit{Silver} and \textit{Platinum} coins. Users can buy these coins and give them to submissions or comments as awards. Given these two revenue streams, in the next section we highlight how we design experiments to measure the cost of interventions.

\subsection{Methods}
In testing the cost of intervention, we break the analysis into two categories 1) \textbf{Before Intervention}: how much revenue/activity were the closed communities bringing and 2) \textbf{After Intervention}: how revenue was lost after closing the communities. In measuring the revenue brought by a closed community before their closure we measure three values: 1) total amount of activity on the particular community, 2) total amount of Reddit currency i.e. coins spent on the community and 3) the number of users brought to the platform by the community.  

\subsection{Method}
list of methods:

\textbf{How much revenue was being made:}
\begin{itemize}
    \item How many users came to reddit for this subreddit
    \item How much gold/reddit currency was distributed here.
    \item How much user activity was generated here daily \\
\end{itemize}

\textbf{How much revenue was lost:}
\begin{itemize}
    \item Qualitative analysis of migration (searching for other platforms names in these communities)
    \item Loss of number of users.
\end{itemize}

\note{talk about how generally moderations can be costly.}


Table:

\begin{center}
\begin{tabular}{ c | c |  c | c | c}
 & \textbf{Banned} & \textbf{Toxic} & \textbf{Control} & \textbf{All} \\
 \midrule
Activity 		& 150M	& XM	& YM 	& KM	\\
Gold	 		& 3.2K	& 2.6K	& 1.3K 	& 250K	\\
Gold per Community 	& 55	& 60	& 43 	& 49	\\
Incoming 		& 1M	& 550K	& 410K 	& -	\\
\end{tabular}
\end{center}

\note{literature review on user migration}
\note{List all the different platforms that users might have migrated to, search their names in all platforms and then look at their revenue}
