%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf Integrating Human-Provided Information Into Belief State Representation Using Dynamic Factorization}
\author{
  \textbf{Rohan Chitnis \hspace{16mm} Leslie Pack Kaelbling \hspace{8mm} Tom\'as Lozano-P\'erez}\\\\
  MIT Computer Science and Artificial Intelligence Laboratory\\
  \texttt{\{ronuchit, lpk, tlp\}@mit.edu}
  \thanks{\hspace*{-1em}Presented at the 2018 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), Madrid, Spain.}
}

\input{preamble.tex}
\input{variables.tex}

\begin{document}

\bibliographystyle{IEEEtran}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}
\setlength{\textfloatsep}{8pt}% Remove \textfloatsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  In partially observed environments, it can be useful for a human to
  provide the robot with declarative \emph{information} that
  represents probabilistic relational constraints on properties of
  objects in the world, augmenting the robot's sensory
  observations. For instance, a robot tasked with a search-and-rescue
  mission may be informed by the human that two victims are probably
  in the same room. An important question arises: how should we
  represent the robot's internal knowledge so that this information is
  correctly processed and combined with raw sensory information? In
  this paper, we provide an efficient belief state representation that
  dynamically selects an appropriate factoring, combining aspects of
  the belief when they are correlated through information and
  separating them when they are not. This strategy works in open
  domains, in which the set of possible objects is not known in
  advance, and provides significant improvements in inference time
  over a static factoring, leading to more efficient planning for
  complex partially observed tasks. We validate our approach
  experimentally in two open-domain planning problems: a 2D discrete
  gridworld task and a 3D continuous cooking task. A supplementary
  video can be found at \texttt{http://tinyurl.com/chitnis-iros-18}.
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{introduction.tex}
\input{background.tex}
\input{related-work.tex}
\input{algorithm.tex}
\input{experiments.tex}
\input{conclusion.tex}

   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}
We gratefully acknowledge support from NSF grants 1420316, 1523767,
and 1723381; from AFOSR grant FA9550-17-1-0165; from Honda Research;
and from Draper Laboratory. Rohan is supported by an NSF Graduate
Research Fellowship. Any opinions, findings, and conclusions expressed
in this material are those of the authors and do not necessarily
reflect the views of our sponsors.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{references}

\end{document}